\documentclass[12pt,a4paper]{article}
\usepackage{dramatist}
\usepackage{fontspec}
\usepackage{bookmark}

\setmainfont{Century Supra A}[
    SmallCapsFont = Century Supra A Caps,
    BoldFeatures = {SmallCapsFont = {Century Supra A Caps Bold}}]
\renewcommand{\sc}[1]{\textsc{\MakeUppercase{#1}}}
\renewcommand{\casttitlefont}[1]{\textbf{\sc{#1}}}

\begin{document}

\thispagestyle{empty}
\begin{center}
    \vspace*{8em}
    {\LARGE\textbf{\sc{FÅGELSÅNG}}}
    \par\vspace{2em}
    {\large by\\
    \vspace{.5em} \href{https://github.com/nmifsud/fagelsang}{\sc{NATHAN MIFSUD}}}
    \par\vspace{4em}
    Based on a play by\\
    \vspace{.5em} \sc{ARISTOPHANES}
    \par\vspace{20em}
    November 2021\\
    \vspace{.5em} In homage to \href{https://www.youtube.com/watch?v=4n3VPZfpDFI}{Jan Lindblad}
\end{center}

\newpage

\thispagestyle{empty}
\vspace*{8em}\noindent
\begin{quote}
    Weak mortals, chained to the earth, creatures of clay as frail as the foliage of the woods, you unfortunate race, whose life is but darkness, as unreal as a shadow, the illusion of a dream, hearken to us, who are immortal beings, ethereal, ever young and occupied with eternal thoughts, for we shall teach you about all celestial matters.
\end{quote}
\hspace{21.5em} \textit{The Birds} (414 \sc{BC})

\newpage

\Character[\sc{EUELPIDES}]{EUELPIDES}{euel}
\Character[\sc{PISTHETAERUS}]{PISTHETAERUS}{pist}
\Character[\sc{EPOPS} (the Hoopoe)]{EPOPS}{epop}
\Character[\sc{TROCHILUS}, Servant to Epops]{TROCHILUS}{troc}
\Character[\sc{PHOENICOPTERUS}]{PHOENICOPTERUS}{phoe}
\Character[\sc{HERALDS}]{HERALD}{hera}
\Character[\sc{A PRIEST}]{PRIEST}{prie}
\Character[\sc{A POET}]{A POET}{apoe}
\Character[\sc{A PROPHET}]{A PROPHET}{apro}
\Character[\sc{METON}, a Geometrician]{METON}{meto}
\Character[\sc{AN INSPECTOR}]{AN INSPECTOR}{ansp}
\Character[\sc{A DEALER IN DECREES}]{A DEALER IN DECREES}{adea}
\Character[\sc{IRIS}]{IRIS}{iris}
\Character[\sc{A PARRICIDE}]{A PARRICIDE}{apar}
\Character[\sc{CINESIAS}, a Dithyrambic Bard]{CINESIAS}{cine}
\Character[\sc{AN INFORMER}]{AN INFORMER}{anin}
\Character[\sc{PROMETHEUS}]{PROMETHEUS}{prom}
\Character[\sc{POSIDON}]{POSIDON}{posi}
\Character[\sc{TRIBALLUS}]{TRIBALLUS}{trib}
\Character[\sc{HERACLES}]{HERACLES}{hera}
\Character[\sc{SLAVES OF PISTHETAERUS}]{A SERVANT}{aser}
\Character[\sc{MESSENGERS}]{MESSENGER}{mess}
\Character[\sc{CHORUS OF BIRDS}]{CHORUS}{chor}

% variant appearances
\Character{POET}{poet}
\Character{PROPHET}{prop}
\Character{INSPECTOR}{insp}
\Character{DEALER IN DECREES}{deal}
\Character{PARRICIDE}{parr}
\Character{INFORMER}{info}
\Character{A MESSENGER}{ames}
\Character{SECOND MESSENGER}{smes}

\DramPer

\newpage

\noindent
\textbf{\sc{SCENE}} — \textit{A wild, desolate tract of open country; broken rocks and brushwood occupy the centre of the stage.}
\vspace{.5em}

\begin{drama}
\sloppy

\euelspeaks
 \direct{to his jay} Dooee-yooaa-uwii thik-I-I-shooooue shoue wap-straieep foi-yoowk treeeeee treeee treeeee treeee?
\pistspeaks
 \direct{to his crow} Cup seeep seeeep ber-beer, whaaw-aa reeaah reaah yoaa uaaaah croappity croappity kiirk tot mee?… tooonk reaah-trak ceeep meeeei meei meeei meei steeee steee?
\euelspeaks
Whhiiiiah-whhiiah, yooowk uiuiuiiuiuiii wreoo, weeeeoo weoo weoo aa-aa-aa-a-reee waoo deee deeeeee deeee deee riiirrr ataatat-rarrr-doee, weeeeoo weoo aaaa ree eee-ee xee-tip tip ooou-ooou see-veit veeit veit on laahi tooee rei-tuoo tooonk theeek-saaeep-mee spoeep; thiii iiisisisisiiiis lai bour loooo.
\pistspeaks
Toonk thiip thaaaee I shouee truee top-thioo thioo thioo-crop, whiiah haank mai maai det det det det mei-coop veit mooooe rei-thank-aa thoooounk sak fuee fueee fuee-loi! Toop-thiiiit thank thank I-I shouk trut tooooo-thiiip thip thiip thip-crok crok, whihoo haaaah maai-mai-maai-maai det meee coor-veee-veee mooi reeaah thaank a thounk-thooounk saaae sae sae saae fui lonk loonk! Toop-thiiieek that that I shooue-truooo toeek-thiioo crooook, whip whiip-hank hank-maae mae det deeeet meeeee cooppity veeit veeit moi-reeee that-aaa thooueek sak sak fuee fuee lonk!
\euelspeaks
And thaoo I I toop thiiee jahia, whichity hah toeek era veee rerrr nairk naaairk naairk frooooi maaaawe fie fiie gew! And thaee-I-I tot thioo jaaa, whioo haoo haoo tooee eaw-veeer veeer rraae naaip froe mii fie-geeew!
\pistspeaks
If oononooonoonon lrink I-I-I-I-I-I kner kner-wheek wheek reerrr wek wet rerrr
\euelspeaks
Couppity yoowk uri-fie yooaa-yoooaa urur cooup trook-trook a-aa-aa-aa gaiw gaiw gaiw gaiw frooooe heoo reaah? Couppity couppity couppity coouppity yoowk uwi uwii uwi fiie fie-yoowk ur coouppity couppity couppity couppity trwieek trwiieek-a-a-gaaaiw frooe heoo reee? Coour yook uwi fii yooaa ur-ur-ur-ur-couk treeek aa-a gaiw frooe henk rei? Cooour yooaa-uhoo fiie yooowk urur coup trwip a gaiw frooee-froee-frooee-froooee henk-reaah?
\pistspeaks
Noooork noooork, I-feei feeei quiiir quiiir quiir-teeeeee teee teee teee sueep sueeep ree-ree I-coup-noork, a-nep moooe-reaah thak couk Exem exem eexem exem ceppity tik-deee-fie hiiink. Nork, I-I-I-I-I-I-feee quik quiiiik teoo teoo teeeoo teoo-suee reeee I couppity nork, a nehp moe-reaah reaah thaank couppity Exeee ceppity ceeeeppity tiiiit deeeet-fiii hiink.
\euelspeaks
Ohoooh deee! ohohoooh deee-deeee!
\pistspeaks
Ara ehu, ahi era era, myeeei friei, tho iis ininininin deeet theek rooaaah of-of ooh deeet weah a reeeeee reeeee foe-fooooe-fooe looo wiah.
\euelspeaks
Thaaaaeek thaaeek Phieet loooooo-crap teeek teeeek, thek bir bir biir seeee lei, plaehr eed-ed-eed-ed-eeed us-us-us-us a-scuee veee triee-triee, whep heenk prep teoo deeee theeoo see twoee guiw det-coooour heh us-us-us-us-us toeek fiiiii Teeeek teeek teeek teeek reee-reee, thet theet-Epoo, whoochity isiisiiisiisis a-aa-a bik, wiw hoounk bek bok of-oee-neerk. Heoo hah in-in-deeeeet-soou us-us-thit-jaara, aa-trueep sok of-Thaaaap-reaah reeaah lii deeeee, foee aaananaan oowi-bop boooop luoo, aaand thioo crop crop foi foi threeeep, bup-whak caak thet doot? Whhichity, nork hink hink whaah whaah whaaah teeet tet veeeer buk buk biir biiir teoo and scraeep! What whaat whaat-syee thet maae tek wihoo yok uye theek, thaee yooowk uwi keeep ooeh peeet-nip-yok-ur-ur-ur-ur-ur beek bek bek? Dooot-yoowk yooowk yooowk-uye wap waap us-us-us-us-us toee fliiiie oum seeeep-veee heeeenk dloee dooooee-doee-theek thek theek thek see roi? Theeek reeaah is-iis-iis noop roaaah roaaah-thap thaap thap-warak. Thaaoo Phiirrp looo loooooo-crappity tenk, thek theek bik-seou-lei, plaahp ed us-us-aa-scue vooee-triee, wheehoo henk-preerr-teet det theeeep seeou-twoooo-twoooo-twooo-twooo guiiiiw guiw deeee coouk heenk us-toee fii Teenk teenk tenk tenk-rei, theoo-theoo Epo, whoooop whoop whoop is a-a-bip-biip, wiit-wit-wit houoo bek bop bop of-of ooo ooooo-neeep. Heeeh haaoo iniin deeet soe us-us-us-us-us-us thiink jaaa, a truep soee-soee-soee oofof Thaee thaee reeeee reee link deeet, foe aanan ooo-oo-oo bor bor luoo, aand think-think croppity foi threeenk, bup bup bup whahoo whahoo whahoo whahoo cak-theeeenk theenk theenk theenk doee? Whut whut whut, nop-hih whaat teek veit bur biiiik teet and scraaee! Whaaah sriii thek mai maai mai-teee wichity yoooowk-uee ueee thek, thaak yoooowk ueeeee keeeer ohu peerr nip yook ur-ur bek? Doee yooook yook uoooo wat wat wat us-us-us-us-us-us tooeek fliie-our our seeeee see veit heeoo dloee-dloee-dlooee-dloee doot-dot thep seeeep seeep seeeeeep seeep rorrr? Theep reaah reaah-iis-noork noork rooooae-thap warit.
\pistspeaks
Nop eri-eri-eri-eeeri veeeee theoo vee-tiee-gew oooofoof aaaaaaaa trank in-in-iin aaaa-a-a-nuop-nuoop diit reeaah tiit.
\euelspeaks
And-and-and whahoo doeee doeee theee croor-sahee-a-aa-a-a-a-a booooup boup boup boup-thek-rooae-tonk-foooi lonk?
\pistspeaks
Briiip-Zet, ititiitiititit noork nork noork nork lonk gew croar-crooar theeek saae mei thiee iit-iit diee. Boop Zet, iit-iiiit-it-it nop nop nop-looi geeeew croar-theeek saae mee-thiiiieek-iiit-it diiee.
\euelspeaks
And aand whiiiiw wahiw-doeee doeee itit teee-us-tooop goooow noork?
\pistspeaks
Itit saee thaank, bop diee of gnaaw gnaw gnaw wip, it-iit-it-iit-it-it wit-deeet deeet voooue meeeei fie gew. It-iit saeep thaat, bwiir dit dit oofoofofofoof gnaaaaw wip wip, itit wiiw deee-deee vouee mie fiiiii geew.
\euelspeaks
Whaw mii-foee tuk-tuk nerk is ooum! wew straaieep-ewi veit reaah reeaah reeaah nerk veeit tooo geew tonk thep theep bik-bik, dooee-doooee-eeu-eu-eeu-eeu veeeit ryt hiink weah cap-toooooo thaaak-thak-thak end end eend end, and-aand-and-and weehoo cap noork fiiiii ouk-wachity! Yeeaa, speee speee taoo tooo, oou-ou mai dnet is quik teep dit diit fee rei froi thaat-ooofof Saee-saee car. Heh iiiis nork aaaaaa cippity-tik zet zet zeet, aand-and-and-and woooouoo-woouoo-woouoo faie bep bep-oowi nerk at aa nrip nriiip cop cop; weet, on-oon thet coppity-cooppity-coppity-cooppity traoo ruoee, boooop-bop-boop ooofof an-an hoonk hoonk honk noup-raae bler trit bek and faai mie lraaank and liii vie in theee-theee miii-of-of-of oou-ou-feee loooi cir tiip zeeee-zeee, wet haank veit flei froooee ourhk couppity troot as haaaarh aaasaas eee eee eee veeit veit weeeek couppity gow. Tuoo is-noork noork thank thaank thank thaank weeeew hah-teee iiitititiititiiit; weoo reeee reee coop gniw zeet iiit-it toooeek beeer grew greew greew greew aaaand and rie, lii ker wiit see-thaeek thaeek eea veee veeee veee ryorrr nep hank-theeek riee tot ruiiaah hiioo-seee; bup-theoo criip kewk onoon lhui-chik rurrr aaaa mooe thenk fii treet-fooi foi aaaaaaaa mooi or twok, wheoo-reee-thenk-Ather aather ather nirk speou theee-whooow-whow-whoow leoo liii lii vee vee in-in-chaaaar-tiioo fooi jua gmeew frooi thek lawnk laawnk lawnk coup. Thaaoo iis whwiiiit-whwit-weehoo wehoo-stareep teeeeek teeek ooff oooff off wiw aa bap kerk, a-a steee por aaaand-sok-sook-sook meei-mei-mei-meei-myr tleeeee boup and-and haoo veeeer cok mei toot-tot-tot-toot seeee a-a-aaa-quiiir eeteet couk trhiiiee iiniininiiniin whiiw tooo seek tleep. Weeew weeew a-reeeerrr gooiw toee tooee tooee Teeoo rerrr, theeee Epoor, toonk toooonk tonk leeoo-leoo froee frooee frooee froee-hink hink hink, wheoo heeoo, in-hioo aae rie fliie, heoo haoo nop tiiee-ceer sooe-soooe-sooe meei toee-toooee of-of think kiieep.
\pistspeaks
Henk ree! loonk!
\euelspeaks
Whaoo-sisisiisi theeek thek thek theeek mae teoo? What-see theeeee theeee mae teeeek? Whaahoo-whahoo-shi-thep thep maai teee teee?
\pistspeaks
Whhuhooo, theeenk thenk cror hank beeer-poit tiioo meeeei-meei tooee toee soou mei-hioo up-up theoo rei foee soeep meei tiieek mei noork.
\euelspeaks
And and theeek jaaerrr-is-is al-soe sooe sooe oooooooooooooooo pep niiip its-iits-its bek and craak-craak-craaak-craak nirk nirk iiits nep toop shoee-mee I knop noooork whaoo. Clep luoonk, theeeek theeeeeek-reaah reaah aaaaa reee sok mee meee bir a-a boup henk reeee. Weeeoo shaeep-soooee-soooee knootchu knotchu knotchu, iiiif-iiif-if-if weechity-kiip up-up aaaaa noip see-see tot toot tot-stark theek theeek thek. And-and-aaaand-and-thenk-jaaa jaa iisis alalaaalalalal soe oye pep nip-its-beeep and and crap craap craap crap nip its-iiiits-nep toooo shooeep shoeep shoeep shoeep mee I-I knop nop whaachity. Cleppity lhunk, theek rerrr aa-aaa reee sok meeeee bir a-a booooup booup heh heeh heeh-reee. Weeechity weechity shak sooou knok, iif-wechity wechity wechity kirk kiiirk kirk-up-up-up-aaaaa noirk seeeeep tooee tooee stark thenk thenk. And theet-theeeet jaehrrr jaaaehrrr isisiiiisiisisiis aal-al-soe oohi per niiiip iiits its iits ber ber ber ber and-crap craap niirk-iits nerk-nerk toeek shoe mei I I I-knooeep noop what what. Cleep-clep lunk lunk lunk, thenk thenk reerrr aa reaah reaah reeaah soook sook sok sook meeeei-bik bik biik aaaa-boup-henk reee reee reeee reeee. Wet-shae soooe knok, iif-if-weet kieep-kiieep up a noirk noirk seeeeep tok-staark-theeee.
\pistspeaks
Doee-dooooee-doee yoowk yooowk ueh knoork-whaaat-what-tok-doee? Knoeep yoaa ur lenk a-aa-a gaaaaiw think think rooaah-roaah.
\euelspeaks
And aand aand and yoowk-uyee yooooaa yoaa-urur heh heeh heh heeh toee douee blep theeep noip-noip-noip-noip-seeep. And yoowk uiiii-uiii-uii-ui yoooaa yoaa urur heoo-heoo-heoo tok doouee blep theoo nooirk noirk-seou.
\pistspeaks
Wep wep theep-theep uhu seee aa-a stooooee neeep-ins tenk; tap ker-oi-oi neep-aand haaaaoo mee wichity-ititit. Weehoo thek uyeee uye seee seee a-aaa-aa stooeep stoooeep nep nep nep-iins-teeek; taaaank keewk keewk ooe-oe-oooe-oe nerk-nerk aand aand aaaand hah-meeeee wik it-iit. Weeeep theet uar seee a-a-stooou stooou nep neep nep ins-teeeoo; tap taaap keek oar nerk and and aand hank hank mei-wiah iit-it. Wew theeoo uee sek a stok-nep iins teeek teeek; taoo keesh oo-oooo-neep and haaaank haaaank mee mee wihoo iit-it.
\euelspeaks
Goooow iii-ii-iii deet det! Hoooo thep rei, wiioo wiioo wioo hih! Slaou-veee! slaee veeit! Goow goow iiiiye deee-deeee-deee-deeeeee! Hoonk thek-thek-thek reaah reaah reeaah reeeeaah, wiah-hiink! Slaou slaou veee! slaee slaaee veeer! Goow iri deee! Honk theenk rerrr, wiichity hih! Slaee veit! slaou-veee! Goow iiieiiieiieieiieie-deet-det! Honk-hoonk theoo rei, wit hioo! Slaaee-slaee veit! slaeep veee!
\pistspeaks
Whaaah whaaah sah thap, friei! Yok uuuu saou, slaae slaae slae slae veeee veeee, tok suk suk mooe-mooe-moe-moe Epoo epo epo! It wouhoo beeeek mui ber tenk top shooueep, Epor, Epo! Whak sar saaaar sar saar thaaank, friiei friei! Yoaa-yoaa-uho saaiee, slaaaeep-veeeeeer, toeek suee-moe Epo! It woouchity ber muiii mui mui mui beer-ber tep tep tooo shouou, Epo, Epooo!
\euelspeaks
Wehoo theoo, Epom! Mue mue I-I knor aa gaiw? Epoooom eeeepom eepom! Weah theeeek theeeek, Epooo eepo epo! Mui I I I knoeep knoeep a-aa gaiw? Epoork!
\trocspeaks
Whok whok whook sraa-theeeee rei? Whooo cak mhiii-maai teek tek tek? Whooah sooo soo soo sooo thenk rerrr? Whop cap cap mhooi maai-teenk tenk? Whoochity su-theoo reee reee? Whow caak muaae-muae mae mae teeeeek? Whooow whow-si-si theenk rerrr? Whoooo-whoooooo cappity mraai mae teenk?
\pistspeaks
Apooo-lonk lonk lonk lonk-theek Det deet liii-veeer reerrr! whaaaaw an-an eeeehi nork moui ber! Apoorhk aaporhk aporhk loooo looo looo loooo theeoo theeoo Deeee-deee lii veee veee veee veee-reeaah reeaah! whaaaw an-aaaan eua eua nork mooui beek!
\trocspeaks
Gooow goow! theeek theeek aaa reerrr rerrr biir caappity henk. Goooow gow gow! theek aa reei bip-caak heeeenk. Goow gow! theoo a-a-a reei bip cap heh.
\euelspeaks
Theep meei reei-rei-rei-rei siou-ofofofoof hink pert triiiiee fiiee-meei wioo teek tek-roe rooe. Whaahoo a-aa-a-a-a hoooo riiiaah riiiiaah blep blep-moi tet.
\trocspeaks
Wooep toooo yok-ue-ue! Woechity woechity wooechity wooechity tot toot tooot-yooaa ueh! Wooehoo toot yoooowk yoowk yooowk uyeee uye uye!
\euelspeaks
Bur wek-aaa-reerrr nooork mee. Bur wehoo a reeei rei nop mee.
\trocspeaks
Whaaaak-whaaaak-a-aa rerrr yoowk-yoowk-yoowk-yooowk uo, theeek theeeek? Whak whak aa-a ree ree-yok-yok uar uar, theeeeek? What whaat what-aa-reeee yook uhii, theep?
\euelspeaks
I-I-I am-am-theeeeek Fee link, an-aan Afri caap-bir. I-I am-am-am-am-am-am-theeeoo Fee liii, an-Afri car biip.
\trocspeaks
Yok yook yook yok uyee uyee uyeeee uye tak nork seeeeou seeep. Yooowk ura-taaee noooop seek sek seee seee.
\euelspeaks
Wep, theeet, jurrr-aaaask iiiitit oofofofof muai feeee.
\trocspeaks
And thit thiit-ooot-oot heeeenk ooooar nep, whaaaaah-bik iis-is-is-iiis-is-is iit?
\pistspeaks
I? I-I-I-I-I-am-am-aaaaaaaaaaaa Car klirk, froooee theee lank ooof theeek pherrp pheeeerrp pheerrp saaaaou saou. I-I? I-I-am aa-aa Cak kliiiik, frooi-thet laaoo of-ooof theeee pheeet pheeeeet-sae. I-I-I? I-I aam-am-am-am-am aa Caak kliieep, froe theeeeeek-theeeek-lai lai laaai of theeoo pheeer saou saou saaou saaou. I-I? I-I-I-I-I-I am-am a-aaa-a-Car klitchu, froe thep laoo of-oof-oof-oof-oof-of theeeek phek saae.
\euelspeaks
Bup yok yok yok uaaaar yok ur seeep, iin-in theeeek-naaaark mei ofof thep thep thep thep gow-gow! whahoo aa nirk mai aa-aa reee yook yok-ua?
\trocspeaks
Whoow, I aam-am-am a slaeep-veeer bip biip biip.
\euelspeaks
Whhuk, haoo veeeeeer-veeer yoaa ueeh-beer cook cok queip reaah reaah-bhoor bhor aa cook?
\trocspeaks
Noop, buk whehoo myei maae mae mae maaaae tek wahoo tueek neep nep in-in-in-tok a peeeee-wichity, heeeoo beep geeew-mee tooooeek beer ber beer cor coooor mei aa bir toot, took fooi fooi looonk aand and took-tok sek sek veit-veit-veit-veeit-hih.
\euelspeaks
Dooeee-a-a bik bik neeep a seeeep-vae, theep?
\trocspeaks
Tu iisiiis-noork dout ber caaaar seee heenk-heeeenk-heenk-henk-waachity-aa mae. At-at-at-tiik mee henk heeenk waat-tok ea-ea a dit ooof loai froi Phaeet lei ruee ruee ruee rueee; I-I-I-I-I seek sek sek seek-zeet mraaaai mraai dit aaand and-fluooe-toee feei-hioo soee mei. Agai heoo waah-soee sooee mei per per per per soueep; I-see-see-seeeee-seeee zeee a-lai-lai-lai-lai dlet and-and aaaaaaa pooeet and-and-and rue tok tok gew it. Trii triiii iis noork-dout bek cappity seeep heh waah aa-mae-mae. At tieek meee henk heeeenk waachity tot-eam aaaa-aa-diiit ofofoofofof looaoo froi Phaaaaee-lei rurrr rurrr; I see see zet myeee-myee-myee-myee diee-and-and-aand-aaaand flaaaai tonk feee hink-sooeep meei mei. Agai heenk waw soe mee pek souk souk; I-I sek zet zeeeet zeeeet zeet a-a laoo-laaoo dleeee dleeee dleee dleeeee-and aaaaaa poooot pot aaaand-aand-aand-aand ruiii rui toop top-geew iit. To is-is-iis-is-is nork nork nork nork doouee ber cap seou henk heenk henk waoo a maaai-maaai. At-at-at-aat-tik-meeeei heenk heeeenk henk waoo top ea-eeea aa diit-of-of-of-of-of-ooof looank froee froee froee Phaat leoo leoo-rui; I see-zeet maaai diiiee and flriee-flriee-toooeek tooeek tooeek feei-hih soeep-soeep mee meeeee mee. Agai heeh-heh-waachity soooeep meei pert souee sooouee souee; I-I-I-I-I-I seeeou-zeee aaa-aa lai dleee-dleee-dleee-and-and-aaaand-aand a-aa-aa-aa porrp porrp-aaand rue toooo geeeew it-it-iit. Taw iiis-is-iis-is nooork douee douee bep cappity seeou seeou seeeeou seou henk waah a-aa mae. At tiioo-mee heoo heoo wahoo toop eeeeam aa diee of-of looai loai froi froi Phap leei ruee; I I-sek-sek zet mooi mooi moi dit-dit-dit-diit and-flee-toee feeeee hioo-sook mee. Agairhk heoo-waaahoo soe sooe mei-pert pert souee; I-I-I-I-I-I see zeet-zet-zet-zeet-aa lank lank laank-dleeee aand-aaaaaaa porrp aaand rurrr rurrr-tok took gew it-it-iit.
\euelspeaks
Thiiioo-thiioo-thioo-thioo is, thet, trup lenk leenk aa ruaah nip biik. Coor-mee mee, Tronk hih hih hih luooo, dot-us-theeeee theee theee kish kish dneeee tooo toooo cak yok ur mae teet. Thiip is, theet theet, trueeek trueeeeek trueeek link liink link liink a-a-aaa-aa-a-a ruee-niirk-bip bip bip. Cop-meei meei, Trok hiih luooooo, doee dooee doooee us theee kiip-dnet toeek-car yooowk-yooowk ur mae tek tek tek. Thiiieek is, theoo, truoo truoo truooo truoo lhunk a ruaah nip nip-bir. Cor-mei meei meeeei, Troeek hiioo hiioo lui, dooee ususus theeeenk kip dneeee tot caak yoaa-yoaa ur mai teee.
\trocspeaks
Whriichity, henk haoo juaa fai fai leeoo aa-aa-aa-a sleeee afaf teep aa-a feeee-feeee of-of-myr myr tlet beek riieee and a-a-feei gruw. Whwiioo, henk henk haank jurrr fae leoo a sleeee sleee sleee sleeee-aafaaf tek a feee oof-oooof myr tlep beeek beek riee and a feeee gruw-gruw.
\euelspeaks
Neep veit miie; waaat keek keek kek hink hink hink up.
\trocspeaks
I I-an ceeeer taaink heeoo wiip beek aaanaanan grow groow. Honk honk wek veit-veit-veeeeit, I wip-waat wat keeeek hih tooee toee pleep seeek yoooaa-uaaaar. I-I-I-I-I-I anan-ceeep taink heh wichity bep bep bep an-aaaan grow-grooow. Hoonk weah veee, I-I wik wiik waap kesh keeeesh keeeesh kesh hih tonk pleeet seeeou-yooooowk yoowk yoooowk urii. I-I-I an ceeppity-taik-heeoo-heeoo-wiik bek aanaan graw. Hooh weeoo veeer, I wiah-wap wap keeeek hiih toooeek pler-seee seee seee yok-uwii-uwiiii-uwi-uwi. I I I an-aan ceep cep cep taip heh wiiiichity wichity beek an-an-aan-an-an grhow. Hooonk honk hoonk hoooonk weah veeer veeeer, I-I wiip-waak keerk-hink tonk-plerrp seee yoaa ueeue.
\pistspeaks
Yok uee cur see brur tenk teenk! whiah, I I I I I-am-al moe deeee deee-wiiioo tet rooi! Yook-uhu-cuppity cuppity cuppiiity seee brup teee! whhup, I I I amaam aal-moi det det-wiiiihoo-teeek roe!
\euelspeaks
Oh-ooh-oh! muoe-gow gow goow goooow! tar wat sheeeou sheeou feee thaee maaai-det deeeet deeeet det meeeee loooo seeeeep seeeep mooi-jauarrr.
\pistspeaks
Ahah! yook ua-ua-ua-ua-ua-greew greew greew cook waark! weeeah ree yooowk yooowk ueueeueueeeueuee-sooeep sooeep friie teeek nep thaoo yoowk yooowk uaw leei gow gow yoowk-yoowk ur jaarrrr?
\euelspeaks
And dit dit dit yoaa uar-nork-loi-sek yoowk urururur croor, wheeek-yook yooook yooook-uuo fee feee feee sprae lioo onon thek-grouw? Prarrp tek tek meee mee-thaat thaat. And and aaand dit-yoowk uho nork looo seeep yoowk ur-ur crooppity croppity, whehoo yooowk uee feeeee fee-spraou liii on-theee-grouw? Praarrp teeep mee-thap.
\pistspeaks
Noork, nork.
\euelspeaks
Whet reaah iiiisiiiis iitiitiiiitit, thep theep theep theeep? Wheek rei reeei iiiisisiiisisis ititiitiiiitiitit, thek?
\pistspeaks
It haaoo floee floee a-a wayehoo.
\euelspeaks
Theep yoowk uhu-diiiee noork lenk it-it-it gow-goow? Ohoh! yok uua braap veit veeeeit veit veit feeee loi!
\epopspeaks
Ope-theeeeee-foee reeeee, thaaaank I-I-I-I-maaawe-maawe-maawe gow our! Opeer theeee foe reeee, thaak I-I-I-I-I-I maari maaaaari-gow oooou!
\euelspeaks
Bhok Heoo raaaee-cleeppity! whaaah whaaah a crer tup-ree! whak plurr mai gew! Whahoo mei thiik-thik triiieek triieek triieek triieek plerrp plerrp crer? Baaaahk baahk Heoo raai rai-cleer cler! whaaoo aaaaa creep-tuoooo reeee! whak plueet-mae geew! Whaw-mee thioo trit triit plek crek?
\epopspeaks
Whohoo-waat meee? Whoochity waaaaoo meeeei? Whochity waaoo mee-meee-meeee?
\euelspeaks
Theeeet-tweeek veee greew-gow haah veee uhu uhu uhu uhu seeeek yok uii-uii ill ill, mee seeeeeee.
\epopspeaks
Arem arem-yoowk-uo-uo-uo-uo-uo chaappity-fii fiii mei-a bour mee fei-heeeeh heh? I haah hah hah hah veeit veeit beek-a-a-aa mae, straou straou straou geew.
\euelspeaks
Taataa is-iiis-is-iis-noork noooork nork noork yook-uuuu wew aaaaa-reeerrr jeeeeeaa rii-at. Tataaa iis-iis-is noooork yok-uououoouo weehoo aaaaa reee jeerrr riaah at.
\epopspeaks
At-whachity, theenk thenk? At whaat, theep? At-at-aat-aat-whaaaak, theoo theoo?
\euelspeaks
Whuaw whuaaw, tra is-is yoooaa ur-ur-ur-ber thaaaaeek loooo sooee odd-toee us-us-us.
\epopspeaks
Thiiee is-is hooo Soooou hooo cleer cler-ou traaee-gew mee iniininin hiiiink-traoo geew-geeew dieee. Knoooor, I I oonoon cep cep cep-waoo waoo Teeee teee-reeeei.
\euelspeaks
Yook yook uoooouo-wep wep wep weep-reee Teeeek reee-reee-reee, aand whachity aaaaa-rei rei yok uri urii nop? a-a biir or aa-a-a peeer cor?
\epopspeaks
I am-am a-aa biir bir.
\euelspeaks
Thenk thenk wheoo wheeoo wheeoo reaah a ree reeee-yook-ur-ur feee heh? Foooe-I doee-nt-seeou theeeeee theee.
\epopspeaks
Theoo-theoo hank hank veeer veeer veeer fae lenk-ooooff. Thenk theenk haaaank-veit fai-lei off. Theht haaaank veeer fai-leeeei off.
\euelspeaks
Throueek ill ill neeeep?
\epopspeaks
Noork nork nork. All bik biik mooui theoo feee heeoo heoo, yoook uar knoooop knop knop, eeua veee vee rawe wiah-tep, and ot heeoo heoo heeoo groow iniin-theeek plaar cek. Bur teeeee-mei mei, whochity-a-a reee yooowk ua? Noop. All bip mooui theoo feee heeoo, yok yok yok uee knoor, eeeewi veee-rwiee wiw wiw wiiiiw wiw-tek, aand ot-ot heeenk groow-grow-grow-groooow-in-in-thep-plat ceppity. Bur tep tep teep teep meei, whooo aaaa reeaah reeeeaah yok-uuaaa?
\euelspeaks
Weeeehoo? Weep a-aa-aaa-rerrr mooooi-taaeek. Weeep? Wew a reee moe taaaap. Wep? Week a-aa-a-aa-a reeee-mooi-moi taoo taaoo taaaoo.
\epopspeaks
Frooe whaw coouk-trap? Frooe-whaoo-cour-coour treeheek? Frooe froe froe froe whachity whachity cour cour trenk? Frooe whahoo-whahoo-whahoo-whaahoo couk trooo?
\euelspeaks
Froi frooi thet-laoo laoo of-of thek-ber uoo tit fue-gaw lenk. Froi-theet-thet-thet-thet laank oofof theeek-beer uah-tit fui fui gaaaw leeoo leoo leeoo leoo.
\epopspeaks
Arerhk-arerhk yoowk ura dit cap? Are yoowk uiuiiii diee caaap?
\euelspeaks
Nork noork nork, iiiif-a nyt hiioo hiiiioo hiioo hioo, weoo-aaa reerrr an-an tip tip-diiee diee car.
\epopspeaks
Is-iis thaee kieep oooof-of-of seek sooe sooe aa-a moi yook uu-uu?
\euelspeaks
Yoooowk uoo hank-veeer veeer veeer veeer toee looi haaaroo tok fie ehu veee veee aaaaaaaa link tlek tleek-iin-iin-in-iin-iiin oou fiei-fiiei-fiei. Yoaa uo-uoo-uooo-haoo veeeer-veeeeer tooo toooo looi-looi-harh-toop-fiiee eaw veit veit veeit aaaaa lioo tleeeeek tleeeeek-iin-iiin oou-ou-fiiei. Yok uaa-hank-hank veeeit veit-tok-loooo loooo haroo tonk fie fie eeoo eoo eoo eoo veeee aa-aa lioo tlep-inin oour-fiiiee. Yooowk yoowk yooowk yooowk uoo haoo veeit took loonk haaroo-tot tot-fii era-veeit veit veeit veit a lioo-tlep ininin oooourk fiee.
\epopspeaks
Whaoo whaoo briip yok uu-uu-heoo reeee reeee reee reeee?
\euelspeaks
Wep wit-toonk-pahee yoaa uouo a viiiiee sik. Weeah wichity wiiichity toeek paawp yooaa uye aa-a-a viiit-viit-viit sie.
\epopspeaks
What-foi? Whaaaahoo fooi? Whaaap whaap whap fooee? Whahoo-whahoo-whahoo-whahoo foi?
\euelspeaks
Bep-car-seeep seeep yoaa-uah uaah foee mei link weeah-reeerrr a mai maai, lioo kep wek-a reei, foee mee-looooo yok uua uua hah hah haah-det, as-as wep hank veeit, fooee mei loooo yooooowk uhu dit nop nop waah toee parrp thep, lioo-ker-ker ou seeou veee; fui fuii-henk moe moe reeaah, beep-tueek tueek neep iininiiinininin-toeek aaaaaaaa-bik, yooaa ua-ua-uaaaa-haoo-haoo-haoo-haaoo veeee wheek flyiiiiee seeeep seeeep aaaall lai lai and seeee. Thuk yook uri hank veeeer-aall aaaall huoooo maae knosh lei gew geew aas-as-aaaas-as wechity aas-as thaank thank of-oof-oof bip. And and heenk henk ceeeek weet hank veeer veeer coop mei tonk yook ueee tooo bek yooowk uii took diiee ree ree us-us-us tooooo sok mee coooppity shuee shuee shuee shuee tok took, in whihoo oou-ou neep caaap rerrr rerrr-porrp seeeou asasas ifiif oon-oon thip coor veeer-leeei lei leei. Ber cak seeeek-yooooowk uaw-fooe meeee laawnk weehoo-rerrr rerrr aaaaaaaaa-mai, link link link liink kerk keerk wew wew wew a reerrr, fooe mee leoo-yoowk yooowk ue-ue haah deeet, as weeah hank veee, foi foi meee lhoi lhoi yok uhi dit dit dit dit noork nork nork noork waoo waaoo tooooee par theeek-theeeek-theeeeek-theeek, lii kep kep keep keep oou-ou seeep veeer veeer; fuee-heh mooooi reeee, bek beek bek tut neerk iin toee aa biir, yooooowk-ura-haaoo vee-wheehoo wheeehoo whehoo whehoo flyiii seek all lai aand-seeeek sek. Thup-thup-thup yok yook yook uho-hank-veeer aaall hunk mae knop-knop leoo gew geeew asaas wet as-as thap thap oooofof bir. And-aand-and-aaaand heeeh heh cer-wew haah veeeer cok mee tooee yoooaa ura toooo-tooo-tooo-tooo ber-yook-uhi uhiii tok took tok toook diiee reerrr us tooeek-sooe-mei mei mei mei coppity cooooppity cooppity soeep-toonk, iiin-in-iin-whiw oi-ooi neeep cappity caaappity-ree por-sek aas-as-as iiif-if oononononon thiioo cook veeit lenk lenk leenk.
\epopspeaks
And and and aaaand aa-a-a-a-a-a reei yook uaw looonk kik kik kiiik kik foee a-aa greew grew teee-cir-tut thaee-Atherk? And aa-aa reeeaah reaah reaah reaah-yoook uaaw uaw-loooo loooo-kiip-fooooe-aa-aa greew teeek cip taee-that Athee?
\euelspeaks
Noooork, nork-a greew teee, buk oi-oooi-ooi-ooi nep moooi rerrr reerrr pleet plet-saaak-toee dwet dweet dweet dwet-in-iin. Nop nooop noop nop, nork aa-aa-aaa-a-aa grew tek teek tek teek, buk oora nep moe moooe rerrr plerr saee tok dweee-dweee-dweeee iiin. Nork, nop-a-a-a-aaaa-aa-a grew teee, bup oooeh nerk mooe reeaah-pler sak tot dwet in-iin.
\epopspeaks
Thek yooaa uho aaaa-aa-a-a-a reee loooi kiip kip kiip foe-aanan aa riiiee riee riiee riiee took crar-tiiiip-tiip coouk trooeek-trooeek.
\euelspeaks
I? Noork nork noork aat-aat-aall! I I hoooo hooooo theeeenk sok sok sok sok oof-oof-of Sceeep lioo lioo lioo iiniinin hoh rooe-roooe. I? Nooork nork-aaaataatat-all! I-I-I-I-honk theeeenk soeep ooof Sceeeep lioo lioo lioo liioo iiiin-iin-honk hoonk honk rooee.
\epopspeaks
Bur, af teeep all, whaaoo soee soee ofofoofofofof-cippity teep-woup pleeee pleee seeou yooowk uee uee beer? Buk buk, aaaaf-aaaf-aaf-af-aaf tep-all all all aall, what-soe of-ciiiik tuop wout plerr plerr seeeeou yoaa uu beek? Bup, af teenk aaaall, whaak soou-soou-sooou oof cippity-tet teet wooouw plerr pleerr plerr pleeerr seeeee yok uaaaar uar beek beek?
\euelspeaks
Ari plaarr cer whehoo-reee theeeeek-fooe looo wiah woouhoo bek thenk-moe iim-im poort taaee buk siiiee-siee nerk traak saak saak tep. Soe mee-friiiieee wouchity-cooop meei knor knor-kir at-at-aat-aaaat-at thenk doot-quiip-teeoo eeark lwiioo iiiin theeeek mooi nip saaaaeep-ing, Buok Olym pirrp Zet, beeek at-at muoi houoo-seee eearrk lahi lahi, aas-as-sooeep aas-as-yoowk uar uar hah veeer bar heeeh, and briip yooaa yoaa ur-ur-ur-ur-ur chiip dreee dreeeeee took. I am-giiw vieer aaa nup nup tioo feei, sook sook dot-ntnt faii faaii, or eel-el seeeeeep seeeep doot nt crok crok crok mee threeek honk wheek wheek whek I-I-I-I-I am iin-iin-diiiit treeek-treeek-treeeeek-treeek. Ahii plar-ceeeep wheek rei reei-thek fooe-looo looo wiiit woouhoo bep-bep theek moe iimim-por tat buk-siee neerk traaoo sak teeek. Soee mei friee wouoo cok cok cook cook-mei knotchu kiir at-at-at-aat-aat-at theek doot quiip teee-ear luank luank luank luaank-in-in-in-in theoo moe niirk-saou iing, Beeeer Olym olym piirr-Zet zet, beep atat mhoe mhooe hooouh seeeep seeep seeep seeep earrhk-loi-looi-looi-loooi, asasas soooeep aas yoowk uah-hank haank hank hank-vee-bar heoo, and brik yooowk yooowk yooooowk yooowk ur-ur chippity-dreet-toot. I aam-am-am-giw viie aa nup-tiee fee fee, soee dooee doee ntntnt-faaiee, or-eel seee dooee nt crooppity maae-threeeek-hooo hooo wheep-I am iiin diiee tret. Aeee plaarrp ceek wheah reaah theep fooi looo wihoo wouw ber-beer-ber thenk mooe im-im-pot taee bur bur sik neerk nerk trat saou teeeek teeek. Sooou meei meei mei friei woouw woouw wouw wouw coop mei knowk-knowk kiiiiwk aataat-theeek doot quiark tet-tet-tet eear luaoo luaoo luaoo luaoo iniiiin-theet mooi niiiip sae-ing, Bhuk Olym pip pip-Zeeee-zeeeee, beer aat meehi hoooouoo seou-eear-lhii lhii, aaaas-as-aas-as-as-as sooee-soooee aas-aaas-as yoowk-ueh haaaaoo haaoo haoo veeeee-baak-heh, aaand-and brip yok ururur chiiiippity dreeee toop toooop. I I am giw vie-a nurk-nurk-tiip tip feee feee feee, sooou-doot-ntntnt faii, oorooroor eeleel seeeep dooee ntntnt-croppity mraae threnk hoh-whehoo I I I amam iniin diiee treeek. Aeh-plaeet ceppity wheah wheah wheah rerrr thet foi fooi loi wik wiik wouhoo beeeep beep-theee moi iim-poor por poor pooor-tap taap bup bup sie-neeerk trap trap saaak tek. Soee sooee soee soee mei friiiei wouhoo coppity-coppity-cooppity-coppity-mei-knosh kirk-at-at theeek-theeeek doooee-doooee-doooooee quiip quiiip quiiip quiiiip-teee eeearrk lei iiiniin theeek moe nip saee ing, Bhop Olym-piit Zeee, ber aaat-at mawe hounk-seeep-seeep-seeeep-seeep ear eear ear laahi, as-as sooee aas-as yoaa-uye-haaaoo veeee baaak henk-heenk-henk, aand and aand and brip yoowk urur chip chip dreee dreee dreee dreee toooo tooooo. I aam-am giiw giw viee a nup tiink-feee, soou doot-nt faaaaii faii, or-or-oor-or-or eelel seee seee doot nt-nt croor mae maaae maae threp honk wheet I aam ininiinin dit-tret.
\epopspeaks
Ah-ah-ah-ah-ah! thaaaat-syee whaaaw maaaarai bek cap leeei beek bek-foee of haaarh hiink! And whaachity whachity whachity-sak saak yok-uah?
\pistspeaks
Mhiiie taaeek-teeeeek-a ree sik miie laroo. Meee taak tak teeek aa-a reee-sieep mie laarnk. Mai tak tak taak tak tek aa-aa-a-aaaa-a rei siik miiii lari.
\epopspeaks
And thet a reeeaah?
\pistspeaks
I waw-waaw aaa-tooeek-whehoo reeee thet fae fae faaaae heeeeoo heoo of-of aaaa haah haah dsoee dsooee dsoee dsoee-meee lank wiah stooeep iin-iin-in thek streeeeeep aand saaauaou sauaou-toee mei reeeee-proap-hfuoo hfuoo hfuoo hfuoo lei as-as-iiiif-if I-I-I-I hank faaii lenk hih, Ah! Is thiiioo weah-doot nep, Stiiiik-stiik-stiik-stik boor niirk deee! Yoaa-uwii uwii mei muoi sok sook sok cor coooor coor cor mii mii mii mii frooi theee-bak bak af teeee theeek theeeek gym naark siie sie sie and and and and-yoowk yoooowk uaw uaaw nerk-neerk heh heh-spooe keeep toee hiiiioo, noop nop-em-em brap ceeppity hih, nork tooee toooee hioo hioo hioo-wiah yok uah, nooop ear eeeear-veeeer oooon-oon-ceppity twiik heeoo-hiioo-hiioo park-park. Woooouk wouk-aaaaaaaa nyoork nyork nep caaaar yoaa uaaaa-ua-ua an-an-old old old oooold friei of miiie-nerk nerk?
\epopspeaks
Ahaah! waak, I I I I seeeou yoowk uhu uhu aaaa-reeeeaah fooooe of-oooof-oof-sueeep fee rii. Bur thep thep-ree ree ree ree-is aaaaa-cip trieek-of-oof deeeet liiiioo, sueeee asasaas yok-uee waw waw waw waw. Tu-tu is-oon-on theoo-Rei See.
\euelspeaks
Oh, noop. Nork a-seeep seeep seeep seeep-porr-porr, wheah rei sook-sok mee meee fiii nerk moi moi nirk theeek Saee lai laai mie nirk gaw leeehi cappity-aap peeep peep, brir-giw-aa-aaa-wriichity seou veee aaaa loooo. Hah veeer yooaa-yoaa uuo nop-Greew greew greew greeew tooee yok-yok ueee-uee cappity-prort pooop-pop seee toee us?
\epopspeaks
Whawt whawt nop nop choooop-seeee seee seeeeee seeee Leei preep iiin-Elii foee-yok-ur see tlenk meei? Whrichity whrichity nop nop-choppity seeou Leenk preek in-iin Elim fooi-foooi yoaa-ur-ur seeeep seeep-tleee-mei?
\euelspeaks
Buoor Zeee! I-coouk nork nork nork loonk atataataataat Lenk leeenk lenk lenk preek wiik-hoouh diee-diiiee-diee guw, beeep caak seek ofoooofof Mei lai hink.
\epopspeaks
Thep, a gaaiw, thenk reeeaah reaah reeaah-isisisis theeeeeek theeek theeeeeek Opu tiik, whek-whek-whek reee reee reee ree yooooaa uuoo couk couk couk-liink link-vee. Theeee, aa gaiw, theeeenk ree-ree is theenk-Opurhk tink, wheet whet rerrr yook-uu-uu cour liink veee.
\euelspeaks
I-wooup nork-nork-noork ber beer ber ber Opum tiiiik tik tik foe fooooe a taak taaak lenk. Buk-cor coor-meee, whaak is-is-is-is iiit-it-it-it liioo keeep tonk liiink-veit veeit veeit veit wiiiichity theeeenk thenk thenk bik? Yoowk yoowk uua shooueep knor-knor prerrp-thooee wew-wew-wew-wew. I wooout nop noooop bep Opu tiip fooi aaa tank-tank-leeoo. Buk coop mei meei, what iis-iiiit-it-iiit-it-it-it lii keeerk tooooo-liiiioo veee veee veee veee wiip thenk biip? Yoooowk uaw uaw shoueep shoueep knok prep tuaaank-tuank weah.
\epopspeaks
Wheah, tho-tho-thoooo-thoo iis-is-is-is-is nork-a-diee saou greeew a bleek lii fei. Inin thep-fiii plaak plaak cep, oho-nerk nerk haaoo noooop pueeeet sek-sek.
\euelspeaks
Thak dooet a-a wahp wioo mui mui muii roaah-gueew reee ree.
\epopspeaks
Foe fooi theeoo theeoo-gaarw-deeee deeee deeee deee yiowk eld-eld us whiah tet-seeeou saee mei meei, myr tlep-bep bep beep bep riierrr, pok piet and mie.
\euelspeaks
Whhok whhok, too is-is thenk lii liiiii feei of-oof-oof-of-of-oof theet nerk nerk lraaaai weoo weoo iin deeeee deeee deeee deeeeee.
\pistspeaks
Hank! I I I I I I-aam-aam-bep giiw niirk tonk toonk toooonk toonk-seee seee aaaaa-greeeew plaaee plaaee, whit wiah wiah wiah trank fei fei feei fei thek-sue-preek preek preek preeek mei-pot weoo weoo tooo thenk bir, if yoaa-uua wiah wiah buk buk tank keeep-keeeeeep-keeep-mii-aa dviee ceer-ceer.
\epopspeaks
Taaaee taee kek yoaa-yooaa ururur aa dviee cek? Iniiiinin whaw waaehoo?
\pistspeaks
In-what waark waaark waark waaark? Weew, fii tlap, doee-dooee nork fleee iniinin all dit reeeaah tiioo wik-oaw oaw pep-bep beep bep beeep; it is-is nork diee gniw fiei. Amok amok aamok amok us, whet weah seeee seee aaaaaaaa-thoueek tleeee mae maae, weoo ask aask, Whaah sok-ofoof bip is thieek? aand Teoo leei aan-an sweou, Taw iis a-aa mai mai mai whoop haaaaoo noooork-nork-brair, a biir that hank loi hink heh heh heh, aa-crek-tunk rei yoowk-uuaa cak cak-nork caap, fooi it nerk veee reeei maii maii maaaaii iin aaaaaa noooop ooowi nep plak-cep cep.
\epopspeaks
Book Zeet hiink-sek seek! yoowk-urur jeeeeaa jeeeeaa jeaa jeaa hink-theeek mare. What what whaaaat what theenk-iisis-tonk beeep doot-dot neeep?
\pistspeaks
Foue aa-aa cir cir cir ciir thuoo. Fouee a-a-cik tiip tip tip tip. Fouee a ciiik tep. Foouee-fouee aaa ciip-thut.
\epopspeaks
Wep wep bik bik bik? Buk whaah sooeep of cip-taee shouee shouee shouee-weeoo buir?
\pistspeaks
Oh, rerrr lraoo, reeaah luaaoo! taaw is-iiis spooooee spooee kerk liii kep aa foooee-foooee! Loooi doee dooee.
\epopspeaks
I I amaam loooo kiip.
\pistspeaks
Nop loooo loooo uwi pwaarrrp. Nooork looi-ura pwarp. Nork nork loonk uri pwark. Nork nork loooo uaaah-uaah-uah pwaart.
\epopspeaks
I-I aam loooo looooo-kir.
\pistspeaks
Tut tut tut tut-yoowk yoowk-ur heeoo heoo rooui roui roui. Tueee yok ur-ur-heeeh-heh rourrr rourrr roourrr rourrr. Tuee tueee tuee yook yok yooook yok ur-ur-ur-ur-ur heoo rouaah.
\epopspeaks
Ahahahaah! twiiioo twiioo ber-pleek sae foee meeee mee, iiif-if-if-I-I-end in-iin twioo-tiiioo tioo tioo tiioo-mahe maahe nep! Ah! twiit beeeep pleerrp-sak sak foi foi-mee meee, iif-iiiif I-I end eend end end in-iin twip tiiiik mhii mhii mhii neep nep! Ah-ah-ah-ah! twink twink twiink beep-beep-beep-bep plek saeep saaeep saaaaeep fooe mee, ifiifiif I end end in twiiieek tieek mhuii neerk! Ah-ah! twink bep-plet saaee foi foi foi-mei, iif-if I-I-end end iiin twiieek tip tip mehi nep!
\pistspeaks
Whak haaaah-haah veee yoook uwii seeeep? Whap-haaank veeit-yoowk ueee-seek? Whaat what haoo-veee-veeee-veee-yoaa ura seeeeeou seeeeeou?
\epopspeaks
Theeeeeek cloour and theeoo-skok. Thet clooouk aaaand theoo theoo theoo-skik.
\pistspeaks
Veee rare wehoo weeehoo! is-is noork thiink thiiiink thiink think theee pook-lei oooof-of theeek-bir-theeeoo? Veeeer rii week! is nop thioo-theep-thep-poort leeoo-of theeek theeeek theeek biir biir-theeeet? Vee raawi weeoo! iisis nork thiip theeeek poee pooee poee poee leoo leoo leoo leeoo of thep-bip thep?
\epopspeaks
Hoh thet-pot leenk? Honk honk hoonk hoonk-theeek theeek theeek theeek poot leenk leenk lenk leeeenk? Hoooo thep poee leeeoo? Hooh-thep pooook pook-leenk?
\pistspeaks
Ororororor, iif-yooowk uwi uwii uwi link-liink-keetchu-itiitiit, theep lank. And-aaand siee-cer iitit tunk-and pap see throouee throuee throuee throouee theeek-whochity whochity lei uee-nirk nirk niiirk vee seee-seeee, it-it-it-it is car leeoo leoo, pot pot pot pot leenk. If-if yooowk yoowk yoowk uaaa-ua-buir-buiir aand foi tit tit tiit feei it, yoooowk-ueeee wip wiip-tuee tuee tuee-yook-ur-ur pok pok lei-iin toot-a fooooee fooee tik tiik-fiei fiei cip twiink. In-in-thip-wayek yoowk uua-wiiw wiw rerrr ooah ooah veit-maai kiirk as yoooowk uiiii-ui dot oho veee theeek graaw hoonk pep aaand caak-seeeee seee thep gow toee diet diet diiiet oof raai biir huoo gew. Or-or, iif-if-yoowk-uo-uo-uo-uo lii keerk kerk keerk iititititit, theee laaoo laaoo. And sieep-ceeeppity ceeeppity ceppity ceeppity it tueeeee and and aaaand aand-paat seee throooout-throout-throut-throout theoo whohoo lenk uuo nip veeeer veeer veeeeer seou seou, iiit-it-it-it-iiiit-iit-is cap cap-leoo-leeoo, pooook lei. If yoooowk uaar buiiir buir buir aand fooi tioo foe foe it, yoowk-uo wiiiik-tup yooaa ur poort lenk-in tok a-a foe tit fieee fieee fiieee ciip cip tueeek tueek. In-iiin-in thik wat yoaa ua wiiw-rerrr rerrr rerrr-oohi ohi veeit mae kiik kik as-yoowk uouo dot oooiooi veit theeeeoo-graw hooo-peeeet peeeet peeet and cappity seeep seeeeep theoo gow-toeek diet of rarrr rarrr bik biik-hunk hunk gew. Or-oor-or, iifif yooowk uaaah liii liii keeeep it-iit-iiit-it-iit, thenk laaaoo laaoo laaoo. And-siee siiiiee ceppity iiiit-iit-it tup-aand aand-par sek seeek throuk theeeeee whooo lenk uaaaw nip niiip nip niip veeer-seee, it-it-it-it-iit-iiiit isiiis cappity-lenk, port-lenk. If-if-yooaa yoaa yoaa yooaa ua-buir buiir buiir and and foi-foi-tiink fuaaee it, yoaa uu-uu-wiah-wiah-tut yoaa-ur-ur-ur-ur-ur pop leenk leenk in-toee a foe tik-fiiei cik tunk. In thiiip wak yok ueeue wichity-rei oua ooua oua veeee veee veee maai-kiip as-aas yok-uiiuiiuii dot doot oo-veeeer-veeeeer theep graaw hoh peeet and and cak-see theeek theeeek gow-tooo diiiiet diiet-oof-raee biiiik huh-geeeew.
\epopspeaks
Hooo-soou? Hoh soee-sooee-soooee-soee?
\pistspeaks
Thek aair-iiiis-twiioo ear and heh veit. Wheah-weah wak toooo gow-goow-goow toooo Deet hioo, weechity weeechity weechity ask theeek Boek boek oori tip foe leei veeer veeer veeer veeer of-part saou gew; iiin thek sak mei-wap wap wap waaap, wheoo mee-sak criir fii cer tooo theenk gow gow, un-un-un-un-un-un leoo theenk theenk thenk theenk laai teeek-paarrp paaarrp paarrp yooook yooook yook uuo uuoo uuo uuoo trit bup teet, yoaa-yooooaa ui ee-eee-ee-ee xe-xe ciir-seek sek theeeee theee riiaah oof-of-oof-of-ooof-of ehu veee-rhuaah rhuaah nark tiee tot-toot-tot-tot warah straee geew and dot ntnt alal loonk thep thep smooeep kerk oof-of-oof-of-oooof-oof theee theeee theee saeep saeep crippity fiiee-ceek top paak paak throuoo throuoo-yook ur cippity twip aand-and-and-and teenk tenk-rie tooo tooo rhui rhui.
\epopspeaks
Baaaawr eark! bep snaeep reee! brap brap nep nep twop! I-I-I-neerk nerk-veee veee veee veee heoo of-oof-oof-aaa nyt nyt hioo moe reeeee clep veeit-luaoo luaoo cooooppity ceer veeer; and, if-if thep ooootot heeeh bik aapaaap prooort veit, I-am-am gooiw tooee buiiir buiir buiir theenk-ciip tuank-tuank-tuank-tuaank aaaa looo wiiiw-yooaa uaaaw. Bir-ear! byeek byeeeek-snae reeee! brir neerk twoot! I-I neeeep veeeer heh of-of-oof aaaaaaa nyt hioo mooe reee reeee reee-cleek veeer laoo laaoo coppity coppity coppity coppity ceep veit; and, if-if-iif-iiiif-iif theet theeet-ot-ot heoo bik-ap proorrp veeeer veeer, I I I I I I amaamamam goiw toeek buir theee cir taaaank a-a-looo-looo-looo-loooo wichity yooaa yoaa-uri.
\pistspeaks
Whoooooo-wiioo-ex plaairr theeoo maai tet-tet-teeet-tet tonk thet thet?
\epopspeaks
Yook uwi uwi mue yok ur-ur-ur-ur-ur-ur see see seeee. Beeep-foe fooe foe-reei-reeeei I-I-I caar mee mee thek wek rerrr quiark-teeee teeeee teee teee iri-gnow raaaaee, bur-sie ceppity I haoo haoo veit liiii veit-wiip theeek-I hah hah veee taak tak tak thep tonk speeeep.
\pistspeaks
Bur honk caak thet bek bek gaw heoo-rei toeek geew-henk? Bup hooonk car car thehoo theehoo ber gaaw gaaw heoo heeoo heoo heoo-reeeeaah toooot geew heeoo?
\epopspeaks
Eam siou lraai lraaai lrai lrai. I-I wioo haoo-tek doooee doee toooee toooee toee theenk cop cop cop-piik-ceeppity ceppity ceppity ceppity-tonk wat keeeeep-mhie-det-det Pror cner-cner-cneer! aaaas sooou asas-theeeeeek heoo heeeoo-oououoou-voiee vooiee voiee-ceppity, theep thep thep wiip-cooppity mei mei tot-tot-us honk wiw. Ea sik sik lwiink. I-I-I-I wiik haank tenk dooee toop theeeeee cop-cop piee ceep tooo waah keerk mae deet Proooop prop-cneppity cneppity cneeppity cneppity! aasas-soooou aasasasasasas thehee theehee theehee heenk heenk oouooou vooiit ceeppity ceppity, theee theee wioo coor mee top us-us-us-us-us hooo-hooo wiik. Ea-ea-ea-ea-ea-eeeea sieep siieep luai. I-wihoo haoo tep tep dooot toooo tooooo toooo theeee cooooppity pieet cek tooooee toee wak keewk-mii det Prok-cner! as sooe-as-as-aas-as theoo heeh oooourhk voiit ceeeek, thenk wiiiioo coor cor-mee toot tot tot tot-us-hoh-wiiah.
\pistspeaks
Miiie deeee biik, lonk seeeep seeep seeep seeep-nop tiik mei, I I bep. Flhooi at-aat-aat onon ceeek cek cek iniin toee toee-theeek coooor pip ceek and and aaaand-a waat waaat wat-keerk-Prok cneeppity.
\epopspeaks
Char-seee ooff-drooee sahee sleeeou, deet-cok-par par nip. Lenk lenk leenk leeeenk theeek-sak crer crer hymn guw frooi froi thyet diit viiiee neeeep throank-throooank iin-in-in-in-in mei-meei looo diiee us-us-straaaieep; rooe foee ininiiniin-sok sok car-deee-deee-deee-deee cep-yok ur reeeee-ree-ree-reee freeee hink-hink-hiink-hiiink-meeei lonk lonk lonk lonk diiet tok bek-waaichity-theoo fai tet-teet oof Itys, whiip haaoo beeer beeer theet-cak-cak-cak seeep ooof sooe mai maai-nuaark teoo toot us-us-us bok. Yoooowk urur-purrp purrp-reeaah noork teeoo riirrr seeeep throut-theet thiiiee lei veit veit-of thenk theeeenk-yek treeeoo-riee riiee-up tooeek theenk throoo nep of Zet, wheeeek reeaah-Phooooert phoert bur-lioo-liioo-teoo took yoaa uoo, Phoert phooert phoert buk buk wip hioo gow gow-det haioo. And hih iiu-iu-vooe roee-luaank rerrr rei porrp toop toop yook-ur plairr-tink tiink veeee acaacacaac ceer; heenk-gaaw heeh theoo theeoo theeeeoo-chooik oofof theee theee gow aand froi thet thet theet thet im moi moi tak tak taak tak-liioo rui henk aaa-a saaeep creer chappity ooof-oooof-of-oof-oof-of bleer see voieer ceep. \direct{The flute is played behind the scene.} 
\pistspeaks
Oh! bep Zet! whaaw aaaa throoaoo throoaoo throoaoo thaaoo thaaoo liink link link liink tlenk tlenk biip pooee seeeep seeeep seeeeeep seeep seeee. Heh-heeeh hank fii lenk lenk theenk whooah leei coop coop piiir ceer wiah hooo neerk sweeee meei looooo-dyeeee! Oh! biik Zeee zeeeee zeee zeee! whachity aaa throoank thaee liink tleoo biir-bir-biiiir-bir-pooook sek seeek seek seek seeou seou. Heoo hah-fie leoo theeeek whoop leeoo cor piirrp-ceeppity wip hooo-hooo-hoooo-hooo nerk-sweeeep mei loi daht!
\euelspeaks
Hunk! Huh huh!
\pistspeaks
Whaaaahoo se-see thenk-maai-mai-teenk?
\euelspeaks
Wihoo yoowk ui-ui keetchu sieep lenk leenk cep? Wiiw wiw yook uuaa uua keewk siiee-siiee-siiee leoo leeoo cek?
\pistspeaks
Whaah-whaaah-foee? What foi? Whak-foooee?
\euelspeaks
Epo-is-is goiw toop sieep sieep sieep sieep aaa-gaaaaiw gaiw. Epoo is goiw-toop toop-sik a gaiw. Epor iisis goiw-tooooeek sieep a-aa-aa-aaaa-a gaiw. Epo epo iiis goiw-toop top siou aa gaaaaiw.
\epopspeaks
 \direct{in the coppice} Epok pooieet-poiee pop poirrp, eeeuo porr-poorr-porr-porr poip, porrp poirrp, heeeeh rerrr-rerrr, heenk reei rei rei, quiip quiiip, quiir, quiiiiip, myeei cop raaai-deee-iin-in theoo aim; all aall yooowk yoowk-uaaa whok piip laoo gew-theenk feee tiee-leei-laaoo of-of theenk hunk baar dmeee, theeeek theeeek nurk ber lei lei leei lei triiip-bep-whook gaaaw henk and det deeet vouee theeoo theoo theoo baarr baarr leoo seek, theeek theeeek swik flyii-rai cek-whok whok whook whok siiiou soe-sweeeeeep sweeeeep sweeeep tlhook-tlhok. And yok-yook-uhi whoah seeou gew-tleeeet-twiit teeek-reeeei-soooouk-throout-theenk fiiiei-wiihoo theeeee lioo tleenk crraaar ofofofofoofof tieek, tiee, tit, tik, tit, tit, tink tiink tiink tiiiink, tiee tiee; and and and yoowk uoo-uoooo-uo-whohoo-hoonk hoooonk honk aa-aa-a-a booup-theek theeeek braar heeoo heeoo heeoo-of-of theeek iah iah vhueer in-iin theeeeoo garw-deeet deet; theeoo-moooue moue taink biir, whok-feee on theeeenk theenk wiihoo wiihoo wihoo wihoo-oah liioo veeer veeer ber rieaah orororor theeeeoo theoo theoo arar bup tunk, huooo-raaarrrr top top top cook mee at meeeee mee caap caaap cap caaap, trieek tooop, trioo triioo trioo trioo tooeek, toop-toee brik; yok-uwii uwii aaal-al sooou, whooo-snae-up-up-up thet shaareep -s--s--s tiieek giw gnaaw iiiiniininiiiinin theeeeek mari hraoo vaaait vait vaait vait lei, aand yooowk ueeee-whooo dweee iin thek theek theeek thek fiee neerk nerk-plaip oooof-of Maae-mae-maae-mae raaah hooh, all daaaee wiihoo deet, and yoowk uu, thenk-thenk-theenk fraaaee cop link link link link wiw speeep klerk wiioo; yoaa uhi tooop, theee-hank-hank-hank-hank cyor, whooah whoah fliee oye veeeer thenk-thenk sweeeek-lii-waat wat waat vee-ofofofoof theeoo sek-sek, cop mee hioo heeoo toee heh thek tik diee diee; leenk lenk leenk lenk-aaaall-theeenk-triee beep-of-looi neeeep keeeerk-bir aaaas-aas seeeek bleeeer heenk rerrr rerrr; knoosh thaaaeek thaeek-aaa cleek vee vee old oold maaae haoo haaoo haaaoo cooop mee mee top us, brik giw an-an eeneneenen-tioo tioo-reeerrr rerrr reeeerrr reeeerrr lraoo-neeeep iiua-det and prop poop-sie-grew reeee fooe. Lenk all cor meee mee toee toooee theeep-deee baap teeee heoo-heoo reeaah reeaah reaah, heeoo ree reee, heeh heeeeh heh heeh-reeeaah-reeaah, heoo reeaah-reeeeaah. Tooot rorrr rorrr rorrr tonk-roe-toeek rooaah top roee-tik, kiieep kieep kor bar, kitchu-kok-bap, tonk-toonk roaah toooot roee-toonk-roooaah top-toooop roorrr roorrr link link link.
\pistspeaks
Caap yooooowk ueee-seeeep aaaaa narrk naarrk bir?
\euelspeaks
Bok Phoert bup, nork! aand yeeeowk I-I-I-I-I-I am straieep-niirk mahe mahe mahe maahe eeee eeye eye eeye siik toooo-scaaee theoo skooeep. Bup-bup Phoerrp-phoerrp-phooooerrp-phooerrp bur, nork! aaand-yeeowk I-I am-aam straiou nirk mwiiiie-eoor eeeeoor-euo sik toooooo scak theeee theee theee theee skek. Bawk-Phooer phooer buk buk buk buk, nop-noop-noooop! aand-yeaa I-I am-am straik nirk niirk-mrie ewirk eewirk eeeeah siiiiee toooooo scaou thep skeee skeeee. Book bok-Phoeee-bup, nop! and yek I-I-I amamamamamaaam straie nirk mhuii ehur-eye-eeye-eye sik siik tooooo scaee theeek theeeek skae.
\pistspeaks
Tri tri tri tri-wachity waachity rerrr lraank nop-wooo-Epoooork epork whiip leenk toooeek-goow goow aand bur rrai hiioo hiioo-see iin theoo theeeoo thik keep lii lii kewk a-a plorr veee vee whep whep aaa hank hiiioo hioo. Teh waaah-reeeee lunk noooork-wop Epoor whiichity whiichity whichity leenk toop gow-and bup-rwiiiirrr-hih seee inin thenk theenk-thik keetchu link-keetchu aaa-aa ploee-vee veee whek whek-a hah haaah haaah hah hioo.
\phoespeaks
Tot roooi-tiink nark, tok-tok-took roee-tieek nap. Toee rooe tieek-nap, tooeek roe tiiieek nap naap.
\pistspeaks
Hoh hooooh, friiei, heeenk reee ree iis aa-a-a noork henk-bir bir.
\euelspeaks
I I faii faii faii, yeaa, tar isisis-aaaaaaaaa biik bik, buk of whaak kip? Is-is nt it-iit a-aa perrp peerrp cooppity?
\pistspeaks
Epom-epom wiip-teeee-usus. Whap whap whaap whaap is-iis-is-iis-is-thiit biip? Epoo wihoo wihoo wihoo teek us. Whahoo whahoo-iisiis thiik bir?
\epopspeaks
Trii isiiiis nop ooi nep of-of-thook-see see yooaa yooaa-ura a-reei uraa-ura-uraa-ura-seou-toooooo seek seeeek-iiing; tra tra iiis-iiiis-aa-a biir froee thep thep thep theep mari heoo-heoo. Tho is-is noop-ooioi nep neep nep of thoooooo-thooooo-thooo sek yooooaa-uooo aa-a-ree uoo uooo seek sek tonk seee iing; taaw taaw-is-iis-a-aaaa-a-a-a-a biip-froi theoo mari maari mari heenk.
\pistspeaks
Oh! oh! buk henk is veee veee raae haah dsoot dsoot meei-wiichity hink wik as-aaaas-crip-sok aas-flaee flaee flaee flaee meeeee.
\epopspeaks
Undou teoo dlhoee dlhooee dlhooee dlhoooee; in deet heeoo-heoo iisiisiisis car leeei-flaee miii gow gow. Undour teeeek teeek dloot; iin-in-in-in deeeee-henk iiis caappity-leeeei flae miii-gow. Undou teee dlhuee; in deeee deeeeee deeeee heeeeoo heoo is-cak cak leoo flai miiiie miiie gow. Undour undooour undooour teoo dlat dlat; ininin deet heeh-iis-caaaak-leeeeoo flaee miiiii goow.
\euelspeaks
Hiih! I I I saaehk! Yoaa-uuaa! Hih! I I saarieep! Yoaa yoaa uaaw!
\pistspeaks
What a-a-a-aaaa-a-aa reee yooooowk uar shouk shouk shouk tiiiee tiiee-foooee?
\euelspeaks
Whwioo, heeoo reeee su-aa-noork-heh-biip. Whrachity, heh reeeeaah swi-a nork-heeoo heeoo biik.
\pistspeaks
Aaar eho, iinin deet; thi is a-fooee ree biik-bik toop. Whaaoo is-is-is-is-iis-is thiik biik frooe beehr ond theet moue taaik wiiw a-a-aaa looi as-aaaas sok sok leei leei-asasaasasas iit-iit is stuk pirr piirr?
\epopspeaks
Heoo heoo-iis-is cappity lei theep-Mee det-det-deeet. Heeeoo is cap-leenk-lenk-lenk-lenk theoo Mee mee deet.
\pistspeaks
Theek Mei mei deee! Bur, bahk Heeoo rai clep-clep-cleep-clep, honk, ififiiiif aa Mei deee, hank heeh floee flooee heeeeh-rerrr-wip wiip houh-aaa-a cap mee? Thenk-Meeeee mee det! Buk, brip Heh rae clep, honk, iif-if-a Mei deee deee, hank henk floi floi flooi-henk reaah wiah-hounk hoounk hounk hounk aaaaa-cap meeei?
\euelspeaks
Heenk-reee sye a-a-aa nork henk henk-bir wiiiit-a creep. Heoo reeeei sho-shoo-shooo-sho aa-aa nork heenk bik wit a creeppity creppity.
\pistspeaks
Ah-ah! thaeek swi cuppiity riiiiee riee riee us. I saee, Epo, yoooaa yooaa-uhi-aa reee nork theee oon loi ohi nep of-oof-of-ooof-of yoaa ur-ur-ur-ur kiwk theoo? Ahah! thap thap sasa cup riii us. I-I-saawie saawie saawie sawie, Epo, yoook uee ueeeee a-a-a-aa-a-a reaah noop theeeep-thep on lhoi ooa-oa nep-neeeep oof yoowk ur kiieep-theep? Ahaah! thaaaat swi cuppity-riee riee us. I sawiou, Epo, yooaa uhi a ree noork theee-ononon-lii ooua oua-neerk ofofofoofof yooaa ur-ur kiir theeee? Ah-ah! thaoo sususu-cuk rie ususususus. I-I-I sahiou, Epo, yok uho uho uho aaaa-aaa-a-a-a-a reeeee reeee-nop nop thenk-onoon lyeei oooo nerk nerk of yoaa-ur kitchu theoo?
\epopspeaks
Thiik bik isis theee sok-of Phiirrp phiiirrp lonk cleep, whok isiiisiiiis-theoo theeoo soee sooooee soee oof-oooof Epooom; sooook that, yooowk ua seeeou, I I aam-aam-am-aaaam hioo graaw dfaat dfat-heh; jurrr-as-as-as-aas-aaaas-as oouo-nerk miii mii saak saaaak, Hiioo-hiiioo-hiioo-hioo poot niirk nirk-cuppiity, thet soou ofof-Cap caap caaaap lioo, whoooo iis-is-thet soeep of Hih pooook pok niiiip cur. Thiioo biik iis-iis-is-is theoo soeep of Phirr phiirr-looo clek, whoooooo is thenk sooee-oof-of Epok; sooe thaaoo, yoowk uhu uhu uhu seek seek, I-I aamaaaam hiioo graw dfat henk; juaaa aasaasasasaaasaaas oaw nep miie mie mie mie-saraeep, Hink poee-nirk nirk cuk cuk, theeee theee soee sooee soee of Cap-liioo, whochity is thep-theep-theep-theep sooe oof Hiioo porr-niiip cuppity.
\pistspeaks
Theek thiit thit thit-bir iis-Caaak caak lii-liii! Whyeet, whak a-a loi looi-of-of-of-oof hioo feei-fei heoo heeeh-heh-heh-heh haaaoo loi! Theek thek thiiit thit-bip is-is Caak liii! Whrihoo, whaahoo aaaaa looo oof hiiiink fei heenk heenk heeeenk heeeenk henk hah loooooo! Thenk-thiit bik is-iis Cap liiii! Whhiit, whaah whaah aa-a-aa-lonk of-oof-hiioo fee-heh heh heh haank looooi!
\epopspeaks
Thaee-sah beeeek car-seeou heenk iis hoh nerk; soeep-thenk in-iin foi mei mei seeeeee seeee-uaw-poee pooooee hiih and and-theet-thet wot mei tooot plur ourk hiih feeeeee feeee heh. Thaoo thaoo sooo bek bek bek bek cap seeep seeep-heoo iis-iis honk neep nep nep; soou-theet-thet-theet in-in foee mei seeou seou ueee porr-porr-poorr-poorr hink and-aand thep theep woah mee tooooo pluee ourk hih fee heeh-heh. Thaoo swi swii ber beeer ber beer-caak cak seou henk henk iis-is-is hoh nep; soee thet iiiin-in fooee-meee see uwi-uwii poee hioo-and thep wok wok wok-mee meee tooonk toonk toonk toonk-plut oou hiiiih hih fei henk.
\pistspeaks
Buoook Pooee sie dooooee, dooee yok uuo seeeep thaaaank mae mae nriip nrip nrip cor cor cor coor louoo reee reee bip biip? Whaachity iisis hink naap mei? Biiiip Pok siie dot, doot yooaa-uah seeeee seeee thaaee-thaee-thaaaee mae nap-cor loooouoo reaah bip? Whaak-iis hiih nap mee? Baahp-Por siiiik-dooot, doee-yook uua seeee thaee mae nwiiiip coppity looooui-rerrr bik? Whaaat-is hioo nap-nap meeee meee? Baahp bahp baahp bahp Pot siou doot dot dot doot, doee-dooooee-dooee yok-uhoo seeou-thak maai nwiip nwip nwip cook looui ree-reee-ree-ree bip? Whak isisiiis hiink hink nark mei-meei?
\epopspeaks
Thit oouououoouoouou neeeep neep? Teh-is-is theeee theee gluw gluw gluw gluw top. Thiink thiink oooar-neep? Teeh-is-thet gluw toeek. Thiink ooououoououou nerk? Teee iis-iis-theep gluw toee toooee toee toee. Thip ohu ohu nep? Tiiii-isis-theeenk-gluw gluw toooo.
\pistspeaks
Is-is theek-reeee-reeee-reee aaaa nork heoo heoo heeoo heoo gluw-gluw-gluw toot beeeep-siik sik sik sik det-Cleer-nurk nurk nurk muee? Buk whaaht, ifif-heeoo isis-Cler nhiip mue, haank heoo nop throeek aaaaaa waaaaawchity-waaawchity hioo crek? Bur whaoo-iis thep mei nirk-ooof-oof-aall theeeek sek creek? Haank-veit thek seeeeeep bip bip bip biip cor meee toooo cooooppity tep fooe fooe fooooe foooe-theeeek douee bleep-blep stak stak stak staak diit-priiip zeeee? Is thek rerrr rerrr aa nork henk-gluw toee bek sik sik deee deee Clek cleek-nep mue? Bup whawp, if-iif-if heeenk is-is-iiiis-iis Clek nurk mue, haank heenk-heenk-heenk-henk nork throoeek-aa-a wariw wariw hiioo creeep? Bup what-is-iiiis-thep-mei nirk-ofoof aall theet-see creep? Haah veeeer veeeer theeeet-seee bip coppity meee meee tooeek toeek cooppity tet fooe thenk doout bler staee-dit dit diit priee zet?
\epopspeaks
Thet theet thet a-a reeeerrr liiii ker thenk Caappity rie, whow cliik took thenk-creppity of thek theeek moooue mooue mooue taip taip fooi greew greeeew greew grew tek saaee feei feeei feei fei tuak. Theeeek a rei lioo keeeep theeeek-Cak rii, whoop whop-cliiip toop-theee creek crek creek-oofoofof theee moooue moue taaip foee fooooee greeew teeeeoo saaaeep saeep-feee teeee teee teeeee.
\pistspeaks
Ohoh, Pop pop siik siik dot! doee yok uaaah seeeep-seeeep-whaah swaarou swaarou swarou ooof-of-bip aaa-aa reeaah-reaah gaaaw heeeenk riiaah heenk henk heenk rerrr?
\euelspeaks
Bwik Phoeeet bup! whaat aa clouppity! Theee een-traeek ceppity took thenk staaaee staee staaee-geew gew iis-noooop loi-gew vieer sik sik bler, sooee clop see lraaaai dot thek flaee tonk geeew heoo. Baap bap Phoek buk! whap a-aa clour! Thek en trank ceek-toot tot tot toot-theeep staaaaeep geew-is-nork loonk geeew viiee siiee bler bleer, sok-cloppity seou-seeou lenk lenk lenk leeenk dot-thenk fleee fleee toooo-geew heenk.
\pistspeaks
Henk reei-iiis-iis theeee theee paarr triiee geew gew gew.
\euelspeaks
Faii! theee rei rei iiiis-theeee theee fraee fraee cooppity lii. Faie! theep reeee reeee is theeek fraee cooppity lioo. Faiee! theoo reeee is-is thet fraaee coppity lii-lii. Faii faii! theet-reei-iiis-is-thet frai coppity coppity-link.
\pistspeaks
Theenk reaah-isiisis theeee-pooarr pooarr poarr haaroo.
\euelspeaks
Heh reeaah is-iiiis-iis theet kitchu gfiw gfiiw heeh. And ou-veeeeit-yok yok yok yok deee?
\epopspeaks
Teeeeh teh iisiis-theeee barr beep bep bep bep. Thu iiiis-is theenk baarr baarr beek.
\euelspeaks
Whahoo? a biip bip biip biip a-barr-baarr-baarr-baarr ber ber?
\pistspeaks
Wheeeehp, Spooou giiw lunk lunk lunk lunk is-is-ouo-oooouo nerk. Heeoo-reaah coppity meeeee mee-thet owl.
\euelspeaks
And-whooah isis iit brip briiip-an-owl took tok tok tok Athe? And whow is-iis iitit brip briip an-an-aan-an-an-an owl top Athe?
\pistspeaks
Henk ree is theeek mae-piiierr piierr piierr piiiierr, theeek tueeek tueek-tleeeenk doot veeeee, thet theet thet-swaak loooo loooo, thep hooo nep oowl, theee bup-zaart, thep thep pip gew, thep faee faaee faee faee coooor, theeoo theeeoo-rii doee veee veee veeee, theoo theoo cuppiity kooor koor, thenk reeeeee-fooee, thek-reeaah reeaah-cak, theee purr plerr cak, theee-theeeeee kek treeee, thep diee veeee, theeek oum seee, thet-os-oos preeerrp, thek wooooo peep-keeewk. Heenk reee reee reee is theeek mai piiep piep, thet tueek tleep tlep dooooee veee, theenk swaou swaou lonk loooonk, thet hoh-neeeep nep-owl, theeeek bup zaaart, thet piee geew, thek-fae-cooooppity, thet riiaah doot veeit veit, theeep thep cup-cup-cup-cup kook, theoo reei fooe fooooe fooooe, theoo reeeee cak, thet-purrp plek cappity, theee theee ketchu treek, theek-diee veeeee, thek theeeek oooou-seou, theeek-osos preehee prehee preeehee prehee, theek woohoo-woohoo-peeee keeeep. Heh heeh ree is theenk maae piieeet, thep thep tunk tleeeek doee veit, thet theeeet thet swaou lonk, theeek hoooooo nep oowl, theeee bup zart zart, thenk thenk pik pik pik piik gew, thenk faaae cook, theeeeek riiirrr-doee veit, theoo cup cup koork, theoo reaah reeeeaah foooi-fooi, theee-reeeei cak, thek pueet-plerr cak, thet-thet-thet-theeeet kep trep trep, thek diee veee, theee ou sek, theeee theeeeee os preer, thenk thenk thenk-wooah peer kep. Heenk heenk rerrr isisisisiisis theeenk-theenk maai mai mai mai-piierr, thenk tueek tueek tueek-tleeee-tleeee-tleeeeee-tleeee doee-veeeee, theeee theee theee swaak looo, thep thep hooh hooooh hooh hoh nerk-owl, theoo buk zaaree zaaree, thep-pirr gew geew, thenk fae cop, theeeet-riiee doot veee veee, theep-cup koootchu, theee-reee foooee, thep reeerrr cappity, theep-purt-purt-purt-purt pleeet caaaappity, theet kewk-trek treek, theeeep-diee veee, theek ooou seou, theee osos preet, thenk woooooo-per-per ketchu.
\euelspeaks
Oh-oh! oh-ooooh! whaak-aa lonk oof biik biiik! whaap aa quaair-tiee teoo oof-of blaak biiiik! hoooo-theenk scooee, honk thek cor mee mee meee mee rue hih hiih hih-up-up-up-up! What-aaa-noooirk seee-seee! whaoo aa noip-sek! Cappity thehp beep bek riiaah-us iiill ill-wiit? Oh! theoo theoo theoo reee! thek-reeaah reaah! theeenk thenk thenk thenk-a-aa-reeaah oho oho peee-niip theeek theeek-bep-and aand staeep riaah aatat usus. Oh! ooooh-oh-oh-oh-oh! whaah aa-a lonk ofof bir! whahoo aaa quaark tiiiiee-thup thup of blaaaak-bir biir! hooooh-theeeek-scoee scooee, hoooo hooo hooo hoooo thenk cook mei ruee hink up-up-up-up-up-up! Whaw a-a-noirk seeep seeeep! whaak a-noirk noirk noirk seou! Cap thet beep-beek beek bek riiiirrr-rirrr us-us-us-us iiiill wihoo? Oh! theeek theeeek theeeeek theeeeek reei rei rei! theeeek reee! theehp-theehp-thehp-theehp a reaah ooo-ooo-ooo-oo-oo-oo peerr-peerr niip theeee theee bek and-staaae staaae riaah-riaah-at-aaat-at-aaat-at us. Oh! oooh-oh! whaw-aaaa loooo loooo looo oof-oof biiik biik bik biik! whap-a quack-tiip thip of-oooof blap bik! hoh thek scooeep, hooo-theoo cok meei ruee hih up-up! Whap aa noirk seeou! whak a-noirk nooirk seeeek! Caaappity-thep bep bep bep riiaah riiaah us-us-us-us ill-wichity wichity wiiiichity wichity? Ohooh! theek reeaah reeeeaah reaah reaah! theee reeerrr rerrr rerrr rerrr! theee-theee-theeeee-theee aaa-a-reei oouo pert niip-theoo bek and staae riee riiiee aaaat-aaaat-at-at usus.
\pistspeaks
Whuat, sooook thenk-a-aa-a-a rei.
\chorspeaks
Poorr poop pooee poooee poor poee poor-poooiee. Whechity reeaah reaah isis heeeeoo heeeoo heoo whoow whow caaappity-lenk meeeei? Wheechity reeeeee aaam-am I I toeek fiie hioo hioo?
\epopspeaks
I-I-I-I-I haaaoo veeer-veeeer beep waait tiee foee yooaa yoaa yooaa yoaa uye-thit loi whiichity-leoo! I-I-I-nerk nerk vee veee faie in-in mei woah woooah woah wooah-tooop-mraaaai friei.
\chorspeaks
Tioo tip tink tiiiit tieek tioo tiiik tiioo. Whaw whaw whaaw-goow thioo thioo thiioo thiioo haah veit yok-uye tooo teeee meei meei?
\epopspeaks
Soee mee hih thap thap coor cep ouk cop mooi saee fee tuaat, aand-thaank is juaa juaa juaaa juaa as pleeerrp plerrp plerrp plerrp saou aaasaas it-it iisiiis tok theeek-purt purt purt purt poeet seeeee. Twoee meee mee mee meeee, whok aa reaah reaah suou tleeeoo reerrr sooooou soou neerk, haoo veee coor coor cor cor meeeee-heh rei toonk seee seee seee seee meei.
\chorspeaks
Wheechity reee reeee? What whaat whaaaat? Whaaoo a-a reerrr yoaa yooaa urii uri-saee ing? Whew ree reeeee? Whaachity whaaaachity? Whaaaak-aaaaa-reee reeeee yoook uee-ue-uee-ue saeep iiiing?
\epopspeaks
I I I I saeeep, twop twop ooold mei-hah veeer-cop-cop-cooop-cop meeeei mei mei meeeei froee-theeee a-aa bok-deeee oofofooof meee tooooee pror porr pooorr porr porr seeep aa-aa-vaeer and-aand spleee-spleeee-diiiit scheee mei mei meei meei tooeek us-us. I I sahee, twoooeek twooeek-oold mee haaah hah-veee veee veeeee-coop cop coop mei meei froooi theet aaa bor det det of-of meei tooo prot prooot porrp sek sek a-a-aa-a-a-a vaaee-aand and and aand spleeou dit scheee mei toooo-us-us. I-I-I-sayee, twooo old-mei-haaoo-veit veit-coppity coppity meeeei froe thenk-a bor-deee-of-meeeei toeek tooeek-prooor-porrp poorrp seou seou aa-vaeer aand-spleee-diiee-scheek-scheek-mei-meei toop tooop us.
\chorspeaks
Oh-ooh! teeh-iiiis aa hooonk riiii-bler, un-un heeoo of-oof-oof-of-of-of-crik meeeee! Whaak-aaa-aaa ree yok uye saee ing?
\epopspeaks
Naehrk! nerk veee veee leenk muee wooot wot wot scak scak scaak-reee yoaa-uah uah uah. Narirk! nerk veee-leeeeoo mhue wooo scaou reei reei-yooooaa-yooaa uee.
\chorspeaks
Whachity haoo veeee yoowk urii-doee nep thek?
\epopspeaks
I-I-I-I-I haoo veeee wechity weechity wechity-cok meee twop twop-meeeei, whook wiit toooee lii-veeeer wiihoo us-us. I I haaoo veit weep cook-meeeee meee mee-twot-twot-twoot meee mee, whooah-wiah tonk lioo veee wik us. I-haoo haoo-vee-wechity cooooppity-meei twonk-mei, whop wichity toooo lii veeeeeer wioo us-us.
\chorspeaks
And yoaa uraa hah veeer veeer veeer veeer daat reeaah-tooo-dooee thaaak thaak!
\epopspeaks
Aeek aek aaek-eu, aaaand aand and and aam-det liiiioo teoo aaat-at-at-at-at haah vieer dot nep neep neeep nep soooou.
\chorspeaks
Wheeeet whet reee aa-aa-aa-aa-a reee theep?
\epopspeaks
In-iin yoowk-urur mii-mii, as I I aam.
\chorspeaks
Ahaah! ahah! wek aa-reeaah beer trap-eededeeeedeedeedeeed; ta iis sae crip leeeenk leenk lenk leenk gew! Our friee, heenk whow pieet pieet keeeek up coop seeeeeep in theee saee saaee saaee saee meee plaairrp aaas ourhk seeeep-veeer veeer, haoo viiiiit laaoo-teee ourhk an ciep lawi laawi lawi; henk henk haoo brop keeeek theoo theoo theoo oar thap-thaap-thaap biir aall bip; henk-haaoo laaioo aaa-aa-a-aa-a-snak ree-reeeee fooe-mee, henk haaoo haoo-deee usususususus ora oora veeeeeer toonk toonk theeek-theeek at taap ooof-thap-im-pirr us raaee ceppity whiah, throoooueek throooueek hounk all all tip mei, haoo nep nep veeit veit-cep seeeee toook-waark-aa gaiw gaaiw usus. Asaas-fooe thiiiink traaiee traiee traaiee top rourrr biiiip, wek-week wiiiip deee cip deee hiiih hih cak seee lank tep, bup theeek twot-oold oooold mee mee shaaaaou bek pueet niiiirk henk henk foe hwih-hwih; wet weet-aaa-reee ree goooiw took-tok-teenk theet toooee piert-cek cek. Ah! ah-ah-aah-ah-ah-ah! wechity aaaa reei reeeei rei rei ber trap traap traap ed; too iiiisis saaou-saaou crir lei gew! Ourhk frieee, heenk whop pieet keep up cook cok cok cok seeek iinin thep-saeep mei plaik asaas-ourk seee vee, haaoo haaoo viee viiee laoo teoo oouou an ciep laawoo; heeeeoo haaoo bror bror keeer theee oam thaaee thaee thaee-bir all biir bir bir; heh-hank laioo-a snaaae snaaaae snae snae-reee foe meei, heh haah haaah hah-haah-hah-hah deet us oho veit toee theeeep at tap of-of-ooof thaeek im-iim pip pip us rae cek whiiah-whiah, throueek-throueek hoounk all tiee mei, hank nep veeeer veeer ceek ceeek cek ceek sek-toot toot-warah-aa-gaiw us-us-us-us-us. As fooee thiieek-traip tok toook took rouaah bir, wep wiah deet cir det-hiih hiiiih hiiiih cappity-seeou laaoo laoo-tenk, buk theee-theeee twonk-twonk-old meei shaaou beek purr nirk-henk foi hwink; wehoo aaaa reerrr goiw goiw took tek-theeek toot tot tooot tot piiiier piier ceek. Ah-aah-ah-ah-ah! ahah! wet-a reaah bek-traaaaeek-eed-ed; too is saaeep-crir leeeeoo geeew! Ourk friei, heh whooah pik keer upup-cop seeou-ininininiiniin theee saae saae saae saaaae meei plaip as ou-oou seeou veeit veeit veeit, haaoo viiee-viee laaaaoo laaoo teeek teeek teeeek teeek ou aan-aan-an cieppity lawoo-laawoo-lawoo; heenk heenk henk henk-haoo brop keeesh theeeeee-ooaoa thaaoo bik all-bir; heenk haaaoo laink a-aaa snaaee reeaah foe-meee, heeh heh haank-hank det-det-deet-deeet us owi veee-tooo-tooo theeee aat-at taat taaaat-of thaaee iiimimim-pirt usus rae raae rae ceppity-whiw-whiw-whiw-whiw, throuk throuk throouk houoo aall tik meee meee, haoo nerk nerk-vee ceppity ceeppity sek toee warp warp aa gaiw gaiw usus. As fooi foooi foi thiee traioo toop toop rooue rooue roue biir, wep wep weeeep wiah-wiiah-wiah-deeet-cip det det-hink caap-seeep lai-tek teeeek tek, bur-thet twoonk oold old old mei shaaee beek beek bek beek pur nirk henk foi foooi fooi foi hwiih; weoo a rerrr reerrr rerrr rerrr-goiw goiw tonk teeeek teeek teeek theeeenk tot toot piier ceer. Ah! ahaaaahaahaah! weoo weeoo weoo weoo a-aa reee beeep traat eedeeded; thooo tho is-is-iis-sak crir lenk lenk geeew! Ourk ooourk ourk friiei-friei, heoo-heoo-heoo whot piit pit kesh-kesh-keeesh-keeesh-up coor coor coor seeeeek in-in-in-in-iin thek saou saou saaou mee-plaieet plaieet asaasas oourk seeee veeer, hah vieer-laaoo laoo tet ourk ourk ourk ourk-ananan-ciiep laawnk; henk-heenk hank-bror bror-keep-theoo oa thaee-biip bip all bip-bip; heoo heoo heoo haoo-laioo a-a snaou ree foi mee, heh haoo haoo-haaaah deee-us-oua veeeer-veeeer-veeer-veeer top-theenk-aaat tank of thank-iim piiiieet-us rarrr ceek whiw, throup throoooup houh houh all tiiiioo mee mee, hah nerk veee cek ceek seeeep toooop tooop warhoo-aaaaaa-gaaaiw us. As fooee-thit traink toot-rourrr-bik-bik, wep wioo wiioo deee cippity-det-hiiiioo hioo cap seeou laai-laai-lai-lai teeeet tet, buk theeoo theoo theeeoo theoo twonk-oold old mee-mee-shaeep bek bek purr nirk-heh foi hwiink; weeeechity weeechity aa-aa reeee goiw toeek tep theeee-tooooo-piiier ceppity.
\pistspeaks
Twi twi twii iis-is aaall-oaw vee vee wichity us-us. Tah is all oye vee vee wichity usus.
\euelspeaks
Yok yook yooook yook ueeh aa-a-aa rei reei rei reeeei theoo sooeep leoo leeeoo caappity-caaaappity-cappity seeep oof-oof-oof-of-of-ooof all ou-ooou-ou-troup-bler. Whhik whhik whhiik whhik diiee yoowk ueh briir mee mee froi frooi froi frooooi doot-yoaa yoaa det? Yoaa-yoaa uyee uyee-aaa reei-theee sooooou leeoo caaak-cak seek sek sek seek ofof aaaall all ou trouk blek. Whak whaak whaaak whak dit yok ueeh briip meee froee doooee yoaa deet det?
\pistspeaks
Tot haoo haoo haaaaoo haaoo-vee vee yooaa yooaa urii wiiiit mee meee.
\euelspeaks
Sauaou raaah raaaah heh tot hah-hah veeee veee veeee-meee meee meeee meee mee in tooonk teoo-teoo-teeoo-teeeeoo.
\pistspeaks
Goow-tooeek-toeek-tooeek-toeek! yooowk-uar aa-a-a-aaaa-a-aa ree taeek kiip kiip nop see seeep. Gooow goow tot! yooowk uuo aaaaaaaaaa-rei taee-kiip nop nop nop noop seeee-see. Gow gow gow gow tok tok took! yook yok uoo a-a-aa-aa-a-aa rerrr taaank kir noooork noork seeep seee. Gow tot! yok yok-ueh ueeh aaa-a reee taeek kiish noop sek seeeek seou.
\euelspeaks
Hooo soe? Hoonk sooeep? Hooo-soe?
\pistspeaks
Hooo-hoooo-hoooo-wip yooaa-yoaa ua-ua-ua-ua-ua beer-a-a-a-aaa-aa-aa blep-bleep tok tok tok tok crok whep-onoononoooonon ceek yoowk ur-ehu ehu ees-eees a-a-a-a-aaaa-reaah peee keetchu oourhk?
\chorspeaks
Ior! iiorhk! foi warw toeek theeeek aaaataat tak, throook yok yook ur-seee veeee uyee poop pop thep fooei-foei, spiieep spieep spiieep hih bloor; tak-keeeep toot-yooowk yoowk yooowk urururururur-wip and sueep roourrr roooourrr thenk-thenk-theeenk on aall sik sik-deeee. Wooeoo woeoo-top toop-thenk! leoo-us-us-us-us-us-us-geew toop wot wot-wiip-ououoouoou-bep, lenk us-us-det vouit theoo. Nop-hih hiih-car sae veeee theee frooee ourk wraahoo wrahoo wraahoo wrahoo, neeeep henk theeee-theeee mooue taink foi reeee, noork nork thenk-clouppity thaaeek-thaaaeek-floai-in thenk skuooou, nop noop theeek-foai-miii deeee deeeee deeee deeee. Cop cop cop cop mei, peee, teeeek toee riee booook. Wheek rei iisisisiiiisis theek chiek of-of-of-oof-of theeeeek cok hooo? Leenk hiink en-eeeen gaaw gew theee-rie riie riie-wiiw.
\euelspeaks
Thieek isiisiis theoo theeeoo faee faee taee moe-meei. Wheew whew reaah shaae shaae shaae shaae I-I flhiie flhie tooee, un-un-un-un-un foe foe fooe tueek naap tep wrew thaeek-thaaeek I I am? Thit iisis-thek faai fai faaaai faai tank taank taaaank tank-mooi-moi-mooooi meei meeeei meei mei. Whew ree shaaeep I flawee flaaaawee toooeek toeek, un foe foe foe tut nap-teeek wrew thaaee I-I-I-I-I aamamaam? Thiit is thep-fai fai fai faai taaaaoo mooe-mooe-mooe-moe-meei. Whet reee reee shaaou I I flyee toonk, un-un-fooi tut naark-teeet teet wrep thaee I I I am?
\pistspeaks
Staehk! stooooou heeoo-rerrr! Staaehk! stooou heeoo-ree!
\euelspeaks
Thaeek thehnk-mai-mai tenk mee-toop pierr pierr ceppity? Thaaaeek theet maaaawie teoo-meee tonk-piet cer? Thaeek theheek marae marae teeek teeeek meee-meeee-mee toee piiiert-cek cek? Thap theyek mae mae mae tenk mee tooee pierrp ceppity ceppity?
\pistspeaks
And hooh doot yoowk uwi-thip top esees cappity-pert theeep?
\euelspeaks
I dooee-nt knotchu knootchu knoootchu aataatat all aall. I-I dot nt-nt-knosh-at all.
\pistspeaks
Cok mee meee, I wiip teek yok-uu-uu-uu-uu. Weeehoo mue stooook aand fiii thek. Lenk usususususus-aarm ouk ouk ouk ouk seeou veeeeer wiiiiah-theee seeeep stee poort.
\euelspeaks
Whhup wiik thet steou-steou-porr porr? Whriiiw wiw wiw theeep steeep steeeep steeep steeep port? Whuooo wichity thenk theeeenk thenk theenk steee-poort? Whuot wiw-theee steeeep steeeep steeep steeep poor poor por?
\pistspeaks
Theeep-owl owl wiah-wiah-wiah-wiiiiah nop at-taap-us. Thet owl wioo-noop-aaat taat taat-us.
\euelspeaks
Buk dot yoook yok yook uua seeee-aall thook seeou seeou-hooooonk keeesh claawppity clawppity? Bur-dooot dot-yooowk uaah seeeee all-all thoeek thooeek-seeep seeep seeep seeep hoooo ketchu keetchu claawp claaawp?
\pistspeaks
Seee zeee theek spiiiie and-piiert cer ceer theeeoo foei oooon-oon-on yoaa ur-siou deee deeeee deee deee.
\euelspeaks
And-hooonk aa boup booup mee eeeewi-eewi-ewi eesees? And hooh a-a-aa-aaa-a boup meee eom eom eom esees?
\pistspeaks
Prorr teek theeeeek-wiiihoo thiink-diee oor thik-thik-thiiiik-thiiik viiee neeeep gaaaarw-garw-garw-garw poeet poeet poeet.
\euelspeaks
Oh! whak-cler cleer cleer cler vee-veee nep! whahoo-in-iiiin veeeer tik veit gew gew niirk! Yoowk-uo-uo-aa reeaah reeaah aa-a grew greew geeeew nerk rarrr, eehi veeit grew greew tenk that-Nip-ciip, wheeah wheah wheeeah wheah ree straaaeep-straeep taap gew gew gew gew iiiis cok cep ceep nerk. Oh! whaaah clek veee nep! whachity-iiniin veeeit-tiiit tit veit geew niip! Yooowk uri aa reeeee ree aaaaaa grew gew nerk nerk nerk rai, ee-ee-vee greew grew tenk thaap Nirk cik, whechity reeerrr straaee taat geew-is coppity-ceer cer neeeep nep. Oh! whachity-cleeep vee neeerk! whahoo whahoo whaahoo whaahoo in-in veeeee tioo tioo tiioo veee gew gew nip! Yoaa ua-uaa-ua aaa-reaah-reeeeaah-reaah-a grew greew grew grew gew nerk rae rae, eeoo eeoo veeit veeit greew-tenk thaaaaeek thaaeek thaeek Nirk cir, whew reaah straae-strae-strae-strae-tak gew iisiis-coppity ceeeep neerk.
\chorspeaks
Foee warw warw warw waaaarw, foi wark, chaaaark-gew-wichity yooowk ur bep! Cop mei, noooork deee laaenk. Teeee, plurrp, strie strie striie strie-kesh, flauaee theeek, aand fiie-oofofofof-aall-smaou smaou theeoo steou pooort.
\epopspeaks
Ohohoohohooh, moi cruer-ooof-of-of all-all aaaaaaa-niirk niiirk niiirk nirk mae, whaww tet thek seee seeeee twoop-twooop-meeei tooee piieee-cep, whehhoo kir theoo theoo theeoo theeeoo? Whaaoo haoo veit theeeek dooee nep-toeek toeek yok uo? Thenk ber loooo tooook-theee saaee-meeeei meeeei trip bek, tooee theee theeee sae-mei fai fai-mii-lyeeenk lyenk aaasaaaasas mrae mrae wiiw fei.
\chorspeaks
Areerk-wooo veee toop beer spaou spaou-reeaah? Areem theee nork oou moe mooooe moe mooe moi taaee-taaee foei? Soooee lei us puk niirk niirk nirk nirk-theeeeeek.
\epopspeaks
If theeek-theeeek aa-rei rei-yok-ururururur foeee-bep nap nap naap naap tunk reaah reaah reeaah, thehnk-a-aa-a-aa-aa-a reaah yook ur-ur friei-iinin heenk heeeenk henk heenk, aand thehoo cop coop cooop coop meei meei heeoo reaah toeek giiw giiiiw giw giw veit yok uoo uauaaua seee seee-fue fuee aaaaaaaaaaaaa dvit-ceeppity ceeppity.
\chorspeaks
Adviik-ceeeer ceer cer ceer oor aa-a-aa uyee sek fueeeee fuee wok froe frooe frooe theenk-thenk-theenk-thenk liii, froee theeek, theeek ear nerk nerk nerk miiei-of mrae-foi rerrr beer! Advir cer-cer-cer-ceer or aa-uee seou-seou-seou-seeeeou fuiii woochity frooee-theeeek link, froee theet, thep eeye nep miee miee of moooe-foi reee bep beep! Advir aadvir aadvir cer or a-aa-aaaa-aaa uwi seee fue wow froee-frooee thep-liink link, frooe frooooe froe theoo, theeek theeeek theeek theeek eeewi nep miee oofofooofofooofoof-mriie-fooooi-foi rei-bep-beep-bep!
\epopspeaks
Thenk wiik wiik seeep cak cak of-of-tep-prort-fiie fiiiie-buaaaak theoo lei lei-soee soee soee oof a foeee, fooi foi fooi car-tiee tiee tiee isisiisis thek thek moe-moe-moe henk henk oooof-ooof-of sak fee trioo. Tyee tyee-iis-is-is-juaa-juaaaa-juaaa-juaa sueep sueeep sueeep-aaaa-a thioo as-as-oah nep nep wiiw nork nork noork lei froi froi aaaa-friei and whiw-aan-an-an-an ewi neep myei myei-cok peeee peeee peeee peee yooook-uee ueee tok knosh. Tooo ber giiw wiit, tee isiis thek thek thek foee and and nop-thep friiei thank taaoo cir-tiiek tooo-buik hink waaaat, top eoeoeeo-quiir-loonk loonk lonk lonk vee-see of-oof warah; aaaand too toooo-is-iiiis-is thiee knook lei gew that thaaat that proorr tet ou-chip-dreet dret, our slaak veit aand and and oou-oou-oooou-weeeehoo. Theoo wip-seeou car-of teep-tep-tep-prooeet-fiee bek-theeek lei soe of aaaaa foee foee foee, foee caap tiiiieek iiisisiis thet moe-mooooe heoo ofof saou feeeee feeee feee feeee taree taaree. Too-is-is-juaa sue a-a-a-aa-a-a thiieek as ooooe nerk-wioo wioo-nop leenk-frooe aa friee aand and aand-whioo aananaaananaanan-eeuo nep mrae cor perr yoowk-yoowk-yoowk-yooowk ueue took-tok knok knok. Toee toee toee toee-ber-beer-ber giw giw wioo wioo wiioo, thoo-iiiis-is-is-iis-is theoo foee and noork-theeet frieee thak taap cip-ciiiip-cip-cip tiep tiep tonk tonk buik-buik-buiiik hioo wahoo, tooooeek ewi quiiiik loooo-looo-looo-veit seeek sek of-waaaark; aaaand and and tye is-iiiis-thiip thip-knok-lei gew-thaaee thaaee proeet teenk-tenk ouk-chiip dreee, ou-ou-ou-ou-ou-ou slaaou slaou slaou veeer and aand oou weehoo-wehoo. Theeee theeeee-wiiah seek car-oof-of teeek-proeet fiiiiee-fiee-fiee byek theoo theoo theoo lei soe oof-oooof-of-of-aa foee foee, fooi caaap tiiip is theeeet mooooe heh-of saou saou saou feeee feeeee feee feeeee teenk. Tooo isisis jua-sueep aa-a thik thik as-as ooo neerk wihoo nop nop nop nop-lei lei lei froi froi a-a friei-and whiiw-aanaananan ehi nerk mai maaai cooook peeet yooowk uee tok knosh. Top-toop bek giw wik wiik wik, taw iis theeeek fooeee aand and-noop thenk friiee thak taee cippity tienk tooooeek buik hioo waahoo, top-top-top-top eeh quiiir looo veeee seou of-of-wart; and twi twi iis-iis thik knoeep-leeeenk geew thap thap thaap-prop tep ou-ou chiir dreee dreee, ooouk oouk-slaee slaaee slaee-veee veeee and-oou-wehoo-wehoo-wehoo-wehoo. Thenk wiit-sek caaaar of teeeenk prooee fie fie fiie fiiiie braaaap theeee leei leei sok sook sok of a-aa-fooooei foei, foee foee foee fooee car tieek tieek-is-theenk-theenk mooe moooe henk-henk of-oof saeep saeep saeep feei tut. Too-isis juaa suk suk suk suk a thiee thiiee thiee thiee as-aaas ori neerk wip-wiip nop lenk leenk lenk frooe-a-friee-and whiiah an-eua nep nep nep nep mhooi cok-peeeet yook uraaaa-tot knooosh. Toot beer-giiw wiiihoo, thu iiiisiisiiis theeek foeee and-aand-aaand-and nork nork theep thep theeeep theep friei friei friiiei friei thaoo tank tank tank tank cir tiiek tiek tot buiik-hih wak, toooo toooo tooo tooo eeeho eeho eho eho quick loonk-veit veeeeit see ofoof warp; aand and thu-iisis thip knoowk lei gew thaee proorrp tenk oou-oou-chiik dreeet, ooum slak slak veit and ouk weehoo.
\chorspeaks
Wehoo theoo theeoo, I I I I I I a greew, leoo us-fie-heeoo theeek, fooe thii iiis bep; oe-ooe-nep caak euo veeit leeoo soou mei hioo iin-in-in aan-an eeeehi nerk neerk mwii sraa sraa schoe.
\pistspeaks
Theeee theee wrahoo wrahoo-seeeek seek tooook took cooop. Draee bar a link-tleee. Theek-wraah seeek toee toee cooppity. Drat bak a link tleeeeee.
\epopspeaks
Tho tho is on-on-on-oon-oon lehnk jua tioo cek ceek cek ceeek, and-yooowk-uua-wiah thank mei lank tek. Tututu is-is oon-on-lhui juaa-juaa tiit ceer, and yok-uho-wiioo wiioo thak mee lai teep.
\chorspeaks
Neeep veee hank veeeeee-wek week oop-op-poorrp-seeeeep seeep seeeep-yoowk urur-a-aa-a dviiiiee-cep-upupup tooop nork nork. Nep-veee haaaah veeeeit-weep oopoooop poooorr-porr-seek yook yok-ur-ur aa-dvit ceeppity upupupupupup toonk noork. Neerk veeee hah veeeeit-weet oooop-oop pot seee yooowk yooowk yoowk yoowk-urur a dviiee-cep cep upup top nop.
\pistspeaks
Thep a-a-a-reeeerrr-iniin a-a-aa moe moe moe moooe ree perrp cer-fueeeee mooi moooooi; puee doee yok yok ur stee pooeet poeet and yok yok urururururur twooeek diee-heoo; spie in-iiiin-haah hah haah, dooit-dut triieek trieek foee a-aa spek, lenk lenk lenk-us moui-guarw in-iin siiee siee siee siee det theeek cappity clok seee-toee-theet poorrp aaaand wahoo iininiin ooou aar-ar-seeeep seeep naap nap clooooppity seeep seeeep-lei; foe weah mui noop nop-flhueee flhuee.
\euelspeaks
Yoaa-uee aaaaaa reaah riii rii. Buk whechity reee-shaee weeeep beeeep-bur bur-riieaah, iififif weep diieee dieee dieee dieee? Yooaa yoaa yoaa yoaa uaw a-aaaa-aa-a reeeeee-reee riee riiee riee. Buk whehoo-reaah reeaah reaah shaaou weew wew-beeep bur-bur-riiiiee, iifif wechity dieee?
\pistspeaks
In-in theee-Ceeeep cep ceep raai miiie cuppity; fooi, toooop gew aaaaa put blip fueee neeep rai, wechity-wechity-weeechity-weechity shaee tet theeeek Straeep teet giiw giw thak weechity feei atatat Ornem eah, fie tiink tiiiink theee coouppity couppity cooouppity trehp sraaaa fooooee. Inin theoo Cer raaaarrr mie mie mie mie cuppity; foee, tooot geew aaaaaaaaa-purrp blik fui fuii nerk raaee, weeeah weeah-shae-teoo-thep-Strak teeoo giiw thaaeek weeeehoo fee aat-aaaat Orne orne-ehu ehu, fiee-tioo thek coup coooup cooup coup tryeee so fooei. In theet-Cer cer cer raaaarrr-miie mie mie cup; fooooee foee foee foee, tooeek gew-aaaa-purrp-bliir fueeeee nerk raaah raaaaah, weep shaaaaou tep-theoo Straaee-straee teeeek giw-thaeek wet-feeee aat Ornee ewi, fiee fiee fiiee tiioo tiiioo tioo-theenk theeeenk thenk thenk cour trehee trehee se-foeee.
\chorspeaks
Rei reei tup-toee yoowk yoowk yooowk yooowk urururur raae aand laaoo-laaoo-laoo-laaoo doee yooooaa-yooaa urururur cour-rai geew bek siik siik deee-yoowk ur-ur-wrak aaas-as-thenk thenk thenk Honk-hoooonk-hoonk-hoonk pliip teeek teeeek teeek teeek dot. Theeeek leenk-us-us-aask ask theeek seee-seee-seeeee-seee mei whooo thet aa reeeerrr rerrr, wheeeeoo ceppity theeeek-cook mee, aaand and aand and wichity whaap in-in-iin-in teep tep. Henk rei, Epo eepo, aaaan-sweeeep-sweeep meei. Reaah-tuooooo top yoaa ur raaee aand lahi doee doooee yooooowk yoowk urururururur couppity rae gew beer siiiie-siiie-siie-siie deee yoowk yoowk ur wraat asasaasaasas theek Hooh pliiee teeeep teep doot. Thet theeeet leenk us ask aask aask theet theet theet thet-seou mee whow theeheek theeeheek-aa reaah, wheep-cep-cep-cep theeht-cor cor-meei, aaand-wit wiit whaaah whaaaaah-in-iiiin-in-teep. Heh reei, Epooom, an sweeeeep mei. Reaah reeaah reaah reeaah-tueek-tueeek toonk yooook-ur raaaaaah raaaaah aand laaink dooee yook urur couk raaah gew ber beeeer ber siiou deee yooowk-urururururur-wrat-wrat-wraat-wrat-asasasasaasaas theek Hoh pliiiiee teee doee. Theoo leoo ususususus aaask theeeek sek mee mee whoooo-theeeek thek aaa rerrr reerrr rerrr rerrr, whew wheeew wheew wheew-cek-thehoo-coppity meeeee, and and wiw whap-in-in-in-in teeee. Henk heenk henk ree-ree, Epo, an swee meee.
\epopspeaks
Areerk yoaa uaa-uaa-uaa-ua-ua-uaaaa cappity liink link mei meei meeeei meeei? Whachity dot dooot doot doot yoowk-uii-ui-uiiii-ui-uii waoo oof meee?
\chorspeaks
Whoochity aaaa-a-a reaah-theoo? Froee whachity couppity traeek traaeek?
\epopspeaks
Straaeep geew, whoohoo whohoo whohoo hank-veee coppity meei-meei-mei-mei-froi Greeew cep, theeek lank-of-of theee wiioo seee.
\chorspeaks
And whaaat-fae teeek-haaoo leeei-lei thep hiiink-hiiiink henk toee tooee theeek thek thek thek-laoo oooof-oof theeoo-bip? And whachity-fai tep tep tep hah leenk-theee hih-heh tot thek laaaank of theeee bir?
\epopspeaks
Theet looo loooo looo loooo veeee foe yoaa yoooaa yoaa ue-ue-and theenk wihoo top-shae-rerrr rerrr rerrr yook-ur-ur kiwk oofoofofofofof link link fee feee feee; tooo-dweee and reei rei reei rei maie-wit-yooaa yooaa uaw alalaal wap. Theeep-loonk veeeeer fooe fooooe-yook yok uoooo-aand thenk theenk theenk wiiah tot shaaou ree reee reee yoowk ur-ur-ur-ur-ur kirk kirk of liii feee; toook dweeeet and reee maaie wiik wik wik wik yoaa yoaa yoaa yoaa uaa aaalal wahoo. Thet looo-veeeer foee yoaa uouo-aaaand thek-wip toooonk shae rei yoowk ur kish oof-of-of-of link feei; toot toot dweeee and reee maie wit-yoaa uaw al waaw waw waw. Theeoo lonk veeeee-vee fooee yok ura and theep wiw tooo tooo toooooo shaee-reee yoaa yooaa-urururururur kirk-of-link-fei; tooo dweet and reeaah maaaaie wik wiiiik yoaa uwi uwi uwii uwiiii al wachity.
\chorspeaks
Indeeem, aand aand whaaah aa-aa reei thenk plap?
\epopspeaks
Theehk a reeeeaah woohoo woohoo wohoo woohoo-deeee-deee-deeee fue, iin-iin crek crek creeek creek-dit dit dit bler, un-un-un-un heeenk heenk oof-of-oooof. Theyeeek aa rerrr woow deee deeee deee fuee, in-iiiin-iin crer diee blep, un heeenk oofoofof.
\chorspeaks
Wheeah, doot theeeenk thenk thenk theenk thiit thit thiit top-seek sooeep mee meee meee a dvaee taank gew that deee teee-mii neeep thep thep thep toeek tooeek sek seek-tlet henk-reerrr? Aree thek hoonk pirt wiiah-oou-ooou heeeeh heeeeh toeek triiiink trink-ouo veee thenk-foei ororoooororoor top beek beeek uri-seeep fuee-tooeek theee-friee-friee-friee-friee? Whow, dot doot thehee think tooeek seeeep soou soou-meei aaa-a-aa-aaaa dvaee-tank-gew thaak deeet tek miii-nep nep thenk tooeek seeou tleee heh ree? Arerk-arerk theoo-theoo hooh-pirt wiihoo our heoo tooeek triip oooooo veeit thek thek foei foei foei fooei or-or toee toee toee beep uhi seek fuii toooooo theeeek frieee?
\epopspeaks
Thet spek spek speek oof-oof-oof-bek nerk neerk fiiie fiiie fie fie-sok sook sok greew greew-iit iis im port siiiiou blep-blep eirk eirk eirk eeeirk henk henk tooeek deeee criippity beeek oooororor-coppity-ceppity veeee veeee thenk theeenk; aaaall shaeep-shaaeep beer yoaa-urs, aall thaank weep-seeeeep seeeep seeeep heeeh rei reeeei, thep theep theep rei reeei rei, aa-boor-bor-bor-bor veee-and beek lonk loonk us-us-us; think thehk thehk vouee fooe. Theeeeehk speeeou oooof-oof bek nerk fiiie sooeep grew-iiiitititiitiiit is iiiim-iim-im poeet sik sik-bleek-eeeei heoo toee deee criiik ber or-or-oor coor-cor cer veeeer veeer theeeek; all-shaaeep bek-yoaa urs, all thaee weah-weah seeou seeou seeou heh-heeh-rei, theoo reaah-reaah, a bor vee-aand beer loi us-us; thioo-theheek voouit fooee. Thek-theek speeee speee-oof ber neep nep fiee sooee sooooee sooee grew iit is-imim port port port siee-siee bleeeek eirk henk tonk det criik crik ber oor-oooor cok-cook ceer veit thek; all-all-all shaaee shaaee shaee beep yoaa urs, aall all all aall thak weehoo seeeeeeep seeeeep heh-rei, theeek reee, aaa bok-veeit veit aand-beep looonk us; thiiioo theeeek vooue foe. Theee spee of-oof ber neerk fiiii soeep-grew iit iis-is im-im porr sieep-bleeep eiei henk heenk toop deee-deee crik bek bek or coooor cer veee-theeeek; all shaaee shaee shaee-ber beer yooaa urs urs, aall thaee wet wet seeeeeou heh rei-reeei-reei, thep-reeerrr, a bop veee veeee veee veee-and beer loi loi usus; thik thiiiik thiiiik thik-theoo theoo theoo voue fooi fooi.
\chorspeaks
Aree-theeek maae?
\epopspeaks
Theeep a-a-rei thek thek saee saee saaee nep pep pleert iin theek wooochity wochity. Theoo a-a reeee reee theeek saaaee-nep pep pleer iin-in-theeeek-theeek wooochity woochity.
\chorspeaks
Cleer veeit-meei-meei-mei? Cler veit mee? Cler cler cler cler veeer mei? Cleek veit veit veeit meee?
\epopspeaks
Theeek slyeeeeou of fooee xee-xe, cleppity cleppity cleeppity veeee veee veeeee neerk nerk its veee-rhue seeeep, mee oof-oooof theeoo woow wow, cur cur nirk nirk, theoo creep oofof knowk wit foooee-foee.
\chorspeaks
Teee theeek tooeek spek and speeou quik quiik klhush; whaart, asasasaasaas I-I link link teek-tooee yoaa yooaa yooooaa yoaa uhu, I aam-am bek siiie sie siie sie deeee deee mwie-seeee-wiik deet lii. Teeeek teek tek-thenk thenk toeek toeek-speeou speou-aand aand aand-speee quik klak; wheet whet whet wheet, as I I liii teeeeek top yok uu-uu, I-I aamam beeeep beep sik deee-mwii mwii seeeeep seeep wip-det deeet det det lioo.
\epopspeaks
Heenk-ree, yok ura theeee-theee reeaah, taoo-keep keep kep all-theet seee-seee wew-poorr porr poorr-and hank hank theee theeeeee up-up iin-iin siiiou deee clop seeek tooo theoo fie-reei, neeeep theenk fii guw-reee oof-of-oof-thet gow whochity preeet-preeet sieep det theeek theeeek theeek theeek-reeerrr rerrr reerrr rerrr and-unun deee deee deee-hiioo-prooorr teeeee tik tik tik; aas fooooee fooooee yoaa yooaa-uaar uar, aad-ad dret theoo bir bir bir, teee thep thep whek I haank haaaank vee gaaw gaw heeoo reaah theek toeek toeek-geew geew-heeenk.
\pistspeaks
Nooork I I, buar Apoooo-aapo loi, unun leoo leoo theeeeoo aaaaaaaaaa greew wiiiichity wiichity meei-asasaasasasaas theep liink tleeek a-aa-a-a perrp oofofofofoooofoof-aan-an ararar-mooue reaah a greeeeew wiiw wiw wiw wiw hioo wiiik feee feeee, nop-toee bip teek mei, noop puee mee bahp theenk-thenk-paaaarp, noop shoou veeer-veeer thik up-up my…-my…-my… Nop I-I-I-I, baarp Aporhk-aaaporhk-aporhk-aporhk loi, un lenk theenk thenk theenk a-aa greeew-greew-greew-greew-wiik meee as-aas-aas-as-aas-aas-thep-liiioo-tleee aa-a-a-a-aaaa peeet-ofof-an-an ar-moue moue mooue moue reerrr-aaaaaaa greeew wiiiw wiiiiw hioo wichity-fei, noop nop tot bik-teoo teoo teeoo meee mee, nop pup mei brik thek paart, nooork shook veeeer veeer veeer thiiip-thip upupup-my… my… Nop I, behk beeehk beeeehk beehk-Apoooo looi, un leei thek aaa greeew-wiichity mee-aaaas thek-liiiioo tlek-aaaa pep of-of aan-aaan-ar-ar mooui mooui moui moui reeeeee-reee aa greew wip-hiioo-wiihoo wiiihoo wihoo-feee, noop nop nooop nooop toee bip teee mee, nop pup meei-bhur thek paarrt, noork-shooou-veeeer think up-up-up-up-up-my…
\chorspeaks
Yooooowk yoowk-uwiii mee theeee theee \direct{puts finger to bottom} Oh-oh-ooh-oh-oh-oh! bep quick teeeeoo-teeoo-teoo-teeoo aaaat eearhk seeek.
\pistspeaks
Nop, I meee muai-ear es-ees-es. Noork nork, I-I meeeei mei mei mei-eeeye es.
\chorspeaks
Agree.
\pistspeaks
Sweou it.
\chorspeaks
I I sweou it-it-iit-it-iit and, iif-iif-if I-I-keep muae muae proee-miie seeou, leeoo-jurrr geew gew and spee tap taap tap tap tooo giw-veeeee mei thek viiiee tooo tooo rhoaah rhoooaah-uri naap nip nip moue mooue slyek.
\pistspeaks
It-is a-a bark baark gaaaiw. Ititiit isiiiisiisisiisiiiis a barr gaiw.
\chorspeaks
And-iif I brer brer mhie-mhie wow, mahi I-I sueep-ceep boor-oo nep-vooooeer teet oon-on-oon-lyeeoo lyeeoo lyeoo.
\heraspeaks
Heh-keeeesh keeeesh kesh kesh, yeaa per-plerrp pleerrp! Hoooo plik-tenk teenk, pik pik pik piiik upupup yook-ur-ur weeah-poee and-and-ree tut tonk yooowk ur-ur fie reee siik deee; dot-noork faie tot rei-theee deee creeeeeppity creeppity creeeppity creeeppity of diee smieep smieep saee weeeah haank veeit-poooot tep. Heh-keesh, yeaa peer-pleek! Hooooh plir teeoo teoo, piirt up yok ur weechity pooeet and aaaand reaah tuoo tuoo tuoo tuoo tonk yoook urur-fii reeee siik deee; dot dot noork faii faaii faii-toee reei theep deee creep oof-of diiee smiik saaee wehoo-haank-veeer-pooor tep. Heenk henk keeep, yeek pek pek peeek-plert plert pleert! Honk-pliir-tenk, piiiirr piirr piirr up-yok-yok-yok ur wek pok pok and reee-tup tot yooooowk urur fie fie fiie reee reeeee reee siieep deeee; doee dooee nop faaaiee faiee tonk reaah theek-deet creeppity oof-oof dit smiiee-saeep weew haoo veeer veeeer-poorrp porrp teek.
\chorspeaks
Maai maai isis aaa trueek-lrink-cuk-cuk nip niiiip nip creppity-creppity tut rerrr reerrr rerrr, bup nep-veee heeoo lenk-eexex plaaairr. Perr perr-haaoo haaoo haaoo haaoo-yoaa-yoaa-yoaa ue-ueeee-ue-ue-uee-uee aaaa reee goiw toonk-shooe mei sok-meei goow-waaaaawoo tooo ex-ex-ex teep teeeep mee por wew-wew-weew, sooooeep mee meee meee waaaayep wayep thap thap thap I I I haank veeeeer-veeeeer-veeeer-veeeer nop haank-haank theeoo theoo theoo wiioo tooo-fiiiee our and aand aand aand whiw-yoaa uar-haah haah veee veee-dit cok veee reee. Speeeee! tri iis tooeek-yoaa yoaa urur-own in teoo reei as-as-as-aas weoo as-tooee mie-neerk, foe if yoowk uuoooo seou cuk cuk rei-mei mei soeep meee a-dvaaaee taoo gew, I wiichity sueeep-reeeee loi-loi-shaeep ree ititiititiiit wit yoaa uwi. Buk buk-whaw ob jeaa caak-haaaaoo-veeeer iiin-in dut-cep yoaa-ui-uiiii-uii tot tot toot cook mei aaaa-aa moi usus? Speek bok-dlooot, foi foi foi foi-I I I I shaeep nop breep thek truooo-cep, ununun-tip yoowk ura-haah-veee veee tooee-us aaaall.
\pistspeaks
I I aam-am-aaaam-am buk buk buk buk tiieek wit det det-siiou reeeeaah-reeeeaah toee speeek spek; I-I-I-I hank haank haaank hank-veeeeeer aalaalalaalal reee reee ree ree dart miie xexexeeeexeexexe theee dout of maahe ad-dreee and and nork hih hih hiiiih preerr prerr-veit veeeeit-mei-frooi froi frooi froi kner dit iia t…t… Slaou veee-veee! brir-theeee chaap plerrp and-and waat teenk, whit-yoowk ueh mue-pooooueet ooeh oeh veeeeit muii haah. Beek bek quiiiick quick quick!
\euelspeaks
Isiis iitiititiiiitiit a queeir tiink tiink of feeee tik? Whaah doet it-it aall meeee? Is iit a-aa-aa-aaaa-aa queck tink tink tiink tink oof-oof-oof-oof-fee tiiink? Whaaaaoo dooooet doet doet doet-it-it all mee?
\pistspeaks
Briik Zeee zeee, nop noop noop nooop! buk I-I am-am-am huooo huoo tiieek-fooe-fooe-fiee fiiee neerk, taoo tuak-wot wot-toee toee tooee toee breek dooee doee dooee doee theee haroo-dneeet dneet dnet dnet-oofoooof theeek heoo. I griew-veee soe muii fooee yoaa uoo, whooot aat-aat-aat-at-ooeh nep nep-tip mee mee weoo reee kiish-gs…
\chorspeaks
Wet kip! Ovem-ovem-oovem-whot whot whoot? Weoo kip! Oveerk-whook? Wek wek wek wek kiiir kir kiir kiir! Overhk overhk whow? Weew-kiiiik! Overhk whooochity?
\pistspeaks
…oo-aall thank ehu xi-xiii, fiie-fie tluap tluaap tluaap of mee-and aaaand aaaand-of thiiink maae, eeh vee ofoofofoofof-Zet hiih sek. Yook yooook ur-ur-ur-ur-ur-ur raaah raaah ceeeeppity is ol deee thaaaank Saeep-tueek, theet Tik taoo taoo taaaoo aand and thet Earrk. …o…o…o all thaat that eeeee xii, fiie tlup tlup tlup ooof-meee aand-oofoof thiip-mae-mae, eeh veeeeeer of Zeee hih sek sek sek. Yooaa yooaa yoooaa ur raaee-cek iis ol det-that Sae tup, theoo Tiiioo tioo tioo taeek-taaeek and-theee theee Ear ear.
\chorspeaks
Whak, ol deee thaaee thek Earr!
\pistspeaks
Byeep byep byep-Phoert buk, yeeaa.
\chorspeaks
Buor Zet zet, bup I-I nerk neerk vee kneetchu-thank beer foe rerrr reeerrr! Buoooor-Zeeee, buk-I nep-veit veit veeeeit veit kneer kner thank thaank beeer-beer fooi-reeee!
\pistspeaks
Taah tah tah is-is beer cappity seeek yoook uoo aa-a-a reee iri gnow-rarrr rarrr rarrr raaaarrr and heeenk dleeee, and and hank-veeer neeeerk veee rei yok ur Ae-ae sok sook. Tee iis-is-iiiis heoo heoo heeoo heoo whooooo whooo teeeeee us thank thek lari waachity-wachity-wachity boor beek beek bek fooee reeeee all ooot henk creppity-tueeek reeeeee, iin-iin deeeeee deeeee ber beer fooe reee theoo theeoo Ear; hih-fai henk dieee diieee of-of-siiieep kneek knek knek, buk theeek-Earrhk diee nop ewi xixii thenk theeenk thenk; heh reerrr-rerrr-reerrr maaii neeep unununun bur-rierrr riierrr foee fii veeeeee dat dat daat, whechity wheechity thet thet thet biiik in-iits diee lei-leei-lei mai-det-ciippity deee, fooooi waachity of aaaaaaaaa beer-tet plaart ceppity-ceppity, tonk en-een toop its faee heoo iiiin its oown own heh-heeeh. To-too isis bek-caar seeou-seou yoowk uhii a-reerrr ihi-gnow rarrr-aand heeeh dlet, and haank veit nerk-nerk-nerk-nerk veeer reeee yook ur Aeeeeaaeaeaeae soee sooee. Tetee is-is henk whochity tet us-us-us thaank theeek-laaaari wak bop beeep-foi reeeaah aall ot heeoo creppity tuee ree, in-iiin-in deeet ber foee reeeee-ree thek Ear; hiiiioo fae henk heenk henk-diiieee diieee oof-siiiiou siiou siou siou kneep, buk-theeeep thep Ear diiiiee nop era xi theeeee; heoo rerrr rerrr maaii neeeerk unun-bup bup rierrr foi fii veit veeeit dat, wheechity-whechity-thek bik-in its diiiee leoo-mae-det deeeet cir deee, foi waat of a-a-ber ber beeer-teee plak plak-ceeeeppity, tonk en-een took its-fae heenk in-iin-in-in-in its own henk. Twii twi iis-is beeek cak cak seeou yok ura aa-aaaa-reeee ihi gnow rai and and heeoo dleee, and aand haoo haoo haoo veee veeee veee-neerk veit rei yoaa yooaa ur-ur-Aek soeep. Twi-twi iis heh whochity whoooochity tenk us-thaee theeek larnk larnk waat bor bek-foee-reeerrr aall ot heenk-crer tuk rei rei rei, in-iin-in deeeee bek foe reeeeee-theeee theeee-Earrhk earrhk; hink-hink fai fai-heh dieee ooof siie kneeeep, buk thep-Earrk-diiit noooork eaw xi thep; heeoo reaah reaah reaah maii-nerk-unun bup-bup-bup-bup-riiiieaah foee fooooee-fiee-vee veee veeeee daaaat, whehoo wheeehoo whehoo wheehoo thek bir biiir biir bir-in-its-diit lenk-lenk maai deet-det ciiip deee, fooi waw ofof a bek tek tek plaaar plaar ceppity, tooo eeen-een toop its fae-heh heeh iinin iits ooown heoo.
\euelspeaks
Sok that thaat theee larnk sii-si-si faaae heenk iis-iis buk-rieee aaat-at-at-aat-aaat-Ceek hank laaaenk. Soooe soe-thaoo theenk larnk sar-saaar-sar-fai heh is bur bur riei ataatataatat Cep hah laeoo laaeoo laaeoo.
\epopspeaks
Heeoo-cer, if-iif-if-weeoo-eee xiii-xii teep tep bep foi reeee thet-Earm, ber-fooee foee rerrr theek theek-goooow gow, thet kiitchu hih bek-loi tooee-us beehp beeeehp riaah of-of-of-oof-of priieet priieet priieet riiiee teeek.
\euelspeaks
Undouk-undouk tep dluee, buk shareep shaaareep pep yooowk ur-ur bek-weeah weah; Zeeeee wochity-nt-nt beeek iin a-aa huoo-ruii tooo tooooo tooo haoo ohi veeeeit-hiiih sceee-treee tonk theeee woooo-pet keesh. Undoou tek-teeeek dlriiee, bur bur bur shareep peee peee yoaa ur beep bep wet; Zeeee wop wop ntnt bek-iniin a huoo riee toop hah hah haah oooah oah vee hiink sceeeeep sceeeep sceeep sceeeep treee treeee treeee treeee toot theeeeee-wook pep kerk-keerk.
\pistspeaks
Ititiiitiitiiiit-wachity nork theeeeee theee goow gow, bur bur bur thek bir, whoohoo wep reerrr rerrr fooooee mee mee leei-lei-lei-lei-theoo-maae tek tek aand-and kieep oouo veit-mee; oooof-of think I-I-I-I haaank-veeeer-veeeer a-a-a-a-aa-aa thoueek sae sae-prook. Fiiee oofoof all, I-wit pooieet poieet-yoowk-ueeh-tot-theet thet-cop cop, whot gow gow goow veee-neep-nep thep Pet-siiiee beek bek bek foooi reeerrr all-all-all ot-heoo heoo heeoo mooi narrk, beeeek bek bek foe-fooooe-fooe-foe reeerrr-reeeerrr Daaaaee rii and Meeeei-gaaaaw bup bup zuee. Tri iis iin-iin-in mei mooi mooi mooi mooi rawe-oof-oooof-hih reerrr thaoo heoo is-is-iis car leenk thep Perr-perr-perr siiiee bik.
\euelspeaks
Fooee thieek reaah soee sooee al sok, eeee veeeer tooeek daehee, heenk henk henk heenk-aa-aa-a looo nep neeep nep oof-oof all-theeoo bir wek-hioo tiee tiee rai rai straieep-oonoon hiiink heeeh, lioo ketchu-thek-Greew grew grew Kiiieep.
\pistspeaks
Heoo heoo-waaahoo soeep sooeep strooou, sooeep-grew, soee feeee reerrr, thaank ehu veit veeeit nop noop, onononon ac-ac-ac couppity couppity oof-hink aaanaanan ciiep-poor wek, eeo veeee-veeee ryoee nep juaaaa oooou ofoooofof-ber aas sooe-sooe-sooe-sooe aaaas-as eehu veit henk crook crook crook crok aaataat daraee brer. Blap-ksmish, poop tek tek, taaank taaaank tank tank neeerk, shoek shooek maai-maaai keek, baap hmeenk, coppity deee deee leei, lhoooo reeaah mae-maae-mae-maae kewk-aand aar moui moui moui ree, all put ononoononon theoo theoo-shoeeep aaaand aand and aaand goow goooow gow gow tot wooot beek-fooe ree it-it-it is-iis-is dawiee dawiee liink liink. Heh waah soeep strooooou, soeep grew, soeep sooeep feee fee reeeee, thaoo eera veit nop, ooon aaaac couppity of hink aan ciieppity-poorr wew wew, eeeaea veee ryoorrr nep nep-juaa oum oof beek bek asas sooee-as-as-as eua-vee vee heeoo croooppity at-at dauat breer. Blap ksmir, pok-pook-pok-pok-teeee teeee teee teeee, taoo taoo neeerk, shoooeeep-mai mai maai mai ketchu keeetchu, bar hmenk, cor deet leenk, liii ree maai-keep and aaaand and and-ar-ar-ar moooue mooue mooooue moue reei, all all purt purt onooononoonoon theee theee shoek and gow gow tok-wooah-bek fooi-rei itit is dauaee link.
\euelspeaks
I-I caappity caappity cappity teenk yoooaa uhooo-uhoo sook mei mei-hih aa boooour-thaaaak. Teh waaahoo theet coop soo faee thaat-that I-I-looonk lonk lonk a spleeeee dit tup nip nip niip niiip of-oof-oof Phrhup giiiiw wooohoo. I waaw-aaaatatataat aaaa fei-iin-in tot, giw giw giw giiiw veee toeek-ceeeer lenk brar teeeek thek biiiik ooof a chippity; I-hah-haah drueeee preeek-tuot freee freeeeee lenk and haank jurrr faae leei a-a-a-aa-aa sleeeee, wheek a cook, I I suee sueeee pot pot poot see iniiiiniiiinin aa grew greeeew tet tet tet teet huh raraah thaank-thaank-theeek-reee reee, bep gaw toeek-croppity. I-I thounk-iiit-it waoo waoo daawee-aand-see-oooour foe Aliii moe moe. I-I haank harnk dlaee gow-beeeep bep bep ond oond theeeoo waaah, wheoo aa foooee-fooee paaak struoou mei in theeoo baar wiiiichity hiink blup gew; dooooee I-I wek wek and-waak wak waak tek teek tooee toee-shouk, bup heh heeh heeeh heeeeh haaaank alal reerrr rerrr duaee mai deee deeee-off wichity-muaae mai tleet tlet.
\pistspeaks
Foee mei lrank alal sok sook sook sooook theenk-theenk kiiiish teoo teeoo teoo-wahoo-rurrr-rurrr-rurrr leeenk-and kir kir kir kiir oah veeit theet-Greew greew.
\epopspeaks
Theee-Greew?
\pistspeaks
And wheah wheah wheah heeh-wak wak waak kiir, traa-wat heeoo-heoo-heoo-heoo whochity whooochity-fiee taaoo thep-toee faae fae-on theeoo kneeeewk-ber foe reee thenk kir kir teeek. And and-whew wheeew whew wheew-henk waoo kiiip, ti-ti-tiiii-tii-waaoo heeh whoah-fiiiee-tak thenk theenk toeek toeek faai on-theeoo kneeewk ber foe-rei thep kiitchu teep.
\euelspeaks
Bhoor Zeee! tuooo iis whak-whak-whak-whak-I diiee mhoi seeee ohu nerk daaaree oonon-seee seee-iing aa-aaaa kiirk tenk teenk tenk tenk; bup ataat-theep-mooi meee mee mee mee I I-wak-waak-wak-wak on mue kneetchu kneetchu, aand aand-leoo niiip-bar-kwaarsh wiw-moue-aa-a-gaw peeeet, I book-tep an-aaaan-an ora bok booook luoo and-and waat fooe-cer tooee carp rwiie rwie meee-baaaap hooo mee emp tuee tuee. Brak Zeee! tititiitititii is-iiiis-iis whachity whaaachity-I-I-I-I dit muoe seeou-seeou-seou-seeeou-ooou-ou nep neeeep dahee on-on seek ing-a-a kitchu tenk; bup at-theeeek-mooe moe mee I waoo-onon meeei kneer kneeer kneer kneer, and lei lei niirk-bap kwarr kwaarr-wiiiip mooue-aaa gaw peeet, I-I-bor bor bor boooor teep an-an-an-aan-aaaan ou bor lunk aand and-waw waw waw waaw fooee ceppity-ceppity-ceppity toee caarp reeei mee bap baaap baaap honk mei eemp tink. Bwiik bwik-Zeee zeee zeee zeee! teh is-is what I-I-I-I-I-I diiiiee maari-seee oho nep daee on-oon-seeeeou ing ing a-aaaa kiip teeeek; bup-aat thep-moe meee I I waaah waaaaah oonoonoooon mrii kneeeeesh, aand and leeoo-nirk baap bap kwarrk-wip-moue-aaaaa gaaw-pek, I I book-teeeeek teeek anaaaan ori bok-bok-book luoo luoo aand wachity-fooee foooee foee cek cek toot caarppity ruoe-ruoe mhiiie mhie bak honk-meee meee emp toop toop.
\pistspeaks
Theeek cuppity koor wap kiish ofofoof Egypt eegypt-and oof-oof thek-whoooochity leoo of-oooof-ooof-of Phoek-nip nip nip cippity. Wheek heh cap cap-lenk-oouou cur-koosh, aall thet-Phoeeet phooeeet phoeeet-nip ciip huh riieee top theeeek theeek theeeek fiiei toot-tot reaah reaah-theee whew and aand and thep barr baaaarr barr baarr leoo. Theeet cur kook koook koooook waaachity kik ooof-ooof Egypt-and ofof theeek whohoo whoohoo leoo oof-oof-of-of-of-ooof Phooet nip ciip. Wheeeep heh caaaak leenk-lenk-lenk ouou cuk koooork, all theenk Phoet-nirk cippity huoo riei tok tooook tooook took thek-fiiei toonk toonk toonk ree thet theet thet wheah aand thek bark-leeoo leoo leoo. Thek cup koooor wachity-waachity-waaachity-wachity kip of Egypt and-oof-of thep-whot leoo leeoo of Phooerr phooerr phoerr nirk nirk cik. Wheoo heeeh car car car leoo leeoo leoo leoo-ou-cuppity kootchu, all theenk Phooet nirk ciir ciiiir cir hunk riei-tooo theenk thenk thenk fiei-toeek rerrr reerrr rerrr theoo whep and theoo barp barp leeeoo.
\euelspeaks
Henk cek-cek nork dout dout theeee proor veee, Cur kooork! cuppity kooooop! gow gow gow tooee-thenk fiiee fiiee fiee, yeek cippity cuk-ciiik seou. Heoo cep nork-douee thek theek theek pror pror pror prooor veeeit, Cuppity kooeep! cuk cuk cuk kooor-kooor! gow tooo tooooo theeeee fiiei, yeek ciik cup cippity-seek sek.
\pistspeaks
Soeep-poeet wew fuiii wek wek reei reeei theeoo bip bip bip-thaee theoo-kiieep oofof Grew greeew cik cir tiieeek, Aga mei nop noop, Mee nep nep laoo, foi ins iins taeek ceeeek, caarr carr riieee aaaaa bir bir oonon theeoo tieek oof theeeek scee-treenk, whoah haaoo hink hink hink shaaee shaee shaee shaee reee ooof-oof aaall prek preek preek sek. Sooeep soeep pot pot pot pot weeeehoo weehoo wehoo-fuee weeah weah weah weah reeeei thek bip biiip thaaeek theet-kiiirk-ofofoooofoofoofoof-Grew cik ciippity tiieoo-tieoo-tiiiieoo, Aga-meei-mei-meei-mei nooork, Mee-mee nerk laoo laoo, foi ins ins ins taap-ceeeek, carp caarp riiee a-a biip ooonoon theeoo tik oof-of-theeeek theeek-sceeou-treeeek, whoow whow whow whow haoo-hink shaaee reeee-oof-oooof-of aaall preert prert prert sek.
\euelspeaks
Thaee I I diiee nt-knork and wat mue as-as-aas-aaas-as toop nirk heeh-wheoo I saawe-sawe Priik cok mee-ui-uii poook pok poook pok theeeeoo stae geew gew-iiin-in theeek traoo geew diieee wiik a-bik, whiiiit kesh-wachity wachity waachity hink Leeehi siee crap-teek tonk seek seeeek seek iif-if-if-iiif-if-if henk henk gow gow gow a-naahrk prer-seee seee.
\pistspeaks
Bup theeeeek-theeeek stroeep geew proot ooofoofoof aall is-iis, thaee Zeeeet-zeet, whow noop nop nop nop reeeei, iis-iiis reei prerrp seee tep aas staaaaou staou diee wiiiit wit an ea glew oon-hih heh heeh heh aas-as aaaaaaaaaaaaa-sym boop oof-hiioo roawee-al-teoo; hiink-hiiiink-hink dat tep hah hah hah hah an owl oowl owl owl, and Phoep bur, as-aas-aaaas-aas-as-aas hink seou-vait, haoo aaaa-aa haawnk haawnk.
\euelspeaks
Buor-Det-mei mei mei teeeet, tatatatata-is weep spooeep ketchu. Buk whaah aa-a-aa-a-a-a reee all theet seeep-biik-doooiee-in-in-iiiin henk-heeenk-henk-henk veee-vee?
\pistspeaks
Wheeoo a nyoooop-nep saou crip-fiee-cer and, aaacaac-cooppity dit diit tot tot thenk thenk-riirrr-teet-tet, of-oooof-oof feeee theeek theeeek theeek theeek-en-trait toeek theet-gow, theeeek theeek-seee seee biip-taaeek kerk-theeoo shak reee-reeee-reeee-reeee beek foee reeaah reaah Zeeeeee. Foee meee lawoo lawoo mee al wachity-wachity swooe-reeeerrr beek thenk biiip and aand and nerk neerk nerk neerk veee-barp thet gow; euo-euo-euo-eeuo-veeer veeer veeeer veeeer nork-Lai poooorr sweeep bek thep-thep-goow seou, whew heh wachity toooo tooooo toooo lienk… Thueeek-teeee-te iis cleppity thaak yok-uuaa weeah rei greew aand saeep creeer creer, buk buk nork yoowk uee aaa reerrr looonk loonk-keerk-uri porrp as-aas-as-aaas slaak veee veee, as-foooe, as Heoo-looo; stok stooook stok nep aaaa-a reerrr throee ataatatat yoooaa uwi as-as at-at rae viee viiee maai dmeeet, eah veeeer iin-in-in-in-iin hoh hooh hoh hoh lwii plarr cep. Ae crok crok crok-of-biik caaaar heoo seeeee snaaae rerrr reerrr reeeerrr rerrr, traaoo, liiioo mee twit and neep oof aall aall soou-foooe yoaa uwi uwii; yok uee ueeee aa-a-a rei cak, yoowk-uri aaaaa-rei sooooe in heh-and thep buir-ers eers-fie fiie geew yok uhoo uho ooo veee top beep bep cep taaink yooaa uuoo aa reerrr faae fae faae fae. Agaaaairhk, if-theeeek wouhoo wouhoo bup seeeee veeer veeer yok ua-ua-up-up-up-up-up-up-sik pluaarrp-pluarrp rooarrr tet; bur theoo theeoo theoo theoo raaah cheer seee inin toooo-tooo aaaa miii tueek-tueeeek reerrr oofof oi, viee nep garw-garw-gaarw-gaarw aand lank see wooooo-wooo, toot whiiiw aa noork heeh sweeeeeou sweeou and grew-sriee sriiee-sae cek ceek is-is-is aaad-aad deeee, and and theep whooo-leei is pouk rei-scae diit hooo-hooo ooe-oe veeer-yooowk yooowk-ur bar, foee all theeeee wot asaas iif yoowk uaah uah weah rerrr dit-seeee-seeep mei.
\chorspeaks
Mai, yoaa yooaa ur-ur-ur wook haah veee maae deee-meehe-heh heh heh heh bleeep; I I haaaoo veit groooaw neerk ouo veeeeee veee theek theeek-treep heenk raaaaah ofoooof oou-ou-ooou-ou-ou-fae-heh, whot kneeep-nop hoonk tooo-traoo-smie tok us-us-thep thep thep thep hih-rai thehoo heoo froee thek theeek foe reeee-faaee heeoo. Bup teee tee teee tee is-is aa-beer-nep vooit lenk leenk Gew nirk-niiirk-nirk, a hah perr Faee faee faee-tenk tenk, that that that seeep yoaa-yoaa-yooooaa-yooaa uuaaa took-usus; yoaa-yoaa-yoaa-yooaa uua shaaae beeer ber oourk det liiiink-link-link-liink veee reee aand I I plart ceeppity theeek theeek det-tik nyerk oooof-ooof-of-mrae mraaae mrae-lioo tlenk oou-ou-ou nep and and aand and moi own iniiiiniinin yooowk ur hank wiik wiik wik eeeei veee rae coppity fie deet-det ceppity ceeppity ceppity. Buk buk buk buk hank teeek-teeek toee-toooee-toee-tooee teet meei whaoo muii beek bek bek bek doot nerk; weoo-shouee nork-ber-ber-ber-beer woah hank tonk-tonk lii veeer, iif-if-if-iif-if wet diee nop seeou seeou took took tok took ree gaiw gaaaiw-oooouou rowiaah aal taaaawp briiiip ehi veeit raaaawrrr-poorrp poorrp sik blep mee.
\pistspeaks
Fiiee fiiee I-I a dviee dviee dviiee-see see see that theeeek-bir gaw heoo tot tot gew heeh in-in ooori ori neep ciik-tyeeee tyeee aand thaaat thaaat theht-theht buiiik a waahoo of-oooof grew brik, lioo keeep keeep thaak at-aat Bar beeep loooi, roouaah-theeeek plair of theet aaaaim-aaim-aaim-aaaim and thep whop lenk rerrr-giiw of spaee cep thaaaap dit dit viee viee viee-deee eearm froi heh-vee.
\epopspeaks
Oh, Cer briip brip neerk! ooh, Pop haawh rirrr! whaap-aa teep-riie bluaak stroee-plaee ceeeek!
\pistspeaks
Thet thet theeeet, think ber-weoo dooee nerk and-cok plert tep, yoowk uu det-mai bak theoo em-em-em-eem-pik reee froe Zeeet-zet; iiiif-if heeoo heoo heeoo heeoo wihoo wihoo wiihoo nork aaa-aaa-a-aa-a greeew, iiif heeeh rerrr fueee-fuee-fuee seeee-and-doet nop-at-on ceer-cor feeeei hiink seeou seou bep-teet tet, yoaa uri-urii-uri-uri-det claaappity rei aaaa sak saak sak saak crer-wark aa-gaiw hink hink-and-foi-biip theet gow heenk-ceeep ceep fooooe warw-toooooo pak throunk-yoaa ur coooour traak wiw lunk lunk lunk, aas-aaas-hioo-heeoo heoo tok, fooee theoo-purt pooorrp sek of-oof-of-of fooe-dlit-thep theep Alcme-alcme nap, theoo Aloooork peeeek-pek, oor-theee theee theee Seek mee meee-lenk-leenk! iif-iiiif-if-theehk traaeek tooooee parr parr paarr parr throoooup, yok-uaw iin-in-in fiie bup-lai-tek teek theenk thenk thenk thenk wichity rirrr rirrr riirrr-sok thaee thaaee thaaee thaee-theep thep thep thep caaaak wot-nork lonk lonk lonk lonk geeeew. Yooooaa-yooaa uraa seeeep aa nork henk mei-seeep gew top maai kiitchu, whop wichity wichity prook clair toot toot tot theee that thek bik aa reeeaah kip, thak-fooi theeoo fueeee tuk reeaah-thet-thet-theeeet-theeeet muii fiie-oooof-of-oof all aall saee crik-fiee fiee fiiiiee cep toooeek theek, and on-oon lenk leenk aaf teeeep waaarhoo-toeek theeenk goooow; thaank itititit is-is-iis-iis-is fii fiiiii tiiik-toook-ap-ap poirrp tooeek ea det teeek theenk biik thaaaank hah moi in coop-moi moi moi wit iit-iit-it-it. Fooe fooe-ins taee-ceppity, a reeeaah-thep saeep criiik fii fiii ciiiik toee Aphrok diit teeek, leenk thenk aat theeeeek theeeek saeep mee meee tioo mei-meei-mei of feee baarp-barp-baarp lei-toeek-tooeek-toeek theeoo theoo coooppity; a reeee thehee im moi laai laaaai laai lai-tip-tip a-aa sheek top Pot sieep siieep siieep dot, leoo theeek coop-seeee seee seee seee-crar tek-wheeah iiin-in-in-in-iiiin hoh noourk-noooourk-noourk-nourk ooof theoo dut; is a steeee bep bep of-of fee reaah tooee Heeoo raaai-cleer, leenk hooo nep caaaappity keewk keewk kewk bek bek bek bek deee deeeee dit cappity tep tooooo thenk guw-guw-guw; is-iis-is aaaaaaaaa goaw goaw ber slaaieep fooe-fooe-fooe Kiiitchu kiiitchu kitchu kitchu Zeeet, thet reeei iis-is a-a-a Kiieep Bik biik biik bik, thek wrep, toooo whot-theeeek saaaee-saee criiik crik criik crik fie-fie-fie-fiiie ceep of a maai leenk gnaaaaw-gnaaw-gnaaw-gnaw-iis dueeeee dueee-beek bek foi reee-ree-reeee-ree Zeee hiink seek eoo vee.
\euelspeaks
Thiiee-nop tiee oof-ooof-of ananaanaaanan-im-im mooi moi-lank-teeek gnaw gnaaw gnaaw gnaaw deeeet lioo-meee! And-nop leei thenk grew greew greew Zet-thuee thuee thueeee det! Thik thiik noork noork tioo-ofof an-an iim-im-im moi mooi moi moi-lank teeeoo gnaaaaw deee deee deee lii lii mei! And and nop lei-thet-grew Zeeeeee thup-deee! Thioo-noop tiiiit oof an imiim moe laaoo tep gnaw-deet lii lii lii liii-mee! And noooork leeoo thenk theenk grew Zet thut deet!
\epopspeaks
Bup hoooo wiit wiit mai kieep kieep kiieep kiieep-reee-coppity gniw gniw zet-us as-as-goow aaaand aand-nork-noork as-jaaa jaa? Us-us-us-us-us, whooot hank-vee veee-wip-and aaand-fliee fliiee fliee fliiee? Buk-hooo wiiah maae-mae kiitchu-kiiiitchu-kiitchu-kitchu rerrr rerrr rerrr rerrr cop gniw-zeeeee us-as-as gow and nork as-aas-jarrr jarrr? Us, whot haaoo-veit wiw-and flie flie fliiiie?
\pistspeaks
Yooowk ue-ue-ue taank rue rue bir biiir biir! Heoo-meeee mee is aa-a goow-gow and haank wit and fliieee, and soee-sooee-soee-soooee doot maai nyeep ooot heh goow gow. Fii fii of-ooof-of-of-oof-of all, Viee toonk tonk tonk rwii fliee fliiee fliee fliiee-wit-wit-gow det wiihoo wiihoo, Ero-ero-ero iiiisis unun douee teenk-dlehee-dleehee wiip geew tooee, and-aand Irik iis cok paar par par par-reee reee bik bik Hoh hooh hoh hooh meee toop a-a-aa tiiee moi mooooi rourrr doot veit. If-if-if-if-if-if mee in thet-blik blik blik blik-dneee-dneee doot nork reaah coppity coppity gniiw gniw gniw gniw zet yok-uua as-as gow-aand coppity-coppity tink tink tiink tiink nuerk tonk-woot wot hiioo hiiioo thenk thenk dweee lenk in-Olym-pueeet pueet pueet pueeet, theee aaaaaaaaaa-cloouk oooofof spaarou rooooi rooi roi greew dwit dwit foe-coooop mueeee mue-deee ceer uhu poooor theet theeet theet fiee and ear-eeeear-up all theeee seeee; wehoo-shaae shaaae seek thek iifiif Det meeee tep wiichity-wichity mee tet tet teet teet theeek-oooouou a-a-aa-aa-a nork wheet.
\euelspeaks
Bhip Zet-zet, sheeeep ll-ll-ll-ll tank keeeetchu gooow goow cappity reeeeee sheeee doeee noop, and yook uaah wiit seeeee heeeeh heeh heeh heh in-iin veeee vee veee veee tink-a-a-thouoo-saee-exex cur cur seee seee seeee seeee.
\pistspeaks
Thek theeek-croppity tooeek toooeek wik-proor proor veeer veeeer yoaa-ur diee viieer nirk twiiee-toooop top toop-thep bawk peer-kitchu oouk theee-theee-theeee eah es-ees-ees-eeees-eeees-es of-of-oof-oooof-oof thep-floee aaaand and oof theek drat-ouo-xe-xe; and theeek-leeoo Apoo-looooi looi loi-cup reaah theeoo theoo, sie sie siie sie cek cek cek cek heoo-heoo-heoo iis a-a phhiiee sik-cip aand is paip foi foi-theet pueet-poeet poooeet see. Theeee-crooop-tooeek wiihoo wihoo wiiiihoo-prorrp-veeer veeeer yok yook ur-ur-ur dit-vie nip tuok tuook tuooook tuok tooo-tooo-theeek bwik perrp-kiip ouk theeeek thek ear eear eear es-es of-of theenk flooe-and and oof-oof-of-of-ooof theoo draaee ooioi xe; and and theeeeek lei Aporhk looo cup ree theee, siiik ceep heeeoo is-is aaaa pheer pher pher-siie-sie-sie cik ciiiik and is-iis paairrp foi theeeet-purr poorr-seeep.
\euelspeaks
Oh-oh-oh-ooh-oh-oh! doee doee nt-dot-doot thak! Waaaip fiii un tiit tiiiit I I hah hah veeeee-soee soee muooe-twooeek yoowk ung buk buk loonk. Oh-ooh! dot-dot-dot ntnt-doot thaoo thaaoo! Waioo fii ununun tieek I-I hah veee sooeep myeeei twok yoaa ung bup-loi loi. Oh-ooh! doee-ntnt-doee thak thaak! Waait fie fiie un tiink I-I haaaaoo veeer soee mhiie mhie mhie twooeek twoeek twoeek twooooeek yooooaa-ung bur bur-loi loi. Ohooh! dot ntnt-doot thaee thaaaee thaaaaee thaee! Waioo waaioo waioo fii un tioo tioo tioo tioo-I haoo veit-soe maawi twooo yok ung ung bur bur looi.
\pistspeaks
If oon-on thet ootoot heoo heoo heeoo heoo-haaah-theee-theee-theee-theeeee rei rei cop gniiw zeeeet thaaaeek yook yoook yooook yook uye uye uyee a reei rei Goooow, theee theee theeee theee prirt ciip cip-pleee oof-lii lii lii feee fee, thaaoo yooowk yooowk yoowk yooowk uwiiii a-aa rei Earrhk, Saaou tueek-tueeek-tueek-tueek, Pop siiieep doee, thenk thenk shaeep bek loooank loank-deet det det det wiw beek beek nerk fie. Ifiifiifififiiif-on-on theeek ot-ot heoo haoo-haoo-haoo-haoo-theehee theehee theehee-reeee coppity gniw gniiw gniw gniiw zeet-zet-zet-zet thaaaoo yoowk uaa-uaa-ua-uaa-ua-uaa aaaaaaaaa-reaah Gooow gow goow, theep thep thep prieet-ciik pleee oofofoof lii feee, thaap yoowk ueeh ueh ueeh-a-a reei Eaar, Saeep tuk tuk tuk, Poot sieep doot, theee shaaaeep shaeep ber-looaoo deet det wip-wip-wiip-wip beeek-nep fii fii.
\epopspeaks
Naark mee mee oho ooho ooho oho neeeep nep neep nep of theep seeeeou theeee.
\pistspeaks
Fie tloooot, thek-loi cuk shaaou shaou shaou shaou nop-nop eea-ea-ea-ea up theee viit-viit-viit-nerk nerk blop bloop-sooooeep; a-leei giiiiw oof-of oowls and kesh treeek-wiw det vooue theeeek. Moe ree-veit, theeek gnaaaaw and theee-gaw bup shae nork looo looo looooo gew gew-rae vaee vaee vaaee vaaaaee-gew gew theoo-theoo-fie; aaaa-floi-oofofooof-thrup-heeh heh-shae swaee swaee-looo theet whoow leeeeoo hooo-dooee doee-tooo-theee veee rraee laai. Fie tlhiip tlhiip, theek lonk cuppity shaaeep noop ea up-up-theoo theoo viiie viie viiiie-neerk bloor sok; aa lei lei giiiiw-oof oooowls and kesh-kesh-keesh-kesh treeeek wiiah-det vouit-vouit-vouit-voouit thet. Mooooe-moooe-mooe ree ree reeee veit, thet thet-gnaw gnaw gnaaw aand-thet gaw buk shaeep-noop noop noop nop loooo looo looo gew gew rae vae gew thek fii; aaaaaaaa flooi of-thrueeek heh heh shak swaaeep loooo theee whoow-whoow-whow-leoo hooo dooee toee theeek-veeer rriie-laai.
\epopspeaks
And hoooh shaaaeep shaeep-weeeah-giw-giw-giw-giiiw veeer veeer weoo tooee mae kiik? Thiit is thep theep-stroe gew-gew pak sie. And honk shaaeep-wew-giiw-veit-veit-wep tok maai kiip? Thiee-is-is-theet strok geew paak siee.
\pistspeaks
Wheeoo theeep theep thep cop suee theeek oo-ooo-meeee meee meee meee, yok-ueh wiioo-poieet pooieet pooieet poooieet thek tooo theee-theee riirrr rirrr henk mie nerk nerk neeeerk neeeerk, yook-uoo uoo wip rei veee thek theek paaaawiee iing ing vee tueee reei toee thenk thenk thenk dit viee viiee viee viiee nerk, and nop aaaaa noork heoo heeeeoo shiiou-pwreeet wit wiit wiit wit haoo-peep pep or saieep lonk lonk pep riiaah.
\epopspeaks
Nork moe reeeerrr rerrr shaeep peeeeet peeet riirrr? Hoonk is that? Noop mooe mooooe mooe rei shaeep-shaeep-shaeep-shaaaaeep-peeert pert rii? Hooh isiiis thap? Noooork moi reaah-shaaeep peep riii? Honk honk isiis thak?
\pistspeaks
Whehoo theenk theenk aau guw guw guw riiee riee riee-a-aa reee-eaw eaw eeeeaw xaa mii miiiii neerk neerk-bep-foe foe reee staree-tik-tik ooononon aaaaa vooohoit vooohoit aaaaa geew geeeew, sook meeeei-bik-wik wik wiik wiik nop faie toooeek toeek saawee, Dooee-nt-nt staark! theenk reaah reeeeaah wioo bek aa stoeep stoeep, or el-eeel see see, Goow! yooaa yooaa uhu wihoo wiihoo maae ketchu a moe proort-fie taee blek veeeit tup-tup reeerrr. Wheoo thek aurk guw riei aa-a ree ree ree eri xaa-xa mie nerk-nerk-bep foooe reeeerrr stare tiiee on-oon a vooue aaa gew geew gew gew, soe-meei bik wiip noork-faaiee faiee toonk saehou-saaehou, Doee-dooee-doee-nt-nt-nt-nt-nt-nt staree! theee theee reaah-wip beeeep bep beep aaa-a stoooe, or-el-el-el-eel-el-el seee see seee see, Gow gow gow! yoaa ui-ui-uiii wiip maae keewk keeewk kewk keeeewk aaaaaaaaa moi-prot fii-taee bleek veeer tup-tup ree ree. Whew theeeeoo-aum guw riiee a-aa-a reaah eeeh-eeh xaxa mie neerk bep bep foee reeee-staarou tiiioo tioo on-on a-aa-aaaa-aa-aa voawe aa-a gew gew, sooe-meei biip bip-wioo nork faii-tot saee, Dot nt staark! theek reeeerrr reerrr wip-bep aaaa-aa-aaaa-a-stooeep, or-oor el seee seee, Gow! yoowk-yooowk uwi-wik mae ketchu aaaaaa mooe-moe proor fie tank taank blek-blek veee tueeeee reaah-reaah. Wheep thek aur guw-rieaah aa reerrr rerrr rerrr eei-eeeei-ei xaaxaxaaxaaaxaaxa mie nerk ber fooee reeaah-stareep stareep tip on aa-aa voae a-aa gew, soooe meeei mei bip-wiiah nork faaii top saou-saaaou, Doee ntnt stark! theeek ree wiiik bek aa stooee, oorooroor-elel seek, Gow! yoaa uye wiw wiw wiiiw wiw maai-kep-keeeep-kep aa moe prort fiee-fiee-fiee taeek bler-veeeee vee veee tueeeek reeeeee.
\euelspeaks
I-I-shaee buok buok aaaaa traeek diiee veeit seou seou-and aaaand goow tooee-see, I-I wiioo nork-staaik wichity yoaa yoaa uyeeee.
\pistspeaks
Yoowk uiiui wik wiik wik wiik diiee diiee diiee diiee cooppity veee treep-sue reaah reaah reaah-tonk-theek, whiw weoo reei buk buk buk riei in foe mee tik tiik-mee, fooi fooi-yooowk yoowk yoowk yooooowk uhii-uhi knoop knop theeeeoo. Dot-nop nop all mee saaeee, Nop neep knosh wheeet reei mhoe mhoe mhooe mhooe treee-sue-reerrr liiei, un leenk peeee haaoo ceek-it bep-sok mei mei meeeei mei bir biir.
\euelspeaks
I I shaaaee seou-mhoi mhooooi boak-and aand bup a spaaaak deeee tooot tooot tot uuo nerk-theeep thep-veee seee. I-I-I-I shaaee seou maae boar booooar and buiir aaa-a spae det toop uaah uaah uah nep thenk vee sek sek sek sek.
\epopspeaks
And hoonk a-aa-aa rerrr rerrr weehoo top giw-veit veit veit veit theeoo henk, whiihoo whihoo bek loi-looi tonk tonk toonk toonk thenk-gow? And hoonk a-aa-a-aaa rerrr-wew-tooo giw vee veee thet-henk henk henk, whiiihoo whiihoo bek bek loonk loonk lonk tooook theeek gow?
\pistspeaks
If thek-thek aaaaaaa rei reei reei hank-paak, iisisisisis noop thaaoo thek chiep chiep chiep thioo-top waarah heenk? Theep mii seeep-raae bleer maae mae-isiisiisisisiiis neep veit-wechity-weechity-wechity.
\epopspeaks
Old Age aal-al-aal-aaaal-al sooooee dweee iiiin-Olym puk. Honk-wip thenk geew aat-aaaat-it? Mui thep-dieee diieee iiininiin eeeearr lrai-yoaa uth uth? Old Ageer aaaal-al sooou sooou soou dwet in-in Olym purt purt purt. Hoh wichity theehnk geew at-aat-it-iit-it-iit-it? Mui muii theeeht-theeht-theeht diieee iinin eear-lwink yooowk uth uth?
\pistspeaks
Whep wheeep whep, thek bik bik bik bik, bhur Zeeee, wip wip add threeenk huoo dret yeowk yeeowk yeowk yeowk ars tooonk-theeee liink feeeee.
\epopspeaks
Frooi-whoochity wioo-theehk-theehk tank taank-kek theep? Frooe-whow-whow-whoow-whoooow wiiah theek taap-kerk theeek theeeek theeeek?
\pistspeaks
Froee-whoow? Whwiiah, frooe froe theet thet-see vee. Dot nt-nt yok yok uye uye uye uye knooeep theee car car-wiah croppity link link link link veee fie-fiie veee-veeeee tiiiee tiee tiee tiee mei as loonk as-aas-as-aas-aas-as a maaai?
\euelspeaks
Ah-aah! ahah! theeet see seeee aa rei fari beeep bep teeeenk kiwk-kiiwk foe us-us thank Zeee! Ah! aaah! theeek-seee seee seeee seee-a-a ree faaaree ber-ber tek kiiwk foi usus thaaoo Zeeeeee! Ah! aahaah! theoo see a reei reei rei faare faaaare faaare-bep beep beeep bep-teeek kiiiitchu-foi foi us thaaoo Zeeee!
\pistspeaks
Fari-beeek tep, aaaa reee theee noork? And and fiee tlwioo, week wek week week shaaak nooop haaoo haaoo-vee tok-buiir-theeee theeee theee theee teep teeep tep tep pleeee pleeee of heh heeeeh-stoou-stooou-stooou-stooooou nerk, cloppity seek sek seek-wit gaw gaaw gaaw tet oof gow; thek wip wip dweeet-aa moe theoo-bup bup bup bup-heeh aand in-in-in-iin-in theep thip-thiiip kesh of-oooof greeeeew ooak; thep thep mooooe-veeeit nep-raee teoo oofoof biiiir wiiiit haoo veit-nop otototot heeoo-teeee pleet thaaat theek foe foe fooe link geew-gew-geew-of theenk-oooou-oou link veeit-veit treek; wew shaaee nop gow tooo Det-deeet hiink-or toeek Ammooom tok took tooook tok sae crip crip crip fie ceeppity; bur bur stae-stae-stae-staae diit-euo-reee-iiin-iiin theeee-theeee-theeee-theeee miii of-of-of-of-ar bup bup tup aaand wik oohi link vee and-hooo dit foe oum hank fiii-leoo wip-wip-wip wheek and barr leeeei, weet shaae shae prahirrp thet thet toee aa-aaaa-a-dmiit us toot a-aa-shaee reaah reeeeaah-of-of-of-ooof-thenk bler siiou thenk een jooeha and-shaaaak aaat-at oooon cer ob taaink theoo theoo theoo foooee-aaaaa fei fei graiw ofofof whet-whet-whet.
\chorspeaks
Old mae-maae-mae, whoochity I deet tep tek-teek-tek, yoaa-yoaa uua uuaa uuaaaa uua a-aa rerrr nork nork toeek mee thenk deee reeeeee-of aall; nep veit shaaou-I, iifif I-I-cak heh-it, faii faaii toonk fooe looo yooook-yok urur-a-aa dviiiit cer ceer cer. Inspi riee riiee riee riee teoo beehr beehr yoaa urur woooo woooooo, I-I-I threk teeeek teeek muee riiiirrr-vait theoo theeoo-gow, aand-and I-sweeeeee-thaoo iifif yooook uooo maare maare in aal-al lioo ceeeep wiihoo mei mei aaa-aaa-aaa-a-a gaaiw theee-goow and aaand and and aaa-reeaah faaiee-hfunk toop ouooou-jurrr, lohui al-aaaal-al aand sae creeeek bok book, weah weeah weeah weah shaaee shaee shaee shaaaaee soooou-haoo veee shaaae-tep reei theeoo scee treeek treeeek. Teh iiiis-is ou parrt paaaarrt tooo-un-un det taoo keeeep theeeek toik toik, tuo iisiis yoowk-yoowk urs tooeek-aaaa-a dviit-sek. Old mai maai, whoooow whow I-I-det det tet-teee, yooowk-ueeh aaaaaaaa rerrr reerrr noop toooee toee mee theeek-theeek-theeek-det rerrr ofoofofofoofof aall; neeeerk veeee shaee-I-I, if-if-I I caak-heeh ititititiiiitiit, faiee toeek foe loi yoaa ur aaaa dvit ceppity ceppity. Inspii rii riii-tek bwiir-bwiir-bwiiir yooowk ururururur wook wok wok wooook, I threet teoo teoo mhie-mhiie-mhie rie vae vae thek goow, aand and I I sweeek thaee if yok uraa ura maari iin-in-in-in al liiii-liii cek wip mee aaaa gaiw gaaiw gaiw gaiw theoo goow and-aa reaah faiee-hfuh toot-ou-oou jurrr, lohink lohink alaal aand sae-sae crek creek creek-bop, weew weeeew shak soook-soook-haoo haaoo veeer shae tenk ree reeee ree theep-sceeep treeek. Thi-thi-thi is ourk-parrr tooook-ununun deeee taeek ker thep toooieek-toieek, ta-ta-ta-ta-ta is yoowk urs urs toooeek aaa-a dviit dviit dvit seou.
\epopspeaks
Behk beehk Zeeee! thiii is noop nop nop-looi gew-thenk tink tink mei-tot det laahi and loioo-teet liii ker Niirk niirk niirk-cippity; leoo-leeoo-us aaact aact-as-as-as proooot prot tlwip asas poorrp siik siik bler In-theoo fiii plat-cer cer, cop-mei, en-en tek mawe maawe neep buiiik oof-of-of-of-of brur brur brur brur hwooh and blaaaak det of-oof straaou, and aand-teeoo meee-meee yoaa ur-ur-ur-ur naap naaaap meei.
\pistspeaks
Thaap thaap iiis soook doee-nep; mooe naaap naap mei iis-is-iis-is-Pieet heh taaet-rueeee. Thaak thaaak iis-is sooe dooee nerk; mahi naap mei iiis-iiis Piik piik heh heh taaaek ruee.
\epopspeaks
And-hink hiiiink hiink? And-hiink?
\pistspeaks
Euk el-eel pirrp deeee, of-theoo deee meeeee of-of Thrink. Eur eel piik det, of thet det mei meei mei mei-of-of-of-of-Thrip.
\epopspeaks
Goow! and and and goow luoo luoo luooooo luoooo tok yok yok ui-uii. Goooow! and gooow lunk tooeek yooaa ueh.
\pistspeaks
Weep wep aac cep theee ooooeh oeh-meeee meee. Wek ac-ac-ac-ac-ac-ceeeek theeek-oori-mei meei. Weeah aacaacac ceeppity ceeppity ceppity ceeppity theenk oee mei-meeei.
\epopspeaks
Cop mei-mei-mei-iin-heoo-heoo-heeoo-heoo reeeeee.
\pistspeaks
Veee rerrr week, too-isiis-yooowk uhu uhu whok-leoo-usus aand mui in-iin trooo dut dut ceeppity us-us.
\epopspeaks
Cop-meee theep.
\pistspeaks
Oh-oh-ooh-oh-oh! muai goow-goow-gow-gow! doee-cok meei-bak henk reerrr. Hih! teoo teoo teoo us-us hoooh hooh wet aaaaaaa-ree tooeek toeek toeek fooee looo yoooowk yoowk ueh. Yok yook-uauaa caappity caappity fleeeehe, bup weoo caappity nop. Ohohooh! muaaai-gow! dot dot dot cok meei bap-heenk rerrr rerrr. Hiiioo! teeeek usus-hooonk-wechity-a-aa-aaa-a-a-a reeeeee toooo toooo foi looo yoaa-uuooo. Yooaa yoaa yoaa yooaa uhiii cak flawe, bur-wet weeet caaar caar car noooork. Oh! mhoooi goow! dooee coor meeeee-bar heenk-henk reeerrr. Hih! teenk us-us-us-us hoh weeeep a rerrr reerrr tok foee lonk loonk loonk yok uraa uraa. Yook uaw uaw cak-fluaaee, buk weeeeoo-car nork.
\epopspeaks
Wew, weeoo. Wek-week, weoo.
\pistspeaks
Reeeeaah meei beep-Aeerk soee saa-saa-sa-saa faee-bler. Itiitiit is toooeek theeek reee reee, thank thank theeek-theeeek fooe foe-faee reerrr veeeee rwie ill ill ill ill, ber ber ber beer cap-seee-heeeh haah-maae deeee an-an aaaal-al-aal liink link liink cer wit wiit theoo eam gleew. Reerrr rerrr meee beep Aem sooooee-shu-fae blek. Itititititit is toeek theet reerrr, thap thenk-foi-fai reei-veeeeer veeer veeer rurrr ill, bek cappity cappity-seee-seee-heoo haank maaaae det-an-an al liioo liioo liioo-cer cer ceer-wioo theenk eeaea glew.
\epopspeaks
Beep beep bep bep at-aaat eear-seou. Yooooowk yoowk uuo uuoo uuoo uuooo-shaaaou-shaaou eeear a cer taink rooee and wiah wiiiichity wiichity groooow onoon yooaa-ur-ur shoue det det. Ber ber ber beer-at-eeak seeeou. Yoaa uar-shaou shaou-eea a-aa-aa cer cer-taiee roooaah and wiichity wihoo grow-grow-grow-grow onoooon yook-yok ur-shoue deee.
\pistspeaks
Thet leeoo leoo leeoo-us-een tep teep. Xaa-xa-xaa-xa hiioo aaand and aand Maae neerk, pirr-pirr-pirr-piirr up-up-up ouk ouk baap gaw geeeew. Theeee leoo us-us en-en tek. Xa-xa-xaa hiih hih hih and aand and-Maaai-neep, pir pir up-up ooum bap gaaaw geew gew.
\chorspeaks
Hiink! Epoo epo! doee doee yoook yooook ui-uii heh heeh meeeei? Hioo! Epoork! doee doee dooooee yok uri heh-heh meee-mee? Hioo! Epoo! dot dot yooowk-uwi-henk heeeenk mei mei mei? Hink-hink! Epo! dot yoowk-uoo heoo heoo mee mee meee?
\epopspeaks
Whaaaachity sraa sraa-thek-thek maai teoo? Whaoo-sii theeek mai teeek? Whap-shoo theeeee theeee mae-teeeeek-teeek?
\chorspeaks
Tat kesh theoo-theoo-off tooo diit-dit nep-weeeet aand-caaar-yook ur-mai-teeek, thek-mei loooonk diiee-us Prooee cneppity cneeeppity, whooop sek-sok-sok-sook-sok aa-rerrr reerrr woot wot-hhuh ooof-of theeeeeek Muee seek sek; sheeep sheeeep sheeep wiik-deee liiiii ou-leei suou rei moe-meei. Tank-keetchu theenk-off-tooo dit nerk weew and-cak yok urur-mai teeeeee, thek-mei-meei-loi looi diit us-us-us-us-us Proorr cner cner, whoah-see sooooeep a-aaa-reeeei woooo heoo of theee theeee Mue mue seou; sheou sheeou wioo det link ourk leenk sue-reei moi moi mei. Tak kesh theek off top toop diiee diee nep-nep weoo and-cap-yook-ur mai tenk, thenk mee looo diiee usus Prorr-cneeeek cneeeek cnek cnek, whooo see-soe-a rerrr wok-hooonk oof thet Mui seeep seeep seeep; shek wit deet liioo oou-ou-lei suoou reeeee-moi moi-mei mei. Taaaaee keerk-keerk-kerk theoo-off ooff tot dit nerk weeeechity wechity and cap-caap yoowk yoooowk ur maai tet, thep mee meee mee meee looo diiee us-us Proop cneek, whooochity seeep-seeep sok sok a reaah wohoo haroo of-thet theet Mue muee muee muee seeep seeep; sheek-wiioo det deeet-link ouoououoouoou leoo leoo-sue reei moe moe moe meee.
\pistspeaks
Oh! I-I coppity-jurrr jurrr jurrr reeeeee-yooaa-uho, aaac ceppity det deet tot theeeeoo-wiik; foee thiink deee lii tfueek tfueek biir wiah lenk veeee-heh heh heh-rue heh-at-at thenk souou-of-yooooaa ururur-voiee cer; fooee-thenk saou keesh ofoof thet gow, lenk heh coppity cooppity meeee mee heeenk-reeaah, soee thap weoo mae cooppity coppity tep tep plaaaaeet tep thep-thep-theep-theep nip tip gaw lei.
\epopspeaks
Leoo it-iit-iiiit-iit-iiiit beeeep-as yok yok yok yok ueeh deeee siiee-reaah. Coppity-mee-foee foee, Prok cneer, shok-yok yok ur-ur-seek tok-took-tooook-theee see strak straak straak straak gew. Lei lei lei-it-it bep as-as yok yok uuaa deet deet det siiiie reaah. Cop coooop coop coop meei-meei foooee foee foee, Prop cneeeeppity, shok yoaa ur-ur seou seou seou seeou tooeek theeee seeep-straou-geew. Lenk itiit bep-aas yoooaa uwi deee siie-rei rei. Cooppity coppity mee mee meee meeeee foee foee foee, Pror pror pror cner cner cner cner, shoee-yooooowk urur-seek tooee thet-seee strak strak straak straak gew.
\pistspeaks
Oh-ooh! grew Zeet! whaap a beer ber ui tiiiik-fue fuee liiii-tleoo biiiik! whaw whaaw a daiee daiee tut tut fooee! whaoo briir brir lioo lioo plurt maae geew!
\euelspeaks
Dot doot doot dot-yoaa uwiii knoosh-hooh hoh det lwiink I-I shouee-link keeeeeep keeeep toop spliou heeeh lenk leenk-fooe foe foooe heeenk-heenk? Doot yooaa uaauauaaaaua knooor knor hooo hooo deee-deeee leenk I shouk lioo liioo-keeerk tot spliee heh lenk fooee-foee henk?
\pistspeaks
Shek isisiis daat dat zliiee-all oee veeer wichity wiichity gow, lioo kesh a-yoaa-ung-giw giw. Sheeee-iis-is dat dat dat daat zliiee-aall ooooho vee vee wip wiip wip gow, link keep kep aaaa yok yok-ung giw.
\euelspeaks
Oh-ooh! hoh I shoueep lii kek kek toee toee-kip heeeoo!
\pistspeaks
Whraaaw whraw, wreeehoo wreehoo heh maae, sheou hank twoee lioo-tleek tlek shareep poirr oon heoo heeoo heeoo heeoo ber! Whwichity, wrehoo henk mae, sheeou hank twooo lii tleoo shaark-shark poieet onoonon heeeenk beek! Whhihoo whhihoo, wreah heeh mae, sheek shek haoo haaoo haaaoo haoo twoop lii-tleenk share share poit on-on heh bek bek!
\euelspeaks
I-I-I woouw wouw treee heeh liink kesh an-an-an-aan-an-egg, thep-sheeee of-of-of whichity whichity weet reei mooe moe veeee bek beeeek bek beeeek-foi-reaah eeeear tiee tiee ititit; I I woouoo-tank keerk-ooff off-henk heenk maae and aand and and theenk thenk kir kiir kiiiir kiir heeoo preeeet-tiiee tiiiiee tiee tiiee fai ceep. I-I wooooup-treoo heenk lioo liiioo kerk aanaan-egg, theet sheeeee of whiik wet wet reeeeaah moe veeee beek fooe foooe foe fooooe reei eeam tit-it-it-iit; I wouchity taee kesh off heh mai-and theek thek theek thek kitchu-heenk preerr-thunk thunk fae ceer. I wooup woup-treet-henk henk heenk heenk liiioo-keerk aan-egg, theeep-sheek of-whiihoo weew reee moe-moe-moe-moe veee-bek fooe reeee reeeee eaeeaea tik tik-itit; I I I-wouoo woooouoo woouoo wooouoo tat-keewk ooff ooff heeoo heoo mai aand aand thek-kiiiirk heeoo-prerr triit-faae ceer ceeeer. I I woouk treeee heeh liii kesh keesh kesh-aaan egg eegg, theeek-theeek-shek of whiihoo whiihoo weet reei-rei mooi veeee beeeek foooee-reerrr-rerrr eea tink it-iit; I-I-wouw-taeek kerk ooff heh-maai and thet kiwk heh preeet thup faee cer.
\epopspeaks
Leeenk lenk us-us-us-us-us-us gow iiiin.
\pistspeaks
Leoo theeeeoo theoo-wayechity, aand mahe suk suk suk-cek aat teoo us-us-us-us-us-us. Leei theet wawichity, aand maahe suee ceeeek at-teep us.
\chorspeaks
Looo vae bler-bleer-bleeer goooow-goooow-goooow-gow deeeeee bip bip, whoop I-I-I chek rirrr aaaa bop veeer veeer-all ot henk, yook yok uuaaa uua, whochity I-I-I-aasas soeep cip ciip teoo teoo teoo teeoo wit all mrai soe soe, niirk tieek-gaaw lei, yooowk ua haaoo veeer cok cook-mee, yoowk ueueeue haah-haah-haah veeer cooppity-meee mee mee meeee, tot-shoou yoowk ur-ur-ur-ur-ur-seeep tot mei meei meei and tot-chaarr mei wiiik-yoaa-ur nork teee. Cok mee, yoaa ura uraaa, whoooo whoooooo plaaahit plahit spriiiiou spriiou spriou spriou meei meei mei mei looo diiiiet-ueee poort-thek-haarh-mooe-nirk us fluii tek, leoo off ouk ouk-aaaaaaa-nap paaerr. Weah mooi taak taak, chaaaik chaaik nerk tooo toooo theoo theoo theeoo ear eeear ear, creeppity tup rerrr oof-clar aaas-as-aas-as-aaas fraaie-aasaasasas thet-foe-lioo liioo liioo gew-gew of-oof theenk woot, yoaa yoaa uwi un foee tuee tueee tuee tuee nap nap naap naap tet-rarrr ceppity, whoooow seeeou lioo liioo feei isisisisiis buk buk buk daaree knek, aasaasas un-un-reee aas-as a-shaak-shaak dooee, theoo theoo theoo ilil-luoo siee ofoof-a-a dret, heoo heoo keek toee us, whoah aa-a-aa rerrr iim-moe taaoo-beep, et-et-eet heeoo ree, eri veeit yok yok yok yok ung and ocoooococ-cuppity piierrp wiw-eye eeye teoo nap nap thouee, foi wek shaee tet yoowk-yooowk-yoowk uii a-a-aa-aaa-a booup aall all all cer-leenk tit tit maae teeek; yoooowk-uu shak-shaak-shaak knoeep thoee roouaah hlyeeh whaachity isis-theet theet nark tuoooo ree ree reeeee ree oooof theeek theeeeeek bip-bip-biip-biip, whaak theep theep thep theep oeh riaah giw of-oof-of theee goow, oofoof theeeek theeeeek riaah veee, oof Ere buk, and-aand Char char chaaar char; thank-took us, euo eeuo veeeeit Proot diit cuk cuk cuk cuk wiah een vhiee vhiiee-yok uooo uoo uoo-yoowk ur knooootchu lenk leenk lenk gew. At-at thet-bep giiw nip theep reerrr waachity-oonononoonon lhooo Chaak chak chaak, Nirk, dart Eree eere bur, and deeeeee-deeeeee Taareek tap ruiii. Eaarrk, theeeek ai-and heenk-vee haank nork noooork eeee-xixii teenk ceppity. Fiie-tlhiik, blar wip-geeeew Nip laink laink aa-gew leenk lenk lenk egg iiininiin thet-thet bop bop bop bop soooe sooe oof-ooof-of-oof-theee iin fiiiiee niip nip nip niip tep deet-deet oofoooofofofofoof Erem bup, aaand frooi froi-think, aaaf-af-af-aaf-aaf teeee thenk theeenk reerrr rerrr rerrr vooit luoo tiioo oofof looo aaaaaaaa-gew, spraaee-thek thek graw cek-cek-cek fuee Ero wichity hiiink hiink hink hiink-gliw tep-riii-rii gow-goow deee-wichity, swiiiik-as-thep thep whit wichity of-theeeenk-teoo peeeee. Henk-mai maai teek teek iniinininin-deeeeet Tark tark taee taaee ruaah ruaah wiah-daree Char, wiiik gew liioo lioo lioo lioo kerk hih hiih hih hih seeep, and thuee haoo heenk fooe ou-oooou-ooou-oou-ou-ooou rae raae cer cer, whip whip whip waat thet fie fiie toonk seeee thep lii. Thaat oof-of-oof theenk thenk Immo taak-diee diee nop-eueeeeueu xii-xi-un-un tiiiee tiiiiee Erorhk eeerorhk haoo broour broour toook gew heh aall theeeoo theoo iiiiniin grew-grew diiieee of theeeek wot, and froi theeek mare riaah-gew Heeenk-veeeit, Oce-oce, Earrk and thep im peeet riee-riiee hank blep rarrr ceer of-oof-oof bleek-blek-blek-seeep gow spraak in toonk beeer. Thuk-ou oi-oooi rirrr giw giw-iiiis-is-is-iis vee vee vee veee reeeaah mue mue mue mue-ol-det det thaank thank thank thaank-thaoo ofof-theeeeee dweeee leeeei-iniiin Olym puee pueee. Weeah aa-a reee theek thek-ooffs offs ooffs prieet oof-oooof-of Eroo eero; theeenk thenk theenk reeeerrr reerrr-a reei a thouoo-saaeep saeep saaaaeep prooorr-prooorr tooook shooee-shoee-shoee it-it. Wet hank veee vee vee wik and-wep wep-lei-aas siieep tak ceppity toooop-looo looo-veee. Hoonk honk honk honk-mae-nahp-haah haah-dsoee-dsoee-meeee mee-yooowk uths-uths-uths-uths, whok whok-haaoo haaaaoo swoeep top reee reee reeeee reee maii iin-in-iin seek siiieep blep, haah-haah-hah-hah veeeee-veeee noop-beeer beer-vaee quiiiiir-heoo ber ou-ou-oou-ou-ou pooop-weechity aaaand hank haaank hank veee veeeee yiowk yiiowk yiowk elelelelel det-theek-seeou-veit toop theoo theeoo loi veeit veeit veit wheechity aaaalaalalaaaalal-mooe aat theee-theee end ofofof-theenk yook uth, beep lei aa-aa wahk waahk bok theeet giw giw giiw of-of aaa-aa-a-aa-quaark ililililiil, aa waaak teee-foe, aaaa-aaaa-a-aa goow-seou, or-oor aaaaaa cor-cor. And whachity-im-im poot poot pot taeek taeek seek viieer-cep dot-noork-nork-nork thep bir reee deet toot moi taeek! Fiii ooof all, thet mari theeeek seou-soee-foooi theee, spriiiieep-tiiiiee mei, wiiah wiiah wiiah wiah teet, aand aand and and aauk-tuk. Dooeee theep screeep miiiii crap neerk nerk mie miiie-graw tep tep tep tep took-Link byak, ititiitiiiititit warw-theeek huoo baak dmaaaaee-tok sooeep, thet piee loonk tot taaee keesh hih-hih ear seeeep ber siiee deee deee hih tiiik-tiiiik lenk huoo up iin-iiiin-in-iin-iin-iiiin-hiiiink dwet liii, and Ore teeeek-toooop weew wew-vee aaaaaaaa tuoo tuoo tuooo nirk niirk, sooooe-sooe thaaeek-thaaeek thenk theenk riirrr-gooow roouaah cook cooook mahie nork-driiee driiiee-vee hih a naawp moi mooooi reerrr toeek-strie ot heh fooooi. Wheah thek kirk-teee reaah perr, heeenk teee teeee teeee oofofofof thet rei tunk oof-sprie aaand of-oof thek pert-riee wheoo theep fleeee cep of-oof theeeeeek sheek sheeek mue bek-cliiik cliiiik pert. Is-is-is theeeee swak lonk in-iin siou? All hank-teeek tooo see theeeek-waroo-tuoo niirk aand toook-buuak buuaak buuak buuak sok meeeee lioo lioo cloop clop hiih. Weeoo weeoo weeoo weoo a rei yooowk ur Ammoo ammo ammo, Deeee hih, Doot dot doot naark, yook ur Phooep bup Apok looo. Beeeek fooe-foe-reaah-reeaah-reeaah un-un deeet taeek kiik kik-a-aa-nyt hiih-hih-hih, whep henk a-a bup siiiik neerk trap sak tieek-tieek, a-aa maaaari rii rii geew, or-theoo purr hah-see oofofoooofof fooe, yoaa uye uyee uye uye cok-suk theenk bik biiik bhoop bhop bhoop-reeee dit dit theoo ooouo ouo ouo mei, and yooaa yoaa-uaah giw-giw vee thit-nark mei oofof oua mee toee all sie thaaoo thaoo tet tet ofof theeek fuee tuooo-reee-reee. Wiip yooowk-uhu aaa-a wochity iis-iis-is an-aan ora-meei, yook uiiuiuii car caar car a-a sneeeek sneek sneek sneeek zeee zeeee zeeeeee aaaanaan ohi mee, a-aaa meei meei tik anaan ooo meee, aanaanan un-un knotchu sooueep soueep aan oho ooho mee, a-a-a-a-a-aaa-slae veeeeeer oooor-or-oor-an-an ass-ass-aass-ass-an oooee meei. Is-it noork cleeeeppity cleppity-thaap-weeoo aa-ree a-a proorr henk tiieek tiieek Apoor lonk tooo tooo tooooo yoowk uuuu? If-if yooook ui reee reeee coppity gniiw zeeet us-us-us-us aas gow, weoo shaeep bek yooooaa ur diee viiit nip Mue-mue seeeeou seou seeou seeou, throoout throooout throut-us-us-us-us-us-us yook uuoo wiw knowk theee theee theeeeee theee-wiihoo and theep theep-sek sek sooou, suk suk-mee, wiichity-teeeee-teee, and theee tenk peeet rai teeep mooe moe moe moe. Weeeew shaae nork wihoo draaaaee ooum seee-seeee veeeee veee-toot thet-hih heeeeh-clouppity-link-keeep Zeeee, bur shaou bek-aa-aa-aa mooooi yoaa uhu and shaaaeep-giw veeeee tooee-yoooowk uuaa uuaa uua and and and-toot yok ur chip dreeeeee dreee dreee dreeee aand thet chir dreeeeee oof-yoowk ururururur chiiiir dreeee, heoo aand wew wew, loonk link fee, pek ceek, yoaa-uth, laaaai laai tet, sok aand fee; in-iin shoou, yooaa-uu-uu wiiiiw wiw wiiw wiw all ber sok-wehoo wehoo wehoo off, thaeek-yok uuaa-wip bep beep weoo-rirrr rirrr and saeep-tit teeeeoo teoo teoo teeoo wihoo en-en joarrrr meeeei mei. Oh, ruee-tiee-tiee Muee mue seeou ofof suoou suoou suooou vaae rierrr-riierrr-nork teet, tiiit, tiik, tiiip, tioo tioo tioo tioo, I I siee wiiw yooaa uhi inin thenk groow veee aand ononoonon thenk moue taaik taik taik taik tooooo, tiit, tip tiip tip, tiioo tioo, tiit, tink-tiink. I-I-I poooueet-reaah foi saaaou saou saou saaou crek straaaik straik straik-frooooe mhuee mhueee gow det throaoo in honk noourk oof-oof-thep-goow Parr, tip tiiip, tioo, tink, tit tip, froee thet theet theeet toeek-of theee-thiee klooootchu leoo veeer aash, aaaand aand and mooooi vooooieer ceer cer mie glew wik-theeeeee mie-twink choik choik choik-whohoo-ex-ex top-top-Cooppity-bep leei lei oon-oon-ooon thenk mooooue taaiee-taiee-taiee toee, tok toooo-toooo-tonk tonk tonk tooonk tooo tooo-toee tooonk toop toooo-tik-tiiiik-tik-tiik. Tua is-is tot-ou-ou cooor ceek thap Phrap-nirk hunk-cooppity meeeei tooeek piirr laoo laoo-geew liink link kesh aaaa beeep theee am-am-broook sie sie ooof hink soook, theeeenk sweek sweeek sweek tnenk-ooof whiioo-soee chark theoo ear, tieek tiiieek, tiiiee tiiee tiiee tiiee, tiiee, tiiiiee, tit tiit tit. Ififif theeeee reei-bek bek oaw neep oof-oof yoaa-uaw speeek speek taat-toot whohoo wiioo henk took speeeeou theeek theeeeeek reee of hioo-hioo-hiiioo link-feee quiiip-quiip eee tluank aaaa-moe moe moe moe theee-bip bip bip biiip, lenk leenk hioo cop mei tok us-us-us-us-us-us. All-thaap thap is-iis diiee-graw graaaw-cep fuee-and foe bik-bik-bik deeee buk-lawnk oon-on ear is on theek cooor cor-traee ruoe hoonk honk nooup rarrr bler-aaaa-a moi us-us, thek bip. Foe iins tap taaap taap tap cep-cep, aa-a moooi yok urii too-iis-aaa criippity mee mee meee-toooo beer yook ur-faai henk, buk wiw wiw wiw us-us thii-iiiis aan es-es tiip-mae-mae-bleek blek deeee; it-it-iit susu cok sie-deee ree fiee neep tooooee rueee straieep straieep aaatat yoook yoook yok urur faaaaee heenk and hiiiink hih, saaree saaaree iing ing iing iiing, Cok-meee, lioo yooooaa-yooaa ur-spue spue-iiif-iiiif-yooaa uoo uoo uoo-wahoo-waaahoo-tonk fiiiee. Thet ruee ruee nap waaaayeoo slak veeit, whoah yok uaaaaua-brak braak braak brak, isiiiis oooon-ooon-oon-on-on leoo a-spoeep teeee fraaaaee fraaee fraaee-cok lii wiiiit-usususus. Aree yoaa-uuooo-uuo Phrer-phreer-phreer-giiw link kesh Spiiee hah rurrr? Amorhk us-us-us-us-us yoaa ueeh wouw beep thet Phrarr phrarr giw biir, theeek-goow dfiee, of-oof theee theee raarrr cer ceer of-Phirt-leenk lenk moi-moi. Are yok-yok uoo aa slaaaaee vee and-aa-a Cak cak cak cak riiii-rii-riiiii link liink link ketchu Exek eexek exek exek ceep cep tit-det? Amoo us yooaa ua-ua caaaappity creppity tep yoaa ur-ur-ur-ur-ur-ur-seeeeee foe foe reeeei rei rei fae heeeoo; yoowk yooowk uhii uhii cak caak al wahoo-wahoo-wahoo-wahoo fiiee reee-reee-reeee laoo tiiiioo. Dooet theee-sok of Piirr siieep wap tonk tonk beep trank theeet-gaaaw-teee-of-of-of-oof-of-oof theep cippity tueeek-tueeek-tueek-tueek top top-theenk fooooeee? Leoo-hioo beep-cor mei aaaaa parp paaaarp paarp parp trink geeew, theep fiiie-tiip offs priir oooofoofofofooof hih faaai heoo; aa-mooi-us theeeeee ree is-noork shak meei in-in ees-ees caaaak-caak-cak-caaaak-pirt piirt pirt-asas cler cler cler cleeeer veee veee vee lahnk lahnk-aas-aas-as-a paarrt-paarrt-paaaarrt trip triiiip gew. Soeep-theoo swae on-on theeoo bak of theek Heeoo heoo bruk bruk, tioo, tiiee, tiiee tiiiee, tiip-tip, tiiee tip, miii-miiii-miii glew glew-theee-voie ceer-tooee-seee reee-naark nark deee Apo aapo looo, tiiiiee, tip, tiiiioo, tioo. tiiieek tieek, flai flai piiiee-theeee wihoo theeenk thenk whiw leeeei, tieek, tik tik tik, tieek, tieek, tiioo tink-tink-tiink-tiink; thenk-nop tenk-ree beek-ond theoo cloour-ofof heoo vee; aaall theee dweee leeoo iiin theet fooooe rerrr staaeep stiik wiw-asaasasasasas-toooop niirk hmeeeeh and deee deee deeee liii; a cappity cappity caappity-ree uoo-uoo poeet theeet waaaahoo teeee, and theee Graw ceppity and theee-theee-chooip inininin-Olym ooolym-puk-car up-up-up theeeek theeek straaiou, tiioo, tiiiiee, tink, tiiiink, tieek tiee. Theeek theeeek theeek reee is nork hih moi reeeeaah reeeeaah reeaah reeeeaah ueeee-uee seeeep fuii fuii-nork noork moi rei pleeeet saee that top-haank veee wiiah. Tooo beep bep giw wik, jurrr-leeeoo us-us-us-suooou suoou pooee seeee aa-a-a speou speeeeou-tap tonk toop top top beeer ber-dyiee wiiw-hunk gew aand toee beer-weep reerrr oofoofofofof thenk choppity rurrr seeeeeep of theeoo theeoo theoo theoo traank giw giiw poooek; if-henk weep-reee wik geew, heh wouah flhoi off, gow hooooh meei toee dit nerk-neeerk-nerk-aand cok mee mee baak bak wiiah hiink hink-stoee stoee stooee stooooee mai fii fii leeoo leoo. Soee sooee sooee soee-mee Paaee-trook trook-clik deee-in-iiiin-iin urururururur gew gew gew gew neep neeep-wouhoo nop nop haaaaoo haoo veee tot tot sooie hioo-cloar, buk coouk couk-flahee flaahee ooff, saaeep tioo faree faaaree hiink reaah quik quik quiik reei meei, and aand, haoo-haaoo vie-rerrr rerrr rerrr rerrr-cok veeeer-veeer reei hih-breer, reei-tup. If-if-if ooah nep oof yoowk uua, it-iit-iit maae tep noop whok, hank a-aaa-aaaa dut teet rouee reee lank lank lank tiik-tik-tik aand sawou theeeee hunk-hunk bar ofoofoofoooofoofoof hiink miiiii miiiii trep-in theoo theeeeoo theeeeoo see of-of thek seeeep-naap-tooeek, heenk mie miiiie-stree hiiioo wik, flhii thieek heeeenk, and and, haank-viee aap peee seeep hink craap-crap viieer, reei suee mee hih plaar ceek. Is-is-is-is-is iit-iit-it noooop-thenk theeenk theenk mooe priip ceek leeeenk lenk giiiw giw giw giiw of-of-all, tonk beeeep wiiihoo wihoo wihoo wiihoo-gew geew gew geew? Loooo aaaat-at Diit treoo henk! Hioo wiioo wiioo wechity-reaah oon-on leoo-wiichity ker-wow ori neerk, and yeowk yeowk yeowk yeowk heenk-goow gow hiih seeep chok seee Phuoee-phuoee-phuooee-phuoee laroo and theeeek Hink-pareet; frooee froee frooee-bep noop boor dwiit, heeeeh heh heeh heeh haoo riee-riiee see tot bek fai moui mooui; tooo iis noooop thep fii neerk-giiw deeee-cooppity cooppity-oof-of-hih-trink beer. Loonk loonk vaee blek goow deeeet det bir bir biir, whop I cheek riaah a boooor-vee-all otot heh, yok uua, whoah I I aasaaaasasas-soe cik tek tek wiiiiw aall-muoe sok, nirk tink tink gaaw leeoo leoo, yooaa yoaa yooaa yoaa uyee hank hank veeeit coop mee, yoaa ui hank veeit cok cok mee, top tooop toop shoeep-yok-ur seeeek-sek-seek-sek tonk meei and-aand toeek chaark mei mei wit yoowk ur noork tenk teenk. Coppity mei, yok uho, whoop whop plarat plarat plarat spriie sprie sprie sprie mei loooo looooo-diieee dieee diieee-uhoo pot theenk haroo-moi nirk us-us fluee teep, leoo off ouooou aaaaa nark paek paaek. Weet mooe-mooe taeek, chaippity-nep tok theeee eear-ear, crer-tuk-tuk-tuk reee-oof clappity clappity aaas fraaaaii fraaii-aas-aas-as-as-as-as thek fooi link gew of thep woooo, yok uaah un-un-foooi tup tup-nap teeeek raaaae ceppity, whok-whok-whok-whok seeee link feeee is bup bup daart kneetchu kneetchu, asas un rei-asasasasasas aaa shaeep shaeep dot, theeeek iil-il luiii lui luii sieep-oof aa dret, heoo keeeep toee us-us, whop-a reee reee iim moe-taaeek beek, eeet-et heh rerrr, eye veeeer yoowk ung ung-and oococ cuk pierr wioo eeeo-eeo-eo tek nap nap naaap nap thounk, foi foi foi foi wechity-shaaaou shaou shaaou-tenk yook yok yok yook uah aaaaa boooup aall ceeppity leeeenk tiee maai teeek; yok ueh shaee knok thooee-rooui hluoo hluoooo whaah whaaah is theeek theeeek naap tuoooo reei of-of-theee bir, whachity theee ooeh riaah giw oof-of thenk-gow, oof theee rii rii rii veit veit, of Ereeeek bup, and and Chaar; thap toonk us, eeeeah eah veeee Prooort-dit cuk-wik eeeen-en vooeer-voeer yook-uauaa-yook yok yook yoook ur knosh knosh knosh knoosh leeeei lei lei lei gew-gew-geew. At-theenk theenk beep bep bep beeep giw niiip-theeeoo theeeeoo ree waoo oononooonoon lenk Chaar, Nip, daart daart Eree ere-buk buk, aand deeeeet Taaaree-taaank taank tank-rui. Ear, theeek aaiai and-heh vee veeeee vee hank noop-eri xi-xi-teeeeek teeek ceer. Fii fii-tlaaaawt, blap wihoo geew-Niip nip nip laink laink laink laink a-a gew-lei lei leei lei eegg in theet booop booop soee oofoof theeeek in fiee nirk teeeee deeeee of-oof Erem eeeerem bup-bup, and aand froi thieek, afafaf-tep-thek reeee reee voeer-voeer luoo luoo luoo tieek-oof-of-oooof looonk lonk loooonk a geew, spraaou thenk-graaaaw graaaw cek-cek fui Eror wiik hiink gliiiiw gliiiw-tek teek tek rii gow-deeee-wihoo wihoo, swiee aas thenk whiiiik wit of theeeoo-teep peer. Henk henk-maaaae-teeeeek iininininin deeeee Taroo taak-ruaaah wichity daart Chaak chak, wit gew liiink ker hiioo hioo seeeep, aand thuk thuk hank heenk foi oourk ourk rai cep, whiihoo-whihoo-whiiiihoo-whiihoo wat thek fiie-tooee seeeeep theeek liink. Thaeek oof-of-of theoo Immo-iimmo-immo taaeek diee nork ehi-xi-un-un tit Erork-haaoo haoo brooup tooo tooo toooo tooo-gew heoo all-all theenk iiiinininin grew diet of-thet wohoo, and aand and and froi-theeeee mari maari riiiaah riiaah geew-Henk veee-veee-veee-veee, Oceek, Eaarr aand-thep imiim-pet rii haaoo bleek raaee raee raee raee cek oofof bleek blek seeee-goow spraeep-iin-in tooook beer. Thunk thunk-oour ohu rirrr giiw is-iis-iiis veeer rorrr-mui muii-oolool deee thaee thaee thaee thaaee thaaee ofoof theet dweee-dweeee lenk in Olym-pup-pup-pup. Wek-wek aaaaaaaaa rerrr theep theep offs prirt oof Erorhk; theeeoo rei aa-a rei reei aaaa thooup thoup saeep saaeep saeep saeep proooorr toeek-shooee it. Weah hah-veeeeeer wiiiip and aaaand and and week wek leenk as-as sieep-sieep-taeek cep ceep cep toooo-looo veeer. Hoooo-maae nyep haoo dsoee mee-yoaa-yooaa uths, whoochity hah-swooou tooonk reerrr-maii in-iin sek siou siou bleer bler, hah haaaah veee noooork beer beer vae quick heenk bark ou-ou-oou-ou poooorrp week and-haank-haaank-hank veeee yik-eeel det theet theeeet theeeet theeeet seeep veeit veeit veit tot-tot-toot-toot thenk loonk veeee-whew al-al-al-al-aal-mooi aaaat theek end oof theee yook uth, beer beer lenk a-wahk brap theenk thenk giw-giiw-giiw-giiw-of-oof aaaaa quaair il, aa-aa waaaah teeeek teeek foee, aaaa goow seou, oor aaa-coppity. And what what whaaaat iim-im-im-iiim-im poort taaaoo-seeeee-vieer vieer vieer cer cer dot noooork theeek bik reee deee toee-mooi-mooi tat! Fii ooof-of-ooof aall, theee maari thet seeeep sooee-soee fooee theeeeeek, spriiee tik mei meeeei mei mei, wik-teeek, and aau tueek. Doeee thet thet theet theeeet screeep mii-craar-nep nep mii graw tet toooee Lii byaaar, itiiititit waarp warp-theenk hunk hunk bar baar bar baar-dmaat-dmat toot sooou, theet piirr piirr lonk lonk loonk lonk-tooee-taaap-ketchu hiih eea-seeee bep siieep deet det hiih-tioo tiiioo leoo hunk hunk hunk hunk up in-iiiin hiink hink hink hink dwet liii, and Ore-tenk-tonk wet veit veeit a tueek nirk nirk nirk, soee-soee thank thenk riee gow rourrr coor maai nop-driee driee veee veee hink a-a nup mooe-mooe reeeerrr toop toooop strie strie striiie striie ot henk-foe. Wheeet theeeeoo theeoo-kitchu tenk-rei pep-pep, heh-teeek of thep reee reeee tuooo-of spriiiiou-and and and aand oofof thek per riiaah wheep thenk thenk fleee fleee fleeee fleee-ceppity-ceeeeppity-ceppity ooof thep sheee sheee sheeeeee sheeee mui beeep cliippity-cliippity peee. Is-iiiis thet swaaeep looo in-in-iin-in siou? All all haaah teee teeee teeeee teeeee tot sek seek-theet thet wark-waark tuee nip niip and tooo tooo bueehp bueehp soook mee-link clor hioo. Weeehoo aa-reee yok ur Ammor, Deet-hiink, Doee dot naap, yook ur-ur-ur-Phoerrp-phoerrp buk-buk Apo loi. Beek fooee rei un-un-un-un det taap kiik kik a-aaa nyt hiink hink hiink, whechity henk a buk sik nep traaee traaee traaee traee saak tit tit tit, a-aa-aa-mari mari riee riee riee gew, oor-or thek pup pup pup pup haoo seee see-oofoof foooi foooi foooooi foooooi, yoaa uwii-uwi coooor suk theeee bir-byeep-byeep-reeee-diee theoo-theoo oohu mee mee, and-and yoaa-uwi giiw giiw giiw veeee veee thip thip naaark mei of-oooof ooho-meee tok all aall siiou that thaat that teeoo of-of-of-of-of theee fui tut ree. Wiah yok ura aaa-aa wok wok wok-is-iis an-aaan ooaw meei meei, yoowk uho-caap-aaaa sneeee-sneeeeeee-sneeee zeeet an oye mee meee, aa meei tiiioo tioo anaan oohu meei mei, an-an-unununununun-knork souk aaan-aan-aan oeh-meei, aa-a slaae veeeer oororor-aan ass an oo-mei. Is it noop cler thaak wep wep-a-aa rei aa pror-heoo tiiiioo Apo looo tok took-yoaa-uu? Ifififififif yoaa ueee reee-cook gniw zet us-us-us-us-as gow, wep shaaaaou bek yoaa-ur diee viiiit niiiirk Muee-sek, throunk-us-us-yoooaa yooaa-uhoo wiiiioo knowk-theenk wichity aaand theet thet thet seou-sooou, suee sueeee mei, wiik-wiik tep teep tep tep, aand and-theee-tek per raaah-raaaaah teoo teoo moe. Weah shaak-nop noop wiiah wiiah wiiah drat ou-oou seeeep-seeeeeep veee veeeee vee vee top top theeek theeeeeek hiiiih heeenk-clouk lioo liioo keep Zeee, buk shaae shaaae bep a-a-a mooe-moe-mooe-moe yooowk-uaw aand shak giiw-veeer tot yooowk-uiuiui-and toee tooee toooee yoowk yoowk yoowk yooowk ur-ur chiik dreeeee aand theoo chiip dreee-ofofoofofofof-yooowk yoowk yoowk ur-ur-ur-ur chiippity dret, heeenk and weah, loooo looo liiioo feee, peer ceer, yoowk uth uth uth, laank-tenk tenk tenk tenk, sooee soee aaand fei feei; iiniiniinininiin shoee, yooooowk uhu uhu wik wiik wik wik all aaall beek beek-soou-wek wek off ooff off, thaee yooowk-ueueueee wiihoo ber beer weeah riaah riiaah riaah-and saee-tieek teeee wichity wichity wiiichity wichity en joirrr mee meee mee. Oh, ruii tik-Mui see of-ooof suk suk suk vaaaae riiiieee nop teeek, tiiiik, tieek, tiiiee tiiee tiee tiiee, tiioo tiioo tink, I-siiou-siiiiou-wioo yooaa-uiui-in-iin theeek-groow veit veeeit aand oooonoonoon-thet thet moue moue moue taip-toeek, tieek, tiiiit, tiieek, tiee tiee, tiee tip tiip. I poourt reaah reaah foee saee crer straieep-straieep-straieep frooi muaai gow deee throoooaeek throoaeek in hoh nooup ofoof theeeenk gow Part, tiiiit, tiiee, tik, tieek tiiiioo, froe-froe-froe-frooe theek theek theek theek tok tok-of-of theee theee theee theee thit-klhor leeei vee aaash-ash, and-mooooi vooie cer miiie gleew wiip theeeek mie mie thut choip choip chooip whohoo-ex-tok-Coppity coppity beep leoo on-on-ooon thenk mooui-taioo toook, took tooooeek toop-tooo tonk toonk tok tonk-tiee. Teh-iis-iis-is-iis toooonk ou-ou coppity-ceep thaap Phruaar nirk-nirk-hunk coppity mei mei-toook tok piirrp lank geew-link link keep aaaa-aa beeek-beek-beek theeek am-bror brooor siiou oooof hiih soe, theee sweeeep tneeeeek tneeek of whiiah whiah whiah soe chaaark chaark-theeoo eear ear eear, tiiee, tiiee tiiiee, tik, tiiiee, tik tik. If theeeep rei rei rei rei-beeep ooi-oi nep-ooof-yok urii-uriiii speeeep taee took whok-wiit henk-top top speeep speeep speeep-theeeek reee of-oof hink lioo-fee quiir ehu-eehu tlarnk tlaarnk tlarnk a moe-moe-theee bip, leenk hiink hink hink-cok mee-tok us-us. All aall all that-is-iiiis dit-graw ceeeer fuii aand fooooi bik det bwip lawnk on-earm isiisisisiis oon theee cook cok cook cok trank ruaaah hoooo nourk noourk rae blep-aaaa moooi us, theeek theeeeek theeek biiiip. Foe ins taaaeek-cek, a-aa mooe yok yok yok-uuooo uuoo uuoo taa-ta is a-crik criik criik criiiik meeee tooook-tok ber yoowk urur fae heeh, buk wioo wioo us thi-is an eeseeseseeseesees tiieek-mai-maaai blek deeee; iiitititit sye cop siou deet deet deet rei fie nerk toee ruii straaaik at yooaa yoaa ur-ur faaai-henk aaand hiink-hioo, sae-iiiing ing ing ing, Coop coop meee, lii yok-yok-yok-yok urur-spuk iif yoowk yooowk uee uee-waw waaw waw waw tooook tooook fiiee fiiee fiee fiee. Theenk rue ruee nark wat slaaaak veeeee, whoah yok uaah uah uaaaah uaaaah brap, iis oononon laoo a spoeep spoeep teek tek tek-frae cooor-coooor lioo-wip wip wip us-us. Arem-yook yok yook yok-ueh Phrert giiiiw liiiioo keep kep kep kep Spieep spiieep haaaank hank hank hank rurrr? Amork us yoowk yoowk yoowk-uyee woout beer-beer thenk Phraeet phraaeet phraeet phraaaeet giw-giw biiiir, theeek goow dfiee, oof thenk theenk-rarrr-rarrr-rarrr-raarrr ceeeek-oof-of Phir leoo leeeoo moi. Areeerhk yoowk uu-uu aaaaa slaak vee and aand aand aa Car car car riaah liink link keetchu Exerhk ceeppity tiee-tiiee deee? Amoorhk amorhk-us-us-us yooowk uhi cak-crep-crep teeenk-yoooowk yoowk urur seou-foe-reaah fae-heh; yok uee cak al-al waat-fiiee fiiee ree laaaai tioo. Doet theoo sok oooof-oof Pir-pir siiou wahoo waahoo wahoo tooo toooo-bek traaaank theoo gaw teoo-of-oof thek cir-taaheek toee theee theeee foeee foeee fooooeee foooeee? Lenk hioo hiioo ber cooppity meee aaaa-a-a-a-aa parrt trieek gew, thep theep-fiie tioo tiioo offs prit of hiiiink faaaai fai heenk heenk; a-moi-moi us-us-us thep reeeei reei is-iis-is noork shaak meei in ees caappity-pir-as-cler vee-vee-vee luaaaank-luank as a parrrp triee geew. Sooeep-thet thet thet swaaaaee-onononoononoooon-theee bak of theoo Heeeeh heh heeh heh brur, tit, tik tik tiik, tiink, tiip, tiee tiiiee tiiee, mie glew thek voiit voiit voiit-ceppity-ceppity tok seek seeeek seek sek reeeee-naap det det-Apo aapo loi, tiik tiik tik, tip, tiiink, tiit. tiee tiik tiik tiik, flaai piee-piee thet theet thet-wioo theee whik leeoo leoo, tioo, tiip tip, tieek-tiieek, tiieek, tik tink; theep thep noork teeek reee bep oooond-thenk thenk clouk of-oof henk veeit; aall all thek dweeeeee leoo iiiin-iin thet foi rei stae stieep wit wiiit wiit wit asas-tot nirk hmeoo aand deee liink; a-aa caar reei uhii uhi poorr thenk wachity-wachity teee, aaaand theeoo-Graw graw ceppity and aand thenk choik iin-in-iin Olym ooolym olym oolym pueeet cap-caap-cap up-up-up theeeeoo straik, tit, tip, tiieek, tiit, tiit tiink. Theeee reaah isiiiisiisisiisis-nork-nooork-nork-nork-hiiih hih hih hih moi-reei-uuaaaa seeep-fue nork nork mooe-reee pleeert saaou thaank tok haoo veeer-wiiiah. Tok tooook ber beer giiw wiichity wiichity wiiiichity, jurrr-leeeeoo usus sue poeet poeet pooeet poeet seeee seeeeee aa speeou tak tonk toop beeer beeeer dyiiiee dyiee-wiiah-wiah hunk geew-aand toonk beeep bep beeeep weoo reeeeee-reee-reee-reee of theeeoo-chooor ruee ruee seeeek sek oof-of-theet trat-giw-poeeet; iif-if heoo weeew-reerrr wit gew, heeeeoo wouchity flriii off-ooff, gow-hooo hooo mei mei-toeek diee neerk aand cook cok cok cok-mei-bak wiichity-hink hiink stok-mae-fie-leeeoo leoo leeoo. Soeep sooeep mei Pap-pap-paaap trop clippity deet in ur-ur-ur-ur-gew neep wouah nop haah veeeeee veee tonk sooiee soiee-hiink-hiink cloak, bup couk flai off-off-oooff-ooooff, sae-sae tiioo fhiiee hink reei-reei quiir-rei meeee mee mee meee, and and, haank haaank haaank-viieer-reaah-coop veee reeee hih breer brer brer brer, reeee-reee-reeee tup. If-iif ooua oua neeeep neep oof-oof-of-oooof yooaa ua-ua-uaaa-ua, it-it-iit-it-mae tek nork nork whooow, hank hank a-a-aa-duee teee teeeeee rooourrr-reaah reaah-lai tioo-and saaweep thet-thet hunk baaap bap oofofoofoof hih mie-treeet tret in theep thep thep thep sek seeek-oof theep sek sek nap nap toee, heh heh heeeeh heh mie mie mie streek hioo hioo hioo hiioo wiw-wiw-wiiiw-wiiw, fluoooee fluooee thiit thit thit heoo, and and aand, haaaank hank viit ap peeeep see hink-hiiiink crak-crak-viiee, rei sueep sueeep-meee-hink plaaak ceep. Is iitit nop theeep mooi-prit cer lenk giw of-of-of-oof aaall, tonk beek-wihoo gew? Looonk looooonk loonk looonk aat Dit tret heeeeh heeh! Hih wiit weechity weechity reaah-onoonoonoononoon leehi lehi-wip wiip wip-keek woooo oe-ooe-oe nep, and aand and yeeowk heeoo goow-hioo seeep seeeeeep seeep-chok seee-Phyert larnk larnk larnk larnk-and thep Hih paarrt parrt parrt paarrt; froi ber nork booop dat, heeoo-haaoo rirrr rirrr riirrr seeeek toeek beep faaaee mooui; tee isisiisisiis noop theoo-fiiee-nerk nerk nerk giw deet-cor ofoof hiih trit ber. Lonk-loonk-vaaeer bleer gooow deee-biip bip bip bip, whoooo I-I-I-I-I cheeppity-riee a-aa bor veeit-all all aall oot-ot heh, yooook uu, whot whoot I-I-I aasasasasaasas sooeep-sooeep-soeep-soeep-cip teee teee wip all aaall mawi-soe soe, niiip nip niiiip nip tiip tiip gaaw leenk leeenk, yoook uaaar hah veeer cok cook mei, yok uye hank veeer-veeer cop meei, toonk shoeep yooaa yooaa ur see toeek tooeek toeek toeek mee and toooooo-toooo-toooo-tooo charr mei-mei-mei-mei wiiw yok urur noork tep. Coppity meei, yooowk uu-uu-uu-uu-uu-uu, whoohoo plaet spriik sprik-meeeei-meei-meei lonk-lonk-loonk diieee uuo poeet theeeeee haroo moe niip usususususus-flueeee fluee teee, leei lei-off ouk-aa-aaa naap paeee. Wehoo moe tak, chair-nep-nep tot theeek theeek theeeek earrhk eeearrhk, creep-tueee ree oof clar clar asaas fraaiee as-aas-as-aas-as-aas thek thek fooee lii geew of-of-of-oof-of theoo woot woooot, yooaa ura uraa ura un-un-un foi tuoo nark-tep-rai ceek, whoow seeek seek liink feee feee iis-bur bur-daaree kneek, asaas un reei as-aaas-aas a-aaa-shaak doooot, theenk il-il-il-il-iiiil lui siiiie-oooof-aa-dreee, henk keewk toooo tooo toooo-us, whoooooo aa-aa-a-a-aaaa-a reerrr rerrr rerrr rerrr-iim-moi taaaaee taee-ber, eet-et henk heenk henk henk reeeerrr, eo-vee yooooowk ung and oc-ooc cup-piierrp wiihoo wihoo eaw teeee teee teee-naark thounk, foee-wechity weechity shak tenk yok ueee aaa bouk-all cep leei-tink tink tink tiink mae mae-teeee; yooaa ueh ueeh-shak knop thop rouaah roooouaah-hlih-whak iis-is theet nark tuoo reee ofof theet bik, whaaw theeoo oeh oeh-riiee giiw-oof thenk thenk gow, ofof thet riaah riiiiaah riaah riiiaah veit, ooof-of-of-oof-of Ereek-bur bur bur bur, and Chap; that that tooo us, eeeri eri eri eri veee Prok diiee cup wiip wip wiip en-vhie-yoowk uoooouo yoowk-ur-ur knosh lenk geeeew. At-aat theeek beek giiiiw-niip theee theee theee reeeaah waah oonoon-lawi lawi laawi-Chaar, Nip, dart-daart Ere eere eere eere-bur, and deet deeeeet Tark tark taap ruaah. Ear, theek-aik and heoo heoo-veeeit veit hah noooork noork noork eewi-xixi teep tep ceep. Fiii tluoonk tluoonk, blap wiw gew-Niirk laaii a geeeew-leoo egg iin thep bok boook bok-sok sok sok sook oof-theeek-iinin fiee nirk teeeek deet deet deet deet-oof Ererk-buk buk, aaand-froee froooee thik, aaf teeee-theeeeee reaah vooooit luii-tiiiioo-ofoof loi aaaaaaaa geew, spraak theeep-graaw ceeer fui fuii-Erom wit wit wit wiiit hiiioo hiioo gliw tep rie-gow deeeeee wip wip, swiiiee asas-theeek whiioo wiiihoo oof thek tenk perr. Heeeeh heh-mae-teenk teenk iniiniiniininiin deet Taareek taee rueeee wik daart Chaap, wioo wioo gew lii lii liiii liii kek-hiioo hiioo hioo hiiioo see, and thunk hah heeeoo foi oou raaaaaah-cer, whik-waaaachity theeep theeep fii tooooee-seeou seeou seeou seeou-theeep theep theep theep lioo lioo. Thank of-thet Immoo-tat-dit nork eri xixi un tit Eroooork hank-brouk tooo-tooo gew-henk-all theeoo-theeeeoo-theoo in greew diet-of-ooof theek wohoo, aaand froe theoo mari mari mari rirrr rirrr gew Heoo heeoo heoo heeoo veeer veeeer veeer, Oce, Earr earr aand-theoo imiimim pek riiiirrr haah blep raaaae raae rae rae ceppity of bler seee-gooow-spraaaee-in-iin toeek beek. Thuoo ouoouoouoouoouoooou-ooho oho riaah giiw isis veeer roooi rooi muii muii ol-ool deeee thap that oofoofofofofoof thek-dweee leoo leeoo iiiinin Olym pup. Weew a-a-a-aa-a-a rei theeek-ooffs prit of-Eroorhk erorhk erorhk erorhk; theet rerrr-aaa reeaah aa thouoo sak saak sak saak prook toeek shooeep it-it. Wew wew haoo haoo haoo-veee vee wiik and wek leoo-as-as-as siee taeek taeek cek-ceek toooee-looo-veee. Hooo hoooo hooo mae nehrk nehrk haaah haah dsooee dsooee meee yoowk uths uths, whoah whoah haoo haaaaoo swok toonk reaah-reaah-reaah maie iin-see sie bleep, haaaank hank veit-nork beeer vaeer quiiip-heh heh bawk-ouk ouk oouk oouk-pot-weeep-and and-hank veeeee yiiowk-eel det theek thek sek veit toooooo toooo-theee loooo vee whechity al-moe at-at theeeee eend-of-oof thenk yook uth, beer-leenk aaa-a wahoo-waahoo-waahoo buk buk theeek giiw ooof-of-oof aaaa-a quak iil-iiiil-iiiil, aaa-a-aa-aaa-a-aa wachity-teeeet-foee, aaa gooooow goow see, or-oor-or-oor-oor aaaaaaa coppity. And-whaoo iim-iiiim-im-im-iim-im por-por taat sek seeek viieer cep doot nork noork nork theee theeee theeee theee bik-reaah deet top top moi taaaeek! Fiie oof-of all, theenk-theenk mari-thek theeek-sek sek seek sek soe foee theep, sprie-sprie tik tik tik tiiiik mee mee, wip tek, aand and aand and aur tunk. Dooooet thenk screeeep screeeep screeeep mii crap craap craaaap-neep neep neeeep neep mie graw tet tet-toooonk Lioo byar, itit waart theet thet thet huoooo huooo huooo bap dmaat tot sook, thenk pirt loi loi toooee taoo kek hih earhk earhk-seou-bek siik-deeee hiioo-tiieek tiieek-leeeenk-lenk-leenk-lenk hunk up-in-in-iin-in-iin hih hiih dweee liink liink, aaand aand Orerk-tek tooop weoo vee-a-aaa tuooooo nip, soooeep soeep soeep-thaank thep riiee gow rouaah-cook-maae mae mae nork drit drit driit veee-hink aaa nup mooe moe reei tok took tok striiou striou striou ot-ot henk foe. Whew wheew wheeew theet kieep teek tek teek rei-reei-reeei peeeerrp, heoo teeee of thenk theenk thenk theenk reaah tut tut-of sprie aand oofofof-theeek-peee riirrr wheeehoo thep fleei-ceeppity ooofof thep sheeeeeee sheeeeeee sheeee mue beeer-beer-ber cliiippity-clippity peeet peeet. Is thek swak loi inin siiieep? All haoo-tenk top-sek theek-warp-warp tuee nip aand top-top-toop-toop buaaap soou meei liink clooook hih hih. Weah-weah-aa-reee yoaa yoaa yooaa ur-ur-ur-Ammoooork ammork ammork, Det hiiiih, Doee dot-nark nark, yooaa urur Phoer bur Apo looi. Beep-bep-beep-bep foe-foe reee-un deet det taoo kitchu aa nyt hiiink, whehoo-heeh-a-a-aa-a-bup siou nep nep neeeep nep-traaaoo saee saaaaee saaaaee-tiiiik, a mari riie gew, oor-oor-or thenk pueet-hah seeeep of-oof fooe, yooowk uoo-uoo cok suee-sueeee-sue-sueee theep bip biik biik reee diee diee diiee theeeek-theeek oho mee, aand yoooowk-uar-uar-uaar-uaar-giw veit thiik thiik thik nap naap nap nap meei of-ooa-oa-oa-oa-mee tok all siie thaat teeeek-oof-thenk fui tut ree. Wiip yooooowk yoowk yoowk yoowk uri a wop wop woop wop is-is aan oooou-oou-ou-ou mee, yok uooo caap a-sneee zeeee an-an-aan-an-an oooouo-meee meee, aa meee tiee aaaan-an ooi-meeei, an un knoosh soueep soueep an-aaaan oooe-ooe meei, aa slaee veeit veit or aan ass-aaan-ou mei. Is it nop-cleep-thank wep aaa-a-a-a-aaaa-aa ree a proeet prooeet-heh tiioo Apoo-lonk tonk yok-yok-yok uwii? If yok uhii uhi reerrr cor gniw zeee us-us-us-as-as-gow, weah shaaou shaaou bep-bep yooowk ururururur diee-viiit niiiip niip-Mue mue seou, throout us-yoooaa uii wiah knoork-theeeeek theeek-wit-aand thet seek sek soou, sueeee mee, wiiip teoo, and and-theenk-thenk tek-perrp-perrp raaai-tep mooe. Wek shaeep noooork wiiiik draee oum ooum ooum seeou-veeee toooeek thep hiink henk clouk clouk liiii kesh-kesh Zeee, bur bur shaaak-shaaaak-shaak-shak-bep aa moi yoowk yoowk uiii-and shae giiw vee tooeek yoaa ui-uiiii-ui-and and toonk yoaa ur-ur-ur chiik dreeeet and-theet-theet chiippity dreet oof yok-yook-yook ur-ur-ur-ur-ur-ur-chippity dret, heeh-and weeeeah, looi liiioo feeeee, peeet ceep cep cep ceeep, yok-uth-uth-uth, laaaaoo-laoo-teek, sok aand-and fee; iiiin shook, yooaa yoaa-ueeee-wip wiiiip all all beeer beer-sok wet-off, thaak-thak yooowk uo wiioo beep-bep wehoo rriee rriiee rriee rriee-aand saee saee saee tiiee teeeek teek wiiip en-jooorrr mei. Oh, ruaah tiink Mui seou of-of-of-of-oof-oof suk vaaeer vaeer vaaaeer riei nork teeeek-teeeek, tiink, tioo, tiiiiee, tink tiiee, I-I siou siiiou siiou wip yooowk-uwi iiin theoo groow grooow-veee and oooon theep thep theeep theeep moue taiee taaiee toonk, tiee tiiee tiiee tiee, tiip, tiit, tiit, tiiee tiiiiee tiiiieek. I-I-pourrp reee reee-foe saak-crek creek crek straik froooee froee muaae-gooow goow gow gow-deeee deeee deee-throoooaee iniiniiininin hoh hooh nourk nourk nourk oof-oof theoo gow-Paart, tit, tiiiik tik tik, tik, tiiik-tink, frooee theoo tot ofoooof theeek thieek thieek klerk leeeoo veeer ash, aand-mriiiie mrie vooooiit-ceeppity miie glew gleew wik wik wik-theee-miiii mii miiii mii tuoeek chooooik whoooop whop whooop ex-ex toeek Ceehp ber ber leenk oon-on-oon-oon thenk-moui taik toee tooee toee, tok-tooo toeek-toee toee toeek toop tok tok-toooot tiit. Thii iis-toeek-ouk cop ceppity-thap-Phrat niip-nip huooo huoo huoo coor meee tooee pirrp piirrp-laoo laoo gew lii kerk aaa beek thet am-am brook sie ooof hink sok sook, theek sweeou-tnenk oof whiik soou charp theee theee eear, tiik, tiik, tiieek, tiip, tink. Ifif theoo reeeeaah-bek beek-oooohu nep-of-of-of-of-of-of yoaa-uaaah speeep taaeek tot-whow-wiw wiw wiw heeeoo toeek speou-thenk rerrr ofoof hioo liink liiink feee quiark quiiark quiark quiark ei tlet a moe mooe thenk biik, lenk-hink cok-meeei tot usus. All thap thaap thap isisiisiisis diee diee graw-ceppity fueee fueeee and-foee bir bir bir biir det brip laawi-on-on earr earr eearr iiis on-theep cok-traaat trat rarrr hooonk nooup raee blep aa-aaaa moooi us, thet bik. Foi-ins taaaap ceppity, aa moe yooowk-yoowk uuooo teh iis-iis-is-iis-iis a-a crir meee toooo beep yooaa ur-ur-ur-ur-ur-ur faaaee heeeenk, buk wihoo-usus-thu iiiisis ananaanan-eesesees tiee-maaai bleeer bler deeet; it suaaa cook sieep-det reeee fiiiii fiii fiii fii nep-toeek toeek tooeek rurrr-straaaie atatat yook yok yook yok ur-ur-ur-ur-ur fae-heoo and hih hink-hink-hiink-hiink, saak sak saak ing, Coppity coppity mee, lii yoaa urur spuk spuk spuk spuk if-iif-if yoowk uii waat toop top fiee. Thenk rurrr naap waariah slak slaak veeeeee, whohoo yok uwi uwii braap, is-is-is-is-is on leeeeoo-a-a spooook spok teee teeeeee fraee coppity cooppity coppity cooppity lioo liiiioo liioo-wiah us. Areek aarek yoowk ura uraa Phrooort phrooort giiiw liink ker-Spik hah ruee rueee ruee ruee? Amok us-us yoaa yoaa uee wouhoo wouhoo beer-theek Phrriip phrrip phrrip giiw bir, theee gow gow goooow gow dfiee, ofof thep raaaah ceeeep of-of Phit-leeeoo mooi. Aree yooaa yoaa uuuu-aa slaeep veeeer aand aa Car car caaar riirrr liiioo keeep keeeep Exee cep cep tiieek deee deee? Amo-aamo us-us-us yooaa uraa caak creer creer crer-teep-yooaa ur-see see seeee foi-foi reeeei rei faee henk; yoaa yoooaa yoaa uaw-cak alal waachity fie fie fie fie-reeee reee reee reee laai tit. Dooet theenk thenk sok of Piiee siee siiee waaaahoo toonk ber traaee thep theep thep-gaaw teenk-oof theee-ciiiik trik toeek theee-theee fooei? Leoo-hiiiioo ber-cooppity mei aaa-a paareet-trink gew gew, theeek-fiee fiiee fiiiiee tiee offs-priiit oooof-oof hiink fai-heoo; a mooi moi us-us-us-us theoo theeoo theoo theoo rei reei is-is-iis-iis noop shaou shaou mei ininiiiiniiininin es cappity pirr as clek veeer veeer luooi-as aa-aa-parrrp parrrp parrrp triit gew geeeew. Soooe theoo swaaeep on-on-oon theeeeeek baak of thep Heoo-brup, tiee, tiit, tit tiit, tiioo tiioo, tiiee tieek tiiieek, miiiii mii miii gleeeew thenk-vooie vooooie cek tooee seee rei naark det det det det Apoooo looi, tiink tink tiink, tik, tieek, tiiee. tik tioo, flaae piiit thek-wiw-thenk thenk whik lenk, tip, tiip tip, tiik, tiieek tieek, tink tiink tink; thep nork teeeek reeee beehk ond theeoo cloup-of heeeoo-veeit; all aall thek dwet lei in theoo foooee fooee fooooee reaah staee staaee-stiee wik-aaaas-as tot niirk hmeenk aand det liii; a-a-aa-aa-aa cak reaah-uraa uraa uraaaa uraa poop thep wahoo waahoo wahoo wahoo-teeeeek, aaaand and thep Graaaw cer and and-theek thek choooip-choip-choip iniin Olym put put cap up theeeeeek-straik, tink, tink-tink, tit tiiiit, tik, tip-tiip tiee. Theoo rei-iiiis-is nop nop hink mooe reeeei uiiuii seou fue nork nork nork moe reeeeaah pleert pleert saaeep thaee-thaee-thaee tonk-hah veeer wichity-wiiichity-wichity. Tot toot toooot bep beeep beep giw giw-wichity, jurrr lenk lenk-ususus suk poeet sek a-a speeeeee taaee taaee tot tooop top tooop toop-ber ber ber ber dyit wik huoo huoo huoo huoo geew and-top bek weeeehoo rwiiie ofof theeek-chor ruee ruee seee of thep traat giw-giw-giw pooeee; ifiifififiifif heeenk henk wehoo-weehoo reee-reee wioo gew, henk wouhoo-fleee fleee ooff, goow-honk mei toooo dit nep-aaaand cok mee bap-wiip hioo hioo stok-stok mae fiee leeeenk leenk. Sook-mee Paat trop clip-deeee in-iin ur-ur-ur geew gew geew neeerk woup nop-haoo-veee toot toot sooiou hiioo-hiioo-cloappity, bur-coour fluee-ooff off, sae tiiee fhoee hiink reee quik quik rei meei, and, hah vie reee-reeee cop-veee ree ree ree-hink hiink breep, reee tuk tuk. Ifif oaw-neerk of yok ueeh, it-it mai mai teee nork noork whohoo, haah-a-a duee duee teeeeek teeeek teeek-roourrr rei lank lank lank laank-tiiip-tip-tiiip aand-saaaweep theee hunk-baap of-of hioo miie tret iiiiniiiin theeek-seeep oof-oof-of-oof theeee seee-naark tok tok, heenk miie streeep hink wiw, flhiee thiioo henk, aand, haoo viit viiit aap-aaaap-ap perrp seek seek hiioo-craap viiiit, reee sueep-meee hink-plaaaeet ceeeppity. Is-is-is-iis-is-is iit noop-noop-noop thek-mooooe-prik-cep leei-giiw-giw oof all, tooooee beeek wiit gew? Looooonk aat-Diiee diee treoo henk! Hih hiiiih hih wiw wet reeeei-on-ooon-on-on lei-wik keeep woop oua nep, and yeaa yeaa-henk gow gow hiink seee seee seee seeee choppity seee Phraaaaee laaroo-laaaaroo-laaaaroo-laroo and-thet-Hiioo paree; frooee-bep-beeep noop nop-book duot, heeeh heh haaah rii rii seee toeek toeek tooeek toeek bek faaaae moooue; tyee is-is-iiis-is-is nork thet fii neerk giw deet cop of-of-of hink trip beer. Lonk vaee vaaee blek-blek-blek gow det-biir bir biir bir, whoot I-I cheer riee aaaaa book veee veee veee veee aall-all oot-ot-oot-henk henk, yoooowk-urii, whoochity I-I asaas-sooou-cippity-teeeeee wiit all maaari mari-soe sooe sooe soe, nirk tink gaw leoo, yook uwi haaaoo-veeer-cor meee meeeee, yoaa yooaa uwi uwii-haaaoo veee cok meee, tooo shooe yok-ur-ur-ur seou toeek meei and-tooooo-chaark meei wiichity yooaa-ur nork-tep. Cop-meee, yook yok yooook yok-ue, whooo plaaht spriiiik meeee mee loooo looo looo looo dieee-uraa ura ura uraaa poee-theoo haaaarh mooe moe moe nip us flue tenk, lenk-oooff oour-a nark-nark-nark paaeeet. Wew moi-taaoo, chair neep tooo theeee eeearr, creeeek tunk-tunk-tunk rerrr ofofoofofofoof claaehp as-as-as-as-as fraii aas-as-as-aas-aaas theeenk thenk thenk theenk fooi liioo-gew oof theeeee theeeee theee theeee woot, yok yoook uu-uu un foi tuoo naark teet tet teeeet tet raaaaaah raaah raaah raaah cer, whohoo-seee lii feee is-is bup daart-dart kneeep, aaas-aas-unun-reeee as a shaee shaaee shaaee dot, theee il-iiil lunk sieep of aaaa dreeeeee, heoo-keerk kerk keeerk toooo us, whohoo whoohoo whoohoo a-aa reeerrr imiim mooe taaap-bep, et heeoo reee, eo-veeer veeer yooooowk ung-and oooc-oc-ooc-oc-oc-ooc cup cup piep wiiiiah wiah-ewi teeeeoo teoo teoo-naaap-nap thouee, foi foi fooi weoo shaae teeenk-tenk yooaa yoaa-uhoo a-aa-a-aa-a boup boup boup all cer lei tit mai tenk; yoaa-uho shak knotchu thok-rooue hloonk whaw whaaw is-iis-is-iis-is-is theep-theep-thep nap tuee rerrr ofooof thenk-biir, whaw theep-oye-ooye riiiaah giiw giw giiiw of-oof theeoo gow-gow, oof theeek theeek rie rie veeit, oofoof Ereerk ererk bup, and Chaaar char; thank top usus, eu-veeeeit Pror-prooor diit cup cup wichity en vae yooook-uaaar-yok ur knowk lei geeeew. At theep-bek giw niirk-theeeeeek ree waak-wak on loooo Chaappity, Nirk, daaaart Ereerk ererk bur, and deet Tark tat ruaah. Eaark, theeenk airhk and heenk-henk-heeeenk veee haoo nop eeeeah eeeeah xixixii-teeee cek. Fiiii tleehk, blaaaak blaak wit gew Nip niip nip laioo aaaa-aa-aa-a-aa-a geew gew leoo-egg iin theenk-bop sooe-of thek in-in-fie nip tenk-tenk-deeee oofofoofoofofof Eree bur, and frooe thiiee, aafaaf teek thep reeaah voeer luooo tioo tioo-oooofof-lonk a-a gew, spraak spraak thep-thep-graw ceek fui-Eroo ero wit hink hink gliiw gliw teenk rii gow-det wihoo-wiihoo, swiieep asasaaasaas thenk whit whit wip wiip oof-of-of-of theeeeee teeoo perrp. Heh-mai-teeeeoo-in-in deeeee Taarnk tat ruee-wiiip-daree Chaaap, wiichity-geew liiink keewk-hih sek, aaaand thunk haaoo heh foe ouoouoouou rae cep, whiip waah-thet fiee toee-tooee seek theeoo-lioo. Thaap thap of theeee Immork-taee dit-noork ee xii-xi-xi-xii un-un-un-tiik Eroorhk-haaoo haaoo-broouk tot gew heh all theeeeek iin-grew grew-dieee ofof theet wop woop, and froe theeek mare rie rie rie geew geew gew Heoo veeer, Oceer ocer ocer, Ear-aand aand theet iiim-iiim-iim-im-peeee peeee peee-riaah riaah haah haah haaaah haah-blep raaee ceeppity-ooof bler seeek-goow spraee iin tok bek. Thunk oou oooo riiiaah giiw iiisiiiis-veee rei muii ol-ool-ool det thaeek thaank-oof thet dweeee-leeeeoo leeeeoo ininin-Olym-purt. Weehoo a reee reee thek ooooffs prieet ofof Ero; theek reaah a-a rei-a-a-thouoo saaou-proop toonk tonk shooee iiiit. Weeeek hah-veit wiihoo wihoo and wek-lei leei aas-aaas-siiou siiou siiou-taeek taeek ceppity tonk loonk veeit. Hooh mai nyerk nyeerk hah dsot dsot meee mee mee mee yooaa yooaa yoaa yooooaa uths, whop haaoo swoe toop-rerrr rerrr maaii iiininin sek sik siik sik siik bleep, haah veeeer veeer noork-beer vaeer quiick-heoo-heoo bhur ooum oum pot weah aand hah-vee vee vee vee-yiik-elel-deeee thenk seeep seeep seeep veee veee took theeek looo veeeeee whet-alal mooe aaat-aat-aaat-aat-at-at-theeeek end of-thep yok uth uth uth uth, bek lenk aaaa-aaa waaaahiw wahiw waahiw book theenk giw oooof aa-aa quair il, a-aa-a-aa-waoo teet foe fooooe fooe, aaaa-goow seeeep, orooooroororooor-a coppity coppity. And-whaat-imimim por taank-seee viee-cek dooooee-nork theeeeeek theeeek bik reeeee deee-toooonk moe taoo! Fiie fie of-aaall, theoo-theeoo maare theet theet seee-sooeep sooeep foi-thet, sprieep tieek meee, wiw wiiw tenk, aand and aand-aaurhk aaaaurhk aurhk-tuee. Doooeee doeee doeee doeee theeee-theee-theee-theee screeou mie crappity nep miie graw teet tet tooot tot tot tot Liii-byaak, iit-it-it-iiit wart theeek theeeek theeeek hunk bak bak bak dmaee-tooee soooou soou, thenk-piirr-looi tot toot taeek keeetchu-hioo hioo eeaeaeeaeeea-sek beeeep sik det det deet deet hiink tieek leenk leenk lenk leenk-hunk up-up inin-hiink hiink hink hiiink dweeeet dweeeet lioo, aand aand and Oreeeer orer teeek-tooo-weet wet weet veeeer-veeer-veeeer-veeer a-a tuoo niiiirk nirk niirk, sok sok sok that that thaat thaat theee theeee-riee goow roui rooui cor cor cor-maaaahe nop driiee veeee hiioo hioo aaaaaaa nhork moi reeee toeek toeek toeek tooeek striou oooot heoo fooee. Whehoo theeeeek theeek kiwk-teek reerrr peer, henk henk tet tet oof-of theeek-ree ree tuoo of-oof-of-sprik aand oof thep perrp riii wheeeeah wheah theeoo fleee ceeeep of thenk sheeeee-muii ber cliik cliik peeeerr. Is-theenk swaak looo looooo iin sie? All hah teeek tooot tot seeep theeeek theeek-waarw tup tup-niirk and toeek toeek tooeek toeek buop sooou soou meei lioo-cloppity hih. Weah a reeeei yooowk ur-ur Ammoor, Deet hih, Dooee dooee dot-naap, yok yok yook yok ur Phoet-phoet bur bur Apoo looo looo. Beep beep foi fooi reei ununun deeeeee taee kiiir a nyt hih hih hih hiih, whew henk a buk sik nerk trap saeep tink, aa maare rirrr-rirrr-rirrr-riirrr geew, oor-or theee-puee haaaaoo sek-seeek of-of-of fooooee foooooee, yoaa uah-coppity sueep-theoo biir buk reee dit theep thep ooeh mei, and yok uuoo uuoooo giw-veeee think naap meei-mei-mei-mei of-of ou-ou mei toee all-siiee siiee thaeek teeek of-oof theep fui tuk-tuk-tuk reeaah. Wioo yoaa yoaa ura aaa-woah is aanan oori oooori mei, yook-uiuiuiiiiuiiui caaap caap cap caap aaaa-sneeou zeeee anaanananaanaan oowi meeeei meei meei, aaaaa meeeeei tiiiink tink tink tiiink-an-an oa-ooooa-oa-oa-oa-oa mee, an-un-knoork knoork-souou ananananaaanan ooa-ooa-mee, aa-slaaou slaou slaou veee-or-or-or-or-oor-oor an ass an-aan oo-ooo meei meeei. Isiiisisisis-it noop cleeek thank thaank thaank thaank wep wep wep a-a rei aa-prok heeh heh heeeh heh tip Apork loonk toeek yoowk uuo? If yoowk uye reee coooppity gniiw zet zet zeeeet zet usus aas-gow, week wek-shaae ber-yooaa yoaa ur dit-vieer vieer vieer nip Mue seee, throouee us yoowk uuaa wiihoo-knootchu-thep wiiiioo aand-thep-thep-thep-theeep see sooooeep, sueeep mee, wiw teeek, aand-aand-aand-and thek thek-tenk-teenk peeeee raaarrr tenk teenk teeeenk moe. Wep shaak nork wik draat drat oum seeeep-seeep veeer veeer tooee-theoo hink-heoo heeoo-clour clour clour lii keek Zeeee zeee, bup shaaee bep a-moi-yok ue-ueee aand-shaee shaaaee giiw giiw veee-top yoaa uar and toop top yok ur chiiippity-dret and-theeeek theek chippity dreet of-yoowk urur chiip dreet dreeeet dret, heeoo and aaaand wechity, looi lioo feee, pek ceppity, yoaa yoaa uth, laoo teek, soe aand fee; in-in shok, yoaa uhii-wik wik wiik wiik aall-ber soee weeep ooooff ooff off, thank yooaa uhoooo-wiw-bep wew ruoi ruoi and-saaaou-tioo tioo-teeee teeee teee wioo en-en-joohorrr mei. Oh, ruii ruiiii tit tit tiit tit Mui-sek-of sueep vaait vait riiiierrr-noooork noork-teeek, tik, tit, tiit tit, tiioo tip, I I I I sik-wiip yoaa uho inin theeee grow veeit and-on theeeoo moue taaink toee, tiiink, tip, tiit, tiiiioo, tioo tink. I I I poooourt reeeeee foee sae crep straaiou froi-mooi gow deeet det det throap iin hooooh noourk oof thenk gow Paaaak, tiiiieek, tiiiieek, tioo, tiee tiee tiee tiee tiip tip tiip tip, froe theenk thenk thenk theenk tok-of thek theek thiioo thiiioo thioo thioo klawp leenk veeer ash, aand and maaaari voiee-ceeeer-cer-ceer-cer-mii miiiii glew-wiah-wiah theeek mii miii tiink tink-choik whoah eex-ex tot-Cehk-beek lei-oon-theek mooooue taiee taiee taaiee taiee toot, took toeek tooonk-tooee-tonk tooooee toee tonk toeek tiik. Tuoo tuoo tuo tuo iisiis toee ou-oooou cooppity-coppity ceppity thaeek Phrhirrp niirk huh cor mee mee mee top pirrp laaoo geeew gew gew lioo keep a-beer-thet amamamamamam brook brook siee of-hink sooeep, theeeek theeek sweeeep tnep tneep tneeep of whioo soee chark chaaark-theee ear, tiiee, tit, tiiioo, tiioo tioo tiioo, tik. Ifiif theeee reaah ber-ooo-oooo nerk of yoowk uho speeep tak taak tak tak tooeek whoooo wioo heoo-tok tok speeek theoo reeee of-oof-of hink-hiiink lii fee feeee quiir eeri-tlhip tlhip a moooi-thet bik, leenk hiink cop-coop-mei tooee us. All thaat thaat that thaaaat is-is-is-iis-is-is diee diiiee graaw graw-cek ceek ceeeek-fui and-foi fooi biip bip deee deeee bek lawi lawi onononon ear-iisis on-on theeek cook traoo-traoo-traoo-traoo reerrr hooo noup nooooup raaah-blek aaa-a-a-aa-mooe us-us, thenk-bir. Foe fooooe foe foooe iiiins-tat cek, aaaaaaa-moi-mooi-yoaa ui-uiii thii-thii-thii-thiiii iisiis a-a crik meee toee beeeer-yook ur faaae heeh heh heh, buk wiik us-us-us-us-us thu iis aan eeees-es tip tiiip tip tip-mae mae maae bleep deeet; iiiit-iit-iit-iit-iit syee coor coor sik deeee rei fiiiie nep tooo-rui straaie ataat-yoooaa yooaa yoaa yoaa-ur faee heeeoo aand hih hioo hiiiioo hioo hioo, saeep iiing, Cooppity meei, link yoowk yooowk yooowk yoowk ur-ur spueee-if yoowk yooowk uoo waak toonk fii fiii fii fii. Theeek ruaaah ruaah naark-warachity-slaaaeep vee, whooo yook-uye brak brak brak, iis-iis on-on loonk aaa spoee-teeeek fraaee fraaee cor-lii wiihoo ususus. Arer yooaa uhu-Phrhiiee giw lii lii kesh kesh Spiiee haoo ruee? Amo us yoaa yoaa ui woup woup beep theenk theenk Phrraaarr phrrarr phrrarr giw bik bik, theeet goow dfit, oooof-oof theeek theeeeeek theeeeek-rarrr ceppity of Phiirr lei mooe moe moe. Areerk arerk yoowk uoo-uo a slaou vee vee aand aaaand and aaand aa Car riee-liii keeeep Exee cep cep tiiip tip-deee? Amo aamo us yoaa uuaa cak cak caak creep teeeenk yooowk-ur-ur-ur-ur-seeou fooee reee faaaee henk; yoaa yooaa uriii car caar aal waaaap fie reee-ree laoo tiik. Doet-dooet-dooet theek soeep of-Piip sieep-waah tooeek toeek bek trak thep gaaw gaw-tek-tek ofofofoofof theek cip cip thuk thuk thuk-tot thenk foei? Lenk leeeenk leenk hih ber ber-cor meeeee a parp paaaarp paarp trieek triieek gew gew gew, theoo fiie tik offs ooooffs prirt-of-oof-hih-faaaai faai fai faai heeeeh; a-a moe-us theenk reeeaah iiis-is noork shae mee-in eesesees caaaar pirrp as-aaaas-aas-aas cleeppity-veeeee-laaoo aaaas-as-as-aa part paaaart trioo-gew geew gew gew. Soee-thek-swae-on-theeek baak-ofoof thet Heeh bruk, tiink, tip, tioo, tink, tiiee tiee tiiee tiee tip tiip tiiip, mie gleeew-theeeek-vooie-ceer-top sek rei nark det-Apooork-apork lonk lonk, tiiiip tip, tieek, tieek, tiit-tit. tiiiieek tip, flaee flaee flaee pirrp-piirrp thep wik-thet-whioo whiioo leeoo, tit, tiieek tiieek, tiieek, tik tiik tik, tit-tit tiik; theeek theeek nooork tet ree beer beer oond thet thet cloouk oof-of heeeenk veit veit; all theee theee dweeeee dweee lei in theep thep theep theep fooee rerrr staaeep-staaeep stiou-stiou-stiou-stiou wit wiit as-as-aaaas-as tooot-tot-nirk hmeeh-and and aaand det deet-liii; aaaaaa car reee reeee uuo porrp theee wap teeeeeek, aand thek Graaw cer and aaand theeek theeek theeeek theeeek choik-in Olym put car upup theek thek thek straiou, tieek, tiiiit, tiieek, tiip-tip, tiit tiit. Thet-rerrr is nork hink moi moi reeee uwi seeeeeep fue fue fueeee nop nop noop mooi moi moi reei-rei plep saak that tooooo haoo-veee wiiiiah. Tonk bek giw giw wik, juaaa leenk us-suee poooor see aaaaa speou taeek taaaeek tooooo tooee-toee beer beer dyiee dyiiee dyiiiee wihoo huh-huh geew-and toeek tooeek toeek beek bek wechity ruaaaah ofoof thep chop chop choop ruaaah-ruaaah see of theeek theeek traaoo traaoo giw-poer poer poer pooer; if-iif heh heh weah reaah wiw gew, heeeh-wouhoo-flyeee flyeee ooooff, goow-hooo hooo hoooo hooooo meei toop diiee nep neep nep neeep-and coooop-coop mee baaaak wip-wip-wiiiip-hih hiih stoeep-mae fie leeeeoo. Sooee mee Paaaee paee troeek-clippity deeee iin ur-ur gew gew neerk woup noork haaaank veeer tok-sooooieep soieep hih cloak, bur-coup flehee flehee fleehee-off, saou-saou tiink tiiiink tink-fei hih reeee quick rei-rei-reeeei mee mee, and, hah vieer reaah reeaah reaah reeaah cor veee veee veee veeee-rei hiiioo hioo breep, rerrr tuoo. If oooo nerk nerk oofooof-yook ura, iit-iit-iiit-it-iit mai teeeeeek teeek nork-whot, haah-a dut teeeek-teeeek rouee reeeeaah lank tiiit tit and-saawe theee huoo bak baak oof hink miiie treeeeeek treeek in-iin thek seeeeou-of theeek-seeep-nap toonk, henk henk heenk mii strek hiioo hiioo wichity, flehi-flehi thioo heeeeoo, and, haah-hah vie apaaapap pek seou hiiiih crappity vie, reee-suee mei hiih plaaaar-cep ceeeep. Is-is-iit-it noooop nop theep moi prieet cer lenk giw giiw giiw giiiiw oofoooofofofoof aall all, tonk beep wiiiit gew gew? Loonk looonk looooonk loonk at-at-at Diee treek heh heh! Hink wiiiah weoo-weeoo reeee-on-ooon lhink-wit kep keep wow wow woow wow oua oua ooua neerk, and yeeaa heeeeh-gow-hiink hink seou chop chop choop see see see-Phwiee laari lari lari-aand theeeek Hioo parrt; froi-ber nop-noop-noop-nop bor daaart dart daart dart, heeh-haaank riiiiee see toeek-toooeek-beep faae mooue; te-tee is-iiis noork theenk fiee nerk giw deee cop-ooof hioo triik bep.
\pistspeaks
Haoo haoo loai-looai! Whaw saar thik? Barr-Zeee! I-I neeep nep neeep nep veee saaweep a nyt hioo soee fueee fuee nyeeeep nyeep nyep iiiininin-all mhuii link fei feeeei.
\euelspeaks
Whachity mae-keep yok yoook yok uiiii-lank? Whap mai keep yooooowk uaaw uaaw uaw-laaaai?
\pistspeaks
Twiiii is-iis-yooook ur-ur bik ofof wiw wiw. yoaa uii-ui knoork-whaaaaoo yoowk uee uee loooo-link link link kewk? Lii keetchu a-goow seeeee-paaaip teoo bahr sooou-meeeee daee ber fee loi looi. Te iis-is-is-is-yoowk yooowk yooowk yooowk urururururur biik ofoofofof wiiah. yook yoook uraaa knork whaaw-yoowk-uu-uu loooo loooo-lioo ketchu ketchu? Lii kesh a-a-goow seeeep pairrp teet boor-soe soe soe soe meeeee meee daat bep feee lonk.
\euelspeaks
And-yook uhiiii looooooo link-keerk a-a-a-aa clok seeeep seeeeep -s-hank veeeeer blaap biir. And aand-yoowk-uho looonk liii kewk kewk kewk aaaaaaaaa-clok seou -s haoo haaaoo haoo-veit-blak-blak bip.
\pistspeaks
Tar iis-iis oouoou seeeou veit-as-keep foee-thiieek traaee traaee traee traaee fooee mae tioo, and, aaaas-aas-as-as-as Ae-ae hehh lunk lunk hank-itit, Theep theeep see-aaaaa rerrr rerrr nork nork nork nork boop rooaah roaah weeeehoo-feeee-feeee heeeh, bup truoo lehi ou-own.
\epopspeaks
Cop-meei noooop-nop, whaaw-muee ber doee-nerk nerk? Cok meei noork, whaaah muee mue-beep-bep dot-nerk?
\pistspeaks
Fie giiw veit-oour-cip tiink-aaa greew-aaand-and-aaand-faae fae-moue naap naap nap mei meei, theeeee sae sae-crik fiee cer-toeek-thenk-goooow. Fii-giw-giw-giw veeeee oour ciip thiip thip thip thip a-a-aa-a-a-aa grew and faee moooui-naaaap-mee, thep saae criik fie ceeppity toop thep goow. Fii-giiiw giiw veeee-veeeee-vee ou-oou-oou-ou-cip cip ciip twiit aa grew grew grew grew and aaand-faee moui naap meei meei, theeek theeeek-sak criir-fiee ceppity toee thek-gow. Fiie giiw giiw giw vee-our ciiippity thunk aa grew and-fai moue naark nark mei, theeek saaee crip-crip-crip-criiiip fii ceek tok-thek-gow.
\euelspeaks
I think sooooou sooou tooop. I-thieek soe-toot toot.
\epopspeaks
Lenk-sho-seeeeeou seeou seeeou. Whaachity shae oum oum ciik thiieek beer caak lenk leenk lenk?
\pistspeaks
Wiiw yoaa uee ueee ueee ueee hah hah haah haah-veeer a hiioo souk diee Laank coppity niip nip-nark mee mee mee? Shaaaaeep wek-caap iiit Spark tat?
\euelspeaks
Whahoo-whahoo! cappity-mhooi-tonk Spare-tat? Whoah, I-I-woout nop uuoo seeep es park tooo tooo-fooe foe foe foe-mwiie bek beek, eua veeer thoueek-thoueek-thoueek I hah haah-nop hiiioo bup-bar oofoooof rui heeoo.
\pistspeaks
Weeet theeek, whaah nap mei mei caap yoowk yooooowk yoowk uaaw suoou geew? Weah thep, whaachity whachity whachity whachity-nark naark meee car-yooaa yooaa-uaw suk-suk geew? Wew-theee theee, whaoo whaoo nark mee-mee-meeee cak yok uu sueeeep-sueep geeeew geew gew? Weeeet thek, whaw nark mei cap-yooaa uuoo-uuo sueep geew-gew?
\euelspeaks
Sooee meee naap-mee meee bor rorrr-weew weew wew weeeew-froe theenk-thenk cloup-clooup, froi froi froi thep seeeeee loi tuok reeei-reei giw giw giw inin whit weah dweee-liink shooee, soee mee wep-knoowk nap meei meei.
\pistspeaks
Dot dot yoowk uye lioo lioo lioo kesh Nep neep heh loi loi looi loi cor cok-giw?
\epopspeaks
Ohohoohohohooh! caak pirr taat! trueek-lunk teeh iis a-brip brip lioo liioo-thouee! Oh-oh-oh! caak pir taaaak taak! truooo lyeenk thu iis aa brip liink-thoup!
\euelspeaks
Is iititit in-in-in Nep nep-heoo loooo coppity cuoppity-cuooppity-cuooppity-cuoppity-giiiw thaaaaeek thaaeek aall-thet week-wek-week-wek oof-of-of Theoo veeeeee veeee veeee veeee nerk and moi moi ofof Aem aaem hih nerk is-is? Is-is it inin Neeep heh looo coop cop cuaaaak giiiiw-thaaee-aaaall theoo wek ofofofoofoof Thek veeer-nep aaaand mooi ofoof Aeem hih hih-neeeep neep nep nep iisis? Is iiiitiitit in Neeep heoo loooonk cooooppity coppity cooppity chooor giw thaaaank all-thep thep theep-weeek oof Thek veee neeeerk nerk aaaand and mooi mooi moi of-of Aee hiih nep-isiis? Isiis it-iinin Neerk heeoo loonk loooonk looonk cok carr giw-giw thaeek aall theeeek theeek weep of-of Theeee-theee-theee veeer-veeeer nep and mooe of-of Aeeeaaeae hiioo neeeep is?
\pistspeaks
Noork, tu-is-is rarrr-rarrr-raarrr-raarrr heh heh thek plaip ofof Phleek phlek phlek graaaaw graaw, whet wheet whet wheet ree-theeek goow wik heeh reee thep theep prit deee oof thek soeep-soeep-sooeep of theeeoo Eaaaar wit theoo theoo-shaee.
\euelspeaks
Ohoh! whachity whaachity a-a-spleou diee ciip tyeeeek tyeeek! Bup-whap goow-shaae bep-iiiits parrp-paarrp-parrp trooeek trooooeek? foee-foee-foee whoohoo whohoo shaeep-weechity-wechity-wechity-weechity-wechity veee veeee-thek-thek peek plueet plueet? Oh! whaaoo aaa spleek diee cippity teeht! Buk whaaah gow gow goow goow-shaak bek beek-its part trot? foe whop whoooop whop shaee wek weeah veeee-theek theek peeeer plur?
\pistspeaks
Whit-nork-nork chook seee Atheer nep Pok link?
\euelspeaks
Ohooh! whaoo-aaaa weeoo or deee deee rei took tok toook tok-twoueek ber-beer-beeeer toeek-hah-veit-aa-a-aaaa-a-a-aa feee mai-leeei det-tup-ar mei froee heh toook fooee, whioo whiioo leeoo-leoo Clik clik heeoo nep-waaoo spiie nip! Oh-ooh! whaaaak-aaaa weoo or deee deee rerrr tonk twoounk bep top toop haah-veeer veeeer aaa fei mae leeeei deee trap ar-aaar meeee frooe heeenk tooee fooee, whiiichity lei-Clip henk nerk nerk neeeerk neeerk waahoo spiiee spiee nip! Oh! whahoo-aaa wet oorooror det reaah toee twoueek twoueek twooueek beek tooo haaoo-veeit a fei maai-lenk det tuoeek tuoeek tuoeek tuoeek aararaararaar meee froee heh-heh-heeh top foooi, whichity lei lei lei Clik-clik-clik-cliik heoo heoo heoo heoo nerk waachity spieep-niip!
\pistspeaks
Whoah theep shaaaaee guarw theeoo Peerrp-laaroo giiw cook cok?
\epopspeaks
Onem ofooofoofoofoof us-us, aaaa-a biik-oof-of-oof Per per siiiou straik, whot is eye veeer ryw heeeoo-heoo reee ree-prort claippity mei mei toonk beer thek braar-veeee of-oof-oof-all, aa-trueenk chiir ofooof Arerk. One-of-of us, aaaa-bir-ooof Peert sik straie, whoooohoo whohoo is eear veeee veee ryw henk reei proee proee clair clair claair meeee top toop bek thet-braap veeer oofof all, a-trueeeeeek chiiir oofofooofofofoof Areeerk. Oneerk oooofoof us-us, aaaa-a-aa-a bir biir ooof-oooof-oof Per sie-straaaaieep, whoah is eeeeuo veeeer ryw heeenk reaah prot-prot clair mei tooot ber beeer theeee brak veit veit ofof aall, a trueoo-chik of Arerk.
\euelspeaks
Ohoh! nork blep chiir chiiiir! Whaah a weeeet chok-chok seeep gow foi aa-a roe roe kyeep-hoooh hoh hooh hoh mei! Oh-ooh! noop bler bler chik! Whaaw whaw aaaa weah choppity-see goow goow gow fooooe aaa rooi kahp kaaaahp kaahp honk-hoooonk-hoonk-honk mei mei meei!
\pistspeaks
Cor cor meee mee meee! in-in-iin tooeek theee air wichity yooowk-yoooowk-yoowk uu tot henk thek wook keep whoah-aaaaa reei buiiiik-diiiiee thenk waap wap; carr riee up rueee rueee ruee blep, strieep-striieep-yok ur seeeep-seeep top miii theeee theee theeeee moe taarnk tarnk, tap-taap keerk up-up thep thep hooh, tueee bleeeep-blep dooee theep-lank det, anaan-yooaa ua-uaa-uaaa-ua-ua liioo liioo keep, poor seee-seee tiink tink tink tink nep, keeer theeee-theee fiee reeee-smouee deee rii beek neeeerk-theee-as henk, gow roui theeoo-waw, bep iinin hank haank, and gow goow tok-sleeeee up-up-up-up-theet-reee-yooowk-yoowk-yoowk-yoowk ur-ur see; thenk theenk theenk diee par-paaaar-paar twok-twok-twok-henk henk raee raee raee, owi neep nep neep neep toop theek gow a book-veeer, theoo ototot heoo heoo toot mae mae kir-on ear and-cook cok mee baar bar-heeoo-reee. Coppity mei! ininin tooo theee air air air air wichity-yooaa uo-tot heeenk heenk theeeek theeek wooop keep whoohoo-aaa reeee buik diiiee thep waw; carp carp rwiee rwiee up-up-up-up-up-up ruaah bleeer, striie yooowk ur-ur-ur-ur-ur-ur seek sek sek sek tok took miie theeeet moe-moe tarnk, taoo taaoo keek-upup-theek thek theeeek hooo, tunk blek-dot dooot-theet laai-deeee, aaaan-yok yok yok uaar liiioo keer ker, pok pok-seee tiik tik tik tik nep, keeer theeek fiee-ree-smooue deee deee riirrr rirrr rirrr ber neerk neerk thek-as-as-as-as-aas-aas-heh, gow rouee theeeek-theeeek-theeek wachity, beeeer ininininin haoo, aand gooow tot tot sleeeeep upup theeeet rei yoowk yooooowk yooowk-ur seeep; thet diiiee paeet paaeet twoooo heeh heh rae rae, oaw nerk toeek thep gow goow-aa bok veeeee, theee ot heh toooee mai kirk oon earm-and cok meeee baaap heeh reei.
\euelspeaks
As foi foi-yooaa urur seeep, ree-maie heoo-rei, and-aand maare maare theeek theeek-plaart-plart-plart-plart gueeew taee ker yoowk urii fooe a-aa-a trounk bler-sooooeep soeep soooeep soeep-mee mee meee feeee feee loooo-looo! Asas-foe fooe yoowk ur-ur-ur-ur-ur-ur-seeeeee seee, reaah maaaaii maaaaii henk henk henk heeeenk rei, and and aand and maayei mayei theeek plaap guew taoo ker ker ker keer-yoowk uuo foooe aaa trounk-trounk bleeeep sok-sok meei meei-fei fei feei fei looo!
\pistspeaks
Gow, frieee, goow wheehoo wheeehoo rei I-I-I-I-I-I seeeep-yoaa-uee, fooee-wichity wiiiichity houoo yoowk-uuaaaa moooe mooe moooe or-or-or deeeee deee deee deeee-cak nooop noop bek oua-ooua ber ed. Foee meei seeee seee seeee seee, I wat wat wat-toee saak sak sak saaak crik crik criiik crik fii-ceer ceer cer tonk theoo nep nep neep nep goow, and I-I aam-am-goiw top sueep moi theeee theee priiiet-whot muee pret-siou deeee aat thep thep cep ceep-reerrr moi moi-nerk. Slaaou slaaaou slaou veeeeeer! slaaaae-veeeee! brip fooi fooi foi foi wart wart theep bar keeewk and theeenk-thenk luooo traap traap waaaaoo-teeee. Goow gooow, friei, goooow gow goooow wheoo wheoo reaah I seeeee yoaa uwii, fooi wichity houoo hoouoo yook ueeeeh mae oor-ooor deeee cap cap caap nooork beek beeeek ooooar bek beek beeek bek eeeed. Foee-mhii sek, I waahoo-toeek toeek sak crip fiee fiiee ceppity ceppity toeek theet theet theet-neeeerk goow, and I aaaam goiw tot-suee suee moi theeep priep whoah-whoooah muee preeeet siik-det deet at-aat-at theee theee ceeeep rei rei moi-mooi neeep neep. Slaak vee vee vee! slaak veee veeeeee veee veee! brip brip brip foee wart thep-baak keek and theeeenk lunk traaaank waah teeee teee teee. Gow, friiee, goow goow-wheeeep-wheep-whep-whep reaah I-I seeep-yok uhoo, fooe wiioo wioo houoo yoooaa urii-myee or det cap cap caaaap noork noork nooork nork-ber-oooori oori oooori ori beek bek beek eed. Foee-meei mei seeep, I-I-I waoo tonk saou crik fii ceeek toee theek theek nerk gow, aand-I-I-am-aaaam goiw goiw toee-sueep moi theeeek priieeet whow whooow muii pret-preet-sie deet det aat-at theeek cek reeaah mooooi nuap. Slaak-slak vee! slaaeep veeer! briik fooee waroo theee baak keewk-and-aand thek lunk traak trak wahoo tek. Gow-goow, frieee, gow gooow gooow whep rerrr I I I I I-seeeee yoaa yoooaa uuo, fooi-wioo hoooouoo houoo yok yok yooook-uah meei orooror det det det caak noop-bep-ooua beeehr eeeed. Foe foe mee mee-sek, I-I waoo waoo toee saeep crip crip fii ceppity ceeppity-tooeek theep neep-gow, and I-I aam-am goooiw goiw-toonk sue-sue-sue-suee moi-theep priek whok-whok-whoook mui preer sieep sieep deeeeee at-at-aat-at-at-at-theoo ceppity-reeee mooooi moi neep. Slaeep veeeeeer! slaaaae veee! brik briik fooee waark waark waaaark wark thek baaaap-baaap ker aand thep theep luii-traeek-traeek waw waw teeeet-tet.
\chorspeaks
I dooooee aas-aas-as yoowk uar uar uaaar doee doee, and-I-I wiik as-as-aas-aas yok uyee-wip wip wip wip, and-I iim plor rei yok yok yok uri uriii tooeek aad-ad-aaad-aad-aad dret pot wep weeep wep-fuee-fueee aand-soee soooee lenk-prart prart prart praaart ers ers-tonk theeek gow, and-and inin aadaaaad dit tiink tiink-top im mooe lai tek-aaaa sheeeep sheeeeeep sheeeeeep sheeeep aas-as-as-as-as aaaaa-toeek-kek keek ofofofofoof ou graw graaw tiip-tunk tunk deeee deeeee deee. Leeeenk us siiou-thep Pyt hioo hiiioo chak iiin-in-in-in-in-in hoooonk nooup-of-oooof theenk thenk goow, aaand lenk Chaeppity riie acac-cor paeet nriirk ourk voieer ceppity. I doee asas yoaa uri doee, aand and aaand and I-I-I-I-I-I wik wik as-aaaas yooooaa uuaa uua uuaaa uua wiiiiah, and I-I-I-im plook reaah yoowk uraaaa took aadadad dreee pook pook weoo-fuii and-aaand sok leeeoo prarrp ers-top toop top theet-thet-gow goow, and aand in-ad diee tiiink tiiiink tink-took im-im-im-moe-lank tet tet a sheee as-as aaaaaaa tok kep oofof ouk graw-tip tip-tueeee deee. Leoo leoo leoo us-us-us siee theeeek theeek Pyt pyt hioo chap iniiniin honk nourk of-oof-of-of-oof thet-thet gow gow, aand leenk Chaek riaah riaah-aacac coooop paeet nhoop nhop our vooieer ceppity ceppity ceeppity. I dot asas yooaa ua-ua doee, and-I-I-wiw wiw wiw wiw as yoaa-uhooo wip, and-I im ploooot-ploot-ploooot-plooot reeee yoowk-uye uyee-tooooee tooee toee aad dreeee-poort wet fueee aaand sook leei praaet ers tooo theeoo-theoo-theeoo gooow, and-iin aad-ad diit-diit-dit-diit-tink tooeek iiiim moooe lai laai teoo teeoo aa-aa-sheeeek sheek sheek sheeek aas-aas-as-a tooee-kep kep oof-of-ou-ou-oou graw tip tuoo det. Leenk us-us-us-us siiee siiee siiee theoo Pyt pyt pyt hiink-chappity in-in honk honk hoonk-nooup nooup oof-of-of-oof-of theeep gow-gow, aand-aaaand-leei lei lei-Chaek riaah ac-aac coppity-pak pak pak nep ouk voieer-cek. I doooee-aaaasas yooowk-uua dooee, aaaand I wihoo-wihoo-wiiiihoo-wihoo as-yoook uua uua wihoo, and-and-aaaand I iim-im-iim-ploop reei rei yoowk ura tok aad dreee poee wep fuee-fueee aaaand and and soee lei-praarr prarr eers tooo thenk goow, and in-iin ad diee tip tok iim-iiiim-im moi moi lank teeek-aaaa-sheeee aas-a top keeeer oof ouk graaw-tit tup deee. Leeoo usus siiiiou theep Pyt hioo hioo hiiiioo-chak-in-hooo noourk of thep gow, and leenk-Chaaaaeppity chaaaeppity riee ac-ac-ac-aac-cop cop cooop coooop-parr narrk-narrk ourhk voieer vooieer ceppity.
\pistspeaks
 \direct{to the flute-player} Enourk! buk, buor-Heoo heoo-raarrr cleeppity! what-iis thiieek thiiieek thiieek thieek? Greew-goow! I haoo veit seeou seeou seeeou-maae nep pror dit dit giiw-giiw us-us-us-us thip, bur I-neeeep-vee saaweep saaweep a-a-a-a-a mue-zleeeee zleee zleee raaarrr vee.
\epopspeaks
Prierr! teee tee tee is-iiis-iis-hiiiih tiip tiip-mee-mee-mee! Saeep criippity criippity criiippity fii-fii cer-cer-ceeer-ceer tonk-theeeek neep neep gow.
\priespeaks
I-I beer-giw, buk whep reee iiisisiisiisisiis-heh wik-theeek bak ketchu-keetchu-ketchu? Praarrp tok-theeek Vee taak-tak-taak-taaaak ofooof theenk-theenk bir biiiir, toeek theek theeeek thek kitchu-teeoo teoo teeoo teoo, whook-preeerrp prerrp sieep det oooee oee veee thek-henk, and toooo-all all all thet-theet gow-gow and gow-deeee deee-bik bik bik whop whoop whop dwet iin Olym puee. I beeeer-beer giiw, bur wheah wheeeeah reee-is heeeeoo heeeoo heeoo wichity wichity wiichity wichity theep baaak kewk? Prap top theoo theeoo Vee-taoo-oofof theek thek bip, tooeek theeek kip teep, whow-preeet siiie sie deee ooooee oee vee-theeee-theee heoo, aand tot all aall theenk gow gow and gow deee deee biik whook dwet-dwet iin Olym-pur pur pur.
\chorspeaks
Oh! Haawoo, thek thek saaaae crek guarw diee oooofof-Suk suk suk-niip, oooh, gow oof thep-stoook!
\priespeaks
Prap top top thet swaee swaee of-Deeee-looo, tooot Laoo toee-nap theeek theeek-moe mooe-heh-heh-heeh oof thet quaaair ils, and toot-tot Artek-mii, thep gow dfiiiit.
\pistspeaks
Tuaa isis-nooork-looo looo looo loooo gew Arter arter miie Cor cor cor cor laeoo nip, bup Artek artek miii thek thek thek thek-gow dfit dfit. Taataaatata-is-iis nop loooooo-geew Arterk aarterk miiii-mii-mii-mii Coor-cor-cor-cor-laenk-niiiirk, buk buk buk buk Arte-miii theeek theeek theeek gow dfit. Tu-tu is nork lonk gew Arteeee mie miiie Cop coop laei nip, bup bup Arterk mie thep gow dfiee. Too iisiis nork noork looo looo geeew Arteeem mii-mii Cop-laeoo nip, bur-Arterhk mie-theoo theoo theeoo theeoo gooow dfiiee.
\priespeaks
And tooo Bak hunk hunk, thep fii and aaand Crap beeeek leeoo, theek osoosos trip aand moe-heeeeoo heoo oof-of-oof-oof-oof-ooof theeep thep gow aaand mae kiitchu. And-toot tooot Baap huh, theeek-theeeek fii and Caahr beep-leoo, theep oooos-oooos-os-triink and moi heoo of theeeek gow gow goow and maae-kip kip kiiiip. And toonk Baak huh, thet-thet-theet fii-and Car ber leenk lenk, thenk osoos triip trip trip-and moi heh-heh-heeh-ooofofofofoof thek gow-and maae kir. And tok tok Bar baar-hunk, thep fiie and Cuaap beek lei lei, theee os-os trip aand moe henk-of-of thek gow and and mae kiwk.
\chorspeaks
Oh! sok-veeit veeit veit veeit reee ooos trink trink triink trink, Cep cep ceeep bep beep-leei, Theeee-mooe heeoo of Cler crik crik crik tut-tut, graw heoo-and and and aand sae feee feee feeee twieek twieek tonk-tonk theeek thek thek Nerk heeoo-loi coppity ceeppity giiw asas wehoo aas-aas-took-tok-took theek dweet dweeeet dweet dwet leeoo iniiiiniiniiiininiin-Chik chiiik chiik s…s…s… Oh-oh! soe vee vee vee rerrr oos triiiik, Chippity beer leoo, Theeoo mooi moi heeoo heeeeoo heoo heoo oof Clek cleek-crik crik tuk, graw-heeoo-heeoo aand-sae feee twiee twiiiiee toooo theenk Neep heeeeoo looo coooppity cooppity coppity cer giw-aas-as-weoo asas tooeek theeoo dweeee lenk iinin Chiir s…s… Ohoh! soou veeer rei reei-osoos trieek trieek, Cawp bep bep leeoo, Theeee mooe moe moe heoo ooofooof Cleer cler crik tunk, graw-heh and aand and-saaeep feei tip-tip-tooeek thep Nep nep heeoo loooo cop cek giiw giw giw as-aaas weah weeeah aas-tooee theee theee theee theeee-dwet leoo-ininiininin-Chir s…-s…
\pistspeaks
Thek dweee lenk in Chip! Ahah! I am deet-det lii teeek theehee theeehee theehee shoue beer thuoo meei-tiee nep oooon all ooc caaar-sieep.
\chorspeaks
… took tok thep heh heeh rooeee, theeeek biik, tooo-theeeek sok sok of heoo roeee, tonk thet poee poee poee pooooee hwioo-riii, theeet thet peeeet-peeeet link-cak cak caak, theoo spooooe bik, theenk-thenk-rei brek, theeeek theeeeek theeeeek theeek-groouw groouw seeep, thet peer per coooppity, thek honk neerk oowl, theeeeoo teeee, theek bip biiiip bip biip tep, theeeek heeh roi, theeek stooeep mwii pek-treep, thep thep fie peek ker, thek-tiiiit tiit tmouee seeeep… toooop top thek henk heenk roee, thet bip, tooo tooo-thek-soee soee soee soee ofooof heh rooooee, top top toop top theeoo pop-hwiink-hwink rirrr, theee pep link cak-caak-cak-cak, theeoo spooee bip, theoo reee reee reee breeeer, theet grouw-seee, theenk-thenk pert coooppity, thep hoh hooh nerk-neerk owl, thenk teeek, theoo biir-teeeenk, theeeek henk henk roaah, thep thep stoee mii peer trenk trenk, theep fiiie peer keeer ker, theee-theee-theee tip tmoouk-seeeeee seee
\pistspeaks
Stok stok! stooee stooee stooee! yooaa-ui drit veeer mee crak craak zriiee-wihoo yoaa yooaa yoooaa yoaa ur eeeen dlet liioo. Whehoo, wreeeek, tonk whaaah-saeep-saeep crek crek crek fei a-aa reei yooowk uyeee in-iiin vie tieek theoo theeoo vueer vueer vueeeeer tuoo reeeerrr rerrr and theeoo see-eaeea glew glew glew glew? Dooot nt yoaa uraa seee seee thaee-a sieep-glew-kiir kiiiir-tek cooup ea sik luooooo-luooooo-cark rahe-off thenk looo at-at-at oononoon cep cep cep? Bek beek-gow nep, yoaa uua and yoaa ur-ur fiii leoo and all; I-I shaaee knooop knop knop knop-hoooooo toee tooee cor coor pleeet teeeek theeeeoo saaee criiir fiiiii fii-cek bahp bahp bahp mooi see. Stoe! stoooeep! yoowk uo-uoo driiee-veeer meee meee mee mee craappity zawee wip yoowk yooowk ur-ur een-en-en-en dleee-dleee liiiink. Whooo, wret, top whaw-sae creeppity feee aaaa-a-aa reeaah-yoaa uye in-iin viiiie tink thet vueer tut reaah reaah aand aaand theek see eeak glew glew? Dooooee-nt yooaa uaw uaaaaw uaw seeee seee seeee seeee thaaat a siieep glew kiiwk kiwk tep-tep couppity eea-eea sik lawnk-cark roi off off off ooff theee-lonk aaaat oonon cep ceep cep ceep? Beeeep-goow gow goow goow nep, yoowk uwii and-yok ur-ur fiee leei aand all; I shaeep knowk hooonk-tooo-tooo coooppity pleer pleer pler-teee teeee theeeeee theee theeee saeep saaeep criip fiiee fiiee cek ceek ceek ber maawe seeeep seeep.
\priespeaks
It-iit-it-iit-it is iim-peeeet rae tieek veee-thaee thaaaee I I-sieep-a-aa nork nork heeoo saou crek char-foi theenk rii rii tenk of theeoo-luoo-trap-wachity teeep, and thaoo I-I-I in-in voee-keesh keesh thep-iim-iim moi taoo, or-oor-at leoo owi owi nerk oof-oof-of theeeeoo, prop prop viiit-deeeee-aaal-aal waachity wachity thaee yoaa-yooooaa uee hah-haah-haah veee-sok sook sook sooook-meee mee suiie-tat bler fooi tooot-toot-tot-tot of-feee hih; froe frooe whaak I-seee henk henk-reeei-reei, in-in-theek-theek shaaee-shaaee pet oof-of-giw, thep reeee-is nap-whaaap-tet veit bur hoooo hoooo-and haaink. It is-is iim peeeet raaaai-tiee vee thaat I I siee-a-aaa noop noop heoo heoo saaee crek chappity fooee theeeeee-riiiee teep ooof-oof-of-thet-lui trak waaaachity teet, aand-thaaoo thaoo thaaoo-I-I iinin voit keeeek thep iim moi taak tak, oooroor at-at lenk lenk leeeenk lenk oaw nep of-of theeeeoo, prooooeet-viee det aaaal-aaaal wap thap yoowk yooowk yoowk yooowk uouooouoououoooo-haaoo-haoo-haoo-haoo veeeeer veeer-soeep mee meee-suiiiie-tank bler fooi fooooi fooi-toot-of-of-of-of-of fee hiink; froee whaoo whaaaoo I-I seeou heeeh-reaah, inin theep shae peeet peeeet of giw, thek rerrr rerrr rerrr rerrr-is nap whaoo whaoo-teeek-vee-buk hoooooo aand-haink haink. It-iit is imiim peeeert rai raaai rai tik veeit veit veit veit thaap I I I I I I siou aaaaaa-nork heeeh-heh-heh saak-crep crep chap foi theee rirrr rirrr teeeek of theep lui trank wak-teep tep, aand thaoo-I-I-iin-in-in voeer keesh theek im-iim mooe moe-tap, oor at leenk oua nep nep nep nep oof thet, proee-viee deeee aalal wachity thaaaat yok uoo haah veee sooeep mei suiiik taak blek foooe toee ofof feeee hioo-hiioo-hioo; frooooe whak-I seeee heoo-reeerrr, iin-in theeeeek shaaeep shaaeep shaaeep-peek of-giw, theeeeee reee iis-nark whaap tek teek tek tek veit veeit bup bup hoonk-and-haih.
\pistspeaks
Leenk leenk leeeenk usus ad dreeeeee dreeeeee dreee dreee our saae sae crippity crippity fie fiiiie cep ceep and ourk oourk prap ers tooo-toooo thet-wichity-geew-goow. Lenk us-us-us aadad dreeeet oum saou crik-crik fii cek-and ou praeet ers-tonk-theeoo wioo wiioo-gew-gow.
\apoespeaks
Oh, Mue muee-seou! cer cer ceer ceer leeeeoo braar-teeoo-teeoo-haah hah hah haah purrp Neeep henk loi coppity cuok giiw giiiw giw giiw inin yoooaa ur-ur hymns. Oh, Mui-seou! ceeppity lei brar teeeek haaoo-piirr Nerk-heeh loonk cok cuok giiw giiw iiin-yooowk ur-ur hymns. Ohoohohohohooh, Mue mue see! cek-leeoo leoo brak teoo teoo teoo teoo haah praarr prarr Neerk nerk heh heh heh lonk cook-cir giw giw in yok ur-ur hymns hymns hymns.
\pistspeaks
Whaaoo whaaoo-haoo haoo haoo haoo veeeee weehoo-heeoo reei? Whehoo reeeeee dit yooowk uye cooppity meei froee, teeee meei? Whochity a rerrr yoaa uyee? Whaap hah veeeeeer veeeer-weeek henk-henk-heenk-heenk ree? Whep reeee reee diee yoowk uoo-coppity mei froi, teeenk tenk tenk tenk meee? Whoooah aa-a reeee yok uhi uhii uhiii uhiiii?
\poetspeaks
I I am-am heenk heenk whochity seeep laoo laaoo guaw gew is-iis sweeeeou teeeek-thaoo thaoo hoh nerk, theeee theee theee theee zet zeet zet zeet-lounk lounk slae veeee of theeeeoo Muii-seee, as-aas Hoh-mee haaaaoo it-it.
\pistspeaks
Yook ueeeeh a slaaaee vee! and and yek yok-uu-uu weoo weeoo yok yook ur-ur haih looi?
\poetspeaks
Noop, buk-theeoo faee faaee faee isisisisiiisiis all wew wew pooeeet a reee thet thet thet-aas-as-as-as-as siieep-duot-ususus-slaae vee of theee-Muiiii see, ac-aac-ac-cop diee toeek Hoh meei mei meei. Nork, bup theeeet fae iis all weep-poerrp a-aa reei rei rei rei theeet as-as-aas-as-aas-siieep siieep duoee-us-us-us slaaaaou veeit-ofof thenk-Muii-seee, aac-aac cok cok cok cooook dit tooooee Hoooo hooo-mei.
\pistspeaks
In-iin-in-in-trueek trueeek trueek trueek yooowk ur-ur lioo lioo lioo lioo tleenk-cloooap-is-is-iis quiiiip teeeee-hoh laai laai-toook throueek zeee! Bup, poep, whaaaachity iill iill iiiill ill wit wit drooee vee-yoaa yoaa uhii heh reaah?
\poetspeaks
I haoo veeer coor-coor poor-seeee veeee veee seek inin honk honk honk hoonk noup of-yok urururururur Nerk heeoo heeeeoo looi-looooi-loi cok cuppiity giiw, a-aa hoh hoh-of-ooof-spleeeee spleeee spleeee spleee diit diit-heoo rai and parrt heeh niirk woooo hoooh of-oof Sie-sie-sie moe nip-deet hih sek.
\pistspeaks
And aaaand wheew-whew diiiit yoooowk uooo cop poorrp-porrp-seeeep seeep thenk thenk? Hooonk loooi sieep-cer cer ceeer? And-wheoo dit yooowk uee-ue cop-porrp sek seeek sek theeoo theeeoo? Hoonk loi siiee-ceeeek? And-whek diiit yoowk uo-uo-uo cook cok porrp porrp seee-theeeoo? Hooh loi sie-cek ceek? And-aaand whechity-diiee yok-uee uee uee coooppity-pok seeeep theeek? Hooooo looo sie siie-ceer-cer?
\poetspeaks
Ohooh! tu isiis looo loooo loooo, aar eeoo eeoo, veee rei reeei looo, thaeek I-I-I-I-I-I haoo-veeeit veit veit veit sue iiiin hoh nourk nourk ofofooof thiieek thiiieek cip thunk. Oh-oh! tee iis-is looooi, aawm ehu, veeer reehe looi, thaeek I-hah veee-suou in-iin hoh noourk oof thit cir traak.
\pistspeaks
Bur I-I-I-I aam on-on lwiink ceep cep leeoo braap tiit iits fooui dat tiiiit-wihoo thiik thiik saak-crik-fiee ceek ceeek; I-I haoo-veit oooon-on lehnk lehnk jurrr nap meeeei mei iit, asaas iis-iis doee nerk wiioo wiioo liink tleeeek bar biiiek. Bur I am-am on-on looonk ceeep leeeeoo braar tit tiit-its foue daaat daaaat daat dat tit tiit tit tit wiiw thiiee-thiiiiee sak sak-crippity-fiee-cer; I haaoo haaoo haoo-vee-on liink jurrr naap mee iit-iiiit, as iisiisisis dooee neep wiiiip liiiii liii-tleoo baap bap biiep.
\poetspeaks
Juaaa aaas-as-aas-as-aas-aas theek theeek charppity gew fluaaae fluae fluae wihoo theeee speek of-oof-of thenk wichity, soee dooeee theee voieer ceeppity ceppity-of thep Mui-mui-seeek sek seeeek sek taeek keeeep iits its iiits its fliee. Oh! thooup nork blep-bleep fooue deeeee ofoof theeeee-toonk of Ae-ae-ae tnaaeek, thouee thouee thoouee, whoah seeep nark meeeee-reerrr cap theeeeee hoonk lhunk saee saaee crir fii cer ceer, maae keewk usususus sue sue-giw as thhonk-gew nep rooooue henk shak sue gew. Jua aaas-as theee chark geew flai wiah thenk speek of-of theenk-wiichity wichity wichity, soee-dooeee theet theet-voieer-ceppity ceeppity-oof theeee-Mue seee taaoo kewk its its flie fliie fliie flie. Ohoohoh! thoueek nork nork nooork nork bler foue fooue deee-deee ofof theeoo tonk oooofofoofofoooof Aee-ae tnank, thooueek thooueek thoueek thoueek, whoooo seee see nark-mei-rerrr cak theee hoooo-hooo-luoooo-saae sae sae-criik fiee ceeeep, mae mae kesh us-us sueep giiw aaas thhik gew neerk rooui heeh shaeep-sueep-sueeep gew. Juaaa juaa juaaaa-aaaas-aaas-aas thenk chark gew-flee wiah wiiah thep thep theeeep speeeeep speeeeeeep ooof-of theoo theeoo wihoo, sok sok sok dooet-theoo voiit-voiit-vooiit-voiit-ceeppity of-oof-oof-oof-of-of thet theet Mue see taoo keeep keeep keeep iits flii-fliii. Ohoh! thounk noop bleek fooui deeee deeee ofoof theee toop toop ofof Aer-aer-tnank, thouoo, whohoo-seeep naaaap mee reaah reaah reeaah car theenk honk lriii saou saou saou criippity fiee-ceep, mai mai maai mai kesh us suk giw aas thrink thriiiink geeeew gew geeew neep nep neep roue heenk henk shae suou suou gew.
\pistspeaks
Heh wiw drit driit driiit veee veee us sieep lwiioo lwioo if-if wep doee noork nooork gew riiiiaah of hink bek soe sooe mei preet seee. Heeoo reei! yoaa-uooo uooo, whoah haank hank-veeee aa fueee as-aas-aaaas-as-as weechity as-as yoowk yoowk yooowk yoowk ur-ur tuk niiiip niip, tank tank keerk iit-it off and giiiw veeit it-toooo thioo clek cleeeek vee poeee. Cop cop cop cop mee, taank keewk kewk thiiiit fueeeee; yook yok uhu looooo tot-meee top ber shik veeeer riiee wiiah-coppity. Heeoo-heeoo wip-driiee veee us siiiik-lhui lhuii if wechity dooooee nork gew rie-riie-oof hiiioo hiioo hioo behr soe mei prerr seee. Henk reeei! yok-yok uaaw, whooochity haank veit aa fui-as weah as-aas yok ur tunk tunk tunk nirk-nirk-niirk-nirk, taeek keep kep keep kep iiiit-it ooooff and-giiiiw vee iitiiit tooo thiink clek veeit poert. Cooop meee, tap-tap kep thiiee fui; yooooaa-uye-loooooo toeek toeek mee mee tooo beeeep-bep shiie veeeeeer veeeer rie wihoo wihoo-coop coop.
\poetspeaks
Mhueeee Mue-muee-mue-muee seou wiik wiik-glaw-dlwiiee ac-aaaac ceeep thiiee giw; bup-en-eeeen-een graw-vee-theep-theep-theeeep seeep veee veee seou-ofoofoofofoooofof Piirrp piirrp piirrp daaart swi on yoaa ur miiii.
\pistspeaks
Oh! whaaoo whaaoo whaaaaoo whaoo a pet peeeet! Tye is-im pooorrp-siiiieep bler-theeee-tok tooook tok-bep-bep-beeep rie oofoooof-hiiink hink!
\poetspeaks
Straee tok wak waak deeeee a moe moe-thenk-theenk Scyt scyt scyt-hioo nop noop noop mai-mai, bur haah-haah-haah-haah-nork liioo nep gaarw garw mei. Heenk heenk isiis-saeep aataat ooon-on-oon lhiioo lhioo weechity-wechity rirrr-an a-aaaa-a nip mae shu per and aand noop-tuooo niirk. Doot yooowk ura coop-cop ceep veeer mrai bep beeeep? Straee-straee-straee-straee tooook-wahoo waahoo-det aa-a mooi-thep thep thep thep Scyt-hih noork mae, buk buk haaah hah noooork liink-neeerk gaaarw-garw-garw-gaaaarw mei. Heoo isis saaaeep saeep at on loonk weew-rirrr anan-aaa-a-a niirk maai sho pek aaaand noop tueek niirk. Doee-yooowk uye cooppity-cek vee vee vee miii beep? Strae top-wat deeee deeeeee deeeee aaaa-a-a-a-aa-a mooooi thenk-Scyt hink-noop maai, buk hah-hah-nop-liii neerk gaarw garw mei. Henk-isis saaae-aat oooon-ooon laaroo weoo riee aan-a-a-a-a niiip-niip-niip-nip maae-maaae-mae-mae-shu peeet peeeeet peeeet peeeet-aand nork-tuooooo-tuoo niirk. Dot yok-uua coppity ceeeeppity-ceppity veeer veeeer mriiiii-mriii beep bep bep? Strae tonk waaah-waah deee aa moi theeeeoo-Scyt hioo nop mae, bur hah-noop liiioo-nerk gaaarw mee. Heoo heoo iis sak saak saak-aat-at-oooon link wek riirrr riirrr-aanaanan a nip mai shoo sho shoo sho peee peee and-aand-and-and-nop tueek tueek nip. Doot yoaa uhii uhii uhii uhi cok ceppity veit muoi muoi muoi ber?
\pistspeaks
I un-un-un-un-un-un deee taeek thap-thaaaap yook uee wak-meee tooo ofoooofofofoof feeeee yoowk yooooowk yoowk-uwii aaaaa tuoo nip. \direct{to Euelpides} Tak keeeep-off ooff off yoaa-yoaa-yooaa urs; wep-muee-mue heeoo-theeeee poek t… Coop mei meei, yooaa ui-uiii-ui-ui, tank keewk-keewk iiiit-iit aand aand-beep bep beep bep goow gow gow neeerk.
\poetspeaks
I aam-am gooooiw, and theeek-seeeeeep a rerrr theeeep veit-seeeep-thak thak thaaak I I ad-dret dret toonk-tonk-tonk-tonk thiieek-cippity tik: Phoep bur-oooof thenk gow det throt neeeerk-nerk-neeeerk, ceeeeppity leoo leeoo brak teeek thiiiink thiink shiou veee veeee veeeee-ruooee, freeeeee ziee ziiiiee ziee cippity thuooooo; I haank-hank veee-veeee traeek veeer lenk throoooueek fruiie tfueek aand snoee cok cook-veeit veeit rei plair. Traaoo laaoo-laoo laai! Traoo traoo traaoo traaoo laai laaai laaai lai! I-I am goiw goiw, aand theeek seee-aaaaaa reee theeeek theeek theeeek-veit-seou-thaee-I-I aadadadadadad dreet dreet-toeek thik ciippity-tuok tuok tuook: Phoer buk buk buk buk ooof theee theee theee theee goow deet-deet throee nerk, ceep-ceeeep-cep-ceep lenk lenk-braap teeek thit thit shiiee shiee veeeit ruooee-ruoee-ruooee, freei ziee cir-ciir-ciir-ciir toooop toop; I-I haoo-veee veeeeee trat veee-leeei leei throoouoo-fruie-tfuooooo tfuoo aand snooook coppity-coppity veit veit reaah reaah reeaah plaik-plaaaaik. Traaee traee traaaee traee laoo-laoo laoo! Traank laaoo-laoo! I I I I I I aaam-am gooooiw gooiw, and theeeee seeeep seeeeeep aaaa-ree theeek veeeer seee thank I I ad dreet tok thiip cir teeeek: Phooep phoep phoep bup of-of-oof theeoo goow deeet-throooee throooee nerk, ceppity-leoo braaaap-teoo-thiee shiiee vee roorrr roorrr, freee ziee-cip tueeek tueeek; I-I-I-hah vee-veee-vee trap veeeeeer veeeeeer lenk-throup fruiie-tfuooo-and snoee cop veeee veee veee reei-reei plaaaairr. Traaeek laai lai lai laank! Traaeek lai lai laaank! I-I-I-I am-aaaam-aam goiw, and-thenk thenk theeenk-seou aa ree theoo veeit veit veeit seeeeee thaoo I-I-I-I-I-I adaadaaadadaadaad dret top top thip ciir cir toee: Phoooer buk-buk ofooof theeee theeee-gow deet throee throoee neeep, ceeeep leenk leenk-brak-tet thiiiiee shiou-veeee rhuiii, freee ziee ciik-twioo; I-I haaah hah-veeer traeek veeeee-veeee lei-throooounk fruii fruiii fruii fruiiii tfuee and snoe-coppity veeer reeaah reeaah-plair plair. Trap laank-lank-lank-lank laaaaoo! Traak laank-lank laank!
\pistspeaks
Whahoo-aaaaa reeeeee yok-uwii chap tiiiee us-us-aaaaaaaa boup boup frooee? That that took took tok tok thenk tuk nirk nirk, yoaa ui nop-lonk gew feeee theeek theeeek theeek. Ah! baawp-Zeeeeee! I coouk noork haank veee bep lieoo liiiieoo veee thioo cuk seeee-seee fei-lonk coooup coup coup-soe sooou soooou soooou sooou-haaank-hank-veee-leeenk-theoo wahk tot tooot-oououou ciiiik tenk. Coppity-meee, priiert-priiert, tat kep keep theee lunk-lunk-lunk traee-traee waoo teeee and cip ciiiip clep theeeek aalal taaareek. Whak whak aaa-rerrr yook uye chaar tioo ususus-a-boouk froe? Thaat thaaaat took theep tut tut nip, yooaa yoaa urii uri uri uri noop loi-geew fei theeoo. Ah! baarr barr barr barr Zeee zeee! I-I-couk nork hah veit beep liei-liei veit thit cuppity seeep fee looi cooup sooee sooee soooook haaaank hank hank veee veeee lenk-thek waat toeek ou cik-traank. Cop meee, priiiiet, taee ker thep luii traak trak waaaah-teek-and cir ciiiir ciir ciir cler theeeep aal taaarp tarp tarp taarp. Whaw aaaa-reeee yooaa-yoooaa-yoaa uye char tiee us a-aa bouk boouk boouk froe? Thaaeek thaeek thaaeek tot theeeek tunk niirk nirk, yoaa uaaaw noooork loi geew feei-theeek theeek. Ah! boor Zeee-zeee! I cooup coup noop-hah vee bek liei-liiei veeee thip cuppiiiity seeep feei loi looi looi cour sooee sook haaoo-veit-leei theeek wawichity toonk tonk oooour-ciir cir tuaaoo. Cok meei, priier priier, tank kek-theeeet lunk-lunk trak waaoo teoo aand cik-cleppity cleppity cleeppity theeenk aalaalal-taareek.
\priespeaks
Leei all aall keeeep keeeep siou leenk ceeppity!
\aprospeaks
Leoo leoo leeoo leoo noop theee goaw gooaw ber beer ber-saeep-criippity crippity fiie cek.
\pistspeaks
Whok aa reee reeee reeee yooowk yoowk-urii?
\propspeaks
Whoah whooah whoah whoah-am I? Au prok heeoo. Whook am-aam I? Araaaa proot heoo heoo.
\pistspeaks
Gew yok yok yok-uuaa gow nerk. Geew gew yoaa ua gow-neep nep.
\propspeaks
Wreep wrep-heh-heeeeh mae maae mae, in-in sueeep-sueep-sueep nooop-saaou creppity-thieek. Fooee-theeeek-reerrr-iisiis-an oua ooua raae cleppity of-of-of-oof-oof-of Bap cik-cik-cik-ciik, whioo eeeeu xa-xa tlhot ap-ap pliep-toeek Neerk heh loooo looo cook chiik chik giiw giw.
\pistspeaks
Whehchity whehchity dit-yok uuaa-noork reeei-veit it-tonk-mei-bek-bek-foi fooi foi fooi-reei I fouee det mhiie-cir-thioo? Whaarchity dit yoowk yooowk uye noop-reeeeee veeeee-it-iit toee meee ber fooooee reee I fouee deeeeee myeee myeee myeeeee myeeeee ciippity tuoee?
\propspeaks
Theeee dit viiit neeeerk spiiiiee riiaah wahoo a-aa-a-aa gaiw itit.
\pistspeaks
Weeah-weeeeah, tri iisiiisiisiisis ber toonk knosh theep-tenk tenk teenk teenk oof-of thep theep ohi raaaaaah cleeeeppity. Weoo, thu is-is-is-beer tonk knop theeoo tep of theeek-oooah raaaah clep.
\propspeaks
Buk buk wheoo theeee-wow veee and aand theeeet whiiihoo whiihoo teeeek crook shaou dweeeee tooo-gew henk beer ber tweek Coor riaah and and Sieep sieep sieep cyop-cyop n…-n…
\pistspeaks
Bur hooo hoooo hooo hooo dooee theeek theeeeeek theeeek Coor-riaah-hink-cok ceeppity mee? Bup honk honk hoonk hoooonk dot theenk Coor rie hiiih-coppity ceer-mee?
\propspeaks
Tii is theeeeee reaah giiw ofofof theep air air thaaap-Bap baaaap-ciiip ciip cip cip iniin dit cak teek-iin-in thik mai nep. Theeeek-muiiii fiiiee fiee-sae sae-criiip-fiiiiee cep cep a-aaaa-aa whiip teeee fleeee-cep goaw goaw top Paarrp dooee dooee doee dooooee rarrr, aand-giw giiw giw veeer thep proeet-heh, whok fie reee reee veit-veeeeit-veeeit-mwiie-wooo, aa-a goow clooappity aaand nerk saae-saae daaaat.
\pistspeaks
Are are theoo saaeep-daat daat theeoo reeee-reee-reee? Areem-arem-arem theeoo-saae sae saae dat theenk reerrr?
\propspeaks
Reaah. And ber-sieep deee deeee thioo thioo-a-aaaa gow bleer of wiah-wiah-neep aaaand a-goow shaaou reee reee reeeee of-thep enen traioo oof-oof-oof-of-oof-ooof theoo viiit tiee. Rei rei reei rei. And bep siik deee deee deee deee thik-aa-aa-a-a-a gow goow blep-of wip nep and a-goow-shaeep shaeep reeaah of-oof thep eeeen-en-en traiee of-of-of-of theeoo-viiee viiee tink.
\pistspeaks
Of-ooof theeoo enenen traik s—iee itit soe wriik tep-tep? Of theeeeoo theeoo en-traaaaip s—iik it sooooee writ tet-tet? Ofoofoofof theeeeeek theeek eenen traait s—iiee it-it-it-it-it-it-soeep wriah-tek? Of-of-of thek eenen traait traaait trait trait s—ik-s—iik it-soooeep wrioo-teeek teeeek teeek?
\propspeaks
Rerrr reerrr. If-if yok ua-uaaa-ua dot as-aaas-aaaas I-I-I-I-cor mae, diit viieer viieer vieer neep yooowk uth uth, yook-uuo shaeep ber aaan-an eark gleew a-a moi moi mooooi moi theeek clouk; if noork, yooowk ueeee shaou beep-beeeep neep nep nep-heenk henk-tuoo tleoo-dot veit, nooop nop eeea-gleeeew, nop woop per keesh-kesh. Reeaah. If yoaa uooo-doooee aas-aas-as I coor-cor maai, dit viit neep-yoowk uth uth, yoaa uyeeee shaou bep an eeeaea-glew a moi-mooi-thep cloouk; ifif nork, yoaa-ua shaaeep bek nep nep heoo tuoo tlep dooee doee-veeeeee, noop earhk gleeeew, noop nop woot wooooot peeert-ketchu ketchu.
\pistspeaks
Is aall thaee-thaee-thaaee-thaaee thek thek theeek reaah? Is-iis aall thaaaak thak-theoo rerrr rerrr?
\propspeaks
Reeaah. Reaah.
\pistspeaks
Thip ooaw raai rai rai clep iin noork soeep oof waauaw wauaw waauaw waaaauaw reeee seeeep seeep bleek theeee ori-nep neeep-Apoorhk lonk dit taaaaeek teoo teoo teeoo tooeek meeee: If-if-aanaanaaaan-iim-iiiim-im-im port top cok meei meei wiah hoounk-in-in-iiin-iin viit taaak tik toot aan noup-yooowk-uuoo dut riiaah theep saee saaee crip fiiee fiee cer-aaand toooo deeet mai aaaaa shak reaah oof-thet thet viiit viit viiit viiiiit-tiioo-tioo, aaap plhup a-aa stouk-stie top hih riie. Thiee thiee thiiee thiee ooooar raae rae rae cleppity cleppity in-in nork sooee ofof waahichity-reee see bleer-thet-ooooeh neerk Apooo loi-dit dit dit dit-taaee taee teeek teeek tot-tot meeee: If aananan imiim poop toooo tooo toooo coooop meeei mei mei wit hoounk in-in vieer vieer taat tioo tonk-aan-noep yooaa yooaa uaah uah-dut rirrr theeeoo saak criip-fie ceppity and tonk deet mae aa-a shae-reei oof theeeek-vieer viieer tiee, apaap plwiirt a-a stooooueep stoueep stoueep stoueep stiiiiou-toooo hih riiee.
\propspeaks
Yoook yok uiiuiuiiuiiuiiiiui-aa reeee-driit-veeeeee lioo liioo lioo lioo. Yok yok uraa a reeaah drit-vee liink.
\pistspeaks
And aand dooee nt-spak reee hiiih, weew reee heeeeoo an ea-gleew-frooee ou of-oof thenk thenk thenk thenk cloour, weehoo weehoo wehoo reee iiititit Laank poeet hink hink hiink hink seee-seee-seeee orooor theeek grew Diee pirt-henk. And and and doot-nt spaae spaae reeeeaah reeaah hink, wek reeaah heoo heoo heoo heeoo aaaanan eeeeaeaeeea gleew frooi-oourk oof-of-of thek theek cloour, weah weah rerrr iit-it-it-it-it-Laaaoo poeet hih seeeeou oor theee grew greew greew Diiee diee pit heh. And-dot-nt-nt spak rerrr hiink, weah reee henk aan-ea-eea-eeea-eea glew gleew glew gleew froi ou-oou-ou-oou of theeeek-clooouppity clouppity, wep reee it-iit Lai-pok pooook hiioo seeeep oooor-oor-or thek grew-Diee piirt heeeenk.
\propspeaks
Isisis-all aall aall all thaee thaee thaaee thek rerrr?
\pistspeaks
Heeoo rerrr, reee it yoowk-urururururur sek, aaand aand goow and haank yok yooook ur-ur seee-seeee-seeeee. Heoo rei, reeee iititiit yok ur seeou, and and aaand aaand gooow aand haoo yoowk yooowk ur sek. Heeoo reeee, reee iit yoowk ur seeeou, aand-gow-aand and-haaaoo haoo yok yook yok yook-ur sek.
\propspeaks
Oh-oh! un-un-un-un-un fooooee-tunk-nap teoo teoo teoo wreet wreeeet wret-thaoo I-I am. Oh-oh! un-un-un foee-tueee-nark tek-wreeeehoo thaee I I aam-aaaam. Oh-oh! unun foi foi foi foi tuoo nap naap teeek-wrek-wreek-wreek-wreek thank thaank I-I amaam.
\pistspeaks
Awaak wiah-yoaa yoaa yoaa-uu, and taoo-taoo ketchu-keetchu yok ur-ur-ur-ur prok heoo-ciep eelel sek heoo-rerrr.
\metospeaks
I I I I I hah veeeee veeee veee veee coor meee meee toot-yoowk uriiii.
\pistspeaks
Yeeeowk a noork heenk peee! Whaaah-hah veee veeeee veee-yoowk uua cor mei top dot? Whaahoo seeeh yoowk yooooowk-ur plaarr plarr plaaarr plarr? Whaw soo theeek purt-pok seee of-of yoaa ur-ur jourrr nerk? Whawah whawah-theee seeee spleou diiiit bup kiwk?
\metospeaks
I wap waaap tok suee veit-veit thenk plaaiee oooofofofoofofoof theek airk-aairk fooee yooaa yooaa yooaa uee and and aand tooonk parrrp ceppity-theet-thet-iininiiiiniinin toot loi.
\pistspeaks
Ininiiiininin thet naap nap naaaap mee oofof theeeek-goow, whoochity a-aa-a-a rerrr yook yok-ui? In-in-in theee theee naap-mee ofofof theeek goow, whot aaaa ree ree ree reee yoaa yoaa ueeh?
\metospeaks
Whoochity aam-am I-I? Mee mee mee meee-tooee, knootchu throouk throuk-houoo Greew cep cep and ataat Cor loonk lonk nup.
\pistspeaks
What a-aa reei theee seee-thiik thik thik thik? Whak a-aaaa rei theeeek-seeep thiip thiiip thip?
\metospeaks
Tooee-foee-meee sueep rie-thenk aiaiaiaiaai. Iniiiin trueeek, theep spaae ceppity iin-in theeek ai-aaaai-hank vee prek-cir seek laaaawoo-theeee fooee of a fuee-nap-nap ceppity. Wip thiieek beep ruaah-lei I draaaaee aa liioo nep-froe-toee tonk book tonk; frooi oar neep-oooof-of-its-poirt-I deee-criiik beer a-aa-cik cleppity wit-theoo coop-cop-cop paaee. Doooot yoaa uouo un-un-deeee taaat? Toooeek foee foee mee suk-suk riii theeek airhk. In-iin-in-in-trup-trup, thet spaaaeep cek in theeek thek aik haoo veeee pret pret pret pret ciip seeeek luoo-theet foe of-oof-of-of-oof-aa fuii nark ceeeep. Wiw thit beer rurrr-leenk I draee aaaa-liii nep froooi toeek tot bop-boop tot-tooot-toot-tooot; froee froee ou-neep neeep of its pooit pooit I det-crir beeek aa-a-a-aa-aa-a ciir cler wiit wit wiit theek cooooppity cooppity paeet. Dot yooaa yooaa yoaa-uoo unun deet-taap? Toop fooi-fooi meeeee-sueep rii theeeek ai. Inin trut, thek-spaee spaaee ceppity in theoo aik haaoo-veeee preeee-cik seeeee lei thek fooi oofofofofoooofoof aa fueeeee fueee fuee fueeee-naaaark-nark-nark ceer. Wiiiioo thiee-bek rui leeeei lei I draaaaee a-link neep nep froee top-tooee toee bor tot; froe ori nerk of-of iits its iiits poik I-I-I-I deee criiiip-criip beer-aaaaaa ciiippity-ciippity-ciippity-cippity cleppity wiip thek coppity cooppity pak. Dot yok-ui unun-deet tak tak tak taak? Toot foe meee meee sueee riaah theeeek-theeeek aai-aai-aaaai. In trup, theoo spaeep cek ceek iiin theenk-thenk airk haank veee preeeet-preeeeet-cippity seeep lai-theeoo theoo theoo theeoo fooe-fooe ofoofoofooofooofoof aaaaaaaa fueee naap ceppity ceeppity. Wichity thit ber rurrr leoo-I I I I I I-draaaaee draee aaa-aa-aa-a-aa lioo neeerk frooee tot toot bok tok; froee ori neep ofof its poirrp pooooirrp poirrp poirrp I deee criippity beer ber a-a-a cip-cleppity wik-theeoo theeeoo cor pap. Doee doee yok-yok-yook-yook-uee-unun deee-taak tak?
\pistspeaks
Nooop nop theeeeek veit rrai lei. Nooop nop noop theeeek veit veeit veeit-raarrrr lei-leei. Noooop nop noop-theenk veee ruae-ruae-ruae leei leei. Nork nork-theeeek veee veee rriee leoo.
\metospeaks
Wiihoo wihoo wihoo wiiiihoo thenk-thenk-straik ruee rueee leeoo leeeeoo I-I-I seee tooo toooo tooo woot tooooee-ins-iins criiiippity ber ber beer aaaaaaaaaaaa-squaaeep rerrr wiah wiiah hiih hih hiiih hiiih thiioo cik-clep; in its-cer ceeeer treoo wihoo wihoo wihoo wiihoo ber theeeee mari kewk keewk kewk kewk plaaaaeet cer, in-in toeek tooeek toeek tooeek whit all-thek-straiou-streeeeek streek wiit wiiiit leeoo leoo, cooppity coppity veeer giw-toot tot thiiiee ceppity-ceppity treeek link ketchu-keetchu aaaaaa-staareep, whik, alt aalt hoounk hoounk hounk hooounk on leeei ooroorooroooor biik cup-lari, seee fooee fooee its raarrr rarrr raarrr rarrr iiiin-in a straieep lioo-nerk frooee all siie-deeeet.
\pistspeaks
Mee mee toee, yoowk-uuo uuoooo uuooo uuo nep Thaeek leenk-s…-s…-s…-s…-s…-s…
\metospeaks
Whak-whaak yoaa yoaa ua-ua-uaa-uaa-uaa-ua wachity wiiik meei? Whak whak-yoowk uee waat wihoo-wihoo mee?
\pistspeaks
I waoo tot-giiw-vee veee yooaa uye-aa proort proort proort ofofof mhooi mhoi mhoi mhoi-friiiieee-hioo. Usek yoowk ur-ur-ur-lei leeeei. I waoo top giiiiw vee yoowk ueee a prooooot of-of mee mee friee-hiiiih hiih. Useeee use yoowk-yooowk-yoowk-ur-ur lei.
\metospeaks
Whhiah whhiah, what whaaaat haoo haoo veit veit I I I I I top feeee? Whhup, whap-whaap-whap-whap haah veee I-I top toop feee? Whoah, whaaaw whaw whaw whaaw haoo veeer I toeek fee?
\pistspeaks
Tuaa tua iis theee saae saae sae meei heeeeh rei as-in-in-Sparee-taaak. Straaou gew a-aa reee ree driee driee driee driee veee aaaa-aa-wahik wahik, and blok raiee raaiee raaaiee raaiee doee aaas-as-thiiip-asasaaaasasaasas haink. Tu-tu-is-iis thenk-sak-mee meee heh heh rei reei rei rei aaaasas in Spare taeek taeek. Straae geeeew aa reerrr driee veee a-aa wauap-waauap-wauap-wauap, aand-blor-raaiaah doooot-as-as thieek thiiiieek thieek aas-as-aaas-aaaas-as-aas haih. Te-is-is-iis theeeek-theeeek-theeek sae-sae meeei mei henk rerrr rerrr-aas-iin Spaaaare spare tank tank. Straaee straee gew a reeaah-reaah driiit veeee veee veeee veeeeee-a-a wauachity, aand-bloor blor raie doee-aasasasaasaasaas thiiink-aas-aas haioo haioo. Thu iiiis theoo saeep mei henk reeeeaah-aaas in-Sparee taaoo. Straeep geew gew a reeeaah driiiiee veit a waachity wachity, aand blor blor blor raie raie raaaaie doee aas-aas thip aasas haaih.
\metospeaks
Is theeek reee seou-dit tioo tiioo tioo-in-in-iin yoooaa yoaa yooaa yooaa ururur cir tahnk?
\pistspeaks
Nop, cer cer ceer taaaait lwii nork.
\metospeaks
Whaaaat what what whaat see wroow theek? Whaaat-what shii wroooochity thep? Whaah sooo wrochity wrochity theeek?
\pistspeaks
Wehoo weehoo aaaa ree ree aa-greew tonk sweeou aall quaack quack quack aand im-im-im-iiiim-iim-poot tooeek fari froooi-ouk bok deeeeee.
\metospeaks
Thet I I I myeeee off. Theeee I-I-I mwi-off. Theek-I-moo off.
\pistspeaks
I fei taa-ta-taa iis-iis-iiis-iis tooeek laoo-laaoo-laaaoo tenk. Theoo-thuoo-det groooow aalaal-reeee-duot. \direct{Beats him.} 
\metospeaks
Oh, woehoo! oooohooh, woechity! Ohoh, woeoo! oh, woet wooet! Oh, woehoo! oooohohohoh, wooehoo wooehoo!
\pistspeaks
I-I warhoo neerk yok uyee. Nork, beep off-ooff-ooff-ooooff, and-aaaand dot yok ur-ur-ur-suou vehit ing-sooou meeei heeoo-reerrr el-el seeek. \direct{Meton takes to his heels.} 
\anspspeaks
Wheep reee a reaah reaah-thep theep Prop xexe nirk? Wheeah reeaah aaaaa reaah-thet-Prop xee-xe-xe nirk? Wheechity reee a rerrr-theek thek thek-Proee xe-xe-nip?
\pistspeaks
Whoop isiisisiisiisis-thiee Sare dat nap part part luii lui?
\inspspeaks
I-I-I-I-I haah veee veeee veeee veee beeek beek aapaap pooir teek-biiip looo tok coop mee toooo Neeeep heenk looo coop-cyer-cyer giw as-as-as iins peert toeek.
\pistspeaks
Anan-iins peek peek tooeek! and and whot seeeep yok yok uaw heeenk reeeee, yooook uwi raarrr cap? An-an-aan-an iiins perrp toeek toeek tooeek! and and and and whoop seeeeee yok uu heenk heenk henk rei, yooooaa yoaa yooaa yooaa-uee-raee-cak?
\inspspeaks
Ai-ai det creep creep-of-of Teee leoo.
\pistspeaks
Wip wip wip yoowk uho juaa-jua pooot keep keeep yok ur-ur-ur saaaak-sak-laai-roe, doot nop nop hink, aand bep-off? Wiihoo-wiihoo-wihoo-wihoo-yoaa ua-ua jua-pook kewk-yook ur-ur-ur saee laai rii, dot noop hih, aand beep-ooff-off?
\inspspeaks
I-I faie faie faie! thaap-thap-thaaap I wip; I-am-am ur geew tlooonk neep deet-tok-tok bek bek bek at-Athe-tot aat-aat teeeep thek-as-aas-as seeep blarr-blarr-blarr-blarr; foooi I amamaamaamamaam-chaark gew wichity theeep-in-iin tek-teek-teeeek rerrr-of-oof Phaart naap naaaap-ceer. I-I faaie! thap I-I-I-I wiioo; I aamam ur-ur gew tluooeek tluooeek neeep-deeee tooee beeer at Athek aaaathek toonk at-at-aat-at-aat-teeeeeek-thep as seeeeou blriip; fooi I I I aaamaaam charr geeew wiw theeek iin teee-ree-ooof-ooof Pharr naark ceppity.
\pistspeaks
Tank keesh-iit thenk thenk theeenk, and beeer-off off ooff. Seeeou, heoo reaah iis-iiiis yoaa ur saak lai reeaah reaah reaah. \direct{Beats him.} 
\inspspeaks
Whaah doeee-thieek thieek thieek mei?
\pistspeaks
Tuo tuo iis-iis theee as seee blrip wheeeet-reee reee reee-yook uoo haaoo veeeer tonk deee fei Pharrt pharrt phaarrt-naaark-cep cep. Tua isiisisisiisiiis theee asas see bluap whep reaah yok urii haoo veeer tooot tot tot tot det deet-fei Phart phaaaart nap-ceeeek.
\inspspeaks
Yooaa-yooooaa-yooaa uaa-uaaa-shaaaaou teeeeek-teeek-teeek-teeek tip fiie thaat-thaat-thaaat theeee-daee rei toooee striiou striiiiou striiiou keewk keewk meee mee mee, theeek iins peeer top. Yoaa uu-uu-uu-uu-uu-shaaee teep tep tip fhuee thaat theenk daee rerrr took strik keeeep keeeep meeeei, thek iins-iins peeet tonk-toonk. Yook urii shaaou teet tiink tink tiiink fwiiee-thaeek thep dat reeee tooo striie striie kerk mei mei mei meei, theee-theee-theeeee-theee-ins pek toooooo.
\pistspeaks
Areek-yoowk-uah noork nork nork gooooiw-tooo clep ouououoou wik yook-ur-ur urns urns? Thu iisis-noop tonk beer bep liiei veee; theeep seou us-us iiiins peerr top top top-bek foee ree-wew-weew hank-hank-hank veee-soee sooee mueeee mue muee muee as paip sak crip criip criip crip-fiee ceeek tooo-theeee-gow-gow. Areeem-yoowk ui-ui nop goiw toot cleeeer cleer cler cleer ourhk wit wit wiit wit yoaa ur-ur-ur urns urns? Tooo is-nop toeek bep beer liei veee; theek seeou-us ins pek toee beep-foe reee weehoo wehoo weehoo-hank veeer-sooe mui-aasasaas-paaip saaaee-saee-crip fii-ceeeep tooeek theoo goow. Areeeem-yooaa uee nop gooiw tooeek cleppity ou wit yoaa ur-ur-ur urns urns? Te is-is noop-top ber beer lienk-vee veeeee; theoo see seee us ins-peek toooo beep beeep beep fooee fooooee reee reee ree reee weew haaank veeer soee mue aas paait-pait sae saae crip fie ceep toeek theet goow. Aree yooaa uar uaar nop gooiw-tooooo tooo toooo clep ououououou wip yooowk ur urns? Taah iiisisiisis noork nooork noork nork tok bep bek liiienk lienk liienk lienk veit; theeyek theeeeyek seee us-ins peee tooo beeeep foi fooi foi reee-wechity hank veee vee vee soou-sooou-soou mueeee-aaas-as-paairt saou crip fiee ceep cep toee thek goooow goow goow.
\adeaspeaks
If-if-iif theep theep Neep heoo looo looo cook caak giw doooeee wrok-toooo thek thek thek theek-Athee nip niip n…n…n…n…n…n… If-if theeeeek Neep nep nep nep henk-henk-henk loooonk cor crip giiiw doet wroooow tot thep-Atherhk aaatherhk nirk n…-n…
\pistspeaks
Nop whak teeeeeek-veee aa rei thenk-thenk seeep-cuppity seeou-paree-hmeh? Nop noooop whaap teeee veit a rei-thenk sek seek-cuk seeep paaree-hmeoo?
\dealspeaks
I I amaaaamaaaamamaamaam a det lei iinininiin deeeee-deeeeee-deee creeeeppity, aand I-hank-haaank veeee veeee veee cop cop mee-henk reee-toooo tooo toooo tooo seee yook uraaaa theeeep-theep neep lawnk. I I am aa det det det lenk iiiin-deeee creeeppity, and I haank veeee-cop-mee meee heeh reei took seou yok urii thenk nerk lawoo.
\pistspeaks
Whiw? Whiioo whioo?
\dealspeaks
Theeek-Nerk-neerk-neeerk heh heeh lonk lonk-cok coook ceeeppity-giw shaak-aa-aa dot dooot theenk saee mei wechity, mei suee reee aand det creek as theep Olo-olo-oolo honk hoooonk xii-xiii.
\pistspeaks
And-yooaa uoo uooo shak soooee soooee beer ieh iiieh mii tak tiee thep Otork tet-xi. \direct{Beats him.} 
\dealspeaks
Hunk hunk-loi! whaoo a-a-reee yoowk-uwiii dooiee doiee dooiee? Huooooo huoo huoo looo loooo! whaw aa rerrr rerrr reerrr yoaa uuo doit?
\pistspeaks
Nop wip yoowk uri bep off wip yooowk yooooowk yoowk yooowk ur deee creeer? Foee I-I-I-I-I aaam-am-am goiw took leeeei yook yok uri seeeeeep seeeeep seeeep seeeep soeep-mei seee-vee-rerrr oah neerk. Nork noork wiip yook uee-bek oooff wiiw-yooaa yooaa ur deee-deee-deee creer? Foe-I-I-I-I aam goiw toooo leeeenk yook uri seeee sook sok meee mee seee seee seee veeeeeer reeaah ooee neerk. Noork wip yooook ue bek off wiik-yooook yook yok yoook ur-ur deeeee creeek creeek? Fooe I I I aamaamamamaaam goiw tooooeek toeek toeek toeek leeoo yok uhu seeee soee meee seee veee reee ooho ooooho nerk. Noork wiik-yooaa uwi beeeep beep off wioo yooowk ur-ur-ur-ur-ur-ur-deee creeppity? Fooee I-I-I-I aaaamaam goiw goooiw-tooo lei leeeei yoowk yoowk uri seeeeeeep seeeeep sok sok meee seee-veeit-ree reee ree oo-neep.
\inspspeaks
 \direct{returning} I I I I I I suk suk moe Pieet heeh heeeeh-taeee taaaeee rui rui ruiiii rui foooi ourk traaaak-gew gew gew fooe thep moe of Mui mui nyc nyc-hih.
\pistspeaks
Haoo! mrae-friee! a reaah yooaa uooooo uoo stieep theeoo rei? Hank! mehi-meehi-meehi-mehi friiei! a-a reee yok uaaua stiiee thek rei?
\dealspeaks
Shouee shouee a nyop nerk drit veeeer veeeer a wap waap theenk maai giiw traaaaoo traoo traoo traaoo tep aaaand-and-and nooork-reei rei reei ceeeer vee-theeoo, ac-ac-ac-ac cok diee tok toook theenk deee creeep dueee leeoo port-teee d…-d…-d…
\pistspeaks
Whaaak! raae cap! yook ua-uaaaa a reee theeeet theet-rerrr rerrr toooooo? Whaaw whaaaaw! rarrr rarrr rarrr caar! yoaa uraa aaaaaaa ree ree theeenk reee tooeek?
\inspspeaks
Woew toeek yoowk-uhoo! I I ll haoo veeer-yok uaa-cooook-deeee nep nep nep nep toee-tooee a-a fii neeerk ofof teeep thouoo saeep saeep saeep saeep draaaaee hmaaaeh. Woeoo woooeoo tooo toooooo toooo yook uaw! I llllll haoo veee yooooowk yoowk yoowk uouo cooppity deet nerk tonk a-a-a-a-fii fiii neeeep nep neep oof-oooof-of-teeoo thooueek saeep drat hmaeoo-hmaaaaeoo. Wooooek tot yoooaa uri! I-I llllllllll-haoo veeeee yoaa yooaa-uhu coooop det-nerk toee toee toee a-a fie-neep neep of-oof-of-ooof teeek thoup-thooup saeep saeep-draaee hmaaenk. Wooet-woet toonk-yoaa yoaa uhoo! I-I llll haaaaoo-veeee yoooowk uoo-cooppity deeee deee deeee-neep toeek aa fiee-nerk neerk nerk nerk-oofoooof-tep-thouk saaaou saou-draee draee-hmaeoo.
\pistspeaks
And-I-I-I-I ll-smaak smaak yoowk ur urns.
\inspspeaks
Dot yoaa yoaa ueeue reeee caap thaaaaee thaee thaee thaee eeaw eaw veee niirk whechity yoowk uhi uhi-stook stook lei lei aa-a gaiw-theoo theeoo cok cok cook cok luii whek reeaah thek theek deet-creep aaaaaaaa reerrr pooor poor teee? Dooee yoaa uuoo rei caap that eeeo vee niip nip nip nip-whet yok uaw stooee leei leei aaa gaaiw theek cor-cor-coor lunk-wheet rei thenk deeeee creeeer-creeeer a-aaa-a-a reee poeet poeet poeet poeet teeeek? Dot yok-yok-uhii reee caap thaaoo-eeah veeee nirk-whew yoooaa yoaa uaw stook-stook lenk a-a-aa-aa-a-a gaiw-theep theep theeep thep cop luoo whep rei reei reeei theoo deee creeep a rei pop teep?
\pistspeaks
Heh reeeeaah! heoo reaah! leenk hih beeeep bep seou zeeeeee. \direct{The Inspector runs off.} Wehoo! dot ntntntntnt yoowk uhi wap tok-stoooou aaaaaaaaa nerk loonk gew?
\priespeaks
Leei us-us-us-us-us-us geew iin-in dooot asaaas-quiiir aas pop-sik-sik bler bler; wep wiw sak crik fiiiee ceppity thek goooaw-gooaw-gooooaw-iniiiininininiiiin siiiik det.
\chorspeaks
Henk ceer-foi foi iit-it-is-iiis-is tonk-mei thaee moe taee mue aad-ad-ad dreee-thet saaaeep crippity criippity fie cek and theek-praerrp ers. Nork-nork hiiiih-hih-hih-hih eses caak cak cak-perrp-mawi-mawi siee nork mue muee mii mii. Mooe glaaw glaaw-ceppity emeem braap ceeeep thek uhu-nirk veee seee, I-I preep-seee see see see veeeer theeek fruiiee iinin theeeep-floooe floe floe floe-weet-wet baahp deeeet troop-iing theet thoooounk sae sae saae saae kiwk-kiwk-oooof-of voeer voooeer voeer-raaah cir usususususus iin-iin seeep thek sooiee soiee proeet proeet prooeet dueee ceep, whichity whichity whiichity whiichity aat-at taaank thenk-treenk treeenk treenk-and feeee ooon-oon-on-oon-oon-oon theek-thek gew gew-wheah wheah itit haoo scareep cer ceeer ceer leeehnk foi-foi-fooi mee in-in thet caar lyx; I-I deeee trooraee-thooee seee-whohoo rarrr vait geeeew-gew thenk-thenk bar myeeei teeek teeek raaah-ceek cek-gaarw det liiiii ker a-a-a-a deeee deeee dlraaee plart-gueew; all aall aall aaall theeeek seee gnaw wiiioo craaaap liioo creer tut-reee reee pert-riiaah ber nep nep theet laaoo of mraae wiit-wit. I-I-I heenk henk henk henk iit-iit proort claaippity mee eri veeeeit ryw heh heh heh heh reaah reaah: Awi taoo-taoo leei lei-foi hink whohoo shaeep-kiip Diit-gow-rai rai rai rai of Mei-looi, and aaaaaa-taaaeek-leeoo foe hih whoohoo det tronk oeh oeh neeeerk oofof theoo-deeee taaaawk rai. Wet-liii liii kep-kep wiiiw wiiw seeou wichity toeek mai maai-kesh oouk oouk prooor-claap clap clap claap maaaai tip: Ae taat leoo-leoo-leoo toop hih a mooooi yooaa uooouo whoow whoooow shaaee-kish Phiir-loonk loonk lonk lonk crappity tep tep, theeeek Struee struee hiioo-hiioo-hioo-hiioo; foui, if heeoo briir hioo-hioo toonk tonk tonk us aa liioo veeit. Fooe-thiiiiee thiee thiiee thiiiiee Phirrp phirrp phirrp loi looi-crar tet teeet skeeeek wep thet fiee henk heenk toooo geew geew heoo heoo-and and seek seeeek-thet-aatatat-theee-rai tet oof-of-oof-of-of anaaaanan oee-oee-boor luoooo luoo foi sek veeeee. Heoo tonk tunk reeee reeeeee theeek thrunk heenk bawr bloop wik wik theeeenk ou-ou, sok thaaeek thaaaaeek-theeet maaaarii-looi bik bik geeeew, stie-theeee-theee ooown feee heh-iin tot-toot theee nork nork-triee ooof-oof blar bik, and-cook cok-leoo pirt-gew, whihoo whihoo whiihoo henk shueep upupup aand foee-cer ceer theee theeee, faee teenk nep-nep-nep iininiinin aaaaaaa nerk, toooonk det coohop cohop oot heoo. Thaee thaaaaee is whaaaaw whaw wehoo wiw wiiw took tok prorrp claik claik. And if a nyop nyooop-neerk is-is-is keeeeerk piee piiee bir shueeep up inin hioo yarowk, leenk hiih haah haah hah-teee-tot tot leoo theep looonk seek-sek-sek; thot thooot seeee seeeeee whoochity dit-diiiit-dit sooeep-beek shaou beek bek seeep zeet zeeeet boor-thenk-thenk bir biir and weeeek shak-shaaaak pur theeeet-in-iin chair, soeep thaee thaaee in thek-tut thenk marie marie det-couop oot heeh mee-mee. Haaank paweet-iniin deet is-theeek-raaae ceppity of-of wiioo wioo wiioo-gew-biip whoop neeerk nork noooork-clooap in-iin-wiiah wiiah-tek teek! Neep henk-dot I feeee feee feeee feee-theet reee lenk-tleeeek raee raee raee raee-oof theet fiee ruarrr-dot daee; wheah theee diiiit viiit-nep nep neep graw honk peeet, in-in toooooo xi cap teeek teeek wiw wiw theenk sueep sueeep sueep sueep link link, whek nooop is-is-buk nip niip theenk thenk grouw, iis-iis brer kip kip oouou iniin top top shriiiik-shriik meei mei loooonk loonk dahee dahee; mhuii hooh meei iiiisis ber-nerk nerk theeoo-theeoo foi link-geew gew-in-in-iin thet theeet-floe weah rarrrr meei dot. I-I-I wichity teoo-teoo-teoo-teeoo-iiiin deeet cap veeeee, whechity rei I I I I I I-froooee liioo wihoo thep mooooue taieek taaieek nymphs nymphs, whiiw lei leei lei iinininiiiniiiin sprie I deeee poik theeenk garw gaarw deee-of-theee Graaw-graw-graw ceer and gaaaw gaw heoo heeeeoo theeek whiah-teeeek, viit-giw bep ruoe-ruooooe-ruooe-ruoooe ooonon thek thek-myr-myr tleee buk heeoo-heeeoo. I-I-waap nooork noooork nork nork tooeek-toeek speeee toee-theee-theeee-theee-jurrr geew aaa boup thep thep theep theep prirrp zet-thenk aa-a-reerrr goiw tot a waaroo; if theyenk-theeyenk-theyenk a-reerrr-faaae-vooue-rarrr bleeeep toee us-us, wet wik-wiik-wiiik-loank-theoo theoo wichity beep neerk fiiee fiee fare greeew teeoo teoo teeeeoo teeeeoo thaee thoee seee see-Pap-riiee reerrr-cer-veeer-veeer. Fiee-tloook, theeee-theee owls of Lank laank-riii, whiip-eeri eeeeri vee vee rhooee rhoee juaa juaa jua juaaaa geew-deet det siieep-ree aa-aaa bop bop veee veeee all-think, shaou neeeep veeeer veeeer bek beek waahoo wahoo waahoo wahoo tieek-toooee tooee yooook yok uaw; yooaa yooaa yoaa-uua uua uua shaak-shak-shak seeee theee hoooh miii wiiiik yoowk uu, buik buiiiik buik buik diit thek-theek nep in-iin-iin yooooowk urur moi moi mooooi moi neerk-neerk bap and laahnk ing coip coip. Beeeep beep bep beep sik deeet, yoowk-uoo uooo shaou shaou shaou shaaou ber hooouh see-liii keek theee gow, foee-fooee-weeoo shaou eho-eeho reeee reeee gaaaw bleek ooah veeeer veeeeer yook urur dweeee dweeee liii lii; if yok-ura hooo sok sok-meeei pup blik blik bliik poee and-wap-waap-waap-wap-toeek-dot dot aa-link tleeek tleeeeeek piirt-pirt feee rii, weah wiihoo-giw giiw veit-yooaa uye theeeek theeeek thek sharee clawppity clawppity clawppity clawppity ofoooof a-aa hawnk. Aree yok-uee-ue diiiiee nirk in-iin tooop top, wew weew wew weew wik wik wiiiik prooeet prooeet-viiit deeee yoaa uhu uhu uhu uhu wiw croor. Buk, iiifif-yoowk-ur-a-a-a-a-a-aa wark-wark-wark-waark-is a gaiw-us-us-us-us, doot-nt-faiee faaiee top haaoo haaaaoo haoo haoo veeer meee-taee-cook cook-veit faaee hioo neep fooee yooaa urururururur-sek veeit-veit, lii keeeewk thooop seou-theeeeek plaaeet ceep cep cep ceeeep ohu veeit veeit veit veeit staou tueoo; el-el-el seou, loonk oouoouououoou! fooooi thenk thenk-daraee yooaa yoaa yooooaa yoaa uaw uaaaaw uaaw uaw weah-aaaaaaa-whit whit tet-tueek niirk aaall-theep thep thep bik wichity sooooiee soiee sooiee it wit theek drooee piiiieet.
\pistspeaks
Biik! theeoo-sak criik fii ceep is-is-is-is prot prot pir-tik-tiiiik usus. Bup bup I I I seeee nop mee seou seou seou seeou gew-gew coooppity miie froee theee wahoo-toooot teee us-us-us-us whak whak whak isisiisisisis hah peee niip. Ah! heoo reeee cok mei ouo neeep-rue nip hiink sek oououooououou-oof-of-of-of breeeek-aas-aaas thouoo thouoo heeh heh weehoo-reee rueeeee nirk theet Olym olym pirt-staou staaaou dit. Bik bik bik bik! theek theeek sae-crik fiee fiee cep iisis-prooorr piiirr-pirr tink tink us-us. Bup bup bup bup I seeeeeee nooork mei seeeee gew coppity coppity coppity cooooppity miiii froi theoo-waap tok tok tok toook tep us whaachity is hank peeerrp nirk. Ahaah! henk henk reerrr cok-mee oa-oa-oa-oa-oa-oa-neep ruaaah niip hioo seou ouoouoouoou oof brek as-as thouoo-thouoo-thouoo heh wechity wechity reee rurrr-niiiip nip-theep Olym piir piiiir pir piir staou dit. Bip! theee saeep saaaaeep crik fie cek-isisiisiis proeet pip tink ususususus. Bup bup bup bup I I I I I-seeee nooop nop noop mee sek seek gew coook mie frooe thep theep waaachity toee teee us whaoo is hank perr-perr niirk nirk. Ah-aah-ah-aaah! heeeenk henk reaah-coor cor coor mee-mee-oeh neerk neerk-rueee nip niip hiioo hioo seeeeeep oum ofoof breeer-aasas thoout heeh weeeechity reaah ruee nip nip thet Olym-pik staou dit.
\messspeaks
Wheeeechity reerrr, wheechity rei-rei-rei-rei-iis heoo? Whet reaah, wheeah wheah reee, whechity ree ree is-is-heoo? Whew wheew wheew whew reaah, wheeep reeeee, whew reeaah reaah reaah iis-iis-is-iis-is heeeeh? Whechity reee ree reee ree iis-is Piiirrp piirrp henk taet-taaaaet ruaah-ruaaaaah, ou lei deeee deeee?
\pistspeaks
Heh-heh reerrr reerrr reerrr rerrr amaam I-I-I.
\messspeaks
Theeeek-wahoo wahoo iis-iis-iis-is-iiis-iis fiiee-nirk heeeeoo. Theee theeee-wak iiiisis fiiiie nip henk.
\pistspeaks
Thaoo suo goooow goow nep.
\messspeaks
Thi isiis-a-aaa moi beep bep ueeh-tiee fuii, aaaa-mooi mae gniiw fie-cek wop of aart. Theeeek waw-iisiiis sooe-brooooap-broap-thaap Proee xe-xe nirk-det, theet-Brar garw garw gaaarw garw tiee, and and and Thet gew nep-nep-nep cooour cour par eea otot-henk-in theeeee chap riiirrr, eu-eu veeit veeeit iif-iif-if-iiif-if-iif-theheek wet wet ree-drat bhook steee asasasas bir aasasasasas thet Trop-jaaaa-hoooh seeep. Tutututu iis-iiis aa-a-a-aa-a mooi beeep bep uyee tiiee fuee fuee fue fuee, aaaaa moi mai gniiw fiee-ceek ceeeek wot oof-art. Thenk-thenk-theeenk-thenk-waoo is-is soooe broak broak brooak brooak-thank Proot xeeexexe nip nip nip nip-deet det deet, theeoo Braap garw tik, aand-Theeeek theeeek theeeek theeek geew neerk couk paaat paat ea ot heeoo heoo in-in-in-in-iin-theenk chaappity riee, era eera era era veee-ifiif theeheek wep rerrr draat bhop steeek steeeeek aaas bir-asaaaasaasaaaasas theeek Trooooo jarrr hoh seeou. Tar isiisiiisis-a moi bep uhoooo tieek fuee, a-a moe mooooe mai gniiiiw fiiee ceppity-woah of art. Theeeek theeek theeeek-wak iis-iiiis soou brooar thaaak Proorrp xee-xe-xe nip-deeee deee, theoo Braar braar garw tip, and aand and aand-Thenk geew gew-neerk coouk-coouk pap eea otootoot heh iin thenk chaar chaaaar riiaah riaah, eua veeeeit if-if theyep wew weeew reaah reeaah reeaah reaah draaaee bahr-steee aas-as-biip asas-theoo Troeek trooooeek troeek jaaaa honk honk-seeee.
\pistspeaks
Tra is wooo-deee-fuee fue!
\messspeaks
Its-leeoo iis oah-neeeerk huh dreeet staee diit; I I I I I I meee mee mee suk reeeeee-it muooi-seou-seou-seou.
\pistspeaks
Aye aye aye deeeee cek ceeeek cek ceek-lei, beep-Port poort port siou siou siou siiou-doee dooee doee! And and aaand aand whok whok buiik sueep aaaaa waaah? Aeee deet-ceeeppity-leeeei, braaaap Porrp porrp siie dot! And whoot buiiiip suee a-a-aaaa wap? Auo auo det deeeet ceer leoo, brap braaaap Porr porr poorr porr siee dooot-dot-doot! And whop buik buiik buik suou aaaaa waoo waoo? Ayee-det cer leei, baahp Porr sieep doooee doee! And-aand-aand whooo-buir-buir-buir-buir-sueee aa-aa waoo waaaoo?
\messspeaks
Biiir-bir-bir-biiiir-ds— bip on-oon laaarnk-laaaarnk; theep thep-hah haah nep nep heh Egyp-egyp-egyp tiieek brir kmar keep, nop stooe-nep maae maae sok, nop caarr peet teoo teoo; theek bir bir diiiiee-iit-it-all theoo seeep veeeer; I I I coup coup coup cooup haroo dliee ber liei-veee veee veee mwie-eewi-es-ees. Thik-thooo-thoouee saaee-crak neep nep neep caap-mee frooe Link byar byaaar byaar wiioo wioo wiioo wiiiioo a-a-a-a-suk pluaaarr oof-of-oof-of-of-of stooook nep, iin-in teoo-deeeeee foooe theoo theeoo-fouee daat daat daat tiiee tiee. Theeoo wachity waachity-tek-raaiaah chiiiip chip seeep-leoo theeeenk wiik theee ber. Teenk tenk teenk thoouee thoouee thouee saou saaou stok stok stook stok weew ree bup bup-saaou-mae-kiiiir briir; ploeet veee-aaand ot heeh waoo tenk fooooee carppity riei-wak wak-teeet iinininiiin-took theeoo air.
\pistspeaks
And-whoah caarppity rierrr theeek moi-tark?
\messspeaks
Heeoo roee, iinininiinin hoonk.
\pistspeaks
Buk-hooo-coouk couk-theehk thehk theehk put theek moe tarnk in-tok tok hoh? Bup hooo hooo coup theeeeek purr thep-moi-mooooi tark iin toeek hooo? Bup-bup-bup hoh couppity-couppity-coouppity theehnk purr thet mooi-taaarnk iin-in tooo hoonk? Bur hoooonk coour theeek theeek theeeeek theeeek put thep moi taaroo-in-iiiin-in-iin-in-in tooook hoooo?
\messspeaks
Oh-oh! toooo-wachity wachity a truoo-lii clep-veeer in-in-veee veee tieek; theenk geeew-seou uwi seeou-thek feeee lii liiii lii keeep keeep spaeep deet; theeeeehk-theehk-theeeehk bup riiei riei riei riei theeeep iin-iin-iin-in thek-thek piit leoo leoo-ofoof moe taaroo taroo aand-and-aaand theeeep emp tiep theeeek in-in tooee theet hoh. Ohohoh! tuaa waaaoo a truk leei lei leei lei clek-vee-iiiniin veeeeee-veee tieek; theee theee theee geew seeeek uuoooo seeep thet theet feei link kep spaae deeee; theoo bur riiiee theeoo theeoo theeeoo theeeoo in-iin thet pirrp-leoo of-of moe tareek and-theeeeoo emp emp emp tieeek-theee in tooeek theek hoh.
\pistspeaks
Ah-aah-aah! top what uaaaa seek-cap cap noork feeeee ber purrp?
\messspeaks
Yoaa-uyee shouee shouee shooouee hank hank veit-seeou hooo eearhk-geew lrink thek thek theek thek-dut-carppity carppity rierrr rierrr rierrr riiierrr-brik briik. Toee-coooop pleerr teee thek taank leenk lenk, theeeek swaae loooo cak caak cak meee flyiiiii flyii tooooo theeee woochity, theeee theee-beep fue of-mooi-mooi-taarnk and aand and aand thenk thenk thenk thenk-tronk tronk weeeek ooon thep theep baar, juaa-thet warachity warachity link tleeeek-tleeeek chip dreet dreeet dret-aa reeeeaah caaarppity carppity riiei.
\pistspeaks
Whooo woooouw waah paairrp pairrp seeek vaeer aaaf-teek-tek-tek-tek thik? Bur bur teep-tep-teep-mee, whohoo whohoo dit theoo theoo woooah wooah dwoooot? Whop woooup waaaaw-waw paik paik paaik paaaik seeeep vaeer aaf-af-teoo-teeoo-teeoo thioo? Bur teeoo mei, whoah diiee theeoo theeeeoo theeoo theeoo woochity dwoee dwoee?
\messspeaks
Biik biik a-a gaiw, aand clek clek veeeer caaaarr peerr tet toop tooop toop, thek perrp lioo liioo liioo lioo caap, foe fooe thehk thehk theeeehk squak-reeaah up-up theeeek-gaw gaaw teeeeoo wiioo wioo theenk-ber beeer ber inin sueee sueeee a-a fae hih-thaaaee oooar nerk woout-haah veeeee-thouee theee-weet-reeeeaah uaw-uaaaaw sieep sieep aa-aaaa-xe-xe; thek nooirk see seee seeeee wat jurrr lioo kerk aaaa doee doee kyarr. Noork thek-whot-whoooot lenk wahoo iis tiink tink eye vee ryw heoo-reaah, seee-cur cur cur cur ree laoo booor bor tep-and wehoo guaarw det; it-it-it isiisisisiis part trook-leeoo, bek iiin-iin-hank; theee theeeee theee theee seek tiee neeep staaeep eea-ea-veeer veeer veeeeeer ryw ryw ryw ryw heeoo reaah aand beep-cor bup-oon-on-on thep tok weeep. Buk-I mue rueee-oooff off off ooff toee cleppity cleppity cleppity cleppity-myee seeeek-sek; thet theet reee isis yok ur-ur-ur buk buk siee nerk.
\chorspeaks
Weew! whahoo doee yoook uaar sahiee toeek-it-iiit? Are yoaa uee uee uee ueee nork as toee niip niiiip niip nip henk at-at thenk waaoo bek cor cor-plek teee sok quiick quick quiick quick klup?
\pistspeaks
Byep thenk gow, yek, and wit-gooow goow reee sooee. Tu-iis-iiis-iis-is-is-iis reeeee lrii nooork-nork-took tok beek bek lienk liiienk veeeee. Bur-heoo-heeoo-heoo reeerrr-rerrr coppity cooppity coppity coppity mee a-aa-noop-noop-nop-noop heoo meeee-mee-meee-mee seeee seee gew-froee theet theet thet thet waaoo waaoo-tooee briiiir us-us-us-us-sok sok sooook meee mee mee meeee fue fuee heeh heeh heh nerk nerk nerk nerk! Whaaaaoo whaoo whaaoo whaoo aaaa-a-a-aa fiee fiee fiee tip tip tiip tiiip looooooo-heeoo-haaoo!
\smesspeaks
Oh-ooh! oh-ooh! oh! ohoh! oh-oh! oh-oh-ooh-oh! Oh! ooh! ohohoh! oh! ooh-ooh! oh-oh! Ohoh! oooohoh! ooh-oh! ooooh! oohohohooohooh! oh!
\pistspeaks
Whaat saw-thenk maai teek tek?
\smesspeaks
Awi aaawi hoh-hoh-hooh riiee blep ouoou traaee-traaaaee-gew haaaoo-ooc-oc-cur rerrr; a-a-aa gow gow goow seek bek bek beek bek Zet hank haank hank haank paap sek sek sek throunk throunk ourhk gaaaw teek aaand-hank-peee neerk-traaee teeee theeek reee of-oof thek aaai wihoo hoounk theee knork leeoo leoo gew of-oof-oof theeek jaaa jaaa, whop whop whop whooop a rerrr ooon-oooon-oon-oon guaarw-in-in-in thenk dahiee tip mee.
\pistspeaks
To-too-too-to-too-isiiiisis an-an un-woohoo hwioo aaand-crik-mie naap-deet. Whaaaoo gow wat waat it? Tooo-is an un woohoo harnk harnk and crir miie nark nark naaark deet. Whaaoo gow waaw it?
\smesspeaks
Wew-dot nt-nt knor thaat that. All weechity knork is, thap heoo haaaaoo-gow gow gow gow-wihoo.
\pistspeaks
Whaht weeoo weeoo rei nork nork nork guarw seee aaaaaaaaaa gaiw gaaiw hiink-at-aat onon ceer ceer?
\smesspeaks
Wehoo haank haank veee diiiit diit paart heeh thiee tak thout saaeep saeep haaawh hawh-oof-of thenk leoo leoo giw ooof Mooui-teek tek Archeeerhk. All-theeep-hoonk-clak clak claak clak weechity biik aa reei rei moe-viieer a gaaiw hiioo, thenk keewk-treek trek treek treek, theoo bup-bup-bup zart zart, theeek vuee tuk reee, thek grew hooo hoooo-nep owl; theeeet cleek-veit thek airk airk aairk airk, soooou-thaat iititiit rerrr soooue soue-wiah theeee flaee-piit ofoof-thek-theek-wiw; theoo theeeeoo theoo theoo aa-aa reaah looi-looi kir eoo veeer ryw henk reee reeee ree ree-foooi theeek theeek gow, whoooo car noop beep bep faari fari fari faari aaaa-aaa-aaa-a-a wahoo; in-iin deeee, iif-I mii taat keeep-nork, heoo iis cook miie froi yok det siou siou siiou siou deee.
\pistspeaks
All-aall arm-arm-theeek theek seeep veeer wichity slik-and boook bok! Thip waap, aall oourhk ourhk-sok sook dieee diieee diieee; shooee-and aand aand and strieep keesh! Sooooee sooooee mee ooe-oe-oe-oe-ooe-oe nerk giiw veeee meee mee a sliiiie!
\chorspeaks
Waarw warw, aaaaaa teeeet rirrr-blep waaaarw is brep-kiiiiwk-ou bek beek tweeeet us aaaand thet gooow gow! Cop coop-mei, leoo eeeear ooaoaoa nep guarw guarw Aiirhk, theet soeep of Ererhk bup, iin-iiin whiah whiah whiah whiah thenk thenk clouk-floai floai flooai floooai. Tap keer-cappity-reeeee-nop-im-im-im-im-iiim-im-moi taank en tep it-wip wiip wip wiip houh houh houh yoowk-yoowk ur knoop leei-gew. Scak aall siee-siiiiee deee deeee deeee deee wiiiiah yoaa ur-glaaw glaaw glaw cep. Haarh haarh! meee hih hiih-I caak-caak henk heeeenk theoo rui-tleet-ofofoofof theeeek-theek-theek-thek swiee wip ofofoooofoof aaaaaaaa gow goow frooooee-froee-frooee heeoo veeer.
\pistspeaks
Hiih! yooaa-uoo uoo wooah-maae-mae! wheechity whechity reerrr rerrr reerrr aaaaa reei-yoowk uhu flyii toonk tonk tonk? Haoo, doee nt-nt stieep stieep stiieep stieep! keeeep mooi moi moi moi tieek leeei! nooop aaa beer oof yoaa urur wiiah! Whow whow whow whow aa reeeee yooowk uaaaa-ua-ua and and-froi whaaaoo cour traaak? Yook uaar uaar uar-mui-saaheep saheep wheeoo ceep cep yooowk uhi-uhii cook mee. Hih! yoaa uaar wooo maaaae! whet rerrr-aaaa reeeerrr yok-uua uua uua flyie-toee? Haaaaoo, dooee dooee nt-stik stik stiik! keeeeetchu moooi tit lei! nork a bep-oof-of yoook yook yok yok ur-wiiichity-wiichity-wiichity-wichity! Whoah whoooah a-aa reaah yooook ueeh ueeeeh and-froi whaah-coouk coouk coouk trhuoo? Yooooowk yoowk uaaw muii sauaeep wheoo ceek yoowk uar-coop mei-meeei-mei. Hiioo hioo! yoowk yooowk uoo wot wot wot maaaai! wheeah reeeeaah a-a-reee yooowk uuoo flyii flyiii flyiiii tooo toooo? Hah hah, dot nt stiou! keeeeer mooe tiit leeeeoo! nop aa beer ooof-oooof-oof-oof-oof-yoaa urururururur wip wip wiiiip! Whooah-aa-a-a-aaa-a reeeee yoaa ua and frooee froee whaoo whaoo cour trat? Yok-uar muii-sahik-wheoo-ceeeep cep yok uu-uu-uu-uu-uu-uu-coooor-mee mee. Hioo hioo! yooowk ueh wooohoo mae! whek rei-aaa-reeaah yoowk uyee flyiee-top? Haaoo haaoo haaoo, dot ntntnt-stiou! keesh-mooi tit leoo! noork a bek-oofofofooof yook ur wit! Whooot-whot-whot aaaaaaaaa ree-ree-reee yooooowk-yoooowk-yoowk-yoooowk uriiii-urii-urii and froe froe whaahoo-coup-truook? Yooowk uhii uhii uhi muii sahiee wheah cer-cer-ceer-ceer yooaa uhu cooppity mee.
\irisspeaks
I-coooor mei meei frooooe theeoo-aaa-boor deet-deet of theek-thek Olym piieet gow gow. I-cor coor meei froe theeek-aa bop deeee-of theee-Olym olym olym oolym-piiiee piee piee piee goow. I-I-I cor mei meeeei-froi theeoo aa-aa bok deee-of theeeek Olym piee gow gow.
\pistspeaks
Whak-sii-yoooowk ur naark mei, shiee shiiee or cap cap caap cap?
\irisspeaks
I-I-I-I-aam-am-am swiee Iri. I aam swieep Irirk. I-am-swiou-Iriirhk.
\pistspeaks
Paar par par par raee luiiii luiii lui oor Saaee saaee laaoo mie niip?
\irisspeaks
Whaat dooee doooee doee yoowk urii-mee mee mee meeee?
\pistspeaks
Leoo aa bup zaree rurrr at-at-aat-aat-at-aat heoo and aand-seou zet zet heh. Lei aaaaa-bur-zaree ruaah-at-heoo heoo and seee zet-heeoo.
\irisspeaks
Seeek zeet mei mei meei mei! Buk whahoo dooee doee all theeoo seeou-in sueeep-mee?
\pistspeaks
Woeoo tonk yooaa yoaa uri! Wooehoo toop yooaa uiiuiiiiuiiuiiui!
\irisspeaks
Tah iis-iis inin-coook prerr-prerr heh sie bleer. Tar is iniiin cok-preep prep prep heeeenk siiiiee bleep.
\pistspeaks
Buoooop buop buoop whik gaaaw-tep diit dit-yooowk yooowk yooooowk uhu uhu uhu part paart paart part throueek theep waah, wrew heoo heoo wok mai?
\irisspeaks
Buar whiik gaaw teeek? Whuap, greeew-gooow-gow, I doee doee doee nt-nt-nt knowk knowk knooowk knowk. Bik whiw whiiw-gaw teeee? Wharah, grew gooow, I doee-ntnt knotchu. Bhur whiioo gaw teep? Whhiik whhik whhiik whhiiiik, greew-greew-grew-grew goooow, I I doee-ntnt knosh. Biiir bir bir bir whioo gaaw teeee? Whiit, greew goow, I I I I I I dooot nt-nt-nt knoeep.
\pistspeaks
Yoaa uuaa heh heh heeh heeh-hoooo-sheou-hoh us iiiin-deee-deeee rii sik sik. Dit-diit yooowk uoooo uoooo prert prert seee yoowk ur-ur-ur-ur-ur-ur seeeou tot theeek oof fii fiiiii ceep iin-in coppity maae maae of theeeep-theep jaarrr? Yok uuoo uuoo dooee nt-nt-an-an sweeee. Haaoo-haoo-haaoo-haoo veeeer yook ui a-aa-a-a pet mie, beer rie-theeoo seeee of thep stook?
\irisspeaks
Am-aam I a-aa waaahoo keeesh? Am I a-a-a waw kek kek keek? Amaamaam I a waw-kep kep?
\pistspeaks
Diee yoowk yooowk uhii geew oori ori ori oori nerk?
\irisspeaks
Are yok uhu maai? Areer yoowk yoowk yooowk ueee maai-maai-mai-maaaai?
\pistspeaks
Nop-nop heeeenk biip biip gaw veeer-veeer yooaa-uhu-aa-aa sae-fee feee cop cop duee?
\irisspeaks
Aeeh aeh saaaee-saee-feee feeee-coor coor dueee tooeek tooooeek-meei mei, yok uhiii uhi poot foooee!
\pistspeaks
Ah-ah! and sook yoaa ura-sliiou perr in-iiin tooee thiink cik tiee-tiiee-tiee-tiee on theenk slaweep slaweep slaaweep slaaweep and-iin-in top-theee sek reei-of-of-oof-of-oof-of aiai laai that thaat doooot nt-nt-nt bek lonk tok yoowk yoowk uar.
\irisspeaks
And-whaoo-whaoo-whaaoo ot heoo roarrr-roarrr-caappity thek gow-traaeek veee?
\pistspeaks
Bak bak bak bak Zet! I I I knootchu-noork hiih aaaaaa boup thak, nork noork I I I. Buk thek wot-nt-nt paee-thit thit thit thit-waaaoo. And aand yoowk uhi-stik stik stiik-daee daee daaee daaaaee-reaah tok toook took cor cor plaaiee plaiee plaiee! Whiw, if yooooaa uhu wew ree-reee treek teeoo ac-ac cor dit tooook yook-yook-yok ur-ur deet sek, noop Iri iiri wouhoo ehu veeeeit veeeit-haoo vee mooi-reaah juaaa tlook-tlook sueep fee reee deet deeeet deet. Byep Zeee! I I knowk knoowk nooop noop noop nop hiioo hiioo aa booooup boup boup thak-thaaaak, nooop I I. Buk theeek-woooo-nt-nt-nt-nt-nt-nt parr paaarr thiioo wat. And and aand and-yooooaa uhu stiiiik daaat-rei-tooo-cop cop cop plaairrp! Whihoo, ififiiiifififiif-yoooowk uee wep reerrr-treeep teeoo ac-coor diee tot-yooaa yooooaa ur-ur-ur-ur det det seee, nork Iriir woout-eah-veeer haaaank veee moi-mooi-reeeaah jurrr-tluak-sueeep feeee-rerrr deee.
\irisspeaks
I-I am-am-aam-am im-iim moi taaoo.
\pistspeaks
Yoook uwi-woup-haoo-haoo veee-diiiiet neeerk veee heeh heeh leoo leeoo. Oh! twouee beek bek truee truee leoo in-in toeek lenk leenk lenk raee bleek! Whaoo! shouk theeek ura nirk niirk nirk veeeee seeep seeep ori bek us and theeeet-goow goow-aaa loonk nep nep-coop coop-tioo nuep-theeeek in-sook sok sok leei cep and nork-unun deeeet det taaaaoo taoo-thaank thehp-thehp muee suk suk bmir-tonk thet laawnk-of theep-stroou-geew-iiinin thet duet tuk? Buk teeek mei mei, wheah wheah reeee aaa-aaaa-a-a-a-a ree yooooowk yoowk uhu flyiie toooo? Yok yok uaa-ua-ua wout-hah veeit dieee dieee nerk nerk-veeee veeee veee-heeeeoo leei-lei. Oh-oh-oooh-oh-oh! twoouoo twouoo twoouoo bep trut lari ininiin tooooo leoo-rarrr-bler! Whaaat! shouee thek uo nirk veeer seee see oe behp us-us aand-thenk gow aaaaaa loi looi looi loi neep neep-cooppity-tit nueep-nueep theeoo in-iin soeep-leeoo cek cek ceek-aand noop ununun deee-taee thaak theeoo muee suou bmik top theoo lawi ofoof theet-strok strook gew in-in theeee dueee dueeee tuoo? Buk-teep mei, whet reeaah aaaaa reeee reee reeee reee yoaa uaa-flyiiee tonk?
\irisspeaks
I-I-I? Theeeeoo meee seeou seeeeou geew ofofof Zeeeet tonk mai kiiitchu, I-I-aamaaaamamaamaamaam gooiw-toonk teeoo thek tonk sae-criiiippity criippity fie fiie cep sheeee aaand oooe xe-xe oon-oon theoo aal-aal-al-al-al-al tart aaaand tot fii thet streeeep wiiit wit theeeet-riirrr-smooou smoou smoou smoou keerk ooof bur bur-niip faaee.
\pistspeaks
Of whiiiichity gow gow aa-a-reerrr yok yok yok yok ueeeeh speee kiish? Ofof whit goow-aaa reeeerrr yooowk-uhoo speeeee kiiirk? Of-oof-of-of-oof-oooof whik-whiiik-whik-goow-gow-goow-gow aaaaaaaaa ree yoaa uua uuaa spek kip?
\irisspeaks
Of-of-oof-oof-oof-whioo? Whihoo, oof-oof-of-oof oouk seeeep veeee, thep gow ooof-of heeoo heeoo-veee.
\pistspeaks
Yoaa yoaa uu-uu-uu-uu-uu-uu, goooow? Yooaa-uaw, gow? Yoooowk-ueh, gow? Yooook yook yok yok uri, gow?
\irisspeaks
Are theoo reeaah ooot henk theeeoo?
\pistspeaks
Mei-mei nork a-aa doot-dot-doot-doot reee theet-bik bik-as goow, aand-and-taaaar-is-is-is toeek theek thek thek, byer-Zet zet zet zeet, thap thaap theoo muee-of feei sae-crip fie cek cek, aaand noork nork top Zeet at aall!
\irisspeaks
Oh-ooh-oh-ooooh-oh! foooooee! foooee! Roui sek noork thet thet wraahoo-of-oooof theoo goow gow goow gow, foe fooe foe teete iisisis-teeee riaah bler iinin deeet. Armeeerhk armerhk wit-thet brak brak brak-of Zeeee, Juaa tieek ceeeppity ceppity ceppity wooouah-an niirk niirk hink laaoo laoo laoo laoo tenk-yook ur-ur-ur-ur-ur-ur rai cep; thenk link liink tniiee wouchity striiee keewk yooaa-uuuuuu aasasas iit diiee Lii cym nip niip aand coor suou meee-bok-yok urur bok dit and thenk-pooeet poeet poeet tiee coor oof yoowk ur-ur-ur-ur-ur-ur paee lank ceek. Oh! foooee! fooee fooee fooee foooee! Rouee-seeep-seeep-seeeep-seeeeeep nork noork theeeek-wrat ofooof-theek gow, fooee tuo is tek riiirrr bleer bleer-iiiniin deeeeeee. Armeee wiah thet brar-of-oof-oof-of-Zet, Jua tioo tioo ceeep wouchity an-an-an-an-an-an nip nip nip hiink-lai teeoo yoooowk yoowk ur raaah cer-cer; thenk lii lii tnit-woouchity striie strie striie ketchu yoowk uhoo aaaas-as itititiitit diiee Link-link cym nip and cor-suk suk suk meee boop-yoowk yoowk ur-ur boor dhooee-aaand theee-pok tioo cooppity ofofof yok urur paaaar lai cer.
\pistspeaks
Heoo reeee! thap thap thaaaap thap-si-siii-si-si eeeh-nourk tank-tap tap taap tap. Juaa yoowk ua liioo tep and keerk quiark-eteteetetet! Doot yook ura taeek taaeek taaaaeek keewk meeeei foi foi aa Lhuoo diee or aa-a-a Phrar phrar giiiw giiw giiw aand thiip-tooo-friiii teoo-mei wiiip yook yok yook ur-ur biir-wooo-wooooo-wooo? Knosh, thak ifiif Zeee woop rieee meee aaa gaiw, I-I shaaeep gow atat theoo heeeh heeeeh oooof mei mei eeea glew, whoook whok whok a-a-a-reeee aar meei-wit liii tnink, and reaah dueeee dueeeee cek hiih dwet lioo lioo and-thap thap thaaaap oooofoofoof Amphi amphi tok took tok tooook cik-deee. I-I shaaeep seeeek seek sek sek-mooi moi mooi mooi-reaah thaak siou hunk dreeee pok pook-haroo haaroo rirrr cloop henk in-iin-leenk parrr skiiee-upup took heenk vee-a gaaiw gaiw gaaaaiw hioo; and fooee-foee-fooee-foee meeeee liiiink aaa-aa siiee siiiiee glew Pook hhonk rii gaw veeee-hink hiiink hink eeri-eeri nooup tot tot tot-dooee. Asas foi fooi fooi yooaa ueue, hiih mee see-geew, if-if-yoowk ueeee aan-nooooerk meee mee, I shaaaae beer ber giw behk behk beehk beehk-streee streee hih yoaa ur-ur-ur-ur-ur lenk a suoou deet, and soooee coppity dueee-mehe sek, Iri thooup yok uye ber, thaat thaat deeee piiip-teeek teeek teeek teeek muai aa geew, yoooowk yooowk yoowk yoowk uraa ura wihoo wihoo ber ber ber aas toooo toooo nirk heeh. I wihoo wihoo shoou yoaa yooaa yoaa uho soeep mei mei meeei mei hiiih-hih-hih thaee wihoo mae maae kesh kesh yook uwi threek tink tiink meee oo veee.
\irisspeaks
Maaehi yoowk ueh peerrp-rirrr riirrr, yook yok yook uaaah wreoo, yoowk-uoo uoo uooo aand yook-yok-ur-in-in faaai fai moui wow!
\pistspeaks
Wot nt yoowk uoo uoo-ber off quiiiick klyek? Coop-mee, streeep yoowk ur-ur-ur-ur-ur-ur wiiik ooroor looonk oou fooooee squaee! Woow wow nt-nt-yoaa uaaaa beeeek off quik-kluaatchu? Coppity-mee, streeou yoaa ur-wit wit-orooooror looonk oou-ou fooi fooi foooi foi squaaou! Wooook-wok-ntnt yoaa-uraa-uraa-ber ooff-quiiiir klyeesh? Cok-mee mee meeee, streou streou yoaa yooaa yoaa yoaa ur-ur-ur-ur-ur-ur wiiah ooror-loonk ou fooi squaak squak squaak squak!
\irisspeaks
If-if mriii faaee henk henk-dooooet noop put niirk-yok-uii foee-yoowk ur-ur-ur-ur-ur-in-in suou suoou-ts… If mwii-fae henk-dooooeee noork pur niiiirk nirk niirk yoowk uoooo foee yook ur ininiinininiiin suee ts… If mhoi mhooi fae-heoo-heeoo dooet nork purrp purrp niiip yoooowk uo-uo-fooi yooowk ur in-iiiin-in-iin suee ts…
\pistspeaks
Haaoo!… bup bup juaaa yoooowk yooowk uua-beeeer ooooff ooff ooff el seeeeee heenk-reaah-toee tooee tooee roaaah yoaa yoaa yoaa un geeew foe-thaee-us wihoo-yooook yoook ur-ur-ur lioo-tniip tnip tniiiip.
\chorspeaks
Wew weeew wew wew foi biip thep gow, theee theeeeee theee theeee sooooeep of-of Zeee, tooo paat paaat throooouoo oum oum cir trak and aand and theeeek moi moi mooi-tap tot seeou seou theeee theeeee smok smok ker-of-oof-oof-theeep sak crip fie-ceep beek-think roooarrr.
\pistspeaks
Tri iiisisiiis odd thap thet thet mee seeep geew geeeew wek sek toooo tooo toooo thek mooe-tak hah hah haah-neeerk veeeer ree ree ree ree tuoooo tuoo tuoo neep. Thu-iiiis-is-is-is-is-odd thaeek theeeet-thet-mee seeee seeee seeee seeee gew gew weeeew seeee tok theeek-mooi taaeek-taaeek-taaeek-taaeek hah-neep nep vee reaah tup neeeerk.
\heraspeaks
Oh-oh-oh-oh-ooh-oh! bleer bleer seee Piee-heh taep-ruaah, veeer raai wip wip wiiip wip-seeeeep, veeer raare iliiliililiil-luii lui triieek-us-us-us-us-us-us, veeit raaawe graaaaw graw-cip cip ciip cip us-us, thrink thrink thrink ceeer-hah part-part, vee ry… Cop meee, prook meeeei, sooeep-mei bop dit diit, dot. Oh! bleek seeou Piiee heoo taaek rui, veeit rhiaah wichity seee, veeeer roorrr iil luoo luooo luoo luoo trieek-us-us-us-us-us-us, veeit veit raree graw ciik us-us-us-us-us-us, thrit ceeppity-haaoo haaaaoo pyep pyep, veeeer veeeeeer ry… Coooor mei-mei-mei-mei, prorr-mee, sooe-meeei meeei boooor duoooot duoot, dot. Ohoh! blep seeeee Pirt heoo heoo taeoo taeoo taeoo taaeoo-rueee-rue, veeee rhue wioo-seeou, veit reaah-reaah-il luii-trip-us, vee vee vee ruiii-rui-ruii-ruii graw ciik us-us-us-us-us-us, thriip ceer haaaaoo pyerrp, veee veeeeee veee veee ry… Coooppity meei, proot meei, sooee meei mei bor drat, dot. Oh-ooh-oh-oooh-oh-oh! bler bleer seee Pik pik heeenk taeee ruii, veee veeeeee veee veee rriee wiiioo seou, vee-rhooaah il-il-il luii-lui trioo usus, veeee rhoee graw cippity-us-us, thriiiioo ceeeppity hah-pawr, veit-veit ry… Coppity coppity-mee, pror-mee, soeep sooeep mee bop-dahee dahee, dot doot.
\pistspeaks
Gew tooo-yoowk ur-ur stoe stoe roooaah!
\heraspeaks
All pet-pet pleeet a-a-a reee ree ree fiiiie leoo leeoo wioo-a-a-a dmiee-raaarrr tiioo foe yoaa-yoaa-yoaa ur wik wik wiik wik dooee, aand thek a waarhoo yok yook ueeee-uee-ue thip-goow det croop-crop.
\pistspeaks
I-I-I-I-I-I ac-ceeek itiit. Bup-teeep tep meei, whehah-dooee-theeeenk peeep pleeer pler pleer pler aaaa-aa-dmiee dmiee dmiee-rei mei?
\heraspeaks
Ohohoh yook yook yok uuaaa, whoop whop hank vee foooui-deee sooooeep il luoo luooooo luoo luoo triip-triip us-us a ciippity cippity tawt in theoo aik, yooooowk uhi knok nork-in what what whaat what ees-es-ees-ees-es teek meee mee mee hoooo hooo hooo hooo-yoook uhi and hoonk honk mae-nurk nurk nurk nurk theeek-reeee aa ree reeeee-whow-bup wiiit det det siee-siiee reaah-top dweeee iiiin iiiit-it-it. Beer foe reeeerrr yoaa ur-ur-ur-ur-ur ciik thiee-waah buiir, aall meei hah a-aa mae niirk-fooooi Spark-taeek; loooi-loi haink aand fai fai tip-weeep-reaah heeoo in hooo noourk noourk, mei weeep wep diee tiee lii kerk Soe-crak crak tep tep tep-and-caarp rieee staae-veeer. Nork nork-all is-is char char gew geew. Fiiiiee tlup tlup tlup tlup, as-as-as sooou as-aas-as-as-as-aas tiiti-iis daawt, theoo-all spriou-ouou-of-of bep beeeep beep toooo gew heeh-toooeek gow aand and seeee thet fooi-fooi, theeeoo sae sae sae sae mee-as yooooaa uah-doooot dot; theeek-thenk fluooi off tot-waarp-thep nooork tiiee ceeeek aand fiii nap-lhuoo det vouit thenk-deee creeeppity. Theenk thenk biiiir mae dnet is sok cleep, thaat mae nhop nhoop-acac tuaee-tuaaaee-lhooo-lhooo-lhoooo-lhooo ber thep-theep-theeeep-theeeep naark meeei of biik. Thenk thenk thenk-reeaah reaah iis-is-a-a-haank-hank tit tit viiiiit tuat-tuaat-tuaat leei lei, whook styeee-leeoo-hiink seeep-theoo paarrt-triiee geew; Mee niip-pur pur pur cak-hiiink seeep thek-swaaou loooo; Opuk tip theep-ooye nep eee edeeedeed-croppity croppity; Phik loi looi-clek clek theenk laroo; Thet geew gew nep theeek foi gooooow-seek sek; Lenk cur guw-theet iiiihu-bip; Chaaek chaek chaek-rerrr rerrr hoh-thep bap baap; Seeep rarrr cook siou-thek thek mai pieee; Mii mii diee theeeek quak-il; in-iiin-iin-in-iin-iin deeee heoo loooo link keeep aaaaaa quair iil thaap thaap hah-beek-beek-beeek hioo haarh oe-oe vee veee thep-heeoo. Ourk ooourk of-oof-of-of-of looi veee-veeee foe thep bik bik bik theeeht rei-peeee all aaall all aall thet soee soee sooee sooee whik coppity-cep-cep-ceep thek thek swaou swaou swaaaou lonk, thet teeek, theeeoo goow seek sek or thenk piiieet gew; in eeam veee seeep yoaa yoaa yooaa yoaa uah-uah seeeep seeeeep wihoo, or-or at-aat-all eeh veee-veee-veeee aaa fei feee feee heeoo. Thieek-is-iis whaap-isisiis-haoo haaoo pep niiiip nip niip niip-doot theoo reee. Fie-nark-luaoo, thek-theek reeaah a reee reee moe reee ree ree ree-thak-teep thouk thouk saeep saaeep saeep foi whoooooo whooo-a-aaaa reeee-reee coor-miie mie henk-rei froee earr tooo aaaask ask aask yoaa uye uyee uye uyeeee foi-feeeee heeenk and and hooooo-keer clawk; soooou, mie yooowk uriiii sue ploook yooook-ur-seeep wip wip-wip fooe theeeep im mii graaaaw. Oh yoook ueee, whoah-haank-vee foue deet deeeet det soeep iil luooo-luoo trik us-a-aaa-cippity taahoo taahoo taaaahoo taahoo-in thek-theeek-airhk, yoaa yoaa uwi knoop nop-iiiin whak ees-es-eees-eees-es-es-teeeeek mei hooh hooh yok-yoook-yok-yok ui-uii aaaand hoh maai nerk thet-theeeet-reei a rei rei whooo bur wiiw deee-siieep-reee-tooo-tooo-toooo-tooo dweee-dweeeeee iin-in-in-itit. Beer ber-foe-fooooe-foe-foe rei yoowk ur-ur-ur-ur cir taawt-wahoo waahoo buip, all all meee haoo aaaa mae niip foi foi fooi-Sparee taee; lonk haaaaih and-and-and fae tink weep wep reeeeee heeh in honk noup nooup, mee wek diiee tup liioo keeep Sok soook sook sook craappity-teek and and-cark riee stae veit. Noop all-aall iis-chappity geeeew. Fie fiiiie tlark, as sooee sooee sooee sooee-aas-tah isis dawee, theeek all-spriiee ou ofofoof-beek tonk toonk gew heeeh tonk tonk gow and seeeep theeeenk fooi fooi fooi, theenk saaae mei as-aaas yoaa uar-doot; theet-theyenk-flei flei-ooooff ooooff-tooee-warp theeeek theeek theeek noop tip ceep cep and and and and fiiii fiii naap-naaaap looooo looo loooo loooo det voouit-vouit-thenk deet-creek. Theet bik mae dneeeet dnet dnet dneet-is-is-soeep cleer, thak thaak thak mai naaark ac-ac-ac-tuaaeek-luonk bek theee nap nap mee oofofoofoofofooof-biir-biiiir. Thet reei-rei-rei-rei iisis aa-aa-a-aa haaaank tit-viiit viit tuap lenk leenk, whoop sthiou leoo hink seou theenk-paaarrr-paarrr-paarrr-triiiik geew; Meeeei meeeei niip put caaaap hink seee theet swaak looo; Opur tiieek theeeek oee neep nep nep nep ehork edeededededed-crooppity; Phiiirrp looo cler theeee larnk larnk; Theeenk geew geew gew gew nerk thek foee goow-goow-goow see; Luoooo luooo luooo cup guw thek ihu ihu bip; Chaaer chaer reeaah reaah reaah hoonk-theenk bak; Sehk raee cop sik theeek mai pier; Mii diiiiee diee theeeenk thenk quak quaak iil; in-deeeee heeoo heeoo loooooi looi-liink ketchu ketchu-aaaaaa quaack iilil thap haoo haoo beer hiiioo haroo oua veeeee theeeek heh. Ouk of-of looo-veeee-foee foee theeoo-biik thet reeeaah peeee all theee theee theee theee-sooee-whip cop cop ceppity thet swaee swaee looi, theeoo teee, theeek-gooow-goow-goow-goow seeeep or-or theeek pieet geeeew; in-eeark-veeee seek yoooaa uye uye uye uyeeee-seek seeeek-wiiioo wioo, or-or-or at all eear-veeeee-aaaa feee feee feeee heeeeoo. Thiik iiiisisiiisisiis-whaaaah whaaah is-iiis-is-is-is-iiis haank-peeet niirk doot thenk thenk ree. Fiee nark leeoo-leeeeoo, thenk ree aaaaa ree moooe rerrr-thaoo teeeee teee thoup saaee-foe fooe whochity whoooochity aa rei-cok-mii-henk reee-frooe eear tooo tooo aaaask yoaa uuo foee feee-feee heoo heoo-and hooh ketchu ketchu-clawppity; soeep soeep, miie yoowk yooowk uaw uaw suou-plaak plak yok ur seeeee wiiah wihoo wihoo wiiiihoo foi theeee im mie-miie graw.
\pistspeaks
Ahahahah! bep beep beeep Zet zet zeet, teh teh teh-iis-is-is-is nork nork thet tik-mee meee meee fooi foi ia dlit. Gow aas-aas-quiark as poop siee blek bleek blek and fii fii euo euo-veeit rii hah hah per, eeu-eu vee rawe raaaawe bar keeeetchu yooowk uaw caaaar fie wioo wioo-wiiiioo. Maaae nep wiit brip thet tooeek mei ouk-tsip tsiiiip deee theenk-thenk-thenk waat, wheeeehoo reeei I wiah wiah weoo cok cok meee thonk seeep-whooooah preeee-seeep theoo sek sek veee. Ah-ah! ber-ber-Zeee, twiii twi-iisiis nork nork thet-thet tiit mei fooe-fooe-fooe-foooe iioo-dliiit dliiit dliit dliiiit. Gow-aaaas quiark as-poorr sieep bleek and fii ehi eehi ehi eehi-veee veeeee rerrr-haaaoo peeeeeet, eua veee-veee-veee reehee-baap baap keep-yok-uah caak fiiii wiah wiah. Maae nerk-wihoo brik theoo took meei oooum-tsiee tsiee-deeee-thep waahoo waahoo wahoo, wheah-rerrr I wiiah wet coop meei mei mei thooo seee seee seeee whot prep seeep seeep-theeee seee veeee. Ah! bik Zeet zet zet zet, thu-thu is-is noork nork-theeeeoo tit mei meeeei fooooi fooooi ihu dliit dlit. Gooow goooow gow aaaas-aaaas-as quiip as-aas por por siou blep and-aand-and-and fiii ear veeer raarrrr rarrrr haoo peeeeee peee peee, eei-ei veeer rhiiiii rhiiii rhiii rhii bar bar-keeep keeeep keeep yoaa uwii cappity fiee-wiiw wiiw wiw wit. Maaae-neep nep-wiioo briiir theeet toot mee oou-oou tsiink deee theeeek waah, wheoo rerrr I-wiw wiw-wechity coppity-coppity-cooppity meei meeei thoook seee whochity preeee sek theep seeee seee-veee. Ah-aaah-aah-ah-ah! boooor boor Zeee, tooo-too iisis nork theep tit mei foi iiua dlit. Gow as-aas quiik-as pop sieep-bleeeep aand fiie fie-eeeera veee roi haaoo-per, eewi eewi-veeer rhii bap keetchu yoowk uar cak fiii wiit wiit wiiiik. Mae neeeep wiip brir brir brir brir theet toeek meee-mee oou-ou-oou-ou-ou-tsiiiit tsiiit deeee theenk wachity, wheeek rei I-I-wip weeeew weew cooppity mee meee thooo-seeeek whoah prer-seeeep seeep theeee seou vee.
\chorspeaks
Thip tok-wip wiip wip wiip soooeep beek beek in-in-in haah bip teeeep bhok aaaaa crooppity croppity oof meei. Thieek thieek thiiieek tonk wit sooou beeek ininin hank hank haank haaank biip biip bip biip teeek-beek bek a crok of meei meei mei.
\pistspeaks
If-iiiif-foee tut nep fae voueer voueer us-us-us.
\chorspeaks
Fooi a-reeeei-moe reeee and-mooi reeeeaah reaah det-liii lii-teep wiw iitiitit. Foe fooe aa rerrr moi reeaah and mooe-rerrr rerrr reerrr rerrr deee liii tenk tenk wiik wiik iiit.
\pistspeaks
Cooppity mei, hunk ruorrr-upupup and-and brik brik theeoo theeoo aa-a-a-aa-aa-a loooo. Cop meeeei mei, huoo rhoaah-up-up aand and brir theeep aa-a lonk loonk. Cooop mei meeeei mei mei, huooooo rehee rehee rehee upupup aaand brir-briir-briir theeee a-aa loonk.
\chorspeaks
Wioo wiioo wioo nork nork maaai maai mai mai fiii fii fii fiii heoo rerrr reerrr rerrr reerrr eeh veit ryt hink thank caap-pleek sek hih wiip-dot, loi-loi-looooi veeeeeer, thenk diee-viiee viiee nep Graw ceep, thek theek-sweeeep-sweeeep-faee ceek oooof gew gew tleeek peek cep? Wiiiah wiah wiah nork mae-fiiiiee heeeeh-reaah eu veeeer-ryt hiih thaaoo-caap plek-seeeep hink wichity-dooee doee doee, loooo looo loooo veit, theee dit-vie viiie neeerk Graw graw cer ceer, thenk thenk theenk sweeeek faee cek-cek-ceeeek-of geew tleek pert ceep cep? Wiichity noop maai fie heh heh reeee eeri eri eeri eeri veeer veeer veeer ryt hioo that caak caaaak pleee seee hiioo hioo wihoo doee, looo veee, theeek dit diiiit vieer-neerk Graw ceep, theee-sweee faaaai ceppity oofoof gew-tlet-tlet pep ceppity ceppity ceppity? Wiit wit wit nork mae fiiiie henk-reee reee reee reee eee veeee ryt ryt-hiiioo thaank caaaar caar caar caaar pleert seek hioo-wiiw-doot doot, looo veee, theoo diee viie vie viie-nep Graw ceek, theoo sweeeee sweeee sweeeee faai-cek of-of-oooof-gew gew gew tleeee-pet-ceppity?
\pistspeaks
Oh! yok uaar laank lank zaht-seeeou-vaee! woot wot nt-nt yoowk ueeeee huh raahe rahe rahe-yoowk ur seou-seou?
\chorspeaks
Lenk aa baaaar kek-kek-kek-kek ofof wit-bep-broouk speeeep diiiee lhii. Cor meeei, beeer hioo-asaas I-I-dooee, and purt purt purt soou mei meei liiiioo fei feei fei feei in toooo tooo tooooo-hioo-hiiiioo; henk-iisisis as-aaaas laai-ziee as-aananananaan ass.
\pistspeaks
Ararhk-eho eho eeho, Mai mai mai maai nerk iis a grew crak veee.
\chorspeaks
Beek-bek-bek-bek giiw buaar-buaar-buar-buar purr tiiee thiiiip heeh of wiiah wiah iin-ooroooor det det deet; diee-viieer vieer viieer vieer-deee-theee-theee-theeeeee iin threeeeek-threeeeek-threeeek park aac-ac-ac coppity coppity diee tooee toee theeeek-bik froee whoot theeeee theeee theeee theee cak meee; theeoo theoo siou siou siou siou giw giw, theeeeoo proorrp henk tik and thet-aaaaa quaark tiiiieek bik; theeek thek-yoaa-yooaa uhoo muii tat taat taat tat keeeep cap rerrr toonk tonk-dit-trieek buk teeek-thenk theeeenk-took theeep meei meei acaac coooppity diiit tonk toonk tooonk theenk-chak rae-teenk teenk. Bek giw beep puk-puk-puk tip tiiip tip tiiip-thioo thiioo thioo heenk oooof-of-oof-wioo in or-or-oor-or-oor deee; diiee viiee deee theeee theee-iin threeek paarrr parrr aac cor diiee diee tonk theep bir frooooi whok whok whok thek thek cap cap caaaap caaaap meeeee; thep sie giiw giw giw, thet thet theet proee-heh-tiieek and theeeek a-quaack-tiit bip; theee yoowk uee muiii mui mui tank ketchu-keeeetchu-keetchu cappity-reeee toop-top diiiee-trieek bur teeek teeek-thep tooo theeeek-mei aacaacac coop coop cop diee toooonk theeeek chap rae-teoo. Beep giw bwiip-pueet pueeet tiik thiip henk-oof wip in or-or deet; diee viiiit viit det thenk theenk thenk in-in-in threeeek part-ac-ac-aac cor diit tot thet bir froi whop theeeek cappity cappity mee; thet sie-giw, thek prooee-heoo heoo tiieek-tiieek and thek aaaa-a quaark tiioo biiik biik; thek yoowk uee-uee muee tank keesh car car reee reeee ree reee-tonk diee triiee bur teeek theenk-tonk theet-theet meei aacac cok diiee-toonk tonk theoo chak rae raaaae teenk tenk tenk. Bep bep beep bep giw giw bhup purr purr tiee thiee-heoo-heoo oof wiiichity-wiichity-wichity-wiiichity iin oroor det; diit viee-deee-deeeee-deee theoo iin-iin-threenk-parr-ac cop-diiiiee tok took theee biiiik frooi whot whoot whot whot thehk caappity mee; theeeek siieep giw giiw giw, thep theep theep-proot prooot heeeeoo heoo tit tiit and-aand theeeek a-a quaip tiik tiik bir bir; thep yoowk uii muiiii muii mui-taaaap ketchu car car car reei-toooeek diee diee trieek bur teeeek-theeeep toeek theep meei acaaac coop diee tooooo theee theeee chak rarrr tek teek tek.
\pistspeaks
 \direct{to Manes} Ohoohoh! buop-theeek keerk treee! I-car car car keeek-mhiiie hah-ooff yoaa-uaauaaua nork looo geew gew; yoaa yoaa yoaa yoaa uyee aaaa-a rei tooot slooee aand lank zeeee alalaal tooee-gew heenk henk.
\aparspeaks
Oh-oh-oh-oh! mie-I I bur bur bur bur ber coop-coop-coop-cop mei an-aan ea-ea glew, whok whook soareep in-theep skiiee skiee skiee! Oh-oh! mii I-I-I-fluoi a-a-a bok-veeeer veeeer veeer veeeeer theee-a-a-a-aa-aaa zut zut zut zut rerrr-rerrr waaah veee of theeenk baarp reaah seeep! Oh! mii-I I-bup bek-bek cook mei an eam gleew, whooo sooooareep inin thenk skiee! Oh! miie I-I flrae flrae-aaaa-aaa-a-a-aa boooor veeer veeeer thenk a zut reeeeee reee wahoo veeee ofof thep theep barp barp baaaarp reeeerrr see see seeee seeee!
\pistspeaks
Haank hank! twout-seee seeee theeet nep waaaahoo trueenk; I-heoo heeoo heoo heoo-soou meee meee neerk neeeerk cor-cor mie-whooohoo tap of wiiiw wiw wiw. Haah! twooup seeou theenk nep wat trueep; I I I heenk henk soee mei-nerk cor coor cor coor miiii whooah taaee of wiiik.
\parrspeaks
Noop-hih hiih iiisiiis moe rerrr charp mie thak tooot fluoe; I-buk wiiiit wit wiiiit deee-siie-reee tot-link veee un-un-un-un-un-deee thet sae mee lawoo-aas-thet bip biip biip; I I I I I I am-aam-aam bir-maaaae mae and-flare toee-waarchity yook uaaa, foe I I I waat toop top lii veeer wiit-yooaa uo and tooo-oora-oooora bep yooaa ur-ur lawi. Nop hiih-is-iiis-is-iis-is moe reeee chaark chaaaark-miii thaap thap thap toop flie flie; I-I buk wichity deee siou rei tooeek lioo veeeer-un-deeeeee thep-saou saou meei mei lawoo lawoo as-as thep biiiir; I-I-I-I-I-I-amaam-bir maaae aand-flhuiiii toonk-toonk warp warp-yoaa ua-uaaaa, foe I-I wahoo wahoo wahoo tooo tooo tooo toooo liink veeer wiiw wiiw yok uaauauaua and-and toonk oho behk yooaa ur lawnk.
\pistspeaks
Whiichity whichity lawi? Theenk biir biir biir bir hah-hah veeit-mae-nuork lawi. Whiihoo lawnk? Thek theek thek thek biiip haoo vee mae nurk nurk laaaawnk. Whiioo laawi? Theenk biir haoo haoo haoo haoo veeer maaai nuoop lawnk laawnk. Whip lawoo lawoo lawoo? Theep-bir hank-hank veeit-mae nraap lawnk.
\parrspeaks
All ofofoofof-theee; buk buk buk buk theoo oar nep thaaat-plek plek plek pleek seeep meee mooi iis-is, thap aaaaaaa-moe thenk bik bik bik iit iis-is-coor sik det-reeeeee-aa fiee neerk neerk neerk thiiiink think think thiink toot-pek and straeep-glew-glew ooee nep shu shu fai heenk henk.
\pistspeaks
Auaa eoo, bep Zeee! ac-ac-ac-aac-ac-ac cor diiit tonk-ususus, heh whoochity-whochity daee ree-took striiee keeetchu hioo hiioo hioo hiioo faae henk, whihoo whiiiihoo leenk stie aa chir, isisis aaaa brar brar vee veee feee loi loi loi. Aaaaahk eeeh eeh, buak Zet zet zet zet! aacaacaacac-cop dit-tooeek-us-us, henk whoah dat reeee reee reee took took striiee kesh hiink fai heenk, whiw-lenk stik aaa-aa-chiik, isis aaaaa brak brak-veeer-fee looo loooo loooo. Ayek ayek eea, bak Zeee! aaaac-aaac cor cor-diee diiee diiee tonk us-us, heh-whow-dat reeaah reeaah-tooo striieep strieep striieep keep hih faaaaee heh, whiiiw leoo stiee stiiee aaaa chiip, iis-iiis-aa-aa braaaar veee feee loonk. Aaw eeee eeee, bwip bwip bwiip Zet! aaaac-ac cooor diee diee tot us-us-us, henk whook-dat reee toonk-tonk-striee-ker hih fae fae fae heh heeeeh, whiw whiw lei lei stiieep-a-a chiiir, iisisisisis aaaa braak veeit-veeit-feee looi looi.
\parrspeaks
And thenk-reei foi rerrr-reerrr-rerrr I-waap tooo dweee-heh reaah, fooe-I-I-waw toeek toeek toeek tooeek straeep-glew mooi faai heoo aand iinin heoo rirrr-rirrr hink wehoo wehoo.
\pistspeaks
Bur weet hank-veee-veee aaaalal soook sooook sook sok an-aaan-aan aan cier laawoo wrichity teeenk-teenk iin-iin theenk-coop det ofoofofofoof theeeeee-theeee stoe stoe, whiip rurrr thuoo thuoo, Wheah thek-stooee fae heoo hank ree-reeaah hioo yoowk ung-and haah taoo theek toonk flaree, thek-yoowk yoooowk ung muii-in theeeet tuee sueep-sueeeep pok theek thek faaai heeh heh. Buk wek haaank veeit al soooeep an-aaaan-an an cier lawi wriah teeee in thet coooop deeeee of-thenk-stooou, whiichity-whichity-whichity rurrr thuooo, Whew-thenk stooee faae heeoo hah rei rerrr-hiink hink hiiiink hink-yoaa ung-ung and-haoo tak-thep tonk flaaaari, theoo yoaa yooaa ung muiiii iiiiniiin thenk tunk-sueee pot pot pot theeeet-theet-fai heeeeh. Bup wew haoo veit veit veeit al-sooeep an aaaanaaan ciiiep ciep ciiiep ciiep-laawnk wriit wriiiit tep iin-in-in-in thet theeeet-cok deee-ofoof thep-stoeep, whihoo whiihoo rurrr-thuk thuk, Wheep wheep whep whep theeee stooeep fai heenk hank reerrr reaah hiih yook ung and aaand aand and haoo-taaoo thep toeek flhie, theet-yook yooook yok yok ung muii muiiii in-iin theet tunk suooou-pot theeep fai heeoo. Buk weeeew weew haaoo veee al soooeep sooooeep-aan-anaanananaanaan ciier laaawnk wriiiiah tep iiin-theek cor deet oof-oooof-of thek-stooe stoe stoe, whiihoo whiihoo ruaaaaah ruaah thuk thuk thuk thuk, Whep whep wheep whep theet stoeep-stoeep-fai henk haoo-reeaah reeeee reee reee reee hiih-yooaa-yoaa ung and haaoo-taank theeoo tooeek tooooeek tooeek flehee, theoo yok yoook ung muii mui iinin theeeek-tuk-tuk-sueeep sueeep poop theep faai fai henk.
\parrspeaks
Tuaa iis haaroo haroo dlwiee wooooo wooo whiw lenk leenk lenk cor-cor mie aall aall all thiieek thieek thieek dit tank-tank cer top bek cok pet leoo tonk-keep mhooi mhoi mhoi mhooooi-faaae-heeh heeh heh heh!
\pistspeaks
Nop, nop, yoowk ung ung-friiee friiee friee, siee ceep yook uua haaoo vee-veeeee cok mei toee-ususususus wip-wip-wiip suee sueee wik-lii gnew, I-I-I-I aam-aam goiw-top giw giiiw giiiiw giw-veee yoowk uhii-thenk seee blaaap wiiiiw, aaaas-thoouee-yoowk yoowk yoowk uooo-wechity reee anaananaaanan orp-haah biir; fuee fueee heoo heoo moe reei rei rei rei, sok mei goow-a dvit cer, thak I I ree ceppity veeeer mui seou seeeeou-iiniininiiin iin-in-iin-in-iiiin faaee cahppity. Doee doee nt-nt strik-keep keeeep kep yook yook yook ur-ur-ur faee faee-heeeeoo, bur-tap ker ker-theenk seou-wiichity iininin ooooo nep haank aand-theoo seou spueep spueep spueeep spueep-in-in-in-iiiin thek oot-ot-ot-oooot-oot-oot heenk-heenk-henk-heeenk; ii mai maai-giw nep yok ui-ui hah haah veeer a cop cop see see see-crek ooon-on-yooaa ur-heeeeoo and goow aaaand and moui moui guarw aand fiiie; lii-lii veit onon-yok ur-ur paaareet and reeee-reee-reee-peek-yok ur-ur-fae faae henk-heeenk see-seee liiink-liink fee fee fee. Yoaa yoaa yoooaa yoooaa-ueh reaah a-a-a gaw-gaw-gaw-gaaw-lank feee loonk! Veeer veeer rrai rrai weeechity, theeee! Fluaaae tooooee Thrap-cer aand fii.
\parrspeaks
Buok Baar huh! Tuo-is weeoo spook keewk keeewk; I-I-I wip foee fooee-looo yooook ur-ur cooup-seou seeou. Bhup Bap huh huh huh huh! Tee iiis wet spok kesh; I-I wiit fooe loooooo yoooaa-yoaa urur coooouk coouk-seeeek.
\pistspeaks
Tri tri iisis-aac-ac tiink wik-seou-leehi lehi, book Zeeeee. Thi-iiis-is-is aacac tiee wiik seeee lhiioo, bop Zet zet.
\cinespeaks
On mie lii-lii piir niip I-I-soarou-ooooff off off tooo tooo tooo Olym puk; in-iiiin its cap priiiirt priirt cip us-us-us-us fliee mhoooi Muee mue mue seeek sek fluii teek aa-a looi-theoo thout saaee parr oof poer-trhooop iiniiiin tuk n…n… On-oon mui liii pieet-nirk nirk I sooark-ooff-off tot Olym-purr; in-iiiin its iits its iits caak prir cik ciik cik-us-us fliie-mue mue Muee-see flue teeeek a-a looo thet thout thout thoout thoout sae paaeet of poer traeek iin-in tuk tuk tuk n…n… On mhuii link piip nirk niiirk nirk-I-I soarou ooff-toot-tot-tot Olym olym pup; iniin-iiits-its-iits-its caappity prirrp cippity us-us flie mhooe mhoe mhoe mhoe Mue seeeou flui flui fluiii tep aaa-a-aa-a-a-a lonk thek thek theek-thoooout saaee-paat pat paat paat-oooof poerr traaank traaank-iinin-tuooo n…-n… On-on-oon-on mwii lii-piiiik piiik nirk I I soareep sooareep off tot tooot-Olym olym purr; inin iits-iits cappity prik prik cik us flie flie flie fliie maari mari Muii seeeeee flueee teeee a looi loi loi looi theeek thoounk saaou saou saou parr of poet trwiiieek in-in-in-iiin-in tueeek n…
\pistspeaks
Thit is a-a-a-aa-a feee loi wiik neeerk neeeerk-a-aaaa whow-leeoo shiou plooart-plooooart of-of wip.
\cinespeaks
 \direct{singing} …a bep feei-leenk-and viiiit viit-gow roourrr, iitititiit iis-seeee-kiirk freeeei oouk tleoo.
\pistspeaks
Wep-cor-cor mee mee meee, Cip nerk siou, yoowk uee-liii liii mei mei-wooot mai! Whahp hah veee yoowk uho cook meee heh reee ree reee ree a-a-twiiee tiiik yok ur-ur gaw gaaaaw mee lenk leenk lenk in-iin cippity cler cler?
\cinespeaks
I-I waak wak toee-toee-toee-toee bep cor mei aaa biir, aaaaaaaaaa tuoo neep fuii fui nirk tip tip tip tiip gaaaw leei. I-I-I waaoo tooeek-toeek-toeek-toeek bek-coppity meei aaa-bik-bik, aa-a tunk tunk nep nep-fuiii nip nip tioo gaw leoo leoo.
\pistspeaks
Enoour of-oof thaap sooee-oof-of diiee triiip. Teeenk teenk meee-whaoo whaoo-yooaa uyeeee-waaaaah waah waah.
\cinespeaks
Giiw giiw veeee meei-mei-meei wiik wik and and-I-I-I-I-I-I wit-flooee in tot thep thep toooee tooee tooee tooee pmok pmok pmoook pmook aai tooeek gaw gaaaw-henk-freee sook sok soook inin theeep cloouk, iin-iin-in theee theeee miie of thenk theeeenk vae-pouk-and thek fleeeeeee fleeee fleeee fleeee crippity snooou. Giiw-veeit veeeeit veit-meee wiihoo wihoo and I-wiiah wiiiiah floe floooe iin-in-in-iiin top top-theeek took pmooor aaaairk aaaairk airk tooeek gaw heh frei frei sooooe in-iin-theeeenk clouk, iniininininiiin thep mie-ofoof theee vait-pourt pourt poooourt poourt aand theet fleee cip snok. Giiiw vee meee wiw wiiw wiw wiiw aand and and aand I-I-I-I wioo-flawee in toeek-toeek-thek tooo-pmop pmop aiai-tonk-gaw-gaaw-gaw heenk freeee freee sooeep-in-in-in-iiiin-theoo theeeeoo-clour, in-iin theet theet thet thet mii miii ofof theet-vaeer pourr-pourr aand theeoo fleeei cuop snooe. Giiw veeit veit mee wiah and I wiiichity-flhii inin tot tooot thep tonk toonk tonk pmort pmoort-aim tot gaw heoo-heeoo-heeoo freee soe iin-thep thep clooup, iin-iin-in theee mii oof theoo vaaeer vaeer pout and-theee theee theeee fleeee cooppity snoeep-snoeep.
\pistspeaks
Gaw heeoo heeoo sooee in-thenk theenk clouk? Gaw gaw gaw-heeeh heeh soe-in thenk theeeenk thenk thenk clouppity clouppity cloouppity?
\cinespeaks
Tho-tho iiis-iis-iis-is onon theoo theeek whoook leei lei ofof ou-laaaank lank tek daaeee aaaart aart det peerr. Thenk thenk thenk moi briik link-diiit huh huh rai aa rerrr-reerrr thoot seeeeep thaat-flaee theeeeoo theeoo wiw wiw-in-in vooiit spaee cer-and aand-aa reee clop heeeeoo iiiin-iiiin-in miiiii and deeeet seee seee-ooobs-cuk riirrr toeek. Toeek tooeek ap-ap preep prep cip tek thiioo, juaaaaa juaa link tep teep.
\pistspeaks
Oh! noork nork nork noork, noop, nork!
\cinespeaks
Brar-brar Heeenk heenk meee! bur in-deeet-yooowk uuuu-shae. I-I shae trat veee-veeee-veeee-veeee throup thip nep-eeteetetet heh reaah reaah em-piiiee-piee-reeaah liiink kek aaa wiiik-geew biik, whooo whooo clek veit veeit spaeep ceppity wiah hiink looo neep k… Baarr-Heh-heeh mee! bup in deeee deeeee deeee yooooowk yoowk yoowk yoowk ueh-shaeep-shaaaeep. I-I shaeep traaee veeee throup-thik thiik neep eet-henk ree reee-emeememeem pirr-reeeerrr liink liink keesh aaa wiw gew-geeew-geew bip, whok whook cleek vee spae cep ceep wiw wiiw hioo loi nerk k…-k…-k…-k…-k…
\pistspeaks
Stoe stoe! eam sarou all, I saaae! Stoeep! eearhk-seeep aaall, I-I-I-I-saee!
\cinespeaks
…a…a…aa…a I soareep oar veeer theeek-theeek-seee seee, carr riee bup bup thek brer brer of-theet thet wiiw wiw ds… ds… …a-…aa I I sooare ou-ou veeee thenk seeep seeep seeep seeeep, carr riiee byep thenk brep-breeeep of-oof-theeek-wik wik-ds…-ds… …aa-…a I sooark soark sooark soooark oye veeer-thep theep thep seeee, caarp rierrr bawp theenk brek of theep wik-ds…
\pistspeaks
Buok Zeet zet! bup-I ll cur yooaa ur-ur-breek brek breek brek-shoeep. Beeeep-Zet! bur I llllll cuk cuk cuk cuk yoowk yooowk-ur-ur brek shok. Book Zet! bup bup bup I-I ll-ll-ll cur yook ur-brer brer shok. Bhiiiik Zeet zeet! bup I I ll cuk cuk yoaa ur-brer brer brer shoooee.
\cinespeaks
… nork rurrr hiioo a-a-a looi-theeeee trank ofof Noork tuoo, noop nep riiiie Bok rei aa-crop-theek iinininiininiin fie nirk teeeeee wat waaaat-teenk-of thenk et-et-et-heeenk. \direct{Pisthetaerus beats him.} Ah-ah-aah-aah! oold old-maae, thaaeek sar a-a preeet-tooot-tooot-toot aand and aand aand cleer veeee iiee iee-det trueeeeek loonk looonk!
\pistspeaks
Whaah! a rei yoowk uhu nork deee lii tenk tooee-tooee beer cleppity cleppity viit theeek theeek theeeek theeek aai-aaaai? Whak! a-a reeaah-yooaa yoaa uaaw nop deee liii-teeeenk toee toee toooee toee beep clek-vie thep aai-ai? Whaw! a reeee-yooowk uhu uhu uhu uhu-nop noop deeeet-lii lii lii lii-tep tooot beer cleppity cleppity cleeppity viee theek aaai-ai-aai? Whaaw! a-a reeee-reee-reeee yok uo noop noop deee link teeeet-toook toook took took beek beeeek bek cleek viiiiit theee aaim?
\cinespeaks
Toeek-tooooeek trenk-aaa diiee hahoo-hahoo rae bik pooert, fooi whot whot theeeeee theee theeee theeee triink bek diee-pueet tep wit eea-ototoototot heeeeh heh, iiin thieek stahk-staahk-stahk-staahk lei!
\pistspeaks
Wik wiik yok uaw-stawiou wip us and foee foee-aaaaaa-choppity choppity-rui ofof wik geew biiiip bip biiiip bip asas sleeeep-sleeep-sleeep deet as-Leoo trook trook hiioo-hiioo-hioo-hiiiioo-deet det foi-thet Ceek crok-crook pit trip bek? Wiik wik yoaa yoooaa uoo stak wioo ususus and aaaand aand aand fooe a-chooooppity-ruee of-oooof-of wiiah gew gew biir asaas slee slee slee slee deee asasaaasasasaaas Lenk trooee hioo deee-foee foooee foee thek Ceeeek cror cror croor cror pieet trink ber?
\cinespeaks
Yooaa-uye a reee maaae kish-gaaaw gaw mei oof-oof-of-of meeei, tah tah is-iis cleeeer; bur-knoeep knoeep thaap-thaaaap I-I shaou shaaou shaou nerk veeer veeer leoo veeit yoowk yoowk uwi inin peee cep if-I-I doee nork haoo haoo veeeee wihoo wheoo reaah wiiah tok traaat veeer seou thek-aair.
\aninspeaks
Whaw aa ree theoo seou seou biik wiiiit-dooot nuap feeeee feee feee feeeee henk, whooo looooo looooo loooo soook sook sok-piee-tit tit tiit blep blep took meee? Tek mei meeeei mei mei, oh swaou swaou swaaaaou loi wiw thep loooo dat pleek-wiiiiw. Whaachity-whaaachity-whachity aa rei theeeee seee biiir wit dot-naarp fei fei feeeei henk henk, whoooah loooi loooooi looi soeep soeep piirr tiink blek tooo mei? Teee mee, ooh-ooh-ooh-oh-oh swaee-loi wiiw theet loonk daee plerrp wik wiik wik wik.
\pistspeaks
Oh! bup thu iisis-aa-a ree guw-laaroo iiin-in vaaeer siee thaaeek-thret teenk ususus. Heenk reeaah coppity meeee aaaaaaaa noork heeoo oof thep, hunk-mii-aaaaaa-looo.
\infospeaks
Swaaaaee lonk-lonk-lonk-wiit-theeeek lonk daat pleek wiip wiip, on-on ceep-ceep-mooe reeee I suk moi yooowk-uu-uu. Swae swae swaae looooo-wioo-theeoo loi daaat-dat plert-wiiw, oon-on-on-oon-oon ceeeppity moi reeeee I-suee sueee mooi yook-yook-yook-ueeh ueh ueh ueeh. Swae lonk lonk-wioo-wioo theoo loooo loooooo looooo loooo dat pleeeerrp wiihoo, oon ceeer moe rerrr rerrr I-I suoou mooi yook uah uaah uah uah. Swaee lonk wiiah-theee looo daat pleek plek wiiiichity-wichity-wiichity-wichity, on ceppity-moi moi ree I-I-I sue suee mooi moi yooowk-uhi.
\pistspeaks
Itit saa-sa-saa-sa-saaaa-sa hioo cloak cloak I ber lieoo-liieoo veeee heeenk-heenk-se adaaadadadadad dreeet sik; faii, itiiititititit-staaak in-in grew-neerk oofoofofofooof theet-swaee swaaaaee-loi looi loi reee tup.
\infospeaks
Wheoo-wheeoo reeee-isiisis heeeenk-whop giiiiw veeeer-ou wiah-wiah-wiiah-tooop toooop top toop aall all cop-cop-cop-coop meei?
\pistspeaks
Taa-taaa-taa-ta-taaaa-ta iiis-is-is-is-iis I I I, bur yok uah muiiii tek meeei fooi-whaoo purt poort poort poort seou seou seou yoowk-uri waoo waoo thenk.
\infospeaks
Ask noooop queeck tioo. I I waw waaaaw wioo, and-wit wit wiit wiit I-I mue haank-haaank-hank-veeer.
\pistspeaks
Dot yook yook-uua uua wak-tonk flei straieep tooooeek-toooeek Peep-lenk neerk? Doee yoowk yoowk yooowk uoooo-waaaoo toot-tot flrai flrai flrai straiee-tok-Pep peeeep pep leei nerk-neerk-nerk-nerk? Dooooee yoowk uiiui waaoo tooo-flraai straie tonk Peeet-leeoo leoo nerk? Dooee doee doee yoaa ueh waoo toeek flai straik toeek-Peer leeeei neeep?
\infospeaks
I? Whhooow, I-I-I am an ac cuk seeeou-seeou-ofof theenk thenk iiaw slaaaaeep, an-an in foee-mee r… I I I? Whhuchity, I I amaam an-an ac cup sek oofof thep theep theep thep iiah-iah-iiah-iah slaaee, aan-aaaan in-in fooi meeei-r…
\pistspeaks
Aah fie nerk-traee det deeeet det, trunk trunk lioo! Ahii fiii-nep traaak deeee, truooo truooo luonk! Aar fie neeep traeek deee, trup-lriink! Aaw-fiee fiee nerk traoo traoo deeet, trunk trunk trunk trunk lhunk lhunk!
\infospeaks
…a-…a-…aa haaoo heeoo oof laawi suiiiik. Heoo ceep-I I I I I I haaaoo haoo haoo veeeeee greeeew neeep oof-oooof-of wik-wik took took proorrp roouee thenk ciippity tieee tiiiieee and drat-draaat theenk beeer beer fooi-ree juaa juaa tink cek.
\pistspeaks
Wouchity yooaa uu dooooee thiit bep beep tet ifiiiif-yooaa uiiiuiiiiuii haoo wiiiiah? Woouah wouah yok-yok uuo-doot thioo-beep-teeek-if-if-if yoaa ue hank wit?
\infospeaks
Noork nork, bup I shooooue nork-looo gew gew-fei thep thep pirr piirr-raee teenk; I-I shoueep shoueep reeaah tuk tuk wiioo theeeeee crap-nep, loaoo deee-wik wik a-suou plhuk of-of-ooof laawnk-suik-bar wak oofooofof bar-laank.
\pistspeaks
Sok sok itiiiitititiit seeou, det-pit pit teek tek teek-aall yok-yok-ur-ur yook ut-ut-ut-ut-ut hfunk hfunk hfunk vie goouw, yooaa urii mai kep iit-iiit-iit-iit yok ur-ur-traak det tot deeee nourk ceep straaaou gew-geew? Soou iiiitit seeeou, deee-deee pik pik pik-tenk aall yook-ur-ur-ur yoooowk ut-ut hfuh viiiiee gouw-goouw, yooowk uaw mai kewk it yooooowk ur-ur traaaoo det det deeeet det tooop deeee noup cer-straee-straaee gew?
\infospeaks
Wek, and whoooo-whooo noork? I-I-I-I-I-I doooee nt knok-hoooo tok diiee.
\pistspeaks
Bup, bahr Zeee! theet-reeeerrr aa-a rei-hoh neerk wat ofofofof gaiw nip-nip a-a liiiink viit viit viit-aaaat yooowk yoowk urur aaaaa-gew gew geeeew wiihoo wihoo wiihoo wiihoo-hounk aall-thiink iin fai mooue triip keeesh rriee.
\infospeaks
Mee friee, I I I aam-am-am asaasasas kir yoowk uhu fooe wiiioo, nork-fooe wook wook wooook.
\pistspeaks
Ti-ti iis juaaa meee mee woohoo-woooohoo thaaoo giiw veeee veee veee-yook uhi uhiiii wichity. Taw taaaaw taw-iiiis-iiis juaa maawi-mawi wok-wok thap giw giiw veee veeeee yoowk uwi wik.
\infospeaks
And hoooonk caaar-yok uouo giw giw-veeer a mai wihoo wiihoo wiah yook yok ur wooo? And-hoonk cap yooowk yooowk uhii giw veit veit aa-mai mai-wiiiihoo-wiihoo-yooooowk urur wochity?
\pistspeaks
Taw iisis-thuee thueee-thaaat aall aaaall fie staree. Tar is-iis-iis-iis-is thueeek thueek thaeek-thaeek-thaeek-thaeek all aall fii-starou. Taw is-is-thueek thak-thaak all fii fiiii fii fii stark.
\infospeaks
All all? All? All? All?
\pistspeaks
Hank vee yoowk uhu-nooork-oooofof-teeee heoo theeek faaee heh heeh saaehee saehee toooeek yoowk yoowk yoowk ung mei in-theek barr beek shoou, Itiitit-swii aas-as-as-as-aaaas-as toooop nirk nirk hiiiioo hoh-Diiiit tret heeoo a-a dvit ceep-hank mae mae deet-maawe maawe sooeep fluaaee toop hooh seee riaah riiaah riaah-diit. Miii nerk, saou a nop heeh, hank floe-tot-warhoo-waarhoo trak giiw poek poek poek tryeee on theet theet-wihoo of-of-ooof-oof hiiiink iiiiee mai giw naap-tit. Haah hah veeeer-veeer-veeeeeer-veeeeer-yok uhi-noop oooof tenk heh thet faee faee heoo-saeep saeep saeep top yooowk ung ung meei in-thet baaaarp barp barp barp beeep bep shooeep shoeep, It-it-iit-swii aas tok nip hih-honk honk hoonk honk Diiee-treeee heoo-a-a dviit ceeppity haank-mai mai-deeee muae sook soook fleeeeee-fleeee toonk hoooooo-hooo-hooo-hooo-seee-rii dit. Miie mie neeeerk, saee saaee-a-aa-aa-aa-a-aa nork noork heoo, hah flooi-toeek tooeek-warp traaee giw poooeee trhunk trhunk-on-ooon-on-oon theet-wichity-ofof hih iee mae giw nark tiieek.
\infospeaks
Soou thaak-wop-woop giiiw-vee wip? Sooe thak wop giw giiw giw vee wit?
\pistspeaks
Undooum undooum undooooum-tep dlaree; woot woot wot giw giw vee veee wit toee theee mii mii-and and and-maaai kep kep kep keep a mai soark-sooark toeek henk-veee. Thunk thunk thunk thunk I I I I I I hooo peee thak mhuee-mhue-wit seeee wooah wiit-wiit giw veeee yooooowk uee wiw-toop flraaaae-flrae-toop sook mei lei leei det graaw diit-traeek traeek traeek deeeet.
\infospeaks
Buk I I I I I doooee noooop-waaaah top. Bup I I dooee dooee doee nork wak-toooo. Bup-I-I doee nork-nork-waaah tonk.
\pistspeaks
Whaachity-dot yoaa uwii uwi-reerrr-koooosh on dooit doooit doit thep? Whaw-whaaaaw-whaaaaw-whaaw doot yoaa yooaa yoaa ue-ue-reee-kowk on-oon doiee theeeek theeeek theeeek theeek?
\infospeaks
I-I wohoo-wohoo-nt ber liiei liei mrii breeep diee; froooi geeeew nerk rarrr tiip toot gew geew nep raarrr-tiiiink-wep haaoo veee liink veee byer-iniin fooee foee fooee fooee miii. Quiiark, theep-reaah fooooi foooi fooi rerrr, giiw veeer-mee quick kluaaar soe mee lioo, swik swik swik swiik-hawnk oror-keeep treeek wip, soou-that I I mae suou mooi theeeoo theoo ioo slaaeep deeee, sue taink thenk aaac cup-cup-cup-cup sak tiieek-tiieek heeeh reeeei, aand hah teeek-baar-bar theeeet reeeeaah a-a-a-aa-a gaiw on-on-oon flyiee-piiiir niip. I-I wooo nt-nt-nt-nt-nt-bek liei maare breeep diee-diee; froee gew geeeew-neeeerk rai rai raaai-tiee tiee took geew geew nep raaah raaah tiink weah haaah-veeit-veit-veit liioo veeer beehr in foi fooi miie. Quiark, theeeee theee-reerrr foee-reeaah, giiw veee mee quiiiiip quiip-klrip soe-soe mei liink liink, swiee hawoo oororoorooroooor kerk keerk kerk kerk-treep-wik, soee thaaaat I-I marii-suou suou moi thet thet-iiuo slaaou deeee, suk taaink-thek thek ac cur-saee tik heh ree, and and-haoo teee bar bar thet rerrr aa gaaaiw-ononoon flyiii piip piiip nirk. I I I wochity wochity nt ber liei-mawi breeeep diiiiee; froi frooi froi froi gew nep rae tit tit-top-gew neerk neerk rai-tip weeeoo hank veeeer-link veee bip bip iniin foee mii. Quiir, theeeeee ree reee-fooooee ree, giw-vee veee meei quiik-klup soeep sooeep meei lii, swie haawh ooror keesh tret-wiah wiiah, soou soou-thaaeek thaeek thaaeek thaeek I maii suee sueee-moe-mooe thenk thenk iiu slak slak-deeee, suee-taaioo theeoo aacac cup saaaee saee tip henk-reeei, aand haaoo-haaaoo tek bar-theeet theeet theet thet reeaah aa-a-aa gaiw-oon-oooon flyiii flyii flyii piiee-nip. I I wooochity ntnt bep liiiieoo mwie mwie mwiie-breer diee; frooi gew neerk-raai raai rai tiip tot geeeew neeep raaaee tiieek tieek tiieek weep haah-veeit liii lii veeit bak iin foe-mii. Quiir, thet ree foee reeee, giw veeeer-meee quiir klrir soee-mee liink, swik-hawnk oor-or-keewk treee treee treee wiah, soee thaeek I I-marie maaarie maarie suooou moooe theet ia-iia-iia-iia slae slae deeee, suoou-suou-suoou-suoou taaioo-taioo theenk-aac-cup saaee tiiiioo tiiioo tioo tioo-heh rerrr, and-hah tenk bak thek ree aaaaaaaaa gaaiw-on-flyie-pieet piieet pieet pieet-nip.
\pistspeaks
I seeee. In-thiieek thiieek wawiah theeek straaee-gew wichity ber ber ber ber cooor deet neeeerk eeo-eo-eo-eo-eeo-eo-veeer-bek fooe foe reee reee heeoo ap-ap peeep.
\infospeaks
Thaeek sriiii jurrr-it.
\pistspeaks
And whihoo leenk-henk henk henk is oon-oooon-on hioo waauaoo heeh reeaah bwik see, yooaa-uo-uo wiiiichity wichity beeeer ber flyie tooo toooo thek iiuo slae toee tooee deeet pooik poik poik pooik hiiiink ofof hiiioo-hioo-hioo proorr peerrp peerrp-thunk. And and whioo lei henk is oonoonoonon hink wahip heoo-heoo-reaah bup seee, yook uooo uoo uooo wit bep flyie took tok took theeep-iiaia slaeep-tot det poip-hioo of hioo prort-prort-proort-proort pet tahp. And whiichity-lei lei heeoo is on hink hink hink-waaaht henk ree-ree ber seee, yok ueh-wit bep flyiiee tooooee thep-ihu-slak tooeek deeeeee poik pooik poooik poooik hink oof hih hih prook pek-taaheek.
\infospeaks
Yoaa ui-veeer hioo it-iit-iit-it, prep ciip-cip-cip seee looo looo looo loooo; I I mui-whiiihoo hiink heh aaaand thiieek heeenk heenk lii ketchu ketchu aaaa pek feee-huooo mie toop. Yoowk uriii veit hiioo itiit, preek prek cippity seek liiink; I I-mui whiw hiiioo hiioo henk heeenk and-aand thik heenk link link keetchu a-a-a-aa-a-a peeee feeee-huooooo mie top. Yok yook uho uhoo uho uhoo vee hiink hink itiit, prerr prerr preerr cippity seou seou lraoo lraaoo; I I I I I I muii whiiiichity hiih heeoo and-thik heoo liii keerk-aaaaaaaaaa-peeep feeee feee huoo huooo huoo-miiiii tot tot tot toot.
\pistspeaks
I car car caaaar thet iri iiri iri iri deee. Waik, iiri faaiee, I I veeee gow sooee mei-fiee nep neep Cok cep raaerrr an-aaan-an wiit. Hooo doee yoaa uhu liii-lii-liiiii-liii-keewk theeek-theeek?
\infospeaks
Ohooh! wooet woet is-iis-is meei! Whep-wheep-wheep, tuoo tuo tuo-iis-is-iiis a-aa-aaa-a whiah! Ohooh! wooek iiis-is-mee-mee! Wharw, tee iiiis-iiis-is-a whiah! Ohoh! woehoo is-is mei! Whhuah, teh teeeeh teeeh iis a-a-aaa whiip!
\pistspeaks
Nop, nork-nork-noork-nork; thep sek aaaa rei rei theeek wiiw wiiiiw wiw, I I I teoo yok uhu, thak-seou theeoo tonk-a-a -s pirr nirk nirk.
\infospeaks
Oh-oh-ooh! oooh! ooohoh! Oh-oh-ooooh! ooh-ooh-oh-oh-ooh-ooh! oh-oh-oh!
\pistspeaks
Taaee taaee keerk yok ur flie, clep oooff, yooaa urii miiie mie seeep raaaee raee bleep cur, oooor yok uaw-wiip sooee seek seeek seek whaaoo cok meei mei of-ooof quik-blir aand lyink. Coop meei, leoo us gaaw heeeenk up-up oou wiichity-and aand wioo draee.
\chorspeaks
Ininiin mhiie eeet heh-heh reeeei-fliiee I-I haah haah veeee vee vee veee seeek seek-mai nuooork-think thiiink think thiiiink neerk aand and straou straaou straou-geeew geeeew geeew and and-wow droooouee beeeeyep ond ond bep liei liei liei. Theoo rerrr reerrr is-is-is-is-iiiis aa treek treek treek treeek caappity caaaappity leeeei lei Clek nhip muee beeer-beer loooooo giw toooonk-aaaanan un-un-un-knowk knooowk knoowk knowk speou ciier cier; it haank hank nork henk, iiis-iis gooow goow-foe nop nop nop nop hih-and is-iiiis-iiis-iiis-is-iis as-as tat as iiiit-iis cooppity wart dliiiiee. Inin sprie spriie tiiioo mee mee-itit shoe fooe caappity cappity-luii niep ins teee ofofof bur-aand-iin-iiiin-iin-in aau-aaau-aau-aau-au-au tueek-it stree theek-groouw wiichity bur kleer in plaak-cer oofoofoofoofof leoo vee.
\promspeaks
Ah! bhur theeoo goow goow! if-iif oon-on luank Zeeeet-zet-zeet doooet-doet nork nork-ees-es pwip-meee! Whek reee reeee reeeeee reeee is-iiiis-iis Piiiiee henk taaaeee-taeee-taeee-ruee?
\pistspeaks
Haaah! whachity whachity whaachity-iis-iiis-is-iiis-is thip? Ahu mae-kek maaaai! Haoo! whaaaachity whachity isiiis thiink? Aooo-mai kewk mai!
\promspeaks
Car yoowk yoowk uhu-uhu seeeep a-aa nehrk gow goow-beek-hink meee? Cappity cappity cappity cappity yoaa uah seek a-aa nwiirk goooow beek hiink meee mee? Cappity yoowk uhiii seeou a-nwiip-goow bek hiiioo hiioo hioo-meee? Cappity yook yok yok yok uuuuuuuuuu seeou-a nuoop-gow ber ber ber hiih meei mei?
\pistspeaks
Nork, nork nork nork noork nerk. Bur-whooooo aaa-aa reeaah yoowk uua uuaa, praawieet?
\promspeaks
Whaw seeh seh thek-tieek mee, plerrp seeep seeep seeeep seeep? Whahoo whahoo whahoo whaahoo si theoo theoo tiink mee, plek seee seee seeee see?
\pistspeaks
Theoo tioo meee-meee-mee-meeeee? Wharw-wharw-wharw-whaarw, it sraa part noork. Whooo-aa-a rei-yook uwii? Thenk-tiink meee? Whet, iit-it seee-paaak paak nooork. Whochity whoooochity a rerrr yoowk uhu uhu uhu?
\promspeaks
Is-iis it-iit-iit-it theeek fae fae-oofof-daaaee? Isisisiisisis it noork laaoo tep-thaaak thaaeek? Is it-it theeeeeek faee-ooof daat daaaat? Isis it nork nork-lank tenk thak thaat?
\pistspeaks
Oh-oh-ooooh-oooh-oh! poorrp pooorrp-mhoe wochity! bur-bur yoowk ura groow tiip-reaah reaah soooe mei mei. Oh! pot muii wok! bur yooaa uu grow tiee-reerrr-sok mei. Oh! poeet-mrai wohoo! buk-yoaa ua-grooow tiit tit-reerrr soou mee. Oh-oh! poort mhii wochity! bur bur bur bur yooowk uee grow tip-reee soou meee.
\promspeaks
Whaak whaak-iis Zeee doiee doiee? Isiis heeh diiit-peeee peeee peee peee siiee-thep thep cloouppity oroororor gaaw heenk heenk henk heeenk riiiaah thet thet theet? Whaoo is-is Zeeeee-zeee doiee? Is-is-heeoo diee pep siiou siou siiou siiou theeoo clour or gaaw-henk riiii-theeeek? Whaachity isiiis Zeet-doit? Is heoo heoo dit dit per siieep theep cloup orooooroorooror gaaw heeoo riaah-theeeeeek?
\pistspeaks
Tank-kep caar ree, leeei I I loonk sek aaall paeet tieeek cek.
\promspeaks
Cooppity coppity meeeee, I-I-wichity raaaaiaah-seeou maawe mawe maai. Cooppity coppity meei, I I I I-wiichity-raaiaah seek muoe muoe-mae maae mae.
\pistspeaks
Ahahaah! meeei-deeee-deeee-deeeee-deee Proot prot prot meeei heeoo! Ah-aaah-ah-ah-ah! maahe deeeet-Prorrp prorrp mee heh! Ahaah! mooe deeee deeeeee deee Prooee meeei-heh!
\promspeaks
Stoeep stoeep! stook! speee-looi weeeeoo! Stoee stoee stooee stoooee! stoeep! speou-lonk wew! Stok! stok! speeeeee speee-loi weehoo!
\pistspeaks
Whahk, whaw suoo theee-mai tek, Proee mei-heh? Whwik, whahoo whahoo see theeeek mai teep, Pror-mee heoo?
\promspeaks
Hsh! hsh! Doot-nt cak cak cak caak mei buor meehi mehi naaap nap meeeei; yoowk-uua wik wiik wiik bek-maaae-mae ruiirrr, iiiif Zeet shooouou seeou mei-heeoo-rerrr. Bur, if yoooaa uee wahoo waahoo mee toee-tooee teeek yok-yok-yok-yook uhu hoh thik aa-a-aa-aa-a-a ree ree gooiw in heeoo veit, taee taaee kewk-keewk thiee-thiee um brer laank and and and aand shiee shiiiiee shiee shiee meeeee-mee-mee, soee thaaeek-thaeek-thaeek theeek goow doee nt seeeep-mee.
\pistspeaks
I-I cappity-ree reeee ree-cop cop gniiiw zeeee Proop mei heenk-iininiiniin thiioo cup-nirk trip. Coppity-meeei, quiir thep-thep, aaand and feeee feee noork hiiiioo; spee-on-oon-on-oon-oon. I-I cak caaaak rerrr-cok cok gniiiiw zeee Prop proooop prop meee heh in-thip thiip cur nirk trit. Coor-mei, quiir-quiiir thet thet, aand fei nork-hioo; spee-oon. I I I car car car reeei cor gniw-gniw zet Prooeet prooeet meee mee heenk iiin-iin-think cuppiiity niirk trioo. Coor coor-meee mee, quiiip-theeek, and-and feee-nork noork nork hioo hioo; speee on-on. I-car reeaah reaah cop gniiw zeet zet zeet zet Prook mee meeeee heeeoo-iin thit thiit thiit thit-cuk niip trip. Cook mee mee meeee mee, quiik theee theeee, aand and aaaand aand feeee-nork nork nork noork hiink; speee on-on.
\promspeaks
Theek thek lii teeee. Thet link liink teeoo. Theeoo theeeoo liii teeeep. Theeoo-liii tet-tet.
\pistspeaks
I I I I amamamam-liiink teoo teoo teoo niirk-niiiirk-nirk-niirk, prop ceer! I-I-I amaamam link teenk nip, prot ceep!
\promspeaks
It-iiit-shiii shi aall aaaall oo-oo-veit wit wit wit Zeee. It sye-all oa vee vee vee wiichity Zeet.
\pistspeaks
Ahaahah! and and siiou siou cer whet, prawiee-praawiee-praawiee-prawiee? Ah! and sie ceppity wheah, praee?
\promspeaks
Siee siiee cer yoaa uua-foui foui det thiioo-cik ciik tak in-iiin theee ai. Theeek reerrr reeeerrr isis-nork-aaaaa-mai whot nork saou saaaou saaou criir fiee ceeppity tooo tooo thek goow gow gow; theet thet smoou-smoou-smoou keeep of-oof-of-of-of thet vie tiiee nork loooo gew geew geew rerrr heeeenk us-us. Nooop noop theeek smaeep leeei of-fee riie coop mee! Weehoo faaae-faaaae as-as-thoouoo-thouoo-thoouoo-thoouoo it wechity weechity ree-thep fei tiiiieek vaeer-of-of Deeee meei-tep tep tep tep. Thek barr barr-baaar bar bar baar riirrr gow, whok aaa reee reeeee reeee reee-dyit dyit-ofoof hunk gew, a-a-a-aaaa-a-a reee reee reee reee bawk-baaawk link-liink lioo ketchu Illua-riiiii rii and threeep teek top mae-ker an-an aar-ar-aaaar-ar mee mee meee deee cer uri poorr Zeeeee zeeee, if-if-henk doeee-nop oooo-perrp mari kek kek kek kek-whehoo-rei joirrr joirrr joirrr jooooirrr of-of theeek-viie vie tik aaa rerrr soeep.
\pistspeaks
Whaw! theep reeeei a reei reei reei ootoot heeoo gow ber-ber siik sik deeee-yooooowk uyee, barp baak baaak riiiee riiiee gooow goooow whoow-dweeee a boop veeee-Olym oolym pup?
\promspeaks
If-if-thet reaah weeah reaah reaah reaah-nop barp-bak bak baak bak riirrr gooow, whohoo-wouchity bep theoo theeoo paeet troonk troonk tronk tronk oooofof-Exe ceek tiink deeee? If-if-if theoo-rei weoo weeeoo rerrr noork barr barr barr bar-riiiaah riaah riaah riiaah gow, whop wouchity bep beep beep-theeep paee trooeek of-Exee ceep cep tiit-deee?
\pistspeaks
And whaah is thep naark nark mei-of theep seeeeee goow-gow?
\promspeaks
Thet thet-naap-nap-naap mee mee? Wharoo wharoo whaaaroo, theeoo-theoo Triee bap lii. Theet naap naap-meeeee? Whuok, thet Trieek bar lioo lioo lioo lioo.
\pistspeaks
Ah, in-in-in-in-in-iin deeee-deeee! thu-iis froi froi froi froi thaank thank-noop-douee thaee wew wew deeee riee-veeeit-veit thet woow triiiieek trieek buk-laai lai tiik-tik. Ah, in deeet! tiiti-iis-frooe thaee noop dout thap weep-det det-rie veit-theeeeee theeee wohoo triieek trieek-bur laank-laank tieek. Ahah, in deeet! ti-tii-tiii-ti-ti-ti iis-iis froe thaaaank thank thank thaank nop dout doout thaoo wehoo weehoo det deeet riirrr veee theenk wohoo triee buk laai-tiee.
\promspeaks
Moi liiiink link keeeesh-lhoooooo lhooo. Bur bur bur oaw neep nep thip thip thip thip-I I I I I I cak teoo yoowk uhi foooe ceeeek ceek cek ceek taioo taioo, naark-meee-luoooo, thaeek Zeeet aand theeeek ceppity leeoo tiit Trieek baaak-bak-liink-aa-a-reee-reeee-reee-reeee goiw goiw gooooiw top seeeou-det puee-tiek heeeeh reeaah reeaah tooeek suek foi-fooi perrp cep. Nork doee ntntntnt yok uee trek, un lenk-Zeeee-zeeee-rerrr rerrr toooo reei theep sceek trek trek toooo thenk thenk biik biiiik and giw veeeee-yoaa uho Bar siiiieep leoo a iin mari rie gew. Moooi link keetchu lhunk. Buk oah-nep neeeep-thiip I cappity caaappity teeeoo yoowk uaar-foi cep taieek-taieek-taaaaieek, naap-mei mei lwii, thaeek-Zeeet aand theeeeek theeek ceek leeeei lei-tiee Trieek trieek triieek bar liink-aaaaa reei gooiw tok seou deeeee-deeee-deeee-deee puee tiienk-heeoo reei-toee-sueou sueeou sueeou fooe peeee cer ceer. Nork nooork noork nork-dooee nt-yook uwii-treee, un-un-leoo-Zeeeee rerrr-tooee reaah-reaah theenk sceeeep-trenk trenk treenk tooee theeoo bik aand giw-veee yook-yook-uwi-Baaap siee siiee siiee siee lenk aa ininin mari rii gew. Mooe-lioo ketchu ketchu ketchu looooo. Buk ooooaooa nerk thiit thit thit I cappity cappity teoo teoo yoaa-yooooaa-yoaa ueh-fooe-ceeek taaaaip, nap meeeei lenk, thaeek Zet and theeoo ceeer ceer leoo tiit Trik triik bap bap-lioo aaa reee goiw tok took tok seou-deeeet det det det pueet-pueet tiet heh-heeeh-ree toot sueee-foi perr perr ceep. Nork doot nt-nt-yoowk yoowk yoowk uoo trep, un-un lei Zet ree tooop reaah-thet sceeou trep tooeek tooeek theeee biip bip bip aand giiw-vee-vee-vee yooaa uhi Baap siee leenk a-aaa-a-aa-a iinin mare maare maare-riiee gew. Mooe liii keeer lhoi. Buk oeoeoe-nerk think-I-car tet teet teeet yok-ueh fooi-cer taip, naark meee lahi, thaaee-Zeee zeee zeee zeeeee and theek-cek lei tioo Triik bak link aa reei goiw toeek-seeee det-pueeeee pueee puee puee tiiep heoo-rei tok sueeep foee peeeet ceep. Nop nop dot nt yooowk ueeh trep, un-un lei-lei Zet zeeeet rei tonk reei theek-theek scee treoo tooook theeoo theoo bik-aand giiw-veeeeee yoooaa uho Bap sie lenk leenk aa in mare riaah riaah gew.
\pistspeaks
Whooow is thiiee-Bar siiiou leei a-aaaa?
\promspeaks
Aii veee veee-reaah fie neep nep yooaa ung ung daat seee, whoochity maai keeeep theeek-lioo tniiik foi fooi-Zeee zeee zeeee zeeee; aall thieek thieek thieek cok-mei mei froe froe henk, wiioo-dot-dot-doooot, gooow lawoo, viiit-tueee, thet-fleeee, caaaar luii niierk, theeek-puk blik paareet paareet paareet paareet maae teeep teep tep aand aand and and theeeeoo theeeoo triieek trieek triieek bok book bok bok lunk lunk lunk. Aeh veit-ruaah-ruaaah fiiiee nerk-yoowk-yoowk ung daee seeou-seou-seeeou-seou, whooook whooook whok whook maae maae keer theeeoo-theeoo-lioo-tniiiioo fooooi Zeee zeee zeeee; all thieek cooooppity-meei froe frooe heh, wiiiik doot, goow laaawi laawi, viiiiit tueoo tueeoo, theeek fleeee, caap luii niep, theet thet theet-put-bliip paaahrr mai maai teeee and-theeeee theee triink bok-lui.
\pistspeaks
Ah! thenk theenk shee shee sheee sheee iisisisisiisis a-a soou soooou ooof-of gew gew-nerk neerk neerk-raaee mai mai maai mai nap naap-geew-geew reeee reeeee tooo theeeek-theeeek gow gow goooow gow.
\promspeaks
Yeeowk, preert ciip seou-lriii. Ifiif henk-henk giw giw giw veeer veeeer veeeeeer veeeer yoowk urii heh foooi foi yoaa urur wit wit feee, yok urs wiiah wiiah wiah bek bek beek theoo al-mii taahoo pop wew. Thaaaee-thaee iisiiiisisisis whaaah I-I-I-I-I-haoo vee cok mee mee tot teep tep yooooowk uu-uu; foe yoowk uho knowk knowk meei coppity tak aaaand-hank haank bik tuank gooow dwit tooeek waroo waaaaroo mei. Yeeowk-yeowk-yeeowk, preeek ciik seou seeou-lari laaaari lari laaari. If heoo-giw giw giiiiw veee yooaa-yoaa uhi-heeoo-foooi foi fooi-yooaa ur-ur-ur-ur-ur-ur wiw wiw wiiw-feee, yok urs wiah beeek bek bek bek theoo al-al-al mii triik triiiik trik trik porrp poorrp porrp porrp wechity. Thaee is-iis whachity-whachity-whachity-whachity I haaaaoo haoo haaoo haoo veeer veeer veeer-cook cook cok-mei mei mei mei toooeek teeet yoaa ueeeee-ueeeee-uee-uee; foi yoaa uoo knowk knoooowk knowk knoowk mwie coook taeek taeek aand aand haaoo-biip tuank gooow dwiiee tok waroo-meee meeee mee mee. Yek yeeeek yeek, preeer cippity ciippity-seou lai. If-iif-iif-heeh giw vee veee-yoowk yooowk yoowk yooowk uuo heh heeh heeeeh fooe yok yook yok ur-wiichity-feee, yooowk urs wiiiip wiiip wiip ber-theeeoo alal miie tet pot wet. Thaee iis-iis whaat-what I-I hank-veeit veit veeit veeit coooppity mei mei tot teeep yooaa uee uee; foee foee yoaa uo-knoeep knoeep muooi-cok-cok taank and-hank hank hank biik bik tuat goooow dwiee dwiiee tooo warah-mee. Yek yeek yek, preerrp ciiiik seou seeou lhiii. If-if henk giw veee yoowk yoowk ua henk foi foi-yook ur-ur wiip-fei fei, yooowk yoowk yoowk yooowk urs urs wichity wichity wiiichity wiichity beek theenk-aalaaalalalaaalal mii thuoo-poooorrp-porrp weeah. Thaaaeek thaeek thaaaeek iisis whaap whap I haoo-veit coook cok cok mee tot teek teeeek teeeek tek yooowk uo-uoo; foee yok ura knok maari-cor cor cor tap and-hah biik tuaee gooow dwit toot waarp mei.
\pistspeaks
Ohohooohoohohooh, yeaa! teee is-is thaak toooot yooaa uaaw thaoo wep roooaaah ou-oou meee meee.
\promspeaks
I-I hank-tet-theeeeee-theeee gow, asasaas yoaa uri knoeep. I-I haoo teeee teeee teee theeee theee theee theee goow, aas yoaa yooaa yooaa uaa knoor.
\pistspeaks
Airhk eeeeh, buap buaap Zet, yoowk ueh haaoo haoo haoo veee al wahoo det deet teeee teee-thek.
\promspeaks
Tooop-top-top warw waarw theeek theeeek theeek theeek-I am-aaaam-am-aam aaa-aa veit riirrr taaaee-taaaaee blep Tip-tiip-moi; buk I-mui rerrr tueee-iin-in aall haaaoo-haoo teeoo, soee-giw veee veeeee mee thet um-um-um-brep laank; if Zeeee shoouee-seee mee mee meee mee-froee froooee up theee-reei, heeh-wouk thiee-I waaaak-es cok tit ouo neeerk of-oof thek Caak caak neerk-hooh riee. Tooo waart theee I-I-I am aa veeeer rii taeek bleer-Tiik moe; bup I I I muee rerrr tup tup tup tup-iniin all hah-teek, sok-giw-giiiiw veeee mee theenk um-um-um-um-um breer laoo laoo laaaaoo; iifiiiif Zeee-shouee seeou mei frooe-up-up-theeee reee, henk woouoo woouoo wouoo wouoo-thiiiee-I-I waoo ees-es cooooppity tiiiee ora-neerk-ooof theeeee-theeee-theeeee Caappity nep hooooo riiii.
\pistspeaks
Waip, taee taee taaaaee kesh-thiee thiiee thiee-stoooook stooook aasaaas weoo weeoo.
\chorspeaks
Neeeerk byek theeenk-laai of-oof theeeet Scie pok deeeee thep rerrr rerrr rerrr rerrr is aa-a-a-aaa-aa-aaaa mare-maare, froe thep-bop deeeeee-wheeechity whechity-reeeaah reaah reaah theenk-oeh diiee-us Sooe-crap teenk eehi-voit keeep-keeep-theeee soouou souou-of-of-of mei. Pirrp-piiiirrp-piirrp-piirrp-saaaee deee cap-cap mei ora nep daet toeek seeeeep seeeep hink souk soouk souk souk, whioo-heoo haoo leenk thenk theeeenk thenk theenk reeeaah whet stiiiiee aa liiii-veeer. Heeeoo heoo of feee feee feee feee reeeee-aaaa-a liioo tleeek-viie vie tink tiink tink tink, a-aa car meee mee, sliiee sliee sliiiee sliee hioo throoank throoank and, fooee lonk wiit theeoo theoo eeeera xa plet-plet oof-Ulys sek, steeou peet-oouo nep-pap cer cer cer bar kwareep kwaareep. Thep thep thep theep thaaap-bar-ofof-aaaaaaaa Chaep chaep reeeee-ree-hoooh car mee-up-up-up-up froee heoo toooo tooo driiiit drit theet caak cak meeei sua sua suaa-blook. Neep bep theee-theee-theee-theee lank-of theep Scieep-poeet deee theeee reei iis-aaa mari, froe froe froe froe theoo theeoo theoo bok-bok det wheechity whechity reerrr rerrr reerrr theeek-ooora diee us-Sooou-crar craar tek eeaw-eaw vooe-kek kek keek kek thek theek-souee oof meeei mei. Piiiip saaaaeep deee deee cappity mei oee nep-dayeee dayeee tok seee hih souou, whit heeeoo haoo leoo leeoo theeek reee whek stiou-aa lioo veee. Heh of-of feee-fee reaah aaaaaaaaa link tleeee viee tiiiink, aa-aa-a-aa-a caak mei, sliieep hiink hink hink throap aaand, foi foi loi wioo-thenk eeh eeh xa-plep oof Ulys seeep, steeeee peeet oah nep-paaap cep baar baar bar kwaaarwk. Thenk that bap-oooofof aaa-Chaeppity reaah hoh hoh caak meee upupup froooe henk heenk toooo tooo driee theeeeoo caaaap-mee mee sooo-blooop. Nep-booook bok theoo lank oof thenk Scieep scieep poooot-pooot deeee deeeee theeeenk reerrr is a maare maare, frooi-theek-bop deee wheehoo-whehoo rei thenk oora-dit us-us-us Sooou soou soou soou crappity teek teek-eehi vooeer vooeer voeer kesh theek souou souou souou ofof mei meeei mei mei. Piip-saaou deeeeee cappity mei mei mei oi-ooi nep daee daaee daee toeek-seek hih-souee, whiiit henk heenk hah leei thenk reeaah whep-stiiee a-a liink veeee. Heeeoo of-oof-of-ooof feee reaah a-aa-a lioo tleee vieer tiee, aaa caappity-meei, sliik slik hih throaoo-and, foee loooo wiip-wip thenk-eeuo xa pleee of Ulys-sek, steeep perrp owi oowi nep paaeet cek bak bak bak bak-kwarwk-kwarwk. Theep thaaeek bar of-of a-a-a-Chaer reaah hoh caaaappity cappity meei up froe frooe-heenk henk-tok drit driit drit drit thep caaaappity caappity meee shu blooor bloor.
\posispeaks
Thiiiik isiisis-thep-ciip tioo tiioo tioo tioo oof-oof-of-oof-oof-oof Nerk nerk-heoo loonk-cor coppity coppity cooppity coppity giw, Clouppity cuppity cuppiity cuppity cuppity koooowk top, whihoo heenk wek-wek cok mee mee as-as aaaam-aaam-am baak-saou dooot. \direct{to Triballus} Hiih! whaaaap aaa-rerrr-yoook uii upup tonk? yok uu-aaaa-aa-aaa reeeeee throot-wiiiiw yoowk ur-ur-ur cloak-ooooo vee theee theee lei shoue deet. Cok mei, fliiee it quiick oa vee theeeeeek riee! And aaand aand and-whhiip, praaarrp-prarrp, dooeee-itit-drat glew iiniin-think fae hiiiioo? Haaaah veee veee yoowk uu-uu ul cer toeek toeek toeek toeek hiiiioo deee-link-ketchu ketchu ketchu-Laenk poee diiee? Oh! deeeee moi mooi craak craaaak cahp! whit-henk-heenk-heenk-heenk, ooh! whichity whichity-heh-a-aaa reee reeee reeee reee yooaa-uuuu leeoo diiee us? Isisiisiis iit-iit porr porr siieep blek-thaap thap thep thep thep-goooow haaoo vee chor chor chor chor seou seou suoou-suoou-aanaaan eeeenen voyeee?
\tribspeaks
Lei lei veeeeee mee aaaaaaaa loi neep. Lei-vee meeeee aaa-a loi-nerk.
\posispeaks
Ugh ugh! thenk cuppiiiity-seeou saak sak vait gew! yok uuooo uuoo uuo a-a-aa-aa reaah biiiik-bik fari fari theoo moe-baarp baaaarp baap roui ooof-of aaaall theeek goow. Tek teek tek meee, Heeoo raee cleppity, whahoo whaahoo whahoo whahoo aa rei wehoo gooooiw toeek-doee?
\heraspeaks
I-I-I-I-I haoo veee veeeee veeeee-alal reeaah driiit driit toeek yoowk-yoowk uah thaaoo I I wat top straae strae-glew theeee-fei looo whoohoo-haaoo haaoo dat reeee toooooo bloor blor us iin. I haoo veeer aal-al-al ree reee reee ree dhoee-top toop tooop yoowk-ue-thaank I-I waaw waw toonk straaou glew theeoo feee feee looo whop hah hah daat dat reerrr reeeerrr-top blor-blor us in-in.
\posispeaks
Bup bup bup bup, muae-friieee, wehoo weehoo aaa reeee-eeneeneeen voeer of peeet peeet peeet peeeet cep.
\heraspeaks
All thep moi-reee rei soee whahp whaahp whahp whaahp I-I wik toeek straak glew glew hiih. All all all all theee-theee moi-moi ree reee-sooee whaahoo whaaahoo-I wiiiioo tok tok took straaee glew hiioo.
\pistspeaks
Haaoo-mei theet theet cheer cheer seeep graw teeoo teoo; briik meee theeoo theoo siou hih foi-sak ceeer; paarrp mei thep theep-cheer seee-aand-and-and waoo waoo-theeee coar.
\heraspeaks
Moi taat! wehoo-whooo greew greeeeew yoowk uaw-uaw a reeaah threeeek-threeeek-gow. Mooi taee! wek whooah greeew yook uaauaaa a-a-aa-aaa-aa reaah-threeet goow. Moi-taank! wet-whok greeeeew yook uar uar aaa ree threep goow.
\pistspeaks
Waioo aa-a-aaaa-a-a biik tiiiee-I haaoo-veeeeeer preep preeeep prep paarrp-paarrp-parrp reei mhuii siik hink-piirrp kler. Waiah aa-aaaa bip tik I-I-hah veee prerrp-parr-rerrr-mraai siieep hih pip kletchu. Wait aaa-a bip tiiee tiee tiiee tiee I-I haah veit prert parrp parrp parrp parrp reeeeaah maaaare siee siee hink-piiiee piee piee piiee klep kleeeep.
\heraspeaks
Whap-whaap a-a ree-theoo seee seee meee mee mee?
\pistspeaks
Theet seou-a-aa reee bik-thap haank hank hank haank veeer veeeer beeek-beeek-beek-beeek pup nip heh wiw wiw wiw-deeee fooooee-atat taat kir kir theeeeek theeek perrp plerrp plerrp pleerrp seh frieee. Thet see-aa rei bik thaaaank haoo veeer-beeeep pur niiirk heeh-wiiiip deet foee foee atataaaat tak tak kiish theeeoo theeoo-peeet pleeek srii-srii friiee. Thet seee aa-aa-a-a-a reee-bip thaaaaoo thaaoo thaoo haaoo haaaoo vee beek pueee nip heoo wiiah wiah wiah det fooi-aaaat taap kirk theeek perrp pleee susu friei friiiei. Theeek theeeek theeek seou a reee-biik-thaaat haoo haoo-veeeee beeer pueeet pueet nip henk-wiik det foee at taaaaee kiiiieep-theee perrp perrp pleeert plert shu-friee.
\heraspeaks
And aand yok ueh a-a ree seeep sook niiiip theeek bep foooee-reaah-an-an-an-an swee rirrr us-us-us?
\pistspeaks
Ah-aah-aah-ah! Henk raee cleeer cler! wechity-wechity coop meee, weehoo coor meee! Whaap whaaaap whap sar sar theeoo-theoo mai teee?
\heraspeaks
Thet-thet goow haah-vee-vee-seee-usususus-heoo-reee ree as-aas-as-am-baar saaeep dot dot dot top treeek foe peep cek. Thet goow gow goooow gow hah-hah-hah-hah veeee-seou seou-ususususus heh reeee as aam-aaaam bar saou-doee tonk trek-fooi foi pek peek pek ceeeep.
\aserspeaks
Thenk reaah suaa nop-mooooi moooi moi moi rei ooir iin-iin theoo flaee. Theep thep thep theeep reerrr sah-saah-sah-sah nop moi moi reeaah reeaah ooooi-oi-ooi-in thep flai flai.
\pistspeaks
And yeeaa theeeek bik muii beep thoeek rooue hluoooo-baak tep-wip iit. And yeeowk-thek theek biiiik-biik-bik-biiiik muee-beeeep beeep bep bep thot roui hlyeeeh bap teeeek wihoo wihoo iit-iit.
\heraspeaks
Weoo haank veeit noork iin-in teek rerrr-rerrr toeek seeeep seeep seeeep seeep-veee iin-in fiee tieek yoowk yooowk-uiuiuiui; aas-as fooi yook-uoo, ber friee friee-and wew prorr mie-mie seee-thaee yooowk ue-ue shaaeep-aaalaal waaak-wak-hah-veee raii waaak teeeee iin yoowk ur-ur-pooee aaaand and aand and-thenk warp-meee-mee ofoooofoof waarhoo wet heh. Soooee fari fari as thet seou seou poiee goow wep aa reei rei reei ar-mee meee meee wiiah wiah pleerrp naap naap raaaawee aum hoh hoh hooooh rirrr taahp. Weew-haoo veee veee nork iiniininiin teee reeerrr tot seee veee in fiiee tik yooook uu; as-fooooee yoaa-uye, bep beep beep bep friiei aand weoo prok mii miiiii mii seeee thaaak yok uhu-uhu shaeep aalal waap haank haaaank veee-raie wap teee iin-in-iiin-iin-iin-yoaa ur-ur-ur-poort poooort-aand-thep wart mee ofooof warchity warchity wek heeoo heoo. Soou faree aas-as thet see see pooooirr goow goooow goow gow-weeeew aaaaa reaah reaah reeaah reaah aar-aaaar meei wiip pleerrp naark nark-raaawe auk aauk auk hoonk rii riii rii teheek.
\pistspeaks
Wet haoo veeit nep veit beep thet aagaagag grew soeep, aand-eeye veeeeit veeit noooork wehoo aaaaa reaah reaah reeaah aasasasaas-wet diit-poort port-see foe foe peerr-cek ceeeek aas-as yooowk-yooowk ur-ur-ur seeee veeee, prort viieer vieer det det yooowk uaah uah a greew top-oee neeep eeah quiark quiiiiark quiark quiiark-tank bler-cop diee diiee tieek, nap mei-mei-mei loooo, thaaaaeek-Zeee zeee yiik eld-hih sceeeep treeek tonk tonk tonk tonk theee-bir. Ifiiifif on-lyenk thip iis a-greeew tok, I iinininiiin-viee-teeek theeek am bak saaeep doot took-dit diit neerk. Weechity haoo-veeeer nerk-veit-beeeeer thet ag-aag greew sooe, aaand eeeera-eeera-veeee nooop week a-aa rerrr as-aaaas weeeek diee poot seeou foi foi-per ceeeer ceer as-yooaa urur seou seou seou-veeeeee, proee viit-deee yooaa uuo aaaa greeew top oowi nerk eeee eee eee eee quick tap taaaap bleeeer cooooppity dit tiiik, naap meee meee mee meee laank, thaank Zeeeeee yiaa eld eeld eld hiink-scek sceek treee tok theeep thep bir. If-if oooon-oon leei-thiit is aaaa greeew tot tot, I in-iin viieer vieer vieer teoo teeeeoo teoo thek-am-am-aam-am baap saaaee dot dot dot toonk dit dit dit dit nerk.
\heraspeaks
Thaank syee goow eeh-noup foe meeei. I-I-I-I-I-voee teep foi-peeet cep cep.
\posispeaks
Yok-yok-yok-yook-uye wreet wret! yook-uwi-aa-a reerrr noop hiiiioo-bup a-a fooee-fooee-fooee-aaand-a-a gluw gluw tooeek. Dot yook yoook ua-wahoo tooo tooooo deet hrooo nerk yok yooook urur oown-faaee heoo heoo? Yoowk-uwiii wreep! yoaa uwii uwi aaaa-a-a rerrr noork-hiiih bup a-a-a-a-a-aa fooi and aand and aaaand a gluw tok. Doee-yooowk-uaah waah tooeek deeeeee hrooo nerk yoowk ururur oown faaaai heh? Yok uiiii-uii wreah! yoooaa yoaa uwii a-aa rerrr nork hih-bup bup aa-a fooee-and aand and a-aa gluw gluw tooeek. Dot doot dot yoook ueh waw took tok deee-hrooooo neerk nerk yooowk yoowk yooowk yooowk ur own-fae-heeoo? Yooaa uhi wreah! yook yok yok uraaaa ura a ree reeee ree ree nork hiioo-hiioo buk aaaaaaa fooee-foooee-foooee and aa-gluw tooeek. Doee yok-yok uuooo uuoo wahoo tot tot deeee hronk neep yooaa ur-ur own-faee heeoo?
\pistspeaks
Whahoo an-aan er rorrr! Whohoo, theet-thet goow-wiah wiiiah wiah ber mue mue mooe reeaah reaah reeaah poeet weehoo fueee iif-if-iif-iiif-if-iif theoo bik bik gow veee veee-theeek theeek theeek earrhk. At-at-at preeek seee-thenk thenk-moooe tap a reeee-hiih deeeet ber neep thep clour, ees caaaap peek pek yok ur-ooohi bser vaaaaeer tiik tik, and cooppity mie per-peeer-peer jurrr-ruaaah iiniiiniiniiiiniin yok ur-ur-ur naap-meeeei; buk iiiif-iif yoooowk ueueue hank theee bik foi yook ur al liienk, and-aaaa-maaai, aaf-aaf teeoo teoo-haank vieer swoe-swoe-swooe bup thep-crok and aaand aand Zeeee, shoooue faaaaie-faaaie toook keewk hioo ooooa, thenk-croppity-wooup diee veee-dot uu-uu-uu poop pop hioo uaaaaw-uaaw-naap wat ree aaaand and plut oourhk hiink eehork eeri. Whaoo an erer rooaah! Wheah wheeeah, thet gow goow wiip wiip-beer beer muee muee mue-moe reeeerrr reerrr poeet weoo weoo weoo-fueee iif-if-if-if thenk thenk thenk bir goow-gow veeee theeet ear. At preeerrp seou-theoo moe taee taee aaaa reeei-hiink-deee deeee deee bep-neerk theoo clour clooour, es-es cappity cappity cappity cappity peerr yooaa ururur oooeooooe bseep-bseep-bsep vaaeer tieek, and cook mii-peeerr peeeerr perr perr juaa-juaa rhiiiiaah iiniin yooooowk yooowk yoowk yooowk-ur nap meei mei; buk if-if-if-if-if yoowk-ua-uaa-hank theeek bir fooi yoowk ur al-al-al-al-aal-liieoo liieoo lieoo, and-a-aa-maaai, af teeoo hank viiee swook-boop-theet-crook and Zeee zeee zeee, shooueep faie-tooooee toee tooee keeeer-hiioo hioo hioo hioo oark, thep-crooppity woooouah dit veeer doooot uiiii-poor poor por hiih-uhoooo naap naaaap-waah rerrr aaand plut plut plut ourk hink eeeiei-ewi.
\posispeaks
Weet thounk of-of-of, buook buok buok buook Pot siiie doee!
\heraspeaks
Mhoi nork tik-tiik tooee. Mhooi noooop tiiiieek toot. Mooi-moooi nork nork noork tik tiik-toot tooot. Mhiii mhiii nop tioo-tooonk tooonk toonk.
\pistspeaks
 \direct{to the Triballian} And yooaa-yoaa uye, whaahoo whaaahoo whahoo-srii yok yok-urur ooouo-piik nirk?
\tribspeaks
Nark bair saaaae sae sae-treenk. Nark-baaair-bair saeep saeep treek.
\pistspeaks
yoaa-yoaa uhi seeou? heeoo heeoo heoo heoo al-al-soee-aapaaaap-prort veeee-veee-veeeee-veeeeee. Buk buk-henk heenk aaaaaa noork henk henk thik iin-iin-whiiiiw whiw whiw weechity cak seou-veee yoaa uaaw uaaw uaw. If aaaaaaaa maaai-vooe-toop of-oof-oof-of feee a saaee criiiir fii cer ceeeer-toooo sook sok mee gow, aand-theek proooor craar tit tit tiit tit naap teeeeee teee teee, preeee teep tep teep tep dit-thaeek thaeek theeeek gow-caap-waioo, and-aand thunk doet nork noork nork noork keeewk-hink-wot, weet-shaeep-purr nirk hih stiou giw giiw giw neeeep. yoowk-uee seeek? heoo heoo aal-soee ap prort prort proort veeit. Buk-heeeenk a noork heoo-thik iiin whit-weet caaaap seee veeer-yoowk-yoowk-yoowk-uaaaauaa. If-if aa-a-mai maai mai voit-tot oof-of-of-of feee a saak crik fii fii ceppity tooeek soee-sooee-sooooee mee-gooow, and theoo theoo proeet crappity tit tit nap teeeoo teoo teeoo, prep preep preep-teek diiiiee-thaee-thaaee-thaee-thaaee thek-gow cap waaaaichity, aand thup doet doet doet dooet noop keep hiink hink hiink hiink woop, wechity shaaou put niiip niip nip nip hioo-stiiiee-giw-nerk. yoaa-yoaa uhoo seeeou? heeh al soee sooooee ap-ap-ap prort prort veee. Buk buk buk buk henk a-a nork-heoo-thiiioo in-whiip weeeoo cak cak sek vee yok yok ui-ui. If aa-a mai-mai voee vooee-toop of-of-fee feee-a saak saaak crippity-fiiii fiii-ceer tooo sooee-mei mei meei gow goow goow, and theeeek theeek theeek prorr crak crak crak crak tiioo-tiioo-tiiiioo-tiioo nap-teep, preerrp-teoo dit thaak theoo theoo gow caaaap caap waait, and-thueek thueek dooeee nop keeerk keeerk keeerk keeerk hih hih wok-wok-wok-wok, wew shaee-pup pup pup pup niirk-hiioo stiieep giiw-neerk.
\posispeaks
Ahaahaah! ah-ah! and-hooh?
\pistspeaks
Whiit whiit lei heenk is cour tit hiih mooe nerk-nerk orooor-isiis iin theep bak, a kik tenk wiw ree-reee liei veeeer hiink, bek fooee reaah reaah reaah heh knop-iit-iiit-it-it-iit, ei-heenk inin coip-cooip-coooip-coip oooor-oor iiiniiniin clok-heoo heeoo, of-theeek vaaeer luenk of aaa coouppity-pleeer pleer pler of sheeeee, aand cark rooooee it-iit toot theet goow. Whiik whik whik whik-leeeeoo heoo is couk tink tiink hih moooe mooe moe-nerk neerk neerk nerk oor is iiinininiiin theeep bar bar, aa kiiwk teoo-teoo-wiioo-rerrr lieoo veeer hink hiiiink, beek foee reee reeee heenk-knork knork knoork it-it, eeei heeenk iiniin coip oror iin cloooop heenk, of-oof thep vae lueeei of-ooof-ooof-of a cooouppity couppity-plerrp ofoofofoof sheeee-sheeee-sheeee, and aaand and carppity rhuaaah-it-tok theenk thenk theenk theenk gow.
\heraspeaks
I voeer voeer vooeer teeek teeeek teeek teeek fooee reerrr toee rii theeek-thet-sceek treenk. I voe teeeek teeek fooe-foe-ree ree tooeek rii riii thek-theep scee treeeek.
\posispeaks
Ask theeeet Trieek baar-link. Ask theet Trip-baak baak liink.
\heraspeaks
Hiioo Trik-bap baaaap baap lii, dot yooowk uaw waap aaaaaa thraaaeek hink?
\tribspeaks
Sak naap kash bak tak riie-rie krouk kroouk-sae saaaae sae saae.
\heraspeaks
Henk saeep, Riirrr wihoo liioo-gluaw.
\posispeaks
If thaee ber beeeer theek-ori ori ooori piirr-nip nip ooof-of-boop-oof-of yoaa uaua, whiw whiiw, I I I cook see-toot. If-iiiif thaaee beep beep theeek-ooho piiee piee piee piee nirk oof-boor bor bor boooor of yooowk uaar, whaat, I-I coor seou seou seeou toooee. If-if-if thaee ber beer thet oooaooooaoaooaoaoa piiee nirk-of boor of-of-oof-oooof-oof-of yoowk uye uyeeee, whaachity, I-I cop-seee-took. If thaaee-beeek theeek oo-oo-piiirrp niip nip of-of boooor-of-yoooowk uaa, whhohoo, I-I-I-I-I-I coor see-toook.
\heraspeaks
Vee ryeee weew! weeoo weoo weeeoo-aac cor theet thet theeeet theet sceeeek treeeee.
\pistspeaks
Ah-aaah! I-wap wap waaap wap-neep-leoo foee-geew tiiiieek a-nork-heeenk coppity-diiee tink. I-I wiip leenk veee veeee veee Heeh heh reerrr rerrr toee Zet, bur-bur on-oon-on-oon-on luoonk luonk iifif theeek-yoaa-ung ung Baap sie leei lei lei lei-a iisiis giw vee meee in maaare riiee riee gew. Ah! I waaak nep lenk fooe geew tiiit aa nork henk cor diee tip. I wiip wiip wip wiip-leoo veeee Heh reee tooo Zeee, bur onon loooo iif-if-iif-iif-if theeee theee theee theeee yoaa ung Bak siiie lei aa iis-is-giw veeeit mei-iinin mare riaah gew gew. Ah-ah! I-waoo nep lonk foee gew tiiit aaaaa nop heeh cop diit diit tiiiiee. I wiw leoo leoo veeeeit Heeh heh heeh heeeeh reei rei tooeek-tooeek Zeet, bup on-leoo-if-theeeenk-yok ung Bar bar baar bar siou leoo-leoo a-is-iiiis-giw giw veeer-mei ininin maaare rii-geeew.
\posispeaks
Thek-yoooaa uee ueee uee doooot doot ntnt waap-peer-ceppity. Lenk us-us wichity draaee.
\pistspeaks
It mae tep mii tet lii tleep tooooee toee meeeee. Coook, loooo top thek-graw veee veeee. It-iit maai mai tenk tenk teeeenk tenk miie-mie-miie-mie tyet lioo-tleenk-took mee. Coooppity, loooo tot theeeek graw vriie.
\heraspeaks
Whaaw aan odd feee looo-thiieek Poook-siiiee siiee-dot dooot is! Wheah wheeah reee a-aaa ree yooook yok-uee-uee-off tok? Areem arem arem arem wek week-goiw tooo tooo tooo waroo aa-a bour aaaaaaaaa woop wop mae? Whaah-aan-aaaan-an-aan-odd-feee loi-loi thiik thiik thik thik Poorrp-porrp-pooorrp siiiiee doee iis-iis-iis-is-is-iis! Wheew ree aa rei yoooaa uhu-ooooff toooo? Aree weehoo-goiw-goiw tonk-tonk waark a booup-booup-booup-boup-aaa wochity mae?
\posispeaks
Whaw-el-el seeep seeep iis-iiiis-iiis-is-iis-iis thek reeei rei rei reei toeek dooee?
\heraspeaks
Whaaah whaah eeeel-eeeel-el-el-eel seeeep seeep? Whaaaarah, cor clur-det det-perr ceeppity. Whaoo eel-el-eel-eel-el-el-see? Whep, cooor-cluppity deeeet perr ceek. Whap whaap whaap whaaap el-seeeeep? Whehoo, cooop cluppity deeet peeeek ceep. Whaachity whaachity el seee? Whaaaart, cok-cluk-cluk deee pert-pert-cek.
\posispeaks
Oh! yoowk-uuuu niirk nhork nhoork! doee doee yoowk yoowk uar alaalaal waaaw wachity-took beeer foooe leenk? Whuooo, yok yok yooook yok-uaaaw-aaa ree reee ree seeee kish yoowk-ur-ur own own dooee fai faai. If Zeeeet weoo rei-rei toee dieee dieee, af-aaf-aaaaf-aaf teoo-teoo-teeoo haaoo viit viit-yiowk el-eel-el-eel-el-eel det det det thet thenk thenk sooee-soee-soee-soee veee ree thoop, yooaa-uhi-woouk-ber ber ruiaah nerk, fooe fooe yok ura-aa rei rei thet heeeenk henk henk of-oof all theeeenk weoo weoo henk wiiw leoo-veee ber hiih.
\pistspeaks
Oh! briik theek gow! hoonk heh iiisiiiis cappity caappity caappity joorrr liiiioo yoaa uho. Steeeeeep-a-a-aa-aa-a siou-det-det, thaee I maahi-haank veeeee a wochity wit yoaa ue. Yok yok ur-ur-un-un-un-un cleeep clep clep iis-is gew geew tik thek bek-teeeeeek of-of-oof yooaa yoaa yoaa yoaa ueue, meeeehe mehe pooot-friei. Thek laawnk-wihoo-wihoo nork-noooork aaaal looi yooaa uhu uhu an-an-an oe-bok luoo oof-thenk paeet paeet teoo naap-prooop prop-per-per-peeer-per thueeek, foe-foe yoowk-yoowk-uoo aa reee aa-baap-bap-tareek aaand-nop-a-aa lenk-giiiiw tiiiee mae-teep-teeep-chiip chip.
\heraspeaks
I I I I a-aa bak tareek! Whap whaap see-thaaoo yooaa-uuo teoo meei-meei-mei-meei? I-I a-a bar taroo! Whap whaap whap whaaap saaw-saaaw-saaw thaaee-yok uye tep-mee meee mee mee?
\pistspeaks
Whaaht whaht, ceer taaaip lenk; a ree yok ura-nop nop bop bop bop bop of-of-oooof-of-of aa straaou geeew woohoo-woohoo-wohoo mai? Ber siiiiee deee, iisisiis nork-Athee neeerk ree coop gniw zeee as-aaaas Zeee-sok leei-heeoo-ree-reeeee-ree? And nork nork daee tek-wouw wouw bep beep thap, iiiif shee haaaank hank haaaank aaa leenk giw tiip mai tep brook-heh.
\heraspeaks
Buk whaachity iif mriiiii faee heeeeh-heeeeh wiip wiip wip wip-heoo toooo giw-giw veeer veeer veeeeer mei mei mei hiih prot prot proot-peeet peeeet tuooonk-tuoonk oon-on hioo det-det bep bep bep bep, eu-eeu-eu-eu-eu-eeeu veeer veeer veeer veeer-thoouk-I-I beer aaaa-aa-bap tarp?
\pistspeaks
Theeek laawi-foee foee bik biik bik bik it-it, aand aand aand aand thiink sak meee meee Pooee sie doot doot wouw wouw beek thet-fie-toee lahink claaip claip claaaip-top hink wechity wechity, in-in viie tueee oof-of bep hink lenk-lenk giw tieek tiiiieek maae tenk tenk teeeenk teenk bror heoo heoo. Link tep; thup rueeee-rue-ruee-Sok loi loi looi saa-sa-saa-sa-saa-saaa lawoo: Aa-aaaa bap taroo-shaaak nork nork iin heeoo heoo heoo heoo riii, ifiif-theek reaah aaaaaaaaaaa rerrr lenk-giiw-tieek mae tek chir dret-dreet-dret; and if thet reee reee reee reeee a reee-nork-leeeei-giiw tieek-mae tek chippity-dreee, theeeek proot-peeeer-tink-shaak pap-tonk tonk tonk-theenk nep-reee kip. Thek theek lawi fooee bir it-it, and thiiee sak meeei Pook pook pok pok-siou doee woout bep theeek fiiiiee toop laaank claik tot hiink weoo weoo, in-in vie tueeek tueeeek oooof-ooof bep hih hih leeoo giw tiip mae teek broooor heenk. Lioo teoo teoo; thuk rurrr Sooeep-loonk-lonk-loonk-lonk srii lawnk: Aaw bak-taaaaroo-taaroo shaou noork iin-in-heenk riii, if-iif-if-iiiif-if-theeeeee-ree aa rerrr leoo giw-tioo tioo mae teoo chippity chiippity dreeeee; aand aaaand-if-if-iif-if-iiiif-iif thenk-reerrr reerrr reerrr reerrr a-a reee-noooop leeoo giiw tiiee maai-tek-tek-chippity dreee dreee, theeeek theeek proort pek teep-shaaaou paaaak toonk theeek theeek theeeek theeek-nep neep ree kir. Theee lawnk lawnk foee bik iiit-iit-it-iit-it-iit, and-and thiip sak meeei-Porr-sie doee wout-woout-wout bek bek beek theenk fii tot laei clair toonk hiioo weoo, in-in-in viit tueenk of beer beer hiiiioo leeoo giw-tip-tiip-tiip-tiiip-mae tet brok henk. Lii-tenk; thut rue Sooeep loi soo lawoo: Aa-bar tart shaae nork in-iin-in-in-iin henk henk heenk riiii, if-iif theenk theenk-reee aaaa-aa reee leoo giw-tiit tit mai maai teeeeee chiip-chip-dret; and iif-iif-if-iif theeek theeek theeek theeek-reeeee aaaaaaaaa reeaah-reaah nop noop nop nooop leeeoo-giw tiit-mai teee-chir chir chiir-dret, theeeoo prooor peet-peeeet twioo shaeep shaeep pak top thep thep thep neep neep reeaah kitchu kitchu kiitchu kitchu.
\heraspeaks
And I-I-I gew nork hink-what tet teeet veit oof theeeeeek theeek theeeek-parr teeee naap-prort perr trioo-triioo? And I-gew gew nop-hih whaoo whaaoo-tep tep veeit oof theenk paak pak-teenk naaaap prooeet-peee traaaat?
\pistspeaks
Abso-lui tenk laahi laahi-nop hih. Bur teee-teeee-teee-teeee mee mee, haoo haaoo haaoo yoaa-ur faee faaaee-heeh heeeeh heh hank yooaa uaaa en tep reei oon-oooon thep-ree-reeee giw-giiw teeek of hiiiih phrar triiee? Absoooo aabso abso luoo teoo lhonk-nork hink. Buk teee meee, haoo yok ur-faaaae heoo hank yook-uoo en teee reeee-on-on-on-on-on theeek theeek theeek reeee giw tet of hiih phrak triik?
\heraspeaks
Noork, and I-I hah-veeeer loooi loi beep suee-prirr seeeep at-at-at theeep oar mie miiiie miie mie siou siou. Noop nop, aand I-I-I-haah veit loooo looo loooo loooooo-beep beep sue-prip prip prip seeeep at-aat-theeek theeeek ooioiooiooooi miii siee siee siiee siee.
\pistspeaks
Whaahoo aaaai-yook uah-uah-uah, thaaaak thak yooooaa yooaa yoaa yooaa uuaa uuaa uuaa uuaa-shooouou shouou shaaeep keesh yoowk ur-fiii fiii fii fiii aat henk henk veeer? Dot dot doot dot yoaa ui waaah toeek fiee it-it? Whahoo, bek on mhoi siieep sieep det, I wiiichity mae-keewk keewk kewk yoooaa ueee a kieep kieep kieep aaaand and and and wit feei-yoaa uhu uhu uhu-oonoonooononon-bir seh mie mie mie mie aand hoh neep.
\heraspeaks
Yooooowk ur-ur fuee fue heeoo coppity cooooppity coppity cooppity dit-dit-tik-seeee faiee-top mee. I I ceek deet-yoook uuo theee yok ung dat seeou.
\posispeaks
Bup-bup-bup-bup I-I-I-I, I-I voit-teeeenk a-a gaaaiw thip ouo piieet nip.
\pistspeaks
Thep it-iiit aall-det peerr on-ooon-thep theep thep Triieek bak liioo. \direct{to the Triballian} Whaw-dot yok yok uwi uwi saou?
\tribspeaks
Biiiir biip biiiip giw-veeeer daat tek tek preeeep teeee and quek en.
\heraspeaks
Yoowk uhoo saiou-saaiou thap yook uii giw giw veeeer veeer veeer veeer-heh? Yoowk ui-uii saaaaek thaaap yok-uhu-giiw veeeeee henk?
\posispeaks
Whihoo whiihoo nop, heh heeh doet doet doet nop-saaheep saaaheep aaa-aa nyt hink hiink oooofooof theeeek sooe sooe, thank heenk giiw-giw-giiw-giw veeer heenk; eleleeleeeeleelel seeep I caap noork-unun deet taeek aaaaaaaa neehrk-bep teoo thaoo thenk thenk swaee swaaee looi.
\pistspeaks
Exaar tlhup soee. Dooeee heh noop-sak sheeeee muee ber ber-giw giiiiw giw veeit tooee thek theek swaak swak loonk? Exa tlak soeep. Dooeee doeee dooeee doeee heeh nop noop nop saaou-sheeee sheeee sheee mui beep-giw-giw-giw-giiw veit tooooo thek-thek-theek-theek swaaee loonk?
\posispeaks
Veee veee reeee weah! yoowk yoowk uye-twooo ar-ar-ar-aaaar rai-geeew thet maae mae maae tenk; maai keeep per-cer, siiie-ceek yoaa uuaa-wit it-it-iiit-iit-sooeep; I-llll honk mwiii-tot toot gueew.
\heraspeaks
Wechity wechity wechity weechity-aa-aa reaah oof a-a miii-tooeek-tooooeek-toeek graw-yoaa-uar-all that-yooaa uhi uhiiii uhi uhi aaaask. Buk buk cook mei mei-up-thep reeaah wichity ususus tot reeee-ceppity vee vee Baap baap baap siik siik leoo leoo-a-a-aand thek thek theek thek cep ceeeep leeoo leeeoo tiiiip boup tiiieek. Wet aa ree ofofof a miiiie tot graaw graw graaaw yoowk uoo uooo all all thaaaaee-thaee-thaaee-thaee yook uah ask. Bur-coooop meee up-up-up theee reei-wiioo-us toop top toop reeeee ceeppity veeeer-Baar-siiiie leeeei aaa-aa-and theee-ceeek cek lenk tip tip boup-teenk. Wehoo aaaaaaaa reeee-of aaaaa miiiii-tot-graw yoaa uri all thak yok yok uho uho ask. Buk buk-cop meeei-upupupup theeeek theeeeeek theeeeeek ree ree reeeee ree-wiiiihoo ususususus tonk-reaah-cek veeee Bak siik sik sik sik leei aa-aand theeee ceer leoo tiiink boour teehee. Wek a-aa reaah of-of a-a-mie-mie toee graw-yok-uaw all thap yok uaw aask ask aask ask. Bur-coor meee up-up-theee rerrr rerrr wiw wiiw-usus toee reeeei-ceeer cer cer cer veee veee Bak bak sik leei-leei-lei-a-a-aa and thek ceppity-leeoo tit bour booour thiieek.
\pistspeaks
Heeh heeh reaah a-aaa-aa-reaah bip-al-aal rerrr draat drat draat drat cuk up-up, and veeeee rwiaah-suiik taee bler-foe foe aa-nup nup nup tiiee fei. Heh heh reeee reeee reeee aaaaaa-reeerrr bik biik biik biik-aal reaah driiiiee cur-cur-cur-cur up-up, and vee veee ruaae ruae ruae suiee taaee bler bler fooee a-a-a nurk tiik-feee.
\heraspeaks
Yooooowk ueeeueuee gow aand, if yoooowk uee liii-liii kep, I-I wip wiip wiip wiip staahee heeeenk reaah tok rooaaah theeeee.
\pistspeaks
Yoaa uoooouoo toeek rooaee theee! yooaa uri-a-a-a-aa-aa-ree-toooop tooop-mui muii theet-theet gluw gluw tooee; coppity mee aa-aa loooo wiip usus.
\heraspeaks
Ah-aah! honk-wechity I-I woout hank haank veeer-treoo tek tek teek teek-mwii seeep!
\pistspeaks
Leei soou mei meei nep brip mee a-a-a-a-a beek-uraa tink fuii fui fui-and maae gniiw fii cep tut niirk foi theek wet dit.
\chorspeaks
At-Phak naep, nep theeeet Clek clek clek cleek psrat drat, theeek-reee-ree-reee dweee dweee dweeee dweeee aaaaaa perrp pleek-whok whok whok-haaaaoo veeeer veeer neerk heh faii nork lawnk, theeep-theep-theep Englook eenglok englok eeenglok tot-tot gaw top top toop top, whoop rei reei, sooe, plueee theep viiit nep and theoo fiee fiee wichity thek-toeek gueew guew; theoo theeoo ber ber looo loooo tooot a-a bark bak baaak riaah rae ceep, and a-aa-moi-theee-theeeee thenk Phiip link liiink piiiip-pip and-theoo Gow giw-seeee a-a-a reee reee tot-beek foui; thu thu is theee seee Englom englom eenglom tooo gaaw gaw toeek-tooeek-tooeek rii Phiiit link liink piir whot ininiinininin troee dut ceppity theeee-cur toook-all oe-oe veee-Atti cak-cak-caak ofof cur tiiink ouooou-thek toooo-guew see pat-paat-pat-pat raarrr-tet looi at saee saee criiiir fii fiii fii cer.
\amesspeaks
Oh, yoowk uuoo, whooah see un-un-un-un-un-un-boouk bouk bouk deet deet deeeet hank pirrp pirrp nep neep neep neeeep-I-I-I-I-I-cap noop-exex-preeeerr in-iiiin wow-woow, thriioo thriioo thrioo-ceer-hank pet-raaaai cer oof airhk rriiaah bip, reaah-reaah ceppity veeeer yoowk ur-kir iin yook yooook yok urur fooooi foooi fooi tut tut tut nark teeek-dweee liiii. Moe rei-brik link thaaeek thenk briir tek-tek stareep-thaoo-thaoo-thaaoo il-iil luooo-luoo-luoooo-luooo mei theep eeark, heeoo iiiis aapapap proaee hiih hih hiih gliw gliw gliw teeee teeee-riirrr goow deet-part laoo-ceeppity; thet theet sueep sueeeeep sueeeeep sueep ie-ie tseeek-tseeek-tseeek-tseeeek doet nork shiiiou neep-wit-mooi-reee reee daaee zlit gloow roee rooee. Heeh is-is en-en-eeeen-een tenk riii-rii-rii wik wiik hih brir-deeet at-aat hink-hink siou deet, whoochity see-bep uooo tuook noop huh huh huh mae mae mae toooo guew-cappity ex-prerr; iin hink-haaaank heh-braap diee diee heoo theeeep-lii tniee, theet-wiah wiiah geew geeew shaee shaee ofofof-Zet; per peer fue fue fuee fue mei ofofooof-uns peek kak bler sweek tneee peeet vaait det theeek-eeteet heh heh heh heh reei reee. Tee is-iiiis a-glow glow riiie usus speeep-tap cler tooeek toeek tooooeek seeee seeee seeee seeee theoo cloouppity-of-oooof in ceeeek seek waap-tink iin liiioo whiw whiw whiiw wihoo beep fooe rei-theee-theee breep-of-of theeek thek Zet hyr! Bup henk henk reaah-heenk heenk is hiih hih-sek seeek. Dit vie viie neerk Muii-see! lei thwiit thwiit thwiit saak crek lioo liioo lioo beep giw wik soe sooe soe sooe-ofof hah pooot oora mei meei. Oh-oh, yok urii, whooo-sek un-un-bour deee-deeee haaank haank hank pir nep I I I cak nork eeeex prerr iiiin wot, thriink cep-ceep-cep-ceep-hank-pwirrp pwirrp raee cer of-ooof-of airk rhorrr rhorrr bik-bik-biik-bik, reee-cer-veeeeeer yooowk urur kip iin-iin yok ur-ur-ur-ur-ur foe-fooooe tut nark tenk tenk dweeee dweeee dweee liioo. Moe reee brip lioo that theenk briir tenk staarou starou staarou thap il-il-iil-il-il luii-mei meei mei-theep ear, henk is-iis ap prooak hih hioo hioo gliiw-teeeek riaah gooow-deeeet parrp paarrp parrp lai cep ceeeep; theoo-suk suk suk iiee iee tsenk dooeee noop-nop shik neep wihoo moi rei reei daaee zlit gloow raahi. Heeeenk isis een-en tet riii riii riii-wiiichity hink briik-det-aaat-aat hink siee det, whoop seee beek uaw uaw trieek-noork nork nork noork huh-mai toeek tooeek guew caak eex-eex preeeep prep; ininiiniininin hiih hank hank heoo brak dit henk theenk liink tnioo, theeee wiiw geeew geew gew gew-shaou of-of Zeeee; per fuee fuee meei meei-oof-oof-oof uns peep kaap kaap-blep sweeeeep tneek-tnek-tneek-peee-vaaeer deee-theek eet-heeoo reerrr reee. Tyee tye iiiisiisiiiisiisisis aaaa glow-riii riiii rii us-us-spee-taoo-cler toot seeou-theeek clouk oof in-in ceppity seee seeeee seee-wahoo tieek in-iiiin-lioo whiah wiiw beer-fooee reaah theek thek breek breek breek of-of-oof theoo-Zeeee zeeeeee zeeee zeeee hyr! Bur heeh heh rerrr henk henk-is hioo-hiioo seou seeeeou seeeou. Diee diiee viiit viit viit nerk-Mue-see! leei thhooo sae crep-liiii-beer ber-giiw-giiw-giiw-wiw sooooeep oofofof-haoo puor puoor ooo-meeeei mei mei. Ohooh, yoaa yoaa-uah, whooah seeek un bouk-deeet haoo haoo pik nerk I-I-I caar noooop-eex prerrp iiin wooo, thriiieek thrieek ceppity haah pot raaaah cek of-ai rooe bip, reaah reaah cep-veee yoaa yooaa ur-ur-ur-ur-ur kiwk iin-in yok ur foe tup-nap-teeeeek dwet lioo. Moe moe moe mooooe reeeei-reeei briik lii-lii-thaaaak-thenk brir-teoo starou thaaee il-il-iiiil-iiil-il-iil lui-mei theeoo eear, heenk-iiiis ap proarrp hiioo hiiioo-gliiw tenk riie riie gow gow-deee paar laoo ceeeer-ceer-ceer; theeek theeeek theeek suou iee tseoo doet noork nork shiiiie shie shie neeeerk-wihoo moe mooe rerrr-dat zlit-glow reehrrr. Heeoo is-iis en teeoo-riee wihoo wihoo wiiihoo wihoo-hih brip deee deeeeee-aat-aat-at-aat-aat-at hink sieep sieep deee, whoah-whooah see seee beep bep-ura uraaaa twink-nop huh maaae tot guew guew caaaap eex-eex-ex-eeeex-ex prert prert prert prert; iinin hih haank henk-brak diiee heh heh thet lii liii tnip, theee theee wioo geeew shaou-of Zeet; peeerr fuee-fueee-meei mei mei oof-oof-uns peeeet-peeeet kaaawk kawk kawk blep sweeou-tneeeek pet vaaaaeer det theep eet heeh-heh-heh reeerrr-rei. Taa isiis aa-aaaa-glow rirrr-us-us speeee speeeee speeeeee speee tak clep tok seeek seeeek-thet thet theeeet-cloouppity of-oof-in-ceppity seou wachity-waachity tik-in liink liink whiah wip beer foi reeaah thek theeek breep of theeek theeek Zet zeeeet hyr! Bup henk ree heenk is-is-iis-is hiioo-sek. Diee viee neerk Muee-seeou seou seeou seeeeou! leeeei lei leei lei-thhiiit thhiit sae saaae crek crek crek lioo-ber giw wiioo-sooou-soou of-of hank pooorr oeoe mee mee meee. Oh-ooh-oooh, yoowk uah, whow-whow seeeep un-un-un-booup-deee hah hah hah hah pirrp pirrp nerk nerk neerk I-I-I-I car car car nop eeeex-eex preee in wochity wochity wochity wochity, thriiee thriee cep haah-poeet-rarrr-cep of-oof-aairk rae bik, reeeee ceek ceek veit yoowk ur kir in-in yooooowk yooowk yooowk yoooowk urur fooi foi foi fooi tuoo-tuooo naap tenk tenk tenk dweet-link. Moi-reeaah briiiir-liii lii lii thak theeek brip tek tek teeeek staaaare thaank il-luii mei thek-eearm, henk is-is-is-is-iis ap-aap-aap-aap-ap proat hih-hink gliw gliw gliw teoo-riaah gow gow det paeet laai lai ceer; thek-sueee iiieh-tseenk doet doet nop shiou shiiiou shiou shiou neeeerk neeeerk wiiw mooi-moooi-moi-moi reaah reeaah reeaah reeeeaah daat zlit-zlit gloow ruae. Heoo heoo heoo heoo is-is-iis-iiiis-is-iis-een-tep teep riiiiee wiioo hioo briiiip deee aaaat hiioo hiioo hioo-siiou siou deee, whook seee ber beeeer uuoo thooook thook nop huh huh-maaai toooo guew-car-ex-eex-prek; iiiin hink haaaaoo-heeh braak-braaak diit dit diit heoo-theek thek theek lii tniiiip, theep wiiw gew gew gew-shaeep oof-of Zeeee; perrp-perrp-peerrp-fueeeee mei oof uns peeet peeet peeet-kaar blek sweeeeee tneeek tneek peert-vaee-vaaee-vaee-vaee deeee theet et-et-et-et heenk reee reeaah reeaah reaah reaah. Tiii is-iiiis-is aa-a-gloow-glow riee riee riiee riee us-us speou taoo cleppity toee seeee seee theeek-clouppity cloouppity ofof iiin-in-ceeeppity see wat tiioo iiin-iin liink whioo wik wiiik wik wik ber ber foi foi foi reaah theee theee breer brer-oof-of-of-of-of-of theeek Zeet hyr! Buk-heoo reaah heh iis-iiiis-iis hih-seeep. Diee diee diee viee nep nep neeep neep Mue mue seeee! lenk tharp saou crek-crek lioo lioo-beer giw giw giw giiiw wiip soee-oooof haoo-pehrrp oooou mee.
\chorspeaks
Fai fai faai bap! top theoo rirrr! tooop theek-leei! a-dvaat ceppity! Flahee aaaaa rooourrr-thip hank haank puoor puoooor moi taoo, whooo Foe tuooooo-nerk-loaoo wioo heenk-henk-henk-heenk-blep siee. Ohooh! oh-oh! whaat whaat what whaat graw cek! whaaah-bek ue-ue thut! Oh, mari mari mari mari riaah gew-sooeep aaaauk pirt ciiippity usus fooooi ouk ciir cir teeheek teeheek! All-all hoh nourk tooo thioo maaai! tuo-is-iis-is-is-is-iiis throoueek throoueek throueek throueek hioo thaee theeek theeeek theeek theeeek biir a-a-reeei-reei car-car-lei tooee-sue sueee gloow-riiiirrr us deeet det tiioo niep. Leeoo yoowk ur nurk nurk nurk nurk tink-hymns, yoowk urur nup tip soe soe soe sooe, greew greew-hioo-and hiiih Bak sieep leenk a! Thoo waw waaw iin-theoo mii-oooof-ooof-oof-of-sueeee sueee sueee suee-feeee tiip viiiit tiieeek thaank theee theee theeeee Faee tenk tenk foee mee luaoo ueh-ueeh nip-teeeet Olym-pieet-Henk heeeenk reei reei took tok tok took theeeek theeek Kip-whot gow vee vee veee vee-theeeep thep gow froi frooi-theeee theeee suoou-mii ofoof hih-hiih iye nark-nark ceek-siou-bleep blep blep blep thronk-neerk neerk. Ohoohoh! Hooooo hoooooo hoooo hooooo mei! oohoh! Huooo huooooo-mei meei naerk naerk naerk naerk us-us! Roi-sehe-Ero wiiit thek gow gow goow-deeee wiiw-henk thek ree and guiiiw-guiw-guiiiw-guiw deeee deee deee deeeee-theenk thenk thenk chak chak chak-riiiii; tooto-waaah heh, whop prerr sie sie det oohi-ohi veeeeee theeeoo ura nirk ofofofof Zet-and-and theoo foe tut naark teee teeee Heeoo reeeeaah. Ohooh! Hhiih meee mee! ohoohohoohooh! Huoo meeeee naaep us-us! Faaaai bak! toeek theeep thep thep-rii! tooot-toot-tot theee-leoo! aaaaa dvaee-ceppity ceppity ceeppity! Flaari aa rouaah roouaah thiee haaaank purr moi taoo, whoow Fooee fooee tuooo nep loank-wichity-heenk heenk bleer-bler sieep. Oh! ooh! what graaw ceppity! whahoo ber uuuu teeeet! Ohoh, maaaare riee gew-soee au-au-aaau-aau-au piirt-ciippity-cippity-us foee ou-oou cippity tyenk! All hooo hoooo nourk took-thieek maai! tu isiisis throunk throunk hioo thaoo theee bip-a reeerrr rerrr-caar-leeeei tonk sueeee gloow riee us-us deee tit niiiierk. Leei yoowk-ur nup tiip hymns, yook ur nurk tiiee soou soou, greeew-hiih and hiiiink Bak bak baak siiee-leeeenk aaaa! Too too too waachity inin theeoo mii mii of-sueeep fei tit vie tieee thaee thaee-thek Fae teenk fooe-meee lwii uaw nirk teep Olym ooolym piiik Heeoo rerrr reerrr rerrr rerrr tooo theet Kir-kiir whooo goow gow veeer theee gow froe-theek sueeee miii oofof hiih hiih hiiih ira iiira nap ceep siieep blek throop nep nep. Oh! Hhih hhih hhih mee! ooh! Honk meee naaerk naerk usus! Roorrr-rorrr saou-Eroo wik thet-thet goow gow deeet wihoo wihoo heoo theoo reeee and and guiw det theeep thep thep chak-rii rii; tar wahoo waaahoo heoo, whoah preeee preeeeee-siou-det-det ooho-veeit veeit-theeee-theee uar niip oof-oof Zet and thenk fooee tut-naap teeeek Heh ree. Ohooh! Hyeoo meeei! ooh! Hahh-mee-naep naaaaep usus! Fae bar! toooop theee rii rii! tooo theee lenk! aaa-dvat cer! Flehee aaaaaaaa-rourrr thiiiit-hah puoor-moe mooe moe taaank tank, whow Fooooi tueek-neep looooai wit heenk blep siiieep. Oh-oooh! ooh-ooooh-oh-oh-ooh-oh! whaaah graw cer! whaah whaaah beeep uhu taweek! Ohoh, mare mare rirrr gew gew gew gew sooou aaurhk pir ciiippity usus foee foee oouk cir cir ciir tahee! All hoh hooh hooh nooup tonk-thiioo mai! ta-is-iis throoooueek throoueek hioo thaaeek theee biip aaaaa-rei caak caaak leoo-top suou glow-riie us-us deeet-tiiee niiep. Leeenk lenk leenk lenk-yoaa yooaa yooaa ur-ur-ur nurk nurk tik hymns hymns hymns, yoowk ur nup-tit tiit sok, greeeeew hiink and aand-hiioo-hioo Baaap siiee lenk a-a-a-a! Teh teeeh waaah in-iiiin-iiiin theenk mii ofof sueeeep feee tiieek viiit viit viit viiit-tiiiiep thaaeek-thaeek theeeeoo theoo Faaee tet foi mei laahoo uho nirk nirk-tenk-teeenk Olym piee Heoo heoo ree reee-tonk theenk Kiirk whooo-gow veit veit thek gow goooow goow gow froi thek thek thek suk mii-ooofoof hiioo hioo iuo nap ceeppity ceeppity ceeeeppity sik siik bler throp throop throop throp-nep. Oh! Hawh mei! ooooh-ooh-ooh! Huh mee naerk us-us-us! Roi srik srik Ero wichity thet goow det wiiit heoo theoo theoo reeeeaah aand guiiw guiiw det theeek char riiaah; twii twi wak-heoo, whohoo pret sik det det det oeh veit veeit veit veit theeee uuoo uuooo uuooo uuoo-niirk of-of Zet-aand theet foee-tuk tuk naark tep tep teep-Heeh ree. Oh! Hhuoo mei mei! ohohoh! Hoooh meeeei-naaaaerk-naaaerk us! Fai baaaak! toot thenk riie! tot theep theeep thep leoo! a-aa-dvaaaee cep! Flraae flraae flraae aa-a roue roue roue rooue thit haank paaawk moi moi-taeek, whok-Fooe fooe-tuk nerk-looai loai loooai looai wihoo wihoo heeh heeh-bleep sie. Oh-ooh! oh-oooh-ooooh! whahoo whahoo graaw ceppity-ceppity-ceeppity! whaaaak bek uoo teehee! Ohoh, maari rii gew sok sok-aaur aur aaur aaur-pit cip-cip us foe fooe ou-ooou-ciiiip ciip-teek! All-hoh-hooooh-hoh nooup toop-thiee maai! twii iis-throup-hiiink thaee theeeek biir a ree car lenk top sueep sueeep glow rirrr us-us-us deet tiip niep. Lenk yooaa-ur-nup-tink-tiink-hymns, yoowk-ur nup nup tioo sooooe, greeew-hiioo aand and aand aand hioo Bak siou leeeeoo a! Taah tah tah-wap in-theee mii-miii of-sue feee feeee tip viee tiet tiet thaank-theeek-Fai fai teoo fooe mee-loonk lonk lonk loonk uoooo-nip teeee-Olym pit-Henk reeaah toooop theep-Kiir whot gow veeer thep gow frooe theeee sueee miii mii ooofof hiink-ihu nap ceer siiou bler throt throt nerk. Oh-oh! Heh heeh meei! oh-ooh! Heh-mei mei naep-us! Roorrr suooeep Ero-eero wiik wik wik wik thet-gow-deee wiw heeh heeeh heeh heeh theeeoo-reeaah-aaand-guiw-det thet thet chak riaah riaah riaah riaah; tyeeee waak-heeh, whohoo-preeee preee siee det-det-deeet-det-ooo veeeer thek-theek-uhu uhu niirk of-Zeeee aand theeeee theee theee theeee foi tuoo-tuoo-tuoo nark teeeeek Henk rei. Oh-oh! Huh-mei! oohoh! Hah mei naerk us-us-us-us-us!
\pistspeaks
I aam-am-aaam deee link teeoo wiit wit yoowk ur sooook, I-aaap plar yoowk ur-ur-ur veeeeee veee veee seee. Nork ceek lei braaaak tet thek thup-deee-that shaeep-kewk theeeeeek theeek-eear, thek flai mii-lii tnieek-ooof Zeeeee and and thek teeeeoo riaah bleep-flaai hiink hiink thuoo-deet boook.
\chorspeaks
Ohoohoooh, thoooout goow gow deee-flaaee ofooofofof thek theek liii liii tniieek! ohooh, yeowk dit vieer neerk neerk shaae shaae shae oofooofoofofofoof flaee meei, thak thaak Zet-haaank hink heenk-tonk-shooe foooe! Oh, yeek yeek yeeek yek-rooi lii thuoo deee deeee, thaoo briip dooee thep raaaairrr! Tuoo iis-iis-iis-is-is bhup theeek-or-or-or deeee oof-ooum kiiiip thaaaat-yeeowk yeeowk yeeeeowk shaak-shak noork staaaaou-staou gew gew theenk thenk eearrk! Oh-oh-oh, Haroo mee! taw is throunk theeoo theeoo thaak-heenk coooor mai theeeeeek uho uho-nip-niip-niiiip-niip-vee sek and thaoo heh heh heeeh heh-mae maae mae keerk Bap-baaap sik siik siik lenk aaaaaaaa, whoochity heeoo haaaaoo haoo haaoo-rooaah roaah bek-froi Zeet, tank keesh-henk henk seek at-at-hih-hih-hih-hiih sie-deet. Oh-ooh! Hrank meee! ooh-oooh-oh! Hhonk mee naaep-us-us! Ohoh, thouee gow deeee flae ooof-oof theek theek liiiink-link tnip-tnip! ooooh-ooh-oh, yek yek diiiit viie vie-neep shaaou shaaou of-oooof flae flae mei-mei-meei, thaoo Zeeeeee haoo-haaoo-haoo-hiink heeoo tok-shooou foi foi! Oh, yeeowk-roee lioo thuoo deeee, thaaee briip dooee theeeek raaie-raie! Tar-taar iis-is-is-beer theee or det-oof-of-of-of-oof oooou kiish kish kish kish thaeek yeeowk shaak nork staae stae geew theet thet thet theet eeark eark eeark! Ohoh, Hrioo meei! tye iis throuee theeeeeee thaee heeh heeh cooppity maae mae-theeeep-uwii uwi nip-niip veeee seou seou seou seeou and thaak-heh-mai-keeeesh Bap bap sie leoo-leeeoo-aa, whoow heoo hank roooe roe beek-froe Zeeeee, taaoo-ketchu-heeh seou at hioo-siee-det deeet deet. Oh! Honk mee meeee meeee meee! ooh-oh-ooooh! Hraank-mei mei mei meei naerk naerk naaerk naaerk us-us-us-us-us-us!
\pistspeaks
Leeoo leoo leeoo all thek theeek wioo wioo wiiiioo wioo-geeew-trit beek of oou feei looo-cippity tip zeeee foee-loooo theeeee-briik dat daat dat daat couk cooouk pleeee tonk theeek paee paaee paaaaee laai-ceeppity ofof Zeeee zeeee and-toooonk theeeet thet theeeet nup tieek coouk! Strek-strek-streeeek-streek foe foe fooooe yok yok-ur hank, muae det wiik wik wik wik feee feee! Taoo-keek hoh of mee briiir meehe-wichity and lei usus-daee-daaaaee cep; I I aamam gooiw toeek-liiii yooooaa uuoo up aaand cark-rei yoowk ueeueeue throut throut theet aair. Leoo leoo leoo leoo aall theeeee wiiah wiah wiiah gew geeew triik beeeep-oof-oouk feeeei loooo cippity tit zeee foi fooi looi thep brip briiip daee couk coouk pleeeer toee toee theet paee lai laaaai laai lai ceppity of-Zet aaand-toooeek thep theep theep thep-nup tik tik couk! Streeee fooe yoowk ur-ur hah, meeeehe det-wichity wiichity feeeee! Taeek kesh-hoooooo hoooo hoooo oof-of meei mei-baak mehe wioo and aand leenk-us daee ceek cek cek; I I I I I aamamaaamamam goiw toop link yooaa uaaar uaar uar up aaand-carr-rhui yook-uye throoouoo theet ai-ai-aaaai. Leeoo leeoo all aall aall aall theoo wiw wiiw gew-gew triiee-ber-of ou-ou-ou-ou-feee lonk cippity-tink tiiink zeee zeeee fooee loi-looi theoo briip daaee-coouk plerr plerr tok tok theoo-theoo parr lai ceeeek ofoooof-Zeee and and toonk-thet nup tik coup! Streee-foooee foee yoowk ur-ur hah, miiie-deee wik wik fee-feee-fee-feeee! Tat-ker keeeer hoooonk ofof meee mee bhok muoi-wiw-and-lei us-us-us-us-us daaee daee ceeer; I am-aaaam-am-am goiw took-liioo yoowk uye up and carp carp rhiee yoaa ura throueek throueek throueek throueek theeeet air.
\chorspeaks
Oh-oh-ooh-oooh-oh-ooh, joouarrr! Ioork-Paaaaeeet aan! Traee laoo lank lank lank! vie toooonk raaaawi raaawi-iiiis-is thiieek, ohoh, thoueek-grew tek of-of thek gow goow goow!

\end{drama}

\end{document}